### 2022-02-25 paper/paper1/ms.tex
Commit the paper to GitHub

\documentclass{aastex631}
\bibliographystyle{aasjournal}

\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{amsmath}
\usepackage{booktabs}

\let\pwiflocal=\iffalse \let\pwifjournal=\iffalse
%From: http://arxiv.org/format/1512.00483
%\input{setup}
%\input{mgs_setup}

\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{#1}}
\providecommand{\adsurl}[1]{\href{#1}{ADS}}
\newcommand{\project}[1]{\textsl{#1}}

\begin{document}
\shorttitle{HPF spectral analysis}
\shortauthors{TBD}

\title{Disperse HPF line strengths of exoplanet host stars}

\author{TBD}
\affiliation{TBD}

\begin{abstract}
    We measure the line strengths of exoplanet host stars in and out of transit.

\end{abstract}

\keywords{stars: fundamental parameters ---  stars: statistics}

\section{Introduction}\label{sec:intro}
\citet{2020ApJ...894...97N} discusses the discovery of helium on exoplanets.

We specified our observations on the HAT-P-67 system due to its unique rotational period. HAT-P-67 is a binary system of an F type sub-giant and a much cooler M2 star with the Saturn-sized planet HAT-P-67b. An extremely low density object, HAT-P-67b loses its atmosphere rather rapidly for transiting an evolved host star.

\begin{deluxetable}{chc}
    \tablecaption{Annotated bibliography for intro\label{table1}}
    \tablehead{
        \colhead{Reference} & \nocolhead{Other Column} & \colhead{Key idea}
    }
    \startdata
    \citet{2020ApJ...894...97N} & - & HPF For Helium Exospheres\\
    \citet{foreman13} & - & MCMC \\
    \enddata
\end{deluxetable}

\section{Methodology}
\subsection{Closed Form MCMC Equivalent Widths}
To estimate the uncertainty in our spectra we used the Monte Carlo MCMC chain \citep{foreman13}. %The equation for our equivalent width was derived with the variables for the Gaussian and the continuum:

The model will consist of a straight-line trend with a Gaussian subtracted from it.  It has five parameters: the straight-line trend slope $m$ and offset $b$, and the Gaussian amplitude $A$, center wavelength $\mu$, and width $w$.

\begin{gather}
    f_\lambda(m, b, A, \mu, w)= 1 - \frac{A}{(m \mu + b)}\cdot e^{-\frac{1}{2} \frac{(\lambda-\mu)^2}{w^2}}
\end{gather}

We then focused on the sub-region defined by the line we were looking at. Using a generative model, we made guesses for the parameter values to create an initial guess fit for the data. We then used Monte Carlo Markov Chain to fine tune the parameters and develop a more accurate fit. The MCMC process spits out results for all five parameters with their corresponding equivalent widths. Using these values, we were able to calculate the equivalent width using the formula
3

\begin{gather}
    W_\lambda=\frac{Aw}{[m (\mu-\textup{calcium line}) + b]}\cdot\sqrt{2\pi}
\end{gather}

We then took the mean and standard deviation of this result to get the equivalent width and uncertainty for each planet.

\section{Observations}
\subsection{Habitable zone Planet Finder}

We observed the HAT-P-67 system with the Habitable Zone Planet Finder spectrograph (HPF) which is coupled to the 10-meter Hobby Eberly Telescope at the University of Texas at Austin's McDonald Observatory. HPF operates in the near-infrared light at 8100-12800 \AA using the \textit{z}, \textit{Y}, and \textit{J} bands. We observed HAT-P-67b with HPF in-transit on 2020 April 28, 2020 May 22, and 2020 June 15 and out-of-transit on 2020 April 27, 2020 May 20-21, 23-24, and 2020 June 13-16, 18. The observations on April 28th began at 06:10:31 and ended at 07:24:26, resulting in a total exposure time of 01:13:55. The observations on May 22nd began at 04:41:05 and ended at 05:55:00, resulting in a total exposure time of
%ask gully if should keep doing this, very rough draft for now without good wording

Table \ref{tab:sample_properties} lists the sources in the sample, and their bulk physical properties.

\begin{deluxetable*}{lccc}[!ht]
    \tablecaption{HPF Observations for HAT-P-67b \label{tab:observation_properties}}
    \tablehead{
        \colhead{Date} & \colhead{Time of Observation} & \colhead{Transit}}
    \startdata
    2020-04-28 & 06:10:31 & In transit\\
    2020-04-28 & 06:16:12 & In transit\\
    2020-04-28 & 06:21:53 & In transit\\
    2020-04-28 & 06:27:34 & In transit\\
    2020-04-28 & 06:33:15 & In transit\\
    2020-04-28 & 06:38:57 & In transit\\
    2020-04-28 & 06:44:38 & In transit\\
    2020-04-28 & 06:50:19 & In transit\\
    2020-04-28 & 06:10:31 & In transit\\
    2020-04-28 & 06:10:31 & In transit\\
    2020-04-28 & 06:10:31 & In transit\\
    2020-04-28 & 06:10:31 & In transit\\
    2020-04-28 & 06:10:31 & In transit
    \enddata
\end{deluxetable*}

\begin{deluxetable*}{lccccc}[!ht]
    \tablecaption{Stellar properties \label{tab:sample_properties}}
    \tablehead{
        \colhead{Name} & \colhead{$T_{eff}$ (K)} & \colhead{$\log{g}$} & \colhead{RV (km/s)} & \colhead{V sin(i) (km/s)} & \colhead{Reference}}
    \startdata
    HAT-P-32 & 6001 $\pm$ 88 & 4.22 $\pm$ 0.04 & -23.21 $\pm$ 0.26 & 20.7 $\pm$
    0.5 & \cite{2019AJ....157...82W}\\
    HAT-P-67 & $6406^{+65}_{-61}$ & $3.854^{+0.014}_{-0.023}$ & -1.4 $\pm$ 0.5 & 35.8 $\pm$ 1.1 & \cite{2017AJ....153..211Z}\\
    \enddata
\end{deluxetable*}

\subsection{TESS Light Curve}
We observed the HAT-P-67 system using data from TESS sector 24 taken from April 16th, 2020 to May 13th, 2020 with an exposure time of 1800 seconds. Using the \textit{lightkurve} package, we attempted to phase fold our exoplanet transit plot to identify the stellar rotation signal and the exoplanet's transit signal. At first glance, the stellar flux decreases by about 0.2\% and the exoplanet transit signal decreases by about 0.7\%. In order to analyze the stellar rotation period, we must mask the planetary transit signal. By folding the normalized lightcurve with a given planetary orbital period of 4.810 days, we omitted the planetary transit signal. We then created a periodogram of just the stellar signal and arrived at an estimate of several parameters for HAT-P-67b: the planetary period is 4.809 days, the original transit time was 1958.082 BTJD, and the planetary duration was 0.25 days. We then created a cadence mask using the Box Least Squares parameters. The resulting periodogram of just the stellar variation described a rotational period of 5.417 days is shown in Figure \ref{fig:stellar_periodogram}.

\begin{figure}
    \includegraphics[width=\linewidth]{stellar_periodogram.png}
    \caption{Periodogram of solely the stellar variation of the flux. }
    \label{fig:stellar_periodogram}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{planetary_periodogram.png}
    \caption{Periodogram of the stellar variation coupled with the planetary transit signal of the flux. }
    \label{fig:planetary_periodogram}
\end{figure}

\section{Analysis}
\subsection{HPF MCMC}
The methodology used to fit the HPF spectra was the Markov chain Monte Carlo (MCMC). After deblazing and normalizing the spectrum, we used a Gaussian line to fit the spectra with five parameters: width, center wavelength, amplitude, slope, and offset.  We focused on each sub-region of the spectrum by cutting of data outside of the $99.9\%-100.1\%*line$ threshold to create a better fit for the data. This threshold was determined as a result of which line we were looking at. The generative model consists of a straight-line trend with a Gaussian subtracted from it. The continuum of the spectrum was given by $continuum=m(\lambda-\lambda_{int})+b$ and the Gaussian fit was subtracted off of the continuum to get the absorption line fit. After applying values to the five parameters for the generative model, we improved our fitting with the MCMC process. We computed the log likelihood of the guessing parameters to determine a quality of fit metric. From there, we ran MCMC with the package \textit{emcee} at 5000 steps for the five parameters. After thinning out and discarding the last 1000 steps, we gathered the final draws for the given parameters with their corresponding uncertainties.

\subsection{HPF Equivalent Width Determination}
In addition to the MCMC method, we verified the precision of our numbers through another fitting method. While the MCMC method produced an accurate result, it lacked the precision required. Thus, we chose to analyze the data again with the summation method.

After collecting the new parameters, we then calculated the equivalent width of the corresponding line with the formula $EW=\sqrt{2\pi}\frac{Aw}{m(\mu-line)+b}$. We then calculated the mean and standard deviation of the equivalent width.
\subsection{Contemporaneous Stellar Activity Quantification}
\subsection{Equivalent Width vs Phase}
\begin{figure}
    \includegraphics[width=\linewidth]{TESS_EW_HAT-P-67.jpg}
    \caption{A boat.}
    \label{fig:boat1}
\end{figure}

\begin{deluxetable*}{lcccccc}[!ht]
    \tablecaption{Equivalent Width \label{tab:ew_properties}}
    \tablehead{
        \colhead{Star Name} & \colhead{Date} & \colhead{ID} & \colhead{Observed Line Center Position} & \colhead{Intrinsic Line Center Position} & \colhead{Equivalent Width (\AA)}}
    \startdata
    HAT-P-67 & Aug 7, 2020 & & $10328.493\pm0.017$ & & $0.1607\pm0.0059$\\
    HAT-P-67 & Aug 8, 2020 & & $10345.007\pm0.019$ & & $0.1122\pm0.0068$\\
    HAT-P-67 & Aug 8, 2020 & & $10344.993^{+0.015}_{-0.016}$ & & $0.1064\pm0.0051$\\
    HAT-P-32 & Aug 8, 2020 & & $10344.991^{+0.016}_{-0.017}$ & & $0.1112\pm0.0055$\\
    \enddata
\end{deluxetable*}

\begin{tabular}{lrrrlrll}
    \toprule
    date       & declination & exposure time & jd           & qidx   & ra        & star name                  & time     \\
    \midrule
    2020-04-28 & 44.763974   & 308.85        & 2.458968e+06 & 6437.0 & 17.106801 & HAT-P-67b\_IN\_1           & 06:10:31 \\
    2020-04-28 & 44.763643   & 308.85        & 2.458968e+06 & 6437.0 & 17.106878 & HAT-P-67b\_IN\_1           & 06:16:12 \\
    2020-04-28 & 44.763456   & 308.85        & 2.458968e+06 & 6437.0 & 17.106957 & HAT-P-67b\_IN\_1           & 06:21:53 \\
    2020-04-28 & 44.763237   & 308.85        & 2.458968e+06 & 6437.0 & 17.107029 & HAT-P-67b\_IN\_1           & 06:27:34 \\
    2020-04-28 & 44.763050   & 308.85        & 2.458968e+06 & 6437.0 & 17.107089 & HAT-P-67b\_IN\_1           & 06:33:15 \\
    2020-04-28 & 44.762969   & 308.85        & 2.458968e+06 & 6437.0 & 17.107158 & HAT-P-67b\_IN\_1           & 06:38:57 \\
    2020-04-28 & 44.762784   & 308.85        & 2.458968e+06 & 6437.0 & 17.107229 & HAT-P-67b\_IN\_1           & 06:44:38 \\
    2020-04-28 & 44.762775   & 308.85        & 2.458968e+06 & 6437.0 & 17.107301 & HAT-P-67b\_IN\_1           & 06:50:19 \\
    2020-04-28 & 44.762575   & 308.85        & 2.458968e+06 & 6437.0 & 17.107363 & HAT-P-67b\_IN\_1           & 06:56:00 \\
    2020-04-28 & 44.762322   & 308.85        & 2.458968e+06 & 6437.0 & 17.107427 & HAT-P-67b\_IN\_1           & 07:01:41 \\
    2020-04-28 & 44.762290   & 308.85        & 2.458968e+06 & 6437.0 & 17.107485 & HAT-P-67b\_IN\_1           & 07:07:22 \\
    2020-04-28 & 44.762212   & 308.85        & 2.458968e+06 & 6437.0 & 17.107541 & HAT-P-67b\_IN\_1           & 07:13:03 \\
    2020-04-28 & 44.762057   & 308.85        & 2.458968e+06 & 6437.0 & 17.107608 & HAT-P-67b\_IN\_1           & 07:18:44 \\
    2020-04-28 & 44.762013   & 308.85        & 2.458968e+06 & 6437.0 & 17.107669 & HAT-P-67b\_IN\_1           & 07:24:26 \\
    2020-05-22 & 44.765938   & 308.85        & 2.458992e+06 & 6587.0 & 17.106844 & HAT-P-67b\_IN\_2           & 04:41:05 \\
    2020-05-22 & 44.765694   & 308.85        & 2.458992e+06 & 6587.0 & 17.106916 & HAT-P-67b\_IN\_2           & 04:46:46 \\
    2020-05-22 & 44.765448   & 308.85        & 2.458992e+06 & 6587.0 & 17.106988 & HAT-P-67b\_IN\_2           & 04:52:27 \\
    2020-05-22 & 44.765338   & 308.85        & 2.458992e+06 & 6587.0 & 17.107057 & HAT-P-67b\_IN\_2           & 04:58:09 \\
    2020-05-22 & 44.765232   & 308.85        & 2.458992e+06 & 6587.0 & 17.107116 & HAT-P-67b\_IN\_2           & 05:03:50 \\
    2020-05-22 & 44.764945   & 308.85        & 2.458992e+06 & 6587.0 & 17.107198 & HAT-P-67b\_IN\_2           & 05:09:31 \\
    2020-05-22 & 44.764912   & 308.85        & 2.458992e+06 & 6587.0 & 17.107269 & HAT-P-67b\_IN\_2           & 05:15:12 \\
    2020-05-22 & 44.764767   & 308.85        & 2.458992e+06 & 6587.0 & 17.107347 & HAT-P-67b\_IN\_2           & 05:20:53 \\
    2020-05-22 & 44.764488   & 308.85        & 2.458992e+06 & 6587.0 & 17.107408 & HAT-P-67b\_IN\_2           & 05:26:34 \\
    2020-05-22 & 44.764364   & 308.85        & 2.458992e+06 & 6587.0 & 17.107473 & HAT-P-67b\_IN\_2           & 05:32:15 \\
    2020-05-22 & 44.764240   & 308.85        & 2.458992e+06 & 6587.0 & 17.107525 & HAT-P-67b\_IN\_2           & 05:37:57 \\
    2020-05-22 & 44.764128   & 308.85        & 2.458992e+06 & 6587.0 & 17.107601 & HAT-P-67b\_IN\_2           & 05:43:38 \\
    2020-05-22 & 44.764087   & 308.85        & 2.458992e+06 & 6587.0 & 17.107653 & HAT-P-67b\_IN\_2           & 05:49:19 \\
    2020-05-22 & 44.763816   & 308.85        & 2.458992e+06 & 6587.0 & 17.107728 & HAT-P-67b\_IN\_2           & 05:55:00 \\
    2020-06-15 & 44.768164   & 308.85        & 2.459016e+06 & 6938.0 & 17.106909 & HAT-P-67b\_IN\_3           & 03:13:19 \\
    2020-06-15 & 44.767792   & 308.85        & 2.459016e+06 & 6938.0 & 17.106979 & HAT-P-67b\_IN\_3           & 03:19:00 \\
    2020-06-15 & 44.767746   & 308.85        & 2.459016e+06 & 6938.0 & 17.107035 & HAT-P-67b\_IN\_3           & 03:24:41 \\
    2020-06-15 & 44.767580   & 308.85        & 2.459016e+06 & 6938.0 & 17.107103 & HAT-P-67b\_IN\_3           & 03:30:23 \\
    2020-06-15 & 44.767436   & 308.85        & 2.459016e+06 & 6938.0 & 17.107145 & HAT-P-67b\_IN\_3           & 03:36:04 \\
    2020-06-15 & 44.767252   & 308.85        & 2.459016e+06 & 6938.0 & 17.107246 & HAT-P-67b\_IN\_3           & 03:41:45 \\
    2020-06-15 & 44.767175   & 308.85        & 2.459016e+06 & 6938.0 & 17.107295 & HAT-P-67b\_IN\_3           & 03:47:26 \\
    2020-06-15 & 44.766835   & 308.85        & 2.459016e+06 & 6938.0 & 17.107368 & HAT-P-67b\_IN\_3           & 03:53:07 \\
    2020-06-15 & 44.766759   & 308.85        & 2.459016e+06 & 6938.0 & 17.107418 & HAT-P-67b\_IN\_3           & 03:58:48 \\
    2020-04-27 & 44.764544   & 308.85        & 2.458967e+06 & 6436.0 & 17.106775 & HAT-P-67b\_OUT\_1\_before1 & 06:29:11 \\
    2020-04-27 & 44.764240   & 308.85        & 2.458967e+06 & 6436.0 & 17.106827 & HAT-P-67b\_OUT\_1\_before1 & 06:35:03 \\
    2020-04-27 & 44.764141   & 308.85        & 2.458967e+06 & 6436.0 & 17.106900 & HAT-P-67b\_OUT\_1\_before1 & 06:40:55 \\
    2020-04-27 & 44.763873   & 308.85        & 2.458967e+06 & 6436.0 & 17.106974 & HAT-P-67b\_OUT\_1\_before1 & 06:46:47 \\
    2020-04-29 & 44.764930   & 308.85        & 2.458969e+06 & 6438.0 & 17.106673 & HAT-P-67b\_OUT\_1\_after1  & 06:34:20 \\
    2020-04-29 & 44.764731   & 308.85        & 2.458969e+06 & 6438.0 & 17.106749 & HAT-P-67b\_OUT\_1\_after1  & 06:40:01 \\
    2020-04-29 & 44.764633   & 308.85        & 2.458969e+06 & 6438.0 & 17.106817 & HAT-P-67b\_OUT\_1\_after1  & 06:45:42 \\
    2020-04-29 & 44.764531   & 308.85        & 2.458969e+06 & 6438.0 & 17.106878 & HAT-P-67b\_OUT\_1\_after1  & 06:51:23 \\
    2020-05-20 & 44.782750   & 308.85        & 2.458990e+06 & 6599.0 & 17.107624 & HAT-P-67b\_OUT\_2\_before2 & 10:43:31 \\
    2020-05-20 & 44.781504   & 308.85        & 2.458990e+06 & 6599.0 & 17.107668 & HAT-P-67b\_OUT\_2\_before2 & 10:49:12 \\
    2020-05-20 & 44.780211   & 308.85        & 2.458990e+06 & 6599.0 & 17.107719 & HAT-P-67b\_OUT\_2\_before2 & 10:54:53 \\
    2020-05-20 & 44.779210   & 308.85        & 2.458990e+06 & 6599.0 & 17.107778 & HAT-P-67b\_OUT\_2\_before2 & 11:00:34 \\
    2020-05-21 & 44.782995   & 308.85        & 2.458991e+06 & 6588.0 & 17.107695 & HAT-P-67b\_OUT\_2\_before1 & 10:23:05 \\
    2020-05-21 & 44.781573   & 308.85        & 2.458991e+06 & 6588.0 & 17.107731 & HAT-P-67b\_OUT\_2\_before1 & 10:28:46 \\
    2020-05-21 & 44.780368   & 308.85        & 2.458991e+06 & 6588.0 & 17.107773 & HAT-P-67b\_OUT\_2\_before1 & 10:34:28 \\
    2020-05-21 & 44.779170   & 308.85        & 2.458991e+06 & 6588.0 & 17.107810 & HAT-P-67b\_OUT\_2\_before1 & 10:40:09 \\
    2020-05-23 & 44.783203   & 308.85        & 2.458993e+06 & 6589.0 & 17.107654 & HAT-P-67b\_OUT\_2\_after1  & 10:16:00 \\
    2020-05-23 & 44.781895   & 308.85        & 2.458993e+06 & 6589.0 & 17.107688 & HAT-P-67b\_OUT\_2\_after1  & 10:21:41 \\
    2020-05-23 & 44.780749   & 308.85        & 2.458993e+06 & 6589.0 & 17.107718 & HAT-P-67b\_OUT\_2\_after1  & 10:27:22 \\
    2020-05-23 & 44.779639   & 308.85        & 2.458993e+06 & 6589.0 & 17.107763 & HAT-P-67b\_OUT\_2\_after1  & 10:33:04 \\
    2020-05-24 & 44.782834   & 308.85        & 2.458994e+06 & 6600.0 & 17.107668 & HAT-P-67b\_OUT\_2\_after2  & 10:22:14 \\
    2020-05-24 & 44.781654   & 308.85        & 2.458994e+06 & 6600.0 & 17.107708 & HAT-P-67b\_OUT\_2\_after2  & 10:27:55 \\
    2020-05-24 & 44.780276   & 308.85        & 2.458994e+06 & 6600.0 & 17.107744 & HAT-P-67b\_OUT\_2\_after2  & 10:33:36 \\
    2020-05-24 & 44.779039   & 308.85        & 2.458994e+06 & 6600.0 & 17.107789 & HAT-P-67b\_OUT\_2\_after2  & 10:39:17 \\
    2020-06-13 & 44.785061   & 308.85        & 2.459014e+06 & 6941.0 & 17.107689 & HAT-P-67b\_OUT\_3\_before2 & 09:13:57 \\
    2020-06-13 & 44.783754   & 308.85        & 2.459014e+06 & 6941.0 & 17.107743 & HAT-P-67b\_OUT\_3\_before2 & 09:19:38 \\
    2020-06-13 & 44.782668   & 308.85        & 2.459014e+06 & 6941.0 & 17.107795 & HAT-P-67b\_OUT\_3\_before2 & 09:25:19 \\
    2020-06-14 & 44.785228   & 308.85        & 2.459015e+06 & 6939.0 & 17.107679 & HAT-P-67b\_OUT\_3\_before1 & 09:08:28 \\
    2020-06-14 & 44.783951   & 308.85        & 2.459015e+06 & 6939.0 & 17.107713 & HAT-P-67b\_OUT\_3\_before1 & 09:14:09 \\
    2020-06-14 & 44.782721   & 308.85        & 2.459015e+06 & 6939.0 & 17.107767 & HAT-P-67b\_OUT\_3\_before1 & 09:19:50 \\
    2020-06-14 & 44.781659   & 308.85        & 2.459015e+06 & 6939.0 & 17.107823 & HAT-P-67b\_OUT\_3\_before1 & 09:25:32 \\
    2020-06-15 & 44.783524   & 308.85        & 2.459016e+06 & 6943.0 & 17.107765 & HAT-P-67b\_OUT\_same3      & 08:59:57 \\
    2020-06-15 & 44.782226   & 308.85        & 2.459016e+06 & 6943.0 & 17.107803 & HAT-P-67b\_OUT\_same3      & 09:05:39 \\
    2020-06-15 & 44.780921   & 308.85        & 2.459016e+06 & 6943.0 & 17.107841 & HAT-P-67b\_OUT\_same3      & 09:11:20 \\
    2020-06-15 & 44.779720   & 308.85        & 2.459016e+06 & 6943.0 & 17.107889 & HAT-P-67b\_OUT\_same3      & 09:17:01 \\
    2020-06-15 & 44.778571   & 308.85        & 2.459016e+06 & 6943.0 & 17.107938 & HAT-P-67b\_OUT\_same3      & 09:22:42 \\
    2020-06-15 & 44.777286   & 308.85        & 2.459016e+06 & 6943.0 & 17.108007 & HAT-P-67b\_OUT\_same3      & 09:28:23 \\
    2020-06-15 & 44.776196   & 308.85        & 2.459016e+06 & 6943.0 & 17.108044 & HAT-P-67b\_OUT\_same3      & 09:34:04 \\
    2020-06-15 & 44.774972   & 308.85        & 2.459016e+06 & 6943.0 & 17.108092 & HAT-P-67b\_OUT\_same3      & 09:39:45 \\
    2020-06-15 & 44.773796   & 308.85        & 2.459016e+06 & 6943.0 & 17.108157 & HAT-P-67b\_OUT\_same3      & 09:45:26 \\
    2020-06-16 & 44.785595   & 308.85        & 2.459017e+06 & 6940.0 & 17.107685 & HAT-P-67b\_OUT\_3\_after1  & 08:51:26 \\
    2020-06-16 & 44.784378   & 308.85        & 2.459017e+06 & 6940.0 & 17.107727 & HAT-P-67b\_OUT\_3\_after1  & 08:57:07 \\
    2020-06-16 & 44.783087   & 308.85        & 2.459017e+06 & 6940.0 & 17.107751 & HAT-P-67b\_OUT\_3\_after1  & 09:02:49 \\
    2020-06-16 & 44.781929   & 308.85        & 2.459017e+06 & 6940.0 & 17.107796 & HAT-P-67b\_OUT\_3\_after1  & 09:08:30 \\
    2020-06-18 & 44.785281   & 308.85        & 2.459019e+06 & 6942.0 & 17.107699 & HAT-P-67b\_OUT\_3\_after2  & 08:58:34 \\
    2020-06-18 & 44.784069   & 308.85        & 2.459019e+06 & 6942.0 & 17.107753 & HAT-P-67b\_OUT\_3\_after2  & 09:04:15 \\
    2020-06-18 & 44.782920   & 308.85        & 2.459019e+06 & 6942.0 & 17.107820 & HAT-P-67b\_OUT\_3\_after2  & 09:09:56 \\
    2020-06-18 & 44.781739   & 308.85        & 2.459019e+06 & 6942.0 & 17.107881 & HAT-P-67b\_OUT\_3\_after2  & 09:15:37 \\
    \bottomrule
\end{tabular}

\section{Results}
\subsection{Is there a difference in equivalent width in transit vs out?}
We can see that there is indeed a helium signature that arises when the planet is in transit with its host star.
\subsection{Stellar Activity (non)detection versus Equivalent Width}
There is a likelihood that a portion of the exoplanet emission spectra originates from stellar activity. Thus, we must identify which stellar features mimic a helium signature. Such features can be narrowed down to the star's radial velocity, star spots, and faculae.
\subsection{Star Planet Interaction}
Characterizing a host star's stellar environment is of utmost importance if we want to understand how exoplanet atmospheres are affected. While cool dwarfs generate high irradiation in the ultraviolet and stellar winds, the sub-giant category

\section{Discussion}

\section{Conclusions}

Reiteration here.

\clearpage
\pagebreak

\appendix
%\section{HPF spectra post-processing}
%\label{methods-details}

\acknowledgements

%ADS
This research has made use of NASA’s Astrophysics Data System.

\facilities{Smith (IGRINS), Gaia, ASAS}

\software{  pandas \citep{mckinney10},
    emcee \citep{foreman13},
    matplotlib \citep{hunter07},
    numpy \citep{2020NumPy-Array},
    scipy \citep{2020SciPy-NMeth},
    ipython \citep{perez07},
    seaborn \citep{waskom14}}

\clearpage

\bibliography{ms}

\end{document}

### 2022-02-25 paper/paper1/ms.tex
Add the abstract from the ill-fated winter 2021 AAS

@@
 
-\title{Disperse HPF line strengths of exoplanet host stars}
+\title{Atmospheric escape and star-planet-interaction in the HAT-P-67 b system}
 
@@
 \begin{abstract}
-    We measure the line strengths of exoplanet host stars in and out of transit.
+    We aim to understand how exoplanet atmospheres evolve across age, stellar irradiation environments, planet properties, and---for extremely close-in exoplanets---direct star-planet interaction (SPI) such as stellar winds, tidal forces, and magnetic interactions.
+The scarcity of exoplanet atmosphere measurements across a range of stellar properties has limited our ability to complete this picture.
 
+    The Helium Exospheres program with the Habitable Zone Planet Finder (HPF) spectrograph on the Hobby Eberly Telescope (HET) in West Texas has targeted 23 exoplanet systems over two years.
+Here, we present a study of HAT-P-67, an F subgiant hosting a low density planet with 0.3 $M_{\mathrm{Jup}}$ and 2.1 $R_{\mathrm{Jup}}$ on a close-in 4.8 day orbit.
+The high energy radiation environment should provide a uniquely harsh testing ground for examining atmospheric escape.  The planet shows prominent in-transit absorption in the He 10830 \AA triplet and infrared Ca II 8542 \AA triplet across 20 visits over the course of a year including in- and out-of-transit spectroscopy.
+We identify the rotational period of HAT-P-67 to be 5.417 days by using contemporaneous data from the Transiting Exoplanet Survey Satellite (TESS).
+We consider multiple interpretations of the HPF and TESS observations.  First, the period measured by TESS may be the rotational period of the star and thus, the star and planet are nearly-tidally locked.
+On the other hand, the period measured by TESS may result from SPI-induced hot spots on the surface that follow the magnetic field lines linked to the planet's orbital period.
+Finally, we consider the possibility of stellar surface inhomogeneity contaminating the He and Ca II transit signals.
 \end{abstract}
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{stellar_periodogram.png}
+    \includegraphics[width=\linewidth]{figures/stellar_periodogram.png}
     \caption{Periodogram of solely the stellar variation of the flux. }
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{planetary_periodogram.png}
+    \includegraphics[width=\linewidth]{figures/planetary_periodogram.png}
     \caption{Periodogram of the stellar variation coupled with the planetary transit signal of the flux. }
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{TESS_EW_HAT-P-67.jpg}
+    \includegraphics[width=\linewidth]{figures/TESS_EW_HAT-P-67.jpg}
     \caption{A boat.}

### 2022-02-25 paper/paper1/ms.tex
Add prose to introduction

@@
-\documentclass{aastex631}
+\documentclass[modern]{aastex631}
 \bibliographystyle{aasjournal}
@@
 \usepackage{booktabs}
+\usepackage{censor}
 
@@
 \section{Introduction}\label{sec:intro}
+
+Exoplanets must possess a range of atmospheric properties well beyond what we have seen in our own Solar System.
+Extreme radiation effects, atmospheric erosion, and unexpected chemistry must exist, but collecting examples of these phenomena remains at the edge of the possible today.
+The minuscule signal strengths of atmospheric shells has hidden all but the most conspicuous patterns of lines.
+Helium 10830 $\AA$ has emerged as the most conspicuous of these, enabling ground-based detection with high-resolution near-infrared (IR) spectrographs.
+
+A total of \censor{xx} systems have Helium 10830 exosphere measurements to date: observations of the most extreme stellar systems reveal dramatic levels of mass loss, up to \censor{xx} $\%/\mathrm{Gyr}$.
+
 \citet{2020ApJ...894...97N} discusses the discovery of helium on exoplanets.
@@
 An extremely low density object, HAT-P-67b loses its atmosphere rather rapidly for transiting an evolved host star.
-
-\begin{deluxetable}{chc}
-    \tablecaption{Annotated bibliography for intro\label{table1}}
-    \tablehead{
-        \colhead{Reference} & \nocolhead{Other Column} & \colhead{Key idea}
-    }
-    \startdata
-    \citet{2020ApJ...894...97N} & - & HPF For Helium Exospheres\\
-    \citet{foreman13} & - & MCMC \\
-    \enddata
-\end{deluxetable}
 
@@
 
-\acknowledgements
-
-%ADS
+\begin{acknowledgements}
     This research has made use of NASA’s Astrophysics Data System.
+\end{acknowledgements}
 

### 2022-02-25 paper/paper1/ms.tex
Save a backup version of the paper

@@
 Here, we present a study of HAT-P-67, an F subgiant hosting a low density planet with 0.3 $M_{\mathrm{Jup}}$ and 2.1 $R_{\mathrm{Jup}}$ on a close-in 4.8 day orbit.
-The high energy radiation environment should provide a uniquely harsh testing ground for examining atmospheric escape.  The planet shows prominent in-transit absorption in the He 10830 \AA triplet and infrared Ca II 8542 \AA triplet across 20 visits over the course of a year including in- and out-of-transit spectroscopy.
+The high energy radiation environment should provide a uniquely harsh testing ground for examining atmospheric escape.
+The planet shows prominent in-transit absorption in the He 10830 \AA~ triplet and infrared Ca II 8542 \AA~ triplet across 20 visits over the course of a year including in- and out-of-transit spectroscopy.
 We identify the rotational period of HAT-P-67 to be 5.417 days by using contemporaneous data from the Transiting Exoplanet Survey Satellite (TESS).
-We consider multiple interpretations of the HPF and TESS observations.  First, the period measured by TESS may be the rotational period of the star and thus, the star and planet are nearly-tidally locked.
+We consider multiple interpretations of the HPF and TESS observations.
+First, the period measured by TESS may be the rotational period of the star and thus, the star and planet are nearly-tidally locked.
 On the other hand, the period measured by TESS may result from SPI-induced hot spots on the surface that follow the magnetic field lines linked to the planet's orbital period.
@@
 
-Exoplanets must possess a range of atmospheric properties well beyond what we have seen in our own Solar System.
+Exoplanets must possess a dynamic range of atmospheric properties far beyond what we have seen in our own Solar System.
 Extreme radiation effects, atmospheric erosion, and unexpected chemistry must exist, but collecting examples of these phenomena remains at the edge of the possible today.
-The minuscule signal strengths of atmospheric shells has hidden all but the most conspicuous patterns of lines.
-Helium 10830 $\AA$ has emerged as the most conspicuous of these, enabling ground-based detection with high-resolution near-infrared (IR) spectrographs.
+The minuscule signal strengths of atmospheric shells has hidden all but the most conspicuous phenomena.
+Helium 10830 \AA has emerged as the most conspicuous exosphere indicator, enabling ground-based detection with high-resolution near-infrared (IR) spectrographs.
 
-A total of \censor{xx} systems have Helium 10830 exosphere measurements to date: observations of the most extreme stellar systems reveal dramatic levels of mass loss, up to \censor{xx} $\%/\mathrm{Gyr}$.
-
-\citet{2020ApJ...894...97N} discusses the discovery of helium on exoplanets.
+A total of \censor{xx} systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A}.
 

### 2022-02-25 paper/paper1/ms.tex
A productive co-writing session with @18ganesha

@@
 
-A total of \censor{xx} systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A}.
+A total of \censor{xx} systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
 
@@
 
-\section{Methodology}
-\subsection{Closed Form MCMC Equivalent Widths}
-To estimate the uncertainty in our spectra we used the Monte Carlo MCMC chain \citep{foreman13}.
-%The equation for our equivalent width was derived with the variables for the Gaussian and the continuum:
+\section{Observations}
+\subsection{Habitable Zone Planet Finder (HPF)}
 
-The model will consist of a straight-line trend with a Gaussian subtracted from it.
+The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-schedule 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R, 2007PASP..119..556S} operates in the near-IR from 8100-12800 \AA spanning the \textit{z}, \textit{Y}, and \textit{J} bands.
+We observed HAT-P-67b with HPF in-transit on 2020 April 28, 2020 May 22, and 2020 June 15 and out-of-transit on a total of \censor{xx} other nights.
+
+\authorcomment1{We may want to put a observation log here, grouped by night.}
+% \input{tables/observation_flat_table.tex}
+
+\subsection{TESS Light Curve}
+HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS][]{2014SPIE.9143E..20R} in Sector 24 from April 16th, 2020 to May 13th, 2020 with a 30 minute cadence.
+
+\subsection{ASAS-SN}
+We retrieved ground-based photometry with the \emph{All-Sky Automated Survey for Supernovae} (ASAS-SN) using the Sky-Portal (\censor{xx}).
+
+\section{Analysis}
+Ideally we seek the pixel-to-pixel substructured spectrum of the helium exosphere, corrected for all the conceivable instrumental, telluric, and stellar contamination artifacts.
+In practice, these corrections are incomplete and so some care is needed to assess the extent of contamination.
+We experimented with a range of pre-processing and analysis techniques to quantify the accuracy and precision of our HPF spectra.
+
+\subsection{MCMC}
+We fit Gaussian line profiles to the He 10830 line with \texttt{emcee} \citep{foreman13}.
+The model consists of a straight-line trend with a Gaussian absorption line.
 It has five parameters: the straight-line trend slope $m$ and offset $b$, and the Gaussian amplitude $A$, center wavelength $\mu$, and width $w$.
 
+We computed the equivalent width with the closed-form integral:
+
 \begin{gather}
-    f_\lambda(m, b, A, \mu, w)= 1 - \frac{A}{(m \mu + b)}\cdot e^{-\frac{1}{2} \frac{(\lambda-\mu)^2}{w^2}}
+    W_\lambda=\frac{Aw}{m \mu + b}\cdot\sqrt{2\pi}
 \end{gather}
 
-We then focused on the sub-region defined by the line we were looking at.
-Using a generative model, we made guesses for the parameter values to create an initial guess fit for the data.
-We then used Monte Carlo Markov Chain to fine tune the parameters and develop a more accurate fit.
-The MCMC process spits out results for all five parameters with their corresponding equivalent widths.
-Using these values, we were able to calculate the equivalent width using the formula
-3
+Ultimately the MCMC method was highly accurate but imprecise, and was replaced in favor of \emph{data-driven} methods.
 
-\begin{gather}
-    W_\lambda=\frac{Aw}{[m (\mu-\textup{calcium line}) + b]}\cdot\sqrt{2\pi}
-\end{gather}
+\subsection{Pre-processing with \texttt{muler}}
 
-We then took the mean and standard deviation of this result to get the equivalent width and uncertainty for each planet.
+The raw 2D echellograms were reduced with the \texttt{Goldilocks} package\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}}, which outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb (LFC).
+The observations were acquired with the LFC turned off, so this unilluminated spectrum was discarded.
 
-\section{Observations}
-\subsection{Habitable zone Planet Finder}
+The sky fiber and target fiber have slightly different sizes and illumination properties so the sky fiber must be scaled prior to subtraction from the target spectrum.
+On average the target fiber sees $93\%$ of the flux of the sky reference fiber, and in detail this ratio depends on wavelength.
+We quantified the wavelength dependence by acquiring calibration observations of blank sky in both the target and sky fiber.
+We applied this wavelength-based scale factor to each target spectrum's associated reference sky fiber to achieve near-imperceptible sky-line residuals.
+A few lines exhibit residuals which may arise from slight differences in the local atmospheric conditions between the target and sky fiber.
 
-We observed the HAT-P-67 system with the Habitable Zone Planet Finder spectrograph (HPF) which is coupled to the 10-meter Hobby Eberly Telescope at the University of Texas at Austin's McDonald Observatory.
-HPF operates in the near-infrared light at 8100-12800 \AA using the \textit{z}, \textit{Y}, and \textit{J} bands.
-We observed HAT-P-67b with HPF in-transit on 2020 April 28, 2020 May 22, and 2020 June 15 and out-of-transit on 2020 April 27, 2020 May 20-21, 23-24, and 2020 June 13-16, 18.
-The observations on April 28th began at 06:10:31 and ended at 07:24:26, resulting in a total exposure time of 01:13:55.
-The observations on May 22nd began at 04:41:05 and ended at 05:55:00, resulting in a total exposure time of
-%ask gully if should keep doing this, very rough draft for now without good wording
+This refined sky-subtraction and all of our other standard pre-processing steps are implemented in a new open-source Python toolkit \texttt{muler} (Gully-Santiago \emph{et al.}, submitted).
 
-Table \ref{tab:sample_properties} lists the sources in the sample, and their bulk physical properties.
+Table \ref{tab:sample_properties} lists the bulk physical properties for HAT-P-67.
 
-\begin{deluxetable*}{lccc}[!ht]
-    \tablecaption{HPF Observations for HAT-P-67b \label{tab:observation_properties}}
-    \tablehead{
-        \colhead{Date} & \colhead{Time of Observation} & \colhead{Transit}}
-    \startdata
-    2020-04-28 & 06:10:31 & In transit\\
-    2020-04-28 & 06:16:12 & In transit\\
-    2020-04-28 & 06:21:53 & In transit\\
-    2020-04-28 & 06:27:34 & In transit\\
-    2020-04-28 & 06:33:15 & In transit\\
-    2020-04-28 & 06:38:57 & In transit\\
-    2020-04-28 & 06:44:38 & In transit\\
-    2020-04-28 & 06:50:19 & In transit\\
-    2020-04-28 & 06:10:31 & In transit\\
-    2020-04-28 & 06:10:31 & In transit\\
-    2020-04-28 & 06:10:31 & In transit\\
-    2020-04-28 & 06:10:31 & In transit\\
-    2020-04-28 & 06:10:31 & In transit
-    \enddata
-\end{deluxetable*}
-
-\begin{deluxetable*}{lccccc}[!ht]
+\begin{deluxetable*}{ccccc}[!ht]
     \tablecaption{Stellar properties \label{tab:sample_properties}}
     \tablehead{
-        \colhead{Name} & \colhead{$T_{eff}$ (K)} & \colhead{$\log{g}$} & \colhead{RV (km/s)} & \colhead{V sin(i) (km/s)} & \colhead{Reference}}
+        \colhead{$T_{\mathrm{eff}}$ (K)} & \colhead{$\log{g}$} & \colhead{RV (km/s)} & \colhead{V sin(i) (km/s)} & \colhead{Reference}}
     \startdata
-    HAT-P-32 & 6001 $\pm$ 88 & 4.22 $\pm$ 0.04 & -23.21 $\pm$ 0.26 & 20.7 $\pm$
-    0.5 & \cite{2019AJ....157...82W}\\
-    HAT-P-67 & $6406^{+65}_{-61}$ & $3.854^{+0.014}_{-0.023}$ & -1.4 $\pm$ 0.5 & 35.8 $\pm$ 1.1 & \cite{2017AJ....153..211Z}\\
+    $6406^{+65}_{-61}$ & $3.854^{+0.014}_{-0.023}$ & -1.4 $\pm$ 0.5 & 35.8 $\pm$ 1.1 & \cite{2017AJ....153..211Z}\\
     \enddata
@@
 \subsection{TESS Light Curve}
-We observed the HAT-P-67 system using data from TESS sector 24 taken from April 16th, 2020 to May 13th, 2020 with an exposure time of 1800 seconds.
-Using the \textit{lightkurve} package, we attempted to phase fold our exoplanet transit plot to identify the stellar rotation signal and the exoplanet's transit signal.
+We observed the HAT-P-67 system using data from TESS Sector 24 taken from April 16th, 2020 to May 13th, 2020 with an exposure time of 1800 seconds.
+Using the \texttt{lightkurve} package, we attempted to phase fold our exoplanet transit plot to identify the stellar rotation signal and the exoplanet's transit signal.
 At first glance, the stellar flux decreases by about 0.2\% and the exoplanet transit signal decreases by about 0.7\%.
@@
     HAT-P-67 & Aug 8, 2020 & & $10344.993^{+0.015}_{-0.016}$ & & $0.1064\pm0.0051$\\
-    HAT-P-32 & Aug 8, 2020 & & $10344.991^{+0.016}_{-0.017}$ & & $0.1112\pm0.0055$\\
     \enddata
@@
 
+\subsection{Calculations}
+Using the contemporaneous TESS lightcurve, we notice that there is a 0.2\% flux variation.
+Assuming that this increase in flux is due to a hot spot with a contrast of 200\%, the hot spot must have a radius that is 12.49 times that of the radius of the Earth.
+Assuming that the mass loss rate of the planet is its mass over 10 billion years, we can assume that this hot spot is not caused by in falling mass from the planetary envelope as the mass is not enough to cause a 0.2\% modulation in the flux.
+
+We can also assume that the system is tidally locked.
+
 \section{Results}

### 2022-02-25 paper/paper1/tables/ew_table.tex
Break out the EW table into a standalone document

--- 2022-02-25 paper/paper1/ms.tex
@@
-\documentclass[modern]{aastex631}
-\bibliographystyle{aasjournal}
-
-\usepackage{graphicx}
-\usepackage[caption=false]{subfig}
-\usepackage{amsmath}
-\usepackage{booktabs}
-\usepackage{censor}
-
-\let\pwiflocal=\iffalse \let\pwifjournal=\iffalse
-%From: http://arxiv.org/format/1512.00483
-%\input{setup}
-%\input{mgs_setup}
-
-\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{#1}}
-\providecommand{\adsurl}[1]{\href{#1}{ADS}}
-\newcommand{\project}[1]{\textsl{#1}}
-
-\begin{document}
-\shorttitle{HPF spectral analysis}
-\shortauthors{TBD}
-
-\title{Atmospheric escape and star-planet-interaction in the HAT-P-67 b system}
-
-\author{TBD}
-\affiliation{TBD}
-
-\begin{abstract}
-    We aim to understand how exoplanet atmospheres evolve across age, stellar irradiation environments, planet properties, and---for extremely close-in exoplanets---direct star-planet interaction (SPI) such as stellar winds, tidal forces, and magnetic interactions.
-The scarcity of exoplanet atmosphere measurements across a range of stellar properties has limited our ability to complete this picture.
-
-    The Helium Exospheres program with the Habitable Zone Planet Finder (HPF) spectrograph on the Hobby Eberly Telescope (HET) in West Texas has targeted 23 exoplanet systems over two years.
-Here, we present a study of HAT-P-67, an F subgiant hosting a low density planet with 0.3 $M_{\mathrm{Jup}}$ and 2.1 $R_{\mathrm{Jup}}$ on a close-in 4.8 day orbit.
-The high energy radiation environment should provide a uniquely harsh testing ground for examining atmospheric escape.
-The planet shows prominent in-transit absorption in the He 10830 \AA~ triplet and infrared Ca II 8542 \AA~ triplet across 20 visits over the course of a year including in- and out-of-transit spectroscopy.
-We identify the rotational period of HAT-P-67 to be 5.417 days by using contemporaneous data from the Transiting Exoplanet Survey Satellite (TESS).
-We consider multiple interpretations of the HPF and TESS observations.
-First, the period measured by TESS may be the rotational period of the star and thus, the star and planet are nearly-tidally locked.
-On the other hand, the period measured by TESS may result from SPI-induced hot spots on the surface that follow the magnetic field lines linked to the planet's orbital period.
-Finally, we consider the possibility of stellar surface inhomogeneity contaminating the He and Ca II transit signals.
-\end{abstract}
-
-\keywords{stars: fundamental parameters ---  stars: statistics}
-
-\section{Introduction}\label{sec:intro}
-
-Exoplanets must possess a dynamic range of atmospheric properties far beyond what we have seen in our own Solar System.
-Extreme radiation effects, atmospheric erosion, and unexpected chemistry must exist, but collecting examples of these phenomena remains at the edge of the possible today.
-The minuscule signal strengths of atmospheric shells has hidden all but the most conspicuous phenomena.
-Helium 10830 \AA has emerged as the most conspicuous exosphere indicator, enabling ground-based detection with high-resolution near-infrared (IR) spectrographs.
-
-A total of \censor{xx} systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A}.
-
-We specified our observations on the HAT-P-67 system due to its unique rotational period.
-HAT-P-67 is a binary system of an F type sub-giant and a much cooler M2 star with the Saturn-sized planet HAT-P-67b.
-An extremely low density object, HAT-P-67b loses its atmosphere rather rapidly for transiting an evolved host star.
-
-\section{Methodology}
-\subsection{Closed Form MCMC Equivalent Widths}
-To estimate the uncertainty in our spectra we used the Monte Carlo MCMC chain \citep{foreman13}.
-%The equation for our equivalent width was derived with the variables for the Gaussian and the continuum:
-
-The model will consist of a straight-line trend with a Gaussian subtracted from it.
-It has five parameters: the straight-line trend slope $m$ and offset $b$, and the Gaussian amplitude $A$, center wavelength $\mu$, and width $w$.
-
-\begin{gather}
-    f_\lambda(m, b, A, \mu, w)= 1 - \frac{A}{(m \mu + b)}\cdot e^{-\frac{1}{2} \frac{(\lambda-\mu)^2}{w^2}}
-\end{gather}
-
-We then focused on the sub-region defined by the line we were looking at.
-Using a generative model, we made guesses for the parameter values to create an initial guess fit for the data.
-We then used Monte Carlo Markov Chain to fine tune the parameters and develop a more accurate fit.
-The MCMC process spits out results for all five parameters with their corresponding equivalent widths.
-Using these values, we were able to calculate the equivalent width using the formula
-3
-
-\begin{gather}
-    W_\lambda=\frac{Aw}{[m (\mu-\textup{calcium line}) + b]}\cdot\sqrt{2\pi}
-\end{gather}
-
-We then took the mean and standard deviation of this result to get the equivalent width and uncertainty for each planet.
-
-\section{Observations}
-\subsection{Habitable zone Planet Finder}
-
-We observed the HAT-P-67 system with the Habitable Zone Planet Finder spectrograph (HPF) which is coupled to the 10-meter Hobby Eberly Telescope at the University of Texas at Austin's McDonald Observatory.
-HPF operates in the near-infrared light at 8100-12800 \AA using the \textit{z}, \textit{Y}, and \textit{J} bands.
-We observed HAT-P-67b with HPF in-transit on 2020 April 28, 2020 May 22, and 2020 June 15 and out-of-transit on 2020 April 27, 2020 May 20-21, 23-24, and 2020 June 13-16, 18.
-The observations on April 28th began at 06:10:31 and ended at 07:24:26, resulting in a total exposure time of 01:13:55.
-The observations on May 22nd began at 04:41:05 and ended at 05:55:00, resulting in a total exposure time of
-%ask gully if should keep doing this, very rough draft for now without good wording
-
-Table \ref{tab:sample_properties} lists the sources in the sample, and their bulk physical properties.
-
-\begin{deluxetable*}{lccc}[!ht]
-    \tablecaption{HPF Observations for HAT-P-67b \label{tab:observation_properties}}
-    \tablehead{
-        \colhead{Date} & \colhead{Time of Observation} & \colhead{Transit}}
-    \startdata
-    2020-04-28 & 06:10:31 & In transit\\
-    2020-04-28 & 06:16:12 & In transit\\
-    2020-04-28 & 06:21:53 & In transit\\
-    2020-04-28 & 06:27:34 & In transit\\
-    2020-04-28 & 06:33:15 & In transit\\
-    2020-04-28 & 06:38:57 & In transit\\
-    2020-04-28 & 06:44:38 & In transit\\
-    2020-04-28 & 06:50:19 & In transit\\
-    2020-04-28 & 06:10:31 & In transit\\
-    2020-04-28 & 06:10:31 & In transit\\
-    2020-04-28 & 06:10:31 & In transit\\
-    2020-04-28 & 06:10:31 & In transit\\
-    2020-04-28 & 06:10:31 & In transit
-    \enddata
-\end{deluxetable*}
-
-\begin{deluxetable*}{lccccc}[!ht]
-    \tablecaption{Stellar properties \label{tab:sample_properties}}
-    \tablehead{
-        \colhead{Name} & \colhead{$T_{eff}$ (K)} & \colhead{$\log{g}$} & \colhead{RV (km/s)} & \colhead{V sin(i) (km/s)} & \colhead{Reference}}
-    \startdata
-    HAT-P-32 & 6001 $\pm$ 88 & 4.22 $\pm$ 0.04 & -23.21 $\pm$ 0.26 & 20.7 $\pm$
-    0.5 & \cite{2019AJ....157...82W}\\
-    HAT-P-67 & $6406^{+65}_{-61}$ & $3.854^{+0.014}_{-0.023}$ & -1.4 $\pm$ 0.5 & 35.8 $\pm$ 1.1 & \cite{2017AJ....153..211Z}\\
-    \enddata
-\end{deluxetable*}
-
-\subsection{TESS Light Curve}
-We observed the HAT-P-67 system using data from TESS sector 24 taken from April 16th, 2020 to May 13th, 2020 with an exposure time of 1800 seconds.
-Using the \textit{lightkurve} package, we attempted to phase fold our exoplanet transit plot to identify the stellar rotation signal and the exoplanet's transit signal.
-At first glance, the stellar flux decreases by about 0.2\% and the exoplanet transit signal decreases by about 0.7\%.
-In order to analyze the stellar rotation period, we must mask the planetary transit signal.
-By folding the normalized lightcurve with a given planetary orbital period of 4.810 days, we omitted the planetary transit signal.
-We then created a periodogram of just the stellar signal and arrived at an estimate of several parameters for HAT-P-67b: the planetary period is 4.809 days, the original transit time was 1958.082 BTJD, and the planetary duration was 0.25 days.
-We then created a cadence mask using the Box Least Squares parameters.
-The resulting periodogram of just the stellar variation described a rotational period of 5.417 days is shown in Figure \ref{fig:stellar_periodogram}.
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/stellar_periodogram.png}
-    \caption{Periodogram of solely the stellar variation of the flux. }
-    \label{fig:stellar_periodogram}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/planetary_periodogram.png}
-    \caption{Periodogram of the stellar variation coupled with the planetary transit signal of the flux. }
-    \label{fig:planetary_periodogram}
-\end{figure}
-
-\section{Analysis}
-\subsection{HPF MCMC}
-The methodology used to fit the HPF spectra was the Markov chain Monte Carlo (MCMC).
-After deblazing and normalizing the spectrum, we used a Gaussian line to fit the spectra with five parameters: width, center wavelength, amplitude, slope, and offset.
-We focused on each sub-region of the spectrum by cutting of data outside of the $99.9\%-100.1\%*line$ threshold to create a better fit for the data.
-This threshold was determined as a result of which line we were looking at.
-The generative model consists of a straight-line trend with a Gaussian subtracted from it.
-The continuum of the spectrum was given by $continuum=m(\lambda-\lambda_{int})+b$ and the Gaussian fit was subtracted off of the continuum to get the absorption line fit.
-After applying values to the five parameters for the generative model, we improved our fitting with the MCMC process.
-We computed the log likelihood of the guessing parameters to determine a quality of fit metric.
-From there, we ran MCMC with the package \textit{emcee} at 5000 steps for the five parameters.
-After thinning out and discarding the last 1000 steps, we gathered the final draws for the given parameters with their corresponding uncertainties.
-
-\subsection{HPF Equivalent Width Determination}
-In addition to the MCMC method, we verified the precision of our numbers through another fitting method.
-While the MCMC method produced an accurate result, it lacked the precision required.
-Thus, we chose to analyze the data again with the summation method.
-
-After collecting the new parameters, we then calculated the equivalent width of the corresponding line with the formula $EW=\sqrt{2\pi}\frac{Aw}{m(\mu-line)+b}$.
-We then calculated the mean and standard deviation of the equivalent width.
-\subsection{Contemporaneous Stellar Activity Quantification}
-\subsection{Equivalent Width vs Phase}
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/TESS_EW_HAT-P-67.jpg}
-    \caption{A boat.}
-    \label{fig:boat1}
-\end{figure}
-
 \begin{deluxetable*}{lcccccc}[!ht]
@@
     HAT-P-67 & Aug 8, 2020 & & $10344.993^{+0.015}_{-0.016}$ & & $0.1064\pm0.0051$\\
-    HAT-P-32 & Aug 8, 2020 & & $10344.991^{+0.016}_{-0.017}$ & & $0.1112\pm0.0055$\\
     \enddata
 \end{deluxetable*}
-
-\begin{tabular}{lrrrlrll}
-    \toprule
-    date       & declination & exposure time & jd           & qidx   & ra        & star name                  & time     \\
-    \midrule
-    2020-04-28 & 44.763974   & 308.85        & 2.458968e+06 & 6437.0 & 17.106801 & HAT-P-67b\_IN\_1           & 06:10:31 \\
-    2020-04-28 & 44.763643   & 308.85        & 2.458968e+06 & 6437.0 & 17.106878 & HAT-P-67b\_IN\_1           & 06:16:12 \\
-    2020-04-28 & 44.763456   & 308.85        & 2.458968e+06 & 6437.0 & 17.106957 & HAT-P-67b\_IN\_1           & 06:21:53 \\
-    2020-04-28 & 44.763237   & 308.85        & 2.458968e+06 & 6437.0 & 17.107029 & HAT-P-67b\_IN\_1           & 06:27:34 \\
-    2020-04-28 & 44.763050   & 308.85        & 2.458968e+06 & 6437.0 & 17.107089 & HAT-P-67b\_IN\_1           & 06:33:15 \\
-    2020-04-28 & 44.762969   & 308.85        & 2.458968e+06 & 6437.0 & 17.107158 & HAT-P-67b\_IN\_1           & 06:38:57 \\
-    2020-04-28 & 44.762784   & 308.85        & 2.458968e+06 & 6437.0 & 17.107229 & HAT-P-67b\_IN\_1           & 06:44:38 \\
-    2020-04-28 & 44.762775   & 308.85        & 2.458968e+06 & 6437.0 & 17.107301 & HAT-P-67b\_IN\_1           & 06:50:19 \\
-    2020-04-28 & 44.762575   & 308.85        & 2.458968e+06 & 6437.0 & 17.107363 & HAT-P-67b\_IN\_1           & 06:56:00 \\
-    2020-04-28 & 44.762322   & 308.85        & 2.458968e+06 & 6437.0 & 17.107427 & HAT-P-67b\_IN\_1           & 07:01:41 \\
-    2020-04-28 & 44.762290   & 308.85        & 2.458968e+06 & 6437.0 & 17.107485 & HAT-P-67b\_IN\_1           & 07:07:22 \\
-    2020-04-28 & 44.762212   & 308.85        & 2.458968e+06 & 6437.0 & 17.107541 & HAT-P-67b\_IN\_1           & 07:13:03 \\
-    2020-04-28 & 44.762057   & 308.85        & 2.458968e+06 & 6437.0 & 17.107608 & HAT-P-67b\_IN\_1           & 07:18:44 \\
-    2020-04-28 & 44.762013   & 308.85        & 2.458968e+06 & 6437.0 & 17.107669 & HAT-P-67b\_IN\_1           & 07:24:26 \\
-    2020-05-22 & 44.765938   & 308.85        & 2.458992e+06 & 6587.0 & 17.106844 & HAT-P-67b\_IN\_2           & 04:41:05 \\
-    2020-05-22 & 44.765694   & 308.85        & 2.458992e+06 & 6587.0 & 17.106916 & HAT-P-67b\_IN\_2           & 04:46:46 \\
-    2020-05-22 & 44.765448   & 308.85        & 2.458992e+06 & 6587.0 & 17.106988 & HAT-P-67b\_IN\_2           & 04:52:27 \\
-    2020-05-22 & 44.765338   & 308.85        & 2.458992e+06 & 6587.0 & 17.107057 & HAT-P-67b\_IN\_2           & 04:58:09 \\
-    2020-05-22 & 44.765232   & 308.85        & 2.458992e+06 & 6587.0 & 17.107116 & HAT-P-67b\_IN\_2           & 05:03:50 \\
-    2020-05-22 & 44.764945   & 308.85        & 2.458992e+06 & 6587.0 & 17.107198 & HAT-P-67b\_IN\_2           & 05:09:31 \\
-    2020-05-22 & 44.764912   & 308.85        & 2.458992e+06 & 6587.0 & 17.107269 & HAT-P-67b\_IN\_2           & 05:15:12 \\
-    2020-05-22 & 44.764767   & 308.85        & 2.458992e+06 & 6587.0 & 17.107347 & HAT-P-67b\_IN\_2           & 05:20:53 \\
-    2020-05-22 & 44.764488   & 308.85        & 2.458992e+06 & 6587.0 & 17.107408 & HAT-P-67b\_IN\_2           & 05:26:34 \\
-    2020-05-22 & 44.764364   & 308.85        & 2.458992e+06 & 6587.0 & 17.107473 & HAT-P-67b\_IN\_2           & 05:32:15 \\
-    2020-05-22 & 44.764240   & 308.85        & 2.458992e+06 & 6587.0 & 17.107525 & HAT-P-67b\_IN\_2           & 05:37:57 \\
-    2020-05-22 & 44.764128   & 308.85        & 2.458992e+06 & 6587.0 & 17.107601 & HAT-P-67b\_IN\_2           & 05:43:38 \\
-    2020-05-22 & 44.764087   & 308.85        & 2.458992e+06 & 6587.0 & 17.107653 & HAT-P-67b\_IN\_2           & 05:49:19 \\
-    2020-05-22 & 44.763816   & 308.85        & 2.458992e+06 & 6587.0 & 17.107728 & HAT-P-67b\_IN\_2           & 05:55:00 \\
-    2020-06-15 & 44.768164   & 308.85        & 2.459016e+06 & 6938.0 & 17.106909 & HAT-P-67b\_IN\_3           & 03:13:19 \\
-    2020-06-15 & 44.767792   & 308.85        & 2.459016e+06 & 6938.0 & 17.106979 & HAT-P-67b\_IN\_3           & 03:19:00 \\
-    2020-06-15 & 44.767746   & 308.85        & 2.459016e+06 & 6938.0 & 17.107035 & HAT-P-67b\_IN\_3           & 03:24:41 \\
-    2020-06-15 & 44.767580   & 308.85        & 2.459016e+06 & 6938.0 & 17.107103 & HAT-P-67b\_IN\_3           & 03:30:23 \\
-    2020-06-15 & 44.767436   & 308.85        & 2.459016e+06 & 6938.0 & 17.107145 & HAT-P-67b\_IN\_3           & 03:36:04 \\
-    2020-06-15 & 44.767252   & 308.85        & 2.459016e+06 & 6938.0 & 17.107246 & HAT-P-67b\_IN\_3           & 03:41:45 \\
-    2020-06-15 & 44.767175   & 308.85        & 2.459016e+06 & 6938.0 & 17.107295 & HAT-P-67b\_IN\_3           & 03:47:26 \\
-    2020-06-15 & 44.766835   & 308.85        & 2.459016e+06 & 6938.0 & 17.107368 & HAT-P-67b\_IN\_3           & 03:53:07 \\
-    2020-06-15 & 44.766759   & 308.85        & 2.459016e+06 & 6938.0 & 17.107418 & HAT-P-67b\_IN\_3           & 03:58:48 \\
-    2020-04-27 & 44.764544   & 308.85        & 2.458967e+06 & 6436.0 & 17.106775 & HAT-P-67b\_OUT\_1\_before1 & 06:29:11 \\
-    2020-04-27 & 44.764240   & 308.85        & 2.458967e+06 & 6436.0 & 17.106827 & HAT-P-67b\_OUT\_1\_before1 & 06:35:03 \\
-    2020-04-27 & 44.764141   & 308.85        & 2.458967e+06 & 6436.0 & 17.106900 & HAT-P-67b\_OUT\_1\_before1 & 06:40:55 \\
-    2020-04-27 & 44.763873   & 308.85        & 2.458967e+06 & 6436.0 & 17.106974 & HAT-P-67b\_OUT\_1\_before1 & 06:46:47 \\
-    2020-04-29 & 44.764930   & 308.85        & 2.458969e+06 & 6438.0 & 17.106673 & HAT-P-67b\_OUT\_1\_after1  & 06:34:20 \\
-    2020-04-29 & 44.764731   & 308.85        & 2.458969e+06 & 6438.0 & 17.106749 & HAT-P-67b\_OUT\_1\_after1  & 06:40:01 \\
-    2020-04-29 & 44.764633   & 308.85        & 2.458969e+06 & 6438.0 & 17.106817 & HAT-P-67b\_OUT\_1\_after1  & 06:45:42 \\
-    2020-04-29 & 44.764531   & 308.85        & 2.458969e+06 & 6438.0 & 17.106878 & HAT-P-67b\_OUT\_1\_after1  & 06:51:23 \\
-    2020-05-20 & 44.782750   & 308.85        & 2.458990e+06 & 6599.0 & 17.107624 & HAT-P-67b\_OUT\_2\_before2 & 10:43:31 \\
-    2020-05-20 & 44.781504   & 308.85        & 2.458990e+06 & 6599.0 & 17.107668 & HAT-P-67b\_OUT\_2\_before2 & 10:49:12 \\
-    2020-05-20 & 44.780211   & 308.85        & 2.458990e+06 & 6599.0 & 17.107719 & HAT-P-67b\_OUT\_2\_before2 & 10:54:53 \\
-    2020-05-20 & 44.779210   & 308.85        & 2.458990e+06 & 6599.0 & 17.107778 & HAT-P-67b\_OUT\_2\_before2 & 11:00:34 \\
-    2020-05-21 & 44.782995   & 308.85        & 2.458991e+06 & 6588.0 & 17.107695 & HAT-P-67b\_OUT\_2\_before1 & 10:23:05 \\
-    2020-05-21 & 44.781573   & 308.85        & 2.458991e+06 & 6588.0 & 17.107731 & HAT-P-67b\_OUT\_2\_before1 & 10:28:46 \\
-    2020-05-21 & 44.780368   & 308.85        & 2.458991e+06 & 6588.0 & 17.107773 & HAT-P-67b\_OUT\_2\_before1 & 10:34:28 \\
-    2020-05-21 & 44.779170   & 308.85        & 2.458991e+06 & 6588.0 & 17.107810 & HAT-P-67b\_OUT\_2\_before1 & 10:40:09 \\
-    2020-05-23 & 44.783203   & 308.85        & 2.458993e+06 & 6589.0 & 17.107654 & HAT-P-67b\_OUT\_2\_after1  & 10:16:00 \\
-    2020-05-23 & 44.781895   & 308.85        & 2.458993e+06 & 6589.0 & 17.107688 & HAT-P-67b\_OUT\_2\_after1  & 10:21:41 \\
-    2020-05-23 & 44.780749   & 308.85        & 2.458993e+06 & 6589.0 & 17.107718 & HAT-P-67b\_OUT\_2\_after1  & 10:27:22 \\
-    2020-05-23 & 44.779639   & 308.85        & 2.458993e+06 & 6589.0 & 17.107763 & HAT-P-67b\_OUT\_2\_after1  & 10:33:04 \\
-    2020-05-24 & 44.782834   & 308.85        & 2.458994e+06 & 6600.0 & 17.107668 & HAT-P-67b\_OUT\_2\_after2  & 10:22:14 \\
-    2020-05-24 & 44.781654   & 308.85        & 2.458994e+06 & 6600.0 & 17.107708 & HAT-P-67b\_OUT\_2\_after2  & 10:27:55 \\
-    2020-05-24 & 44.780276   & 308.85        & 2.458994e+06 & 6600.0 & 17.107744 & HAT-P-67b\_OUT\_2\_after2  & 10:33:36 \\
-    2020-05-24 & 44.779039   & 308.85        & 2.458994e+06 & 6600.0 & 17.107789 & HAT-P-67b\_OUT\_2\_after2  & 10:39:17 \\
-    2020-06-13 & 44.785061   & 308.85        & 2.459014e+06 & 6941.0 & 17.107689 & HAT-P-67b\_OUT\_3\_before2 & 09:13:57 \\
-    2020-06-13 & 44.783754   & 308.85        & 2.459014e+06 & 6941.0 & 17.107743 & HAT-P-67b\_OUT\_3\_before2 & 09:19:38 \\
-    2020-06-13 & 44.782668   & 308.85        & 2.459014e+06 & 6941.0 & 17.107795 & HAT-P-67b\_OUT\_3\_before2 & 09:25:19 \\
-    2020-06-14 & 44.785228   & 308.85        & 2.459015e+06 & 6939.0 & 17.107679 & HAT-P-67b\_OUT\_3\_before1 & 09:08:28 \\
-    2020-06-14 & 44.783951   & 308.85        & 2.459015e+06 & 6939.0 & 17.107713 & HAT-P-67b\_OUT\_3\_before1 & 09:14:09 \\
-    2020-06-14 & 44.782721   & 308.85        & 2.459015e+06 & 6939.0 & 17.107767 & HAT-P-67b\_OUT\_3\_before1 & 09:19:50 \\
-    2020-06-14 & 44.781659   & 308.85        & 2.459015e+06 & 6939.0 & 17.107823 & HAT-P-67b\_OUT\_3\_before1 & 09:25:32 \\
-    2020-06-15 & 44.783524   & 308.85        & 2.459016e+06 & 6943.0 & 17.107765 & HAT-P-67b\_OUT\_same3      & 08:59:57 \\
-    2020-06-15 & 44.782226   & 308.85        & 2.459016e+06 & 6943.0 & 17.107803 & HAT-P-67b\_OUT\_same3      & 09:05:39 \\
-    2020-06-15 & 44.780921   & 308.85        & 2.459016e+06 & 6943.0 & 17.107841 & HAT-P-67b\_OUT\_same3      & 09:11:20 \\
-    2020-06-15 & 44.779720   & 308.85        & 2.459016e+06 & 6943.0 & 17.107889 & HAT-P-67b\_OUT\_same3      & 09:17:01 \\
-    2020-06-15 & 44.778571   & 308.85        & 2.459016e+06 & 6943.0 & 17.107938 & HAT-P-67b\_OUT\_same3      & 09:22:42 \\
-    2020-06-15 & 44.777286   & 308.85        & 2.459016e+06 & 6943.0 & 17.108007 & HAT-P-67b\_OUT\_same3      & 09:28:23 \\
-    2020-06-15 & 44.776196   & 308.85        & 2.459016e+06 & 6943.0 & 17.108044 & HAT-P-67b\_OUT\_same3      & 09:34:04 \\
-    2020-06-15 & 44.774972   & 308.85        & 2.459016e+06 & 6943.0 & 17.108092 & HAT-P-67b\_OUT\_same3      & 09:39:45 \\
-    2020-06-15 & 44.773796   & 308.85        & 2.459016e+06 & 6943.0 & 17.108157 & HAT-P-67b\_OUT\_same3      & 09:45:26 \\
-    2020-06-16 & 44.785595   & 308.85        & 2.459017e+06 & 6940.0 & 17.107685 & HAT-P-67b\_OUT\_3\_after1  & 08:51:26 \\
-    2020-06-16 & 44.784378   & 308.85        & 2.459017e+06 & 6940.0 & 17.107727 & HAT-P-67b\_OUT\_3\_after1  & 08:57:07 \\
-    2020-06-16 & 44.783087   & 308.85        & 2.459017e+06 & 6940.0 & 17.107751 & HAT-P-67b\_OUT\_3\_after1  & 09:02:49 \\
-    2020-06-16 & 44.781929   & 308.85        & 2.459017e+06 & 6940.0 & 17.107796 & HAT-P-67b\_OUT\_3\_after1  & 09:08:30 \\
-    2020-06-18 & 44.785281   & 308.85        & 2.459019e+06 & 6942.0 & 17.107699 & HAT-P-67b\_OUT\_3\_after2  & 08:58:34 \\
-    2020-06-18 & 44.784069   & 308.85        & 2.459019e+06 & 6942.0 & 17.107753 & HAT-P-67b\_OUT\_3\_after2  & 09:04:15 \\
-    2020-06-18 & 44.782920   & 308.85        & 2.459019e+06 & 6942.0 & 17.107820 & HAT-P-67b\_OUT\_3\_after2  & 09:09:56 \\
-    2020-06-18 & 44.781739   & 308.85        & 2.459019e+06 & 6942.0 & 17.107881 & HAT-P-67b\_OUT\_3\_after2  & 09:15:37 \\
-    \bottomrule
-\end{tabular}
-
-\section{Results}
-\subsection{Is there a difference in equivalent width in transit vs out?}
-We can see that there is indeed a helium signature that arises when the planet is in transit with its host star.
-\subsection{Stellar Activity (non)detection versus Equivalent Width}
-There is a likelihood that a portion of the exoplanet emission spectra originates from stellar activity.
-Thus, we must identify which stellar features mimic a helium signature.
-Such features can be narrowed down to the star's radial velocity, star spots, and faculae.
-\subsection{Star Planet Interaction}
-Characterizing a host star's stellar environment is of utmost importance if we want to understand how exoplanet atmospheres are affected.
-While cool dwarfs generate high irradiation in the ultraviolet and stellar winds, the sub-giant category
-
-\section{Discussion}
-
-\section{Conclusions}
-
-Reiteration here.
-
-\clearpage
-\pagebreak
-
-\appendix
-%\section{HPF spectra post-processing}
-%\label{methods-details}
-
-\begin{acknowledgements}
-    This research has made use of NASA’s Astrophysics Data System.
-\end{acknowledgements}
-
-\facilities{Smith (IGRINS), Gaia, ASAS}
-
-\software{  pandas \citep{mckinney10},
-    emcee \citep{foreman13},
-    matplotlib \citep{hunter07},
-    numpy \citep{2020NumPy-Array},
-    scipy \citep{2020SciPy-NMeth},
-    ipython \citep{perez07},
-    seaborn \citep{waskom14}}
-
-\clearpage
-
-\bibliography{ms}
-
-\end{document}

### 2022-02-25 paper/paper1/ms.tex
Add references from @18ganesha and a few more

@@
 
-\subsection{MCMC}
-We fit Gaussian line profiles to the He 10830 line with \texttt{emcee} \citep{foreman13}.
+\subsection{Pre-processing with \texttt{muler}}
+
+The raw 2D echellograms were reduced with the \texttt{Goldilocks} package\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}}, which outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb (LFC).
+The observations were acquired with the LFC turned off, so this unilluminated spectrum was discarded.
+
+The sky fiber and target fiber have slightly different throughputs and illumination properties so the sky fiber must be scaled prior to subtraction from the target spectrum.
+On average the target fiber sees $93\%$ of the flux of the sky reference fiber, and in detail this ratio depends on wavelength.
+We quantified the wavelength dependence by acquiring calibration observations of blank sky in both the target and sky fiber.
+We applied this wavelength-based scale factor to each target spectrum's associated reference sky fiber to achieve near-imperceptible sky-line residuals.
+A few lines exhibit residuals which may arise from slight differences in the local atmospheric conditions between the target and sky fiber.
+
+We masked spectral regions predicted to have significant telluric lines with a template generated by \texttt{telfit} \citep{2014AJ....148...53G}.
+We shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W} as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A}.
+
+We flatten the spectral to continuum indices near the He 10830 features and compute the equivalent width (EW) defined over the spectral region \censorbox{xx,xxx}$-$\censorbox{xx,xxx} shown in Figure \censorbox{XX}.
+
+The sky-subtraction, telluric masking, barycentric correction, and all of our other standard pre-processing steps are implemented in a new open-source Python interface \texttt{muler}\footnote{\url{https://github.com/OttoStruve/muler/}} (Gully-Santiago \emph{et al.}, submitted).
+
+\subsection{EW Uncertainty quantification with MCMC}
+We assessed the uncertainty in our equivalent fit Gaussian line profiles to the He 10830 line with \texttt{emcee} \citep{foreman13}.
 The model consists of a straight-line trend with a Gaussian absorption line.
@@
 Ultimately the MCMC method was highly accurate but imprecise, and was replaced in favor of \emph{data-driven} methods.
-
-\subsection{Pre-processing with \texttt{muler}}
-
-The raw 2D echellograms were reduced with the \texttt{Goldilocks} package\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}}, which outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb (LFC).
-The observations were acquired with the LFC turned off, so this unilluminated spectrum was discarded.
-
-The sky fiber and target fiber have slightly different sizes and illumination properties so the sky fiber must be scaled prior to subtraction from the target spectrum.
-On average the target fiber sees $93\%$ of the flux of the sky reference fiber, and in detail this ratio depends on wavelength.
-We quantified the wavelength dependence by acquiring calibration observations of blank sky in both the target and sky fiber.
-We applied this wavelength-based scale factor to each target spectrum's associated reference sky fiber to achieve near-imperceptible sky-line residuals.
-A few lines exhibit residuals which may arise from slight differences in the local atmospheric conditions between the target and sky fiber.
-
-This refined sky-subtraction and all of our other standard pre-processing steps are implemented in a new open-source Python toolkit \texttt{muler} (Gully-Santiago \emph{et al.}, submitted).
 
@@
 
-\begin{deluxetable*}{lcccccc}[!ht]
-    \tablecaption{Equivalent Width \label{tab:ew_properties}}
-    \tablehead{
-        \colhead{Star Name} & \colhead{Date} & \colhead{ID} & \colhead{Observed Line Center Position} & \colhead{Intrinsic Line Center Position} & \colhead{Equivalent Width (\AA)}}
-    \startdata
-    HAT-P-67 & Aug 7, 2020 & & $10328.493\pm0.017$ & & $0.1607\pm0.0059$\\
-    HAT-P-67 & Aug 8, 2020 & & $10345.007\pm0.019$ & & $0.1122\pm0.0068$\\
-    HAT-P-67 & Aug 8, 2020 & & $10344.993^{+0.015}_{-0.016}$ & & $0.1064\pm0.0051$\\
-    \enddata
-\end{deluxetable*}
-
-\begin{tabular}{lrrrlrll}
-    \toprule
-    date       & declination & exposure time & jd           & qidx   & ra        & star name                  & time     \\
-    \midrule
-    2020-04-28 & 44.763974   & 308.85        & 2.458968e+06 & 6437.0 & 17.106801 & HAT-P-67b\_IN\_1           & 06:10:31 \\
-    2020-04-28 & 44.763643   & 308.85        & 2.458968e+06 & 6437.0 & 17.106878 & HAT-P-67b\_IN\_1           & 06:16:12 \\
-    2020-04-28 & 44.763456   & 308.85        & 2.458968e+06 & 6437.0 & 17.106957 & HAT-P-67b\_IN\_1           & 06:21:53 \\
-    2020-04-28 & 44.763237   & 308.85        & 2.458968e+06 & 6437.0 & 17.107029 & HAT-P-67b\_IN\_1           & 06:27:34 \\
-    2020-04-28 & 44.763050   & 308.85        & 2.458968e+06 & 6437.0 & 17.107089 & HAT-P-67b\_IN\_1           & 06:33:15 \\
-    2020-04-28 & 44.762969   & 308.85        & 2.458968e+06 & 6437.0 & 17.107158 & HAT-P-67b\_IN\_1           & 06:38:57 \\
-    2020-04-28 & 44.762784   & 308.85        & 2.458968e+06 & 6437.0 & 17.107229 & HAT-P-67b\_IN\_1           & 06:44:38 \\
-    2020-04-28 & 44.762775   & 308.85        & 2.458968e+06 & 6437.0 & 17.107301 & HAT-P-67b\_IN\_1           & 06:50:19 \\
-    2020-04-28 & 44.762575   & 308.85        & 2.458968e+06 & 6437.0 & 17.107363 & HAT-P-67b\_IN\_1           & 06:56:00 \\
-    2020-04-28 & 44.762322   & 308.85        & 2.458968e+06 & 6437.0 & 17.107427 & HAT-P-67b\_IN\_1           & 07:01:41 \\
-    2020-04-28 & 44.762290   & 308.85        & 2.458968e+06 & 6437.0 & 17.107485 & HAT-P-67b\_IN\_1           & 07:07:22 \\
-    2020-04-28 & 44.762212   & 308.85        & 2.458968e+06 & 6437.0 & 17.107541 & HAT-P-67b\_IN\_1           & 07:13:03 \\
-    2020-04-28 & 44.762057   & 308.85        & 2.458968e+06 & 6437.0 & 17.107608 & HAT-P-67b\_IN\_1           & 07:18:44 \\
-    2020-04-28 & 44.762013   & 308.85        & 2.458968e+06 & 6437.0 & 17.107669 & HAT-P-67b\_IN\_1           & 07:24:26 \\
-    2020-05-22 & 44.765938   & 308.85        & 2.458992e+06 & 6587.0 & 17.106844 & HAT-P-67b\_IN\_2           & 04:41:05 \\
-    2020-05-22 & 44.765694   & 308.85        & 2.458992e+06 & 6587.0 & 17.106916 & HAT-P-67b\_IN\_2           & 04:46:46 \\
-    2020-05-22 & 44.765448   & 308.85        & 2.458992e+06 & 6587.0 & 17.106988 & HAT-P-67b\_IN\_2           & 04:52:27 \\
-    2020-05-22 & 44.765338   & 308.85        & 2.458992e+06 & 6587.0 & 17.107057 & HAT-P-67b\_IN\_2           & 04:58:09 \\
-    2020-05-22 & 44.765232   & 308.85        & 2.458992e+06 & 6587.0 & 17.107116 & HAT-P-67b\_IN\_2           & 05:03:50 \\
-    2020-05-22 & 44.764945   & 308.85        & 2.458992e+06 & 6587.0 & 17.107198 & HAT-P-67b\_IN\_2           & 05:09:31 \\
-    2020-05-22 & 44.764912   & 308.85        & 2.458992e+06 & 6587.0 & 17.107269 & HAT-P-67b\_IN\_2           & 05:15:12 \\
-    2020-05-22 & 44.764767   & 308.85        & 2.458992e+06 & 6587.0 & 17.107347 & HAT-P-67b\_IN\_2           & 05:20:53 \\
-    2020-05-22 & 44.764488   & 308.85        & 2.458992e+06 & 6587.0 & 17.107408 & HAT-P-67b\_IN\_2           & 05:26:34 \\
-    2020-05-22 & 44.764364   & 308.85        & 2.458992e+06 & 6587.0 & 17.107473 & HAT-P-67b\_IN\_2           & 05:32:15 \\
-    2020-05-22 & 44.764240   & 308.85        & 2.458992e+06 & 6587.0 & 17.107525 & HAT-P-67b\_IN\_2           & 05:37:57 \\
-    2020-05-22 & 44.764128   & 308.85        & 2.458992e+06 & 6587.0 & 17.107601 & HAT-P-67b\_IN\_2           & 05:43:38 \\
-    2020-05-22 & 44.764087   & 308.85        & 2.458992e+06 & 6587.0 & 17.107653 & HAT-P-67b\_IN\_2           & 05:49:19 \\
-    2020-05-22 & 44.763816   & 308.85        & 2.458992e+06 & 6587.0 & 17.107728 & HAT-P-67b\_IN\_2           & 05:55:00 \\
-    2020-06-15 & 44.768164   & 308.85        & 2.459016e+06 & 6938.0 & 17.106909 & HAT-P-67b\_IN\_3           & 03:13:19 \\
-    2020-06-15 & 44.767792   & 308.85        & 2.459016e+06 & 6938.0 & 17.106979 & HAT-P-67b\_IN\_3           & 03:19:00 \\
-    2020-06-15 & 44.767746   & 308.85        & 2.459016e+06 & 6938.0 & 17.107035 & HAT-P-67b\_IN\_3           & 03:24:41 \\
-    2020-06-15 & 44.767580   & 308.85        & 2.459016e+06 & 6938.0 & 17.107103 & HAT-P-67b\_IN\_3           & 03:30:23 \\
-    2020-06-15 & 44.767436   & 308.85        & 2.459016e+06 & 6938.0 & 17.107145 & HAT-P-67b\_IN\_3           & 03:36:04 \\
-    2020-06-15 & 44.767252   & 308.85        & 2.459016e+06 & 6938.0 & 17.107246 & HAT-P-67b\_IN\_3           & 03:41:45 \\
-    2020-06-15 & 44.767175   & 308.85        & 2.459016e+06 & 6938.0 & 17.107295 & HAT-P-67b\_IN\_3           & 03:47:26 \\
-    2020-06-15 & 44.766835   & 308.85        & 2.459016e+06 & 6938.0 & 17.107368 & HAT-P-67b\_IN\_3           & 03:53:07 \\
-    2020-06-15 & 44.766759   & 308.85        & 2.459016e+06 & 6938.0 & 17.107418 & HAT-P-67b\_IN\_3           & 03:58:48 \\
-    2020-04-27 & 44.764544   & 308.85        & 2.458967e+06 & 6436.0 & 17.106775 & HAT-P-67b\_OUT\_1\_before1 & 06:29:11 \\
-    2020-04-27 & 44.764240   & 308.85        & 2.458967e+06 & 6436.0 & 17.106827 & HAT-P-67b\_OUT\_1\_before1 & 06:35:03 \\
-    2020-04-27 & 44.764141   & 308.85        & 2.458967e+06 & 6436.0 & 17.106900 & HAT-P-67b\_OUT\_1\_before1 & 06:40:55 \\
-    2020-04-27 & 44.763873   & 308.85        & 2.458967e+06 & 6436.0 & 17.106974 & HAT-P-67b\_OUT\_1\_before1 & 06:46:47 \\
-    2020-04-29 & 44.764930   & 308.85        & 2.458969e+06 & 6438.0 & 17.106673 & HAT-P-67b\_OUT\_1\_after1  & 06:34:20 \\
-    2020-04-29 & 44.764731   & 308.85        & 2.458969e+06 & 6438.0 & 17.106749 & HAT-P-67b\_OUT\_1\_after1  & 06:40:01 \\
-    2020-04-29 & 44.764633   & 308.85        & 2.458969e+06 & 6438.0 & 17.106817 & HAT-P-67b\_OUT\_1\_after1  & 06:45:42 \\
-    2020-04-29 & 44.764531   & 308.85        & 2.458969e+06 & 6438.0 & 17.106878 & HAT-P-67b\_OUT\_1\_after1  & 06:51:23 \\
-    2020-05-20 & 44.782750   & 308.85        & 2.458990e+06 & 6599.0 & 17.107624 & HAT-P-67b\_OUT\_2\_before2 & 10:43:31 \\
-    2020-05-20 & 44.781504   & 308.85        & 2.458990e+06 & 6599.0 & 17.107668 & HAT-P-67b\_OUT\_2\_before2 & 10:49:12 \\
-    2020-05-20 & 44.780211   & 308.85        & 2.458990e+06 & 6599.0 & 17.107719 & HAT-P-67b\_OUT\_2\_before2 & 10:54:53 \\
-    2020-05-20 & 44.779210   & 308.85        & 2.458990e+06 & 6599.0 & 17.107778 & HAT-P-67b\_OUT\_2\_before2 & 11:00:34 \\
-    2020-05-21 & 44.782995   & 308.85        & 2.458991e+06 & 6588.0 & 17.107695 & HAT-P-67b\_OUT\_2\_before1 & 10:23:05 \\
-    2020-05-21 & 44.781573   & 308.85        & 2.458991e+06 & 6588.0 & 17.107731 & HAT-P-67b\_OUT\_2\_before1 & 10:28:46 \\
-    2020-05-21 & 44.780368   & 308.85        & 2.458991e+06 & 6588.0 & 17.107773 & HAT-P-67b\_OUT\_2\_before1 & 10:34:28 \\
-    2020-05-21 & 44.779170   & 308.85        & 2.458991e+06 & 6588.0 & 17.107810 & HAT-P-67b\_OUT\_2\_before1 & 10:40:09 \\
-    2020-05-23 & 44.783203   & 308.85        & 2.458993e+06 & 6589.0 & 17.107654 & HAT-P-67b\_OUT\_2\_after1  & 10:16:00 \\
-    2020-05-23 & 44.781895   & 308.85        & 2.458993e+06 & 6589.0 & 17.107688 & HAT-P-67b\_OUT\_2\_after1  & 10:21:41 \\
-    2020-05-23 & 44.780749   & 308.85        & 2.458993e+06 & 6589.0 & 17.107718 & HAT-P-67b\_OUT\_2\_after1  & 10:27:22 \\
-    2020-05-23 & 44.779639   & 308.85        & 2.458993e+06 & 6589.0 & 17.107763 & HAT-P-67b\_OUT\_2\_after1  & 10:33:04 \\
-    2020-05-24 & 44.782834   & 308.85        & 2.458994e+06 & 6600.0 & 17.107668 & HAT-P-67b\_OUT\_2\_after2  & 10:22:14 \\
-    2020-05-24 & 44.781654   & 308.85        & 2.458994e+06 & 6600.0 & 17.107708 & HAT-P-67b\_OUT\_2\_after2  & 10:27:55 \\
-    2020-05-24 & 44.780276   & 308.85        & 2.458994e+06 & 6600.0 & 17.107744 & HAT-P-67b\_OUT\_2\_after2  & 10:33:36 \\
-    2020-05-24 & 44.779039   & 308.85        & 2.458994e+06 & 6600.0 & 17.107789 & HAT-P-67b\_OUT\_2\_after2  & 10:39:17 \\
-    2020-06-13 & 44.785061   & 308.85        & 2.459014e+06 & 6941.0 & 17.107689 & HAT-P-67b\_OUT\_3\_before2 & 09:13:57 \\
-    2020-06-13 & 44.783754   & 308.85        & 2.459014e+06 & 6941.0 & 17.107743 & HAT-P-67b\_OUT\_3\_before2 & 09:19:38 \\
-    2020-06-13 & 44.782668   & 308.85        & 2.459014e+06 & 6941.0 & 17.107795 & HAT-P-67b\_OUT\_3\_before2 & 09:25:19 \\
-    2020-06-14 & 44.785228   & 308.85        & 2.459015e+06 & 6939.0 & 17.107679 & HAT-P-67b\_OUT\_3\_before1 & 09:08:28 \\
-    2020-06-14 & 44.783951   & 308.85        & 2.459015e+06 & 6939.0 & 17.107713 & HAT-P-67b\_OUT\_3\_before1 & 09:14:09 \\
-    2020-06-14 & 44.782721   & 308.85        & 2.459015e+06 & 6939.0 & 17.107767 & HAT-P-67b\_OUT\_3\_before1 & 09:19:50 \\
-    2020-06-14 & 44.781659   & 308.85        & 2.459015e+06 & 6939.0 & 17.107823 & HAT-P-67b\_OUT\_3\_before1 & 09:25:32 \\
-    2020-06-15 & 44.783524   & 308.85        & 2.459016e+06 & 6943.0 & 17.107765 & HAT-P-67b\_OUT\_same3      & 08:59:57 \\
-    2020-06-15 & 44.782226   & 308.85        & 2.459016e+06 & 6943.0 & 17.107803 & HAT-P-67b\_OUT\_same3      & 09:05:39 \\
-    2020-06-15 & 44.780921   & 308.85        & 2.459016e+06 & 6943.0 & 17.107841 & HAT-P-67b\_OUT\_same3      & 09:11:20 \\
-    2020-06-15 & 44.779720   & 308.85        & 2.459016e+06 & 6943.0 & 17.107889 & HAT-P-67b\_OUT\_same3      & 09:17:01 \\
-    2020-06-15 & 44.778571   & 308.85        & 2.459016e+06 & 6943.0 & 17.107938 & HAT-P-67b\_OUT\_same3      & 09:22:42 \\
-    2020-06-15 & 44.777286   & 308.85        & 2.459016e+06 & 6943.0 & 17.108007 & HAT-P-67b\_OUT\_same3      & 09:28:23 \\
-    2020-06-15 & 44.776196   & 308.85        & 2.459016e+06 & 6943.0 & 17.108044 & HAT-P-67b\_OUT\_same3      & 09:34:04 \\
-    2020-06-15 & 44.774972   & 308.85        & 2.459016e+06 & 6943.0 & 17.108092 & HAT-P-67b\_OUT\_same3      & 09:39:45 \\
-    2020-06-15 & 44.773796   & 308.85        & 2.459016e+06 & 6943.0 & 17.108157 & HAT-P-67b\_OUT\_same3      & 09:45:26 \\
-    2020-06-16 & 44.785595   & 308.85        & 2.459017e+06 & 6940.0 & 17.107685 & HAT-P-67b\_OUT\_3\_after1  & 08:51:26 \\
-    2020-06-16 & 44.784378   & 308.85        & 2.459017e+06 & 6940.0 & 17.107727 & HAT-P-67b\_OUT\_3\_after1  & 08:57:07 \\
-    2020-06-16 & 44.783087   & 308.85        & 2.459017e+06 & 6940.0 & 17.107751 & HAT-P-67b\_OUT\_3\_after1  & 09:02:49 \\
-    2020-06-16 & 44.781929   & 308.85        & 2.459017e+06 & 6940.0 & 17.107796 & HAT-P-67b\_OUT\_3\_after1  & 09:08:30 \\
-    2020-06-18 & 44.785281   & 308.85        & 2.459019e+06 & 6942.0 & 17.107699 & HAT-P-67b\_OUT\_3\_after2  & 08:58:34 \\
-    2020-06-18 & 44.784069   & 308.85        & 2.459019e+06 & 6942.0 & 17.107753 & HAT-P-67b\_OUT\_3\_after2  & 09:04:15 \\
-    2020-06-18 & 44.782920   & 308.85        & 2.459019e+06 & 6942.0 & 17.107820 & HAT-P-67b\_OUT\_3\_after2  & 09:09:56 \\
-    2020-06-18 & 44.781739   & 308.85        & 2.459019e+06 & 6942.0 & 17.107881 & HAT-P-67b\_OUT\_3\_after2  & 09:15:37 \\
-    \bottomrule
-\end{tabular}
+\input{tables/ew_table.tex}
 

### 2022-05-03 paper/paper1/ms.tex
add some software references
latex formatting tiny

@@
 
-\subsection{Pre-processing with \texttt{muler}}
+\subsection{Pre-processing with \texttt{muler} }
 
@@
 \begin{acknowledgements}
-    This research has made use of NASA’s Astrophysics Data System.
+    This research has made use of NASA's Astrophysics Data System.
 \end{acknowledgements}
 
-\facilities{Smith (IGRINS), Gaia, ASAS}
+\facilities{HET (HPF), TESS, ASAS}
 
-\software{  pandas \citep{mckinney10},
-    emcee \citep{foreman13},
-    matplotlib \citep{hunter07},
-    numpy \citep{2020NumPy-Array},
-    scipy \citep{2020SciPy-NMeth},
-    ipython \citep{perez07},
-    seaborn \citep{waskom14}}
+\software{  \texttt{pandas} \citep{mckinney10},
+    \texttt{emcee} \citep{foreman13},
+    \texttt{matplotlib} \citep{hunter07},
+    \texttt{numpy} \citep{2020NumPy-Array},
+    \texttt{scipy} \citep{2020SciPy-NMeth},
+    \texttt{ipython} \citep{perez07},
+    \texttt{seaborn} \citep{waskom14},
+    \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A},
+    \texttt{muler} (Gully-Santiago et al., submitted),
+    \texttt{telfit} \citep{2014AJ....148...53G},
+    \texttt{jupyter} \citep{Kluyver2016jupyter}}
 

### 2022-05-03 paper/paper1/ms.tex

@@
 \section{Analysis}
+
 Ideally we seek the pixel-to-pixel substructured spectrum of the helium exosphere, corrected for all the conceivable instrumental, telluric, and stellar contamination artifacts.
@@
 
-\subsection{Pre-processing with \texttt{muler} }
+\subsection{HPF analysis with \texttt{muler} }
 
@@
 The sky-subtraction, telluric masking, barycentric correction, and all of our other standard pre-processing steps are implemented in a new open-source Python interface \texttt{muler}\footnote{\url{https://github.com/OttoStruve/muler/}} (Gully-Santiago \emph{et al.}, submitted).
+
+\authorcomment1{Add overplots of He and Ca II.}
 
@@
 \subsection{TESS Light Curve}
+
+\subsubsection{Stellar rotation rate from periodogram analysis}
+
 We observed the HAT-P-67 system using data from TESS Sector 24 taken from April 16th, 2020 to May 13th, 2020 with an exposure time of 1800 seconds.
@@
 The resulting periodogram of just the stellar variation described a rotational period of 5.417 days is shown in Figure \ref{fig:stellar_periodogram}.
+
+\subsubsection{Revised exoplanet parameters with exoplanet framework}
+\authorcomment1{Todo: Figure of TESS Transit}
 
@@
 
-\section{Analysis}
 \subsection{HPF MCMC}
@@
 \subsection{Contemporaneous Stellar Activity Quantification}
-\subsection{Equivalent Width vs Phase}
+
+\input{tables/ew_table.tex}
+
+\section{Results}
+\subsection{Detection of Helium with Orbital Phase}
 \begin{figure}
@@
 \end{figure}
-
-\input{tables/ew_table.tex}
-
-\subsection{Calculations}
-Using the contemporaneous TESS lightcurve, we notice that there is a 0.2\% flux variation.
-Assuming that this increase in flux is due to a hot spot with a contrast of 200\%, the hot spot must have a radius that is 12.49 times that of the radius of the Earth.
-Assuming that the mass loss rate of the planet is its mass over 10 billion years, we can assume that this hot spot is not caused by in falling mass from the planetary envelope as the mass is not enough to cause a 0.2\% modulation in the flux.
-
-We can also assume that the system is tidally locked.
-
-\section{Results}
-\subsection{Is there a difference in equivalent width in transit vs out?}
 We can see that there is indeed a helium signature that arises when the planet is in transit with its host star.
@@
 While cool dwarfs generate high irradiation in the ultraviolet and stellar winds, the sub-giant category
+\subsection{Gas Motion Relative to Planet}
+\subsection{Parker Winds Model}
+\subsubsection{p-winds model failure}
+\subsection{Geometry of the Escaping Exosphere}
+We can depict the transit of HAT-P-67b from the orbital phase versus equivalent width plot.
+The plot exhibits helium absorption occurring before the planet is in-transit.
+We can attribute this shallow increase in the equivalent width to the shape of the helium exosphere.
+Because the absorption gradually increases, we created a leading tail that begins transit 2 days before the planet does.
+As a result, we mold the shape of the helium exosphere to mimic the irregular absorption with constraints on the velocity and length
 
 \section{Discussion}
+\subsection{Hot Spot Scenario}
+Using the contemporaneous TESS lightcurve, we notice that there is a 0.2\% flux variation.
+Assuming that this increase in flux is due to a hot spot with a contrast of 200\%, the hot spot must have a radius that is 12.49 times that of the radius of the Earth.
+Assuming that the mass loss rate of the planet is its mass over 10 billion years, we can assume that this hot spot is not caused by in falling mass from the planetary envelope as the mass is not enough to cause a 0.2\% modulation in the flux.
 
+\subsection{Tidal Locking Calculation}
+From section 3.3.1, we determined the rotational period of the star from contemporaneous TESS data. Given the orbital period of the planet, we concluded that the system is tidally locked.
+
+\subsection{Mass Loss Rate}
+Parker wind models, such as those implemented in the Python tool p-winds, are incapable of accurately measuring mass loss rates for systems as extreme as HAT-P-67.
+Instead, we must constrain the mass loss rate to the mass of the planet over the course of the age of the universe.
+The resulting value is $2.045*10^{12}$ g/s.
+
+The first scenario is where the mass from the exosphere falls onto the surface of the star.
+The TESS lightkurve for this system exhibits a reoccurring 0.2\% increase in the flux that is not attributable to the planet’s transit.
+Assuming that this modulation is due to a hot spot on the stellar surface, we conclude that gravitational potential energy alone is not sufficient to increase the flux by such an amount.
+Larger mass loss rates could cause brighter hotspots, but this would cause the planet to disappear entirely over its lifetime, which is unphysical.
+
+\subsection{Confinement to Stellar Wind}
+\subsection{Limits of Stellar Activity Metrics}
+\authorcomment1{3D Heat Map Interpolation figure that mimics MacLeod paper}
+\subsection{Comparison to Other Systems}
+\authorcomment1{Parameter plot with HAT-P-67 system with others from exoplanet archive}
 \section{Conclusions}

### 2022-11-07 paper/paper1/ms.tex
Some uncommited changes to the paper text

@@
-\documentclass[modern]{aastex631}
+\documentclass[twocolumn]{aastex631}
 \bibliographystyle{aasjournal}
@@
 
-A total of \censor{xx} systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
+At least 8 systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
 
-We specified our observations on the HAT-P-67 system due to its unique rotational period.
+Here we present a study of the exosphere of HAT-P-67b.
 HAT-P-67 is a binary system of an F type sub-giant and a much cooler M2 star with the Saturn-sized planet HAT-P-67b.
-An extremely low density object, HAT-P-67b loses its atmosphere rather rapidly for transiting an evolved host star.
+HAT-P-67b stands out for a few reasons.
+It has a relatively low surface gravity, which could make it amenable to rapid atmospheric mass loss, all else being equal.
+It orbits an evolved star, which means it could have changed its instellation recently as the star's size and radiaiton properties have changed.
+The star appears close to the star, making it conceivable that star-planet interactions could be at play.
+These and other reasons make HAT-P-67b a unique laboratory for measuring the properties of exospheres and their interactions with their host stars.
 
@@
 
-The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-schedule 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R, 2007PASP..119..556S} operates in the near-IR from 8100-12800 \AA spanning the \textit{z}, \textit{Y}, and \textit{J} bands.
-We observed HAT-P-67b with HPF in-transit on 2020 April 28, 2020 May 22, and 2020 June 15 and out-of-transit on a total of \censor{xx} other nights.
+The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R, 2007PASP..119..556S} operates in the near-IR from $8100-12800~\mathrm{\AA}\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands.
+We observed HAT-P-67b with HPF in-transit on 2020 April 28, 2020 May 22, and 2020 June 15 and out-of-transit on a total of \censorbox{xx} other nights.
 
-\authorcomment1{We may want to put a observation log here, grouped by night.}
-% \input{tables/observation_flat_table.tex}
+\input{tables/observations_flat_table.tex}
 

### 2022-11-09 paper/paper1/ms.tex
one word
Add table of orbital properties, populated with Zhou et al. 2017 column at the moment

@@
 %\input{mgs_setup}
+
+%% General
+\newcommand{\msini}{\ensuremath{m \sin i}}
+\newcommand{\mplsini}{\ensuremath{\mpl\sin i}}
+\newcommand{\teff}{\ensuremath{T_{\rm eff}}}
+\newcommand{\logg}{\ensuremath{\log{g}}}
+\newcommand{\vsini}{\ensuremath{v \sin{I_\star}}}
+\newcommand{\feh}{\ensuremath{\rm [Fe/H]}}
+\newcommand{\logl}{\ensuremath{\log{L}}}
+\newcommand{\vmac}{\ensuremath{v_{\rm mac}}}
+\newcommand{\vmic}{\ensuremath{v_{\rm mic}}}
+% Activity index R'_HK
+\newcommand{\rhk}{\ensuremath{R^{\prime}_{HK}}}
+% log of R'_HK
+\newcommand{\logrhk}{\ensuremath{\log\rhk}}
+% S average value
+\newcommand{\Savg}{\ensuremath{\langle S\rangle}}
+
+%% ---------------------------------------------------------------------
+%% Solar quantities 
+\newcommand{\rsun}{\ensuremath{R_\sun}}
+\newcommand{\msun}{\ensuremath{M_\sun}}
+\newcommand{\lsun}{\ensuremath{L_\sun}}
+\newcommand{\loglsun}{\ensuremath{\log{L_\sun}}}
+\newcommand{\teffsun}{\ensuremath{T_{eff,\sun}}}
+\newcommand{\rhosun}{\ensuremath{\rho_\sun}}
+\newcommand{\loggsun}{\ensuremath{\log{g_{\sun}}}}
+
+%% ---------------------------------------------------------------------
+%% Stellar quantities 
+\newcommand{\rstar}{\ensuremath{R_\star}}
+\newcommand{\mstar}{\ensuremath{M_\star}}
+\newcommand{\lstar}{\ensuremath{L_\star}}
+\newcommand{\astar}{\ensuremath{a_\star}}
+\newcommand{\loglstar}{\ensuremath{\log{L_\star}}}
+\newcommand{\teffstar}{\ensuremath{T_{\rm eff\star}}}
+\newcommand{\rhostar}{\ensuremath{\rho_\star}}
+\newcommand{\loggstar}{\ensuremath{\log{g_{\star}}}}
+
+%% ---------------------------------------------------------------------
+%% Earth
+\newcommand{\rearth}{\ensuremath{R_\earth}}
+\newcommand{\mearth}{\ensuremath{M_\earth}}
+\newcommand{\learth}{\ensuremath{L_\earth}}
+\newcommand{\teffearth}{\ensuremath{T_{\rm eff,\earth}}}
+\newcommand{\rhoearth}{\ensuremath{\rho_\earth}}
+
+%% ---------------------------------------------------------------------
+%% Planetary
+\newcommand{\rpl}{\ensuremath{R_{p}}}
+\newcommand{\mpl}{\ensuremath{M_{p}}}
+\newcommand{\lpl}{\ensuremath{L_{p}}}
+\newcommand{\teffpl}{\ensuremath{T_{\rm eff,{p}}}}
+\newcommand{\rhopl}{\ensuremath{\rho_{p}}}
+\newcommand{\ipl}{\ensuremath{i_{p}}}
+\newcommand{\epl}{\ensuremath{e_{p}}}
+\newcommand{\gpl}{\ensuremath{g_{p}}}
+\newcommand{\loggpl}{\ensuremath{\log g_{p}}}
+
+\newcommand{\arstar}{\ensuremath{a/\rstar}}
+\newcommand{\zrstar}{\ensuremath{\zeta/\rstar}}
+
+%% ---------------------------------------------------------------------
+%% Jupiter
+\newcommand{\rjup}{\ensuremath{R_{\rm J}}}
+\newcommand{\mjup}{\ensuremath{M_{\rm J}}}
+\newcommand{\ljup}{\ensuremath{L_{\rm J}}}
+\newcommand{\teffjup}{\ensuremath{T_{eff,{\rm J}}}}
+\newcommand{\rhojup}{\ensuremath{\rho_{\rm J}}}
+\newcommand{\gjup}{\ensuremath{\g_{\rm J}}}
+
+\newcommand{\rjuplong}{\ensuremath{R_{\rm Jup}}}
+\newcommand{\mjuplong}{\ensuremath{M_{\rm Jup}}}
+\newcommand{\ljuplong}{\ensuremath{L_{\rm Jup}}}
+\newcommand{\teffjuplong}{\ensuremath{T_{eff,{\rm Jup}}}}
+\newcommand{\rhojuplong}{\ensuremath{\rho_{\rm Jup}}}
+\newcommand{\gjuplong}{\ensuremath{\g_{\rm Jup}}}
 
@@
 
-Exoplanets must possess a dynamic range of atmospheric properties far beyond what we have seen in our own Solar System.
+Exoplanets possess a dynamic range of atmospheric properties far beyond what we have seen in our own Solar System.
 Extreme radiation effects, atmospheric erosion, and unexpected chemistry must exist, but collecting examples of these phenomena remains at the edge of the possible today.
@@
 
-The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R, 2007PASP..119..556S} operates in the near-IR from $8100-12800~\mathrm{\AA}\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands.
+The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R, 2007PASP..119..556S} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands.
 We observed HAT-P-67b with HPF in-transit on 2020 April 28, 2020 May 22, and 2020 June 15 and out-of-transit on a total of \censorbox{xx} other nights.
@@
 \subsubsection{Revised exoplanet parameters with exoplanet framework}
+
+\begin{deluxetable*}{lrrrh}
+    \tablewidth{0pc}
+    \tabletypesize{\scriptsize}
+    \tablecaption{
+        Revised orbital and planetary parameters
+        \label{tabOrbit}
+    }
+    \tablehead{
+        \colhead{Parameter}   &
+        \colhead{Zhou et al. 2017} &
+        \colhead{Ivshina \& Winn 2022} &
+        \colhead{This Work} &
+        \nocolhead{Alternate}
+    }
+    \startdata
+    %%
+    ~~~$P$ (days)             \dotfill    & $4.8101025_{-0.00000033}^{+0.00000043}$ & x & y & z \\
+    ~~~$T_c$ (${\rm BJD}$)  \dotfill    & $2455961.38467_{-0.00064}^{+0.00076}$ & x & y & z \\
+    ~~~$T_{14}$ (days)  \dotfill    & $0.2912 \pm 0.0019$ & x & y & z \\
+    ~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ & x & y & z \\
+    ~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ & x & y & z \\
+    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ & x & y & z \\
+    ~~~$b \equiv a \cos i/\rstar$
+    \dotfill    & $0.12_{-0.08}^{+0.12}$ & x & y & z \\
+    ~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ & x & y & z \\
+    \enddata
+\end{deluxetable*}
+
 \authorcomment1{Todo: Figure of TESS Transit}

### 2022-11-14 paper/paper1/ms.tex
Orbital parameters based on TESS data
Checkout out some archival datasets--- mostly red herrings
Add a paragraph about Dasch non-constraints

@@
 Here we present a study of the exosphere of HAT-P-67b.
-HAT-P-67 is a binary system of an F type sub-giant and a much cooler M2 star with the Saturn-sized planet HAT-P-67b.
+HAT-P-67 is an F type sub-giant with the Saturn-sized planet HAT-P-67b.
 HAT-P-67b stands out for a few reasons.
-It has a relatively low surface gravity, which could make it amenable to rapid atmospheric mass loss, all else being equal.
-It orbits an evolved star, which means it could have changed its instellation recently as the star's size and radiaiton properties have changed.
+It has a relatively low surface gravity, which could make it amenable to rapid atmospheric mass loss.
+It orbits an evolved star, which means its instellation may have increased as the star's size has grown.
 The star appears close to the star, making it conceivable that star-planet interactions could be at play.
 These and other reasons make HAT-P-67b a unique laboratory for measuring the properties of exospheres and their interactions with their host stars.
+The system appears to consist of a binary with an M dwarf companion HAT-P-67B separated by $9\farcs0$.
 
@@
 
+\subsection{DASCH}
+We searched for observations of HAT-P-67 in other archives.
+It appears in the Harvard Plate Archive, with 5809 measurements digitized through DASCH \censorbox{citation}, spanning over 120 years of coarse photometric monitoring.
+In principle these datasets could inform long-term variability trends such as stellar cycles.
+In practice the 0.15 magnitude jitter appears too coarse to perceive any genuine astrophysical variability, with no conspicuous trend seen.
+We can therefore place a relatively mild constraint that the star is stable at the $30\%$ level over periods of tens of years.
+
 \section{Analysis}
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{../../figures/Gaia_HAT_P_67_AB.png}
+    \caption{HR Diagram of F star HAT-P-67A with its assumed M-dwarf main sequence companion HAT-P-67B.
+The density of stars comes from the \emph{Kepler} prime field estimated by \citet{2020AJ....160..108B} using \emph{Gaia DR2}.}
+    \label{fig:gaiaHRD}
+\end{figure}
 
@@
     %%
-    ~~~$P$ (days)             \dotfill    & $4.8101025_{-0.00000033}^{+0.00000043}$ & x & y & z \\
-    ~~~$T_c$ (${\rm BJD}$)  \dotfill    & $2455961.38467_{-0.00064}^{+0.00076}$ & x & y & z \\
-    ~~~$T_{14}$ (days)  \dotfill    & $0.2912 \pm 0.0019$ & x & y & z \\
+    ~~~$P$ (days)             \dotfill    & $4.8101025_{-3.3\times 10^{-7}}^{+4.3\times 10^{-7}}$ & 4.8101046$\pm1.7\times10^{-6}$ & 4.81011 & z \\
+    ~~~$T_c$ (${\rm BTJD}$)  \dotfill    & $-1038.61533_{-0.00064}^{+0.00076}$ & 1958.08059$\pm$0.00032 & 1958.07933 & z \\
+    ~~~$T_{14}$ (hours)  \dotfill    & $6.9888 \pm 0.046$ & x & 7.0636 & z \\
     ~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ & x & y & z \\
     ~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ & x & y & z \\
-    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ & x & y & z \\
+    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ & x & 0.08231 & z \\
     ~~~$b \equiv a \cos i/\rstar$
-    \dotfill    & $0.12_{-0.08}^{+0.12}$ & x & y & z \\
+    \dotfill    & $0.12_{-0.08}^{+0.12}$ & x & 0.45616 & z \\
     ~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ & x & y & z \\

### 2022-11-14 paper/paper1/ms.tex
Add some text on other archival data sources

@@
 We can therefore place a relatively mild constraint that the star is stable at the $30\%$ level over periods of tens of years.
+
+\subsection{Gaia DR3}
+HAT-P-67A has a parallax of \censorbox{x} in \emph{Gaia} DR3,
+
+\subsection{Other archives}
+We searched for observations of HAT-P-67 in public archives.
+It has one $R\sim8000$ spectrum from the Intermediate Dispersion Spectrograph on the INT, centered near 4000 $\AA$.
+It has 26 photometry points from \emph{Pan-STARRS} spread across its 5 filters.
+The other archival observations have been previously reported by \censorbox{Zhou et al.
+2017}, including Keck HIRES, Keck NIRC2, and WIYN High-Resolution Infrared Camera.
+The northern source does not appear in ESO archives, nor the Gemini Archive, and it is not publicly accessible in the Zwicky Transient Factory (ZTF) archive.
+It was not targeted by Spitzer or Hubble.
 

### 2022-11-14 paper/paper1/ms.tex
Gaia Dr3 parallaxes

@@
 \subsection{TESS Light Curve}
-HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS][]{2014SPIE.9143E..20R} in Sector 24 from April 16th, 2020 to May 13th, 2020 with a 30 minute cadence.
+HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS][]{2014SPIE.9143E..20R} in Sectors 24, 26, 51, 52, 53 with 2-minute cadence.
 
 \subsection{ASAS-SN}
-We retrieved ground-based photometry with the \emph{All-Sky Automated Survey for Supernovae} (ASAS-SN) using the Sky-Portal (\censor{xx}).
+We retrieved ground-based photometry with the \emph{All-Sky Automated Survey for Supernovae} (ASAS-SN) using the Sky-Portal \citep{shappee14,2017PASP..129j4502K}.
 
@@
 \subsection{Gaia DR3}
-HAT-P-67A has a parallax of \censorbox{x} in \emph{Gaia} DR3,
+HAT-P-67A (\emph{Gaia DR3 1358614983131339392}) has a parallax of $2.69\pm0.01$ mas in \emph{Gaia} DR3, placing it at about 372$\pm$1.4 pc, slightly farther than previously estimated by \citet{2017AJ....153..211Z} using Gaia DR1.
+Its coarse Gaia-based estimates for RV and Doppler broadening are consistent with the more precise values published in \citet{2017AJ....153..211Z}.
+Its wide companion HAT-P-67B (\emph{Gaia DR3 1358614983131339904}) \citep{2019MNRAS.490.5088M} has statistically identical parallax ($2.58\pm0.05$) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
 
@@
 It has 26 photometry points from \emph{Pan-STARRS} spread across its 5 filters.
-The other archival observations have been previously reported by \censorbox{Zhou et al.
-2017}, including Keck HIRES, Keck NIRC2, and WIYN High-Resolution Infrared Camera.
+The other archival observations have been previously reported by \citet{2017AJ....153..211Z}, including Keck HIRES, Keck NIRC2, and WIYN High-Resolution Infrared Camera.
 The northern source does not appear in ESO archives, nor the Gemini Archive, and it is not publicly accessible in the Zwicky Transient Factory (ZTF) archive.

### 2022-11-14 paper/paper1/ms.tex
TESS 2-minute cadence has about 1 ppt RMS

@@
 \subsection{TESS Light Curve}
-HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS][]{2014SPIE.9143E..20R} in Sectors 24, 26, 51, 52, 53 with 2-minute cadence.
+HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS][]{2014SPIE.9143E..20R} in Sectors 24, 26, 51, 52, 53 with 2-minute cadence, and in Sector 25 with 30-minute (FFI) cadence.
 
@@
 We experimented with a range of pre-processing and analysis techniques to quantify the accuracy and precision of our HPF spectra.
+
+\subsection{TESS Light Curve}
+
+\subsubsection{Revised exoplanet parameters with exoplanet framework}
+We assembled a composite lightcurve from TESS Sectors 24, 26, 51, 52, 53, which were reduced with the default SPOC pipeline \citep{2020RNAAS...4..201C}.
+These TESS data exhibit a native RMS scatter of better than 1 part-per-thousand (ppt).
+We fit a Keplerian orbit model to the TESS lightcurve using the \texttt{exoplanet} framework \citep{exoplanet:joss}.
+
+\subsubsection{Stellar rotation rate from periodogram analysis}
+
+Using the \texttt{lightkurve} package, we attempted to phase fold our exoplanet transit plot to identify the stellar rotation signal and the exoplanet's transit signal.
+At first glance, the stellar flux decreases by about 0.2\% and the exoplanet transit signal decreases by about 0.7\%.
+In order to analyze the stellar rotation period, we must mask the planetary transit signal.
+By folding the normalized lightcurve with a given planetary orbital period of 4.810 days, we omitted the planetary transit signal.
+We then created a periodogram of just the stellar signal and arrived at an estimate of several parameters for HAT-P-67b: the planetary period is 4.809 days, the original transit time was 1958.082 BTJD, and the planetary duration was 0.25 days.
+We then created a cadence mask using the Box Least Squares parameters.
+The resulting periodogram of just the stellar variation described a rotational period of 5.417 days is shown in Figure \ref{fig:stellar_periodogram}.
+
+\begin{deluxetable*}{lrrrh}
+    \tablewidth{0pc}
+    \tabletypesize{\scriptsize}
+    \tablecaption{
+        Revised orbital and planetary parameters
+        \label{tabOrbit}
+    }
+    \tablehead{
+        \colhead{Parameter}   &
+        \colhead{Zhou et al. 2017} &
+        \colhead{Ivshina \& Winn 2022} &
+        \colhead{This Work} &
+        \nocolhead{Alternate}
+    }
+    \startdata
+    %%
+    ~~~$P$ (days)             \dotfill    & $4.8101025_{-3.3\times 10^{-7}}^{+4.3\times 10^{-7}}$ & 4.8101046$\pm1.7\times10^{-6}$ & 4.81011 & z \\
+    ~~~$T_c$ (${\rm BTJD}$)  \dotfill    & $-1038.61533_{-0.00064}^{+0.00076}$ & 1958.08059$\pm$0.00032 & 1958.07933 & z \\
+    ~~~$T_{14}$ (hours)  \dotfill    & $6.9888 \pm 0.046$ & x & 7.0636 & z \\
+    ~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ & x & y & z \\
+    ~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ & x & y & z \\
+    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ & x & 0.08231 & z \\
+    ~~~$b \equiv a \cos i/\rstar$
+    \dotfill    & $0.12_{-0.08}^{+0.12}$ & x & 0.45616 & z \\
+    ~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ & x & y & z \\
+    \enddata
+\end{deluxetable*}
+
+\authorcomment1{Todo: Figure of TESS Transit}
 
@@
 \end{deluxetable*}
-
-\subsection{TESS Light Curve}
-
-\subsubsection{Stellar rotation rate from periodogram analysis}
-
-We observed the HAT-P-67 system using data from TESS Sector 24 taken from April 16th, 2020 to May 13th, 2020 with an exposure time of 1800 seconds.
-Using the \texttt{lightkurve} package, we attempted to phase fold our exoplanet transit plot to identify the stellar rotation signal and the exoplanet's transit signal.
-At first glance, the stellar flux decreases by about 0.2\% and the exoplanet transit signal decreases by about 0.7\%.
-In order to analyze the stellar rotation period, we must mask the planetary transit signal.
-By folding the normalized lightcurve with a given planetary orbital period of 4.810 days, we omitted the planetary transit signal.
-We then created a periodogram of just the stellar signal and arrived at an estimate of several parameters for HAT-P-67b: the planetary period is 4.809 days, the original transit time was 1958.082 BTJD, and the planetary duration was 0.25 days.
-We then created a cadence mask using the Box Least Squares parameters.
-The resulting periodogram of just the stellar variation described a rotational period of 5.417 days is shown in Figure \ref{fig:stellar_periodogram}.
-
-\subsubsection{Revised exoplanet parameters with exoplanet framework}
-
-\begin{deluxetable*}{lrrrh}
-    \tablewidth{0pc}
-    \tabletypesize{\scriptsize}
-    \tablecaption{
-        Revised orbital and planetary parameters
-        \label{tabOrbit}
-    }
-    \tablehead{
-        \colhead{Parameter}   &
-        \colhead{Zhou et al. 2017} &
-        \colhead{Ivshina \& Winn 2022} &
-        \colhead{This Work} &
-        \nocolhead{Alternate}
-    }
-    \startdata
-    %%
-    ~~~$P$ (days)             \dotfill    & $4.8101025_{-3.3\times 10^{-7}}^{+4.3\times 10^{-7}}$ & 4.8101046$\pm1.7\times10^{-6}$ & 4.81011 & z \\
-    ~~~$T_c$ (${\rm BTJD}$)  \dotfill    & $-1038.61533_{-0.00064}^{+0.00076}$ & 1958.08059$\pm$0.00032 & 1958.07933 & z \\
-    ~~~$T_{14}$ (hours)  \dotfill    & $6.9888 \pm 0.046$ & x & 7.0636 & z \\
-    ~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ & x & y & z \\
-    ~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ & x & y & z \\
-    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ & x & 0.08231 & z \\
-    ~~~$b \equiv a \cos i/\rstar$
-    \dotfill    & $0.12_{-0.08}^{+0.12}$ & x & 0.45616 & z \\
-    ~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ & x & y & z \\
-    \enddata
-\end{deluxetable*}
-
-\authorcomment1{Todo: Figure of TESS Transit}
 
@@
     \texttt{telfit} \citep{2014AJ....148...53G},
-    \texttt{jupyter} \citep{Kluyver2016jupyter}}
+    \texttt{exoplanet} \citep{exoplanet:joss},
+    \texttt{jupyter} \citep{Kluyver2016jupyter},
+}
 

### 2022-11-14 paper/paper1/ms.tex
First pass orbital constraints from TESS, we should fit circular orbit and do MCMC

@@
 \subsubsection{Revised exoplanet parameters with exoplanet framework}
-We assembled a composite lightcurve from TESS Sectors 24, 26, 51, 52, 53, which were reduced with the default SPOC pipeline \citep{2020RNAAS...4..201C}.
-These TESS data exhibit a native RMS scatter of better than 1 part-per-thousand (ppt).
+We assembled a composite lightcurve by stitching TESS Sectors 24, 26, 51, 52, 53, which were reduced with the default SPOC pipeline \citep{2020RNAAS...4..201C}.
+These TESS data exhibit an RMS scatter of better than 1 part-per-thousand (ppt) at native 2-minute sampling.
 We fit a Keplerian orbit model to the TESS lightcurve using the \texttt{exoplanet} framework \citep{exoplanet:joss}.
+We obtained a best fit orbital period of $4.81011$ days, non-zero eccentricity of 0.19, an impact parameter of 0.46, planet-to-star radius of 0.0823, transit depth of 0.74\%, and $T_0$ of 1958.07933 in BTJD.
+We did not attempt MCMC sampling to quantify degeneracy among these parameters, and we suspect that the orbit is adequately modeled by a circular orbit.
 

### 2022-11-14 paper/paper1/ms.tex
Estimating Rsini

@@
 HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS][]{2014SPIE.9143E..20R} in Sectors 24, 26, 51, 52, 53 with 2-minute cadence, and in Sector 25 with 30-minute (FFI) cadence.
+The Sector 25 FFI data appeared malformed, possibly due to problems with pipeline CCD smear correction, and was disregarded.
 
@@
 \subsubsection{Revised exoplanet parameters with exoplanet framework}
-We assembled a composite lightcurve by stitching TESS Sectors 24, 26, 51, 52, 53, which were reduced with the default SPOC pipeline \citep{2020RNAAS...4..201C}.
+We assembled a composite lightcurve by stitching TESS Sectors 24, 26, 51, 52, 53, which were reduced with the default SPOC pipeline \citep{2020RNAAS...4..201C}, and lightly post-processed with \texttt{lightkurve} \citep{geert_barentsen_2019_2565212}.
 These TESS data exhibit an RMS scatter of better than 1 part-per-thousand (ppt) at native 2-minute sampling.
@@
 We obtained a best fit orbital period of $4.81011$ days, non-zero eccentricity of 0.19, an impact parameter of 0.46, planet-to-star radius of 0.0823, transit depth of 0.74\%, and $T_0$ of 1958.07933 in BTJD.
-We did not attempt MCMC sampling to quantify degeneracy among these parameters, and we suspect that the orbit is adequately modeled by a circular orbit.
+We did not attempt MCMC sampling to quantify degeneracy among these parameters, and we suspect that the transit is adequately modeled by a circular orbit.
+Figure \ref{fig:transit} shows the best-fit orbit overlaid on the detrended TESS lightcurve.
+Table \ref{tabOrbit} lists a previous orbit determination and solutions reported here.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/best_fit_orbit.png}
+    \caption{Best fit orbit overlaid on the composite TESS lightcurve.  The 1 ppt TESS precision improves upon the ground-based detection and refining the orbital properties and ephemerides.}
+    \label{fig:transit}
+\end{figure}
 
@@
 
-Using the \texttt{lightkurve} package, we attempted to phase fold our exoplanet transit plot to identify the stellar rotation signal and the exoplanet's transit signal.
-At first glance, the stellar flux decreases by about 0.2\% and the exoplanet transit signal decreases by about 0.7\%.
-In order to analyze the stellar rotation period, we must mask the planetary transit signal.
-By folding the normalized lightcurve with a given planetary orbital period of 4.810 days, we omitted the planetary transit signal.
-We then created a periodogram of just the stellar signal and arrived at an estimate of several parameters for HAT-P-67b: the planetary period is 4.809 days, the original transit time was 1958.082 BTJD, and the planetary duration was 0.25 days.
-We then created a cadence mask using the Box Least Squares parameters.
-The resulting periodogram of just the stellar variation described a rotational period of 5.417 days is shown in Figure \ref{fig:stellar_periodogram}.
+The TESS Sector 26 lightcurve exhibits a weak $\sim3\;$ppt peak-to-valley out-of-transit modulation on timescales comparable to the exoplanet orbit.
+TESS Sectors 51-53 do not show as conspicuous a modulation signal as does Sector 26.
+Figure \ref{fig:TESSmodulation} shows this modulation in the minimally processed TESS lightcurve.
+During the exoplanet orbit fitting, we fit the TESS lightcurve modulation with a quasiperiodic Gaussian Process (GP) model using \citep{celerite} \citep{celerite1,celerite2}.
+The GP model fit to the entire composite lightcurve yields a period of 4.68 days; when fit to individual sectors alone the periods hover around 5.9 days.
+
+If we assume the TESS modulation signal is attributable to stellar activity, we obtain a rotation period $P_\mathrm{rot}$ between 4.7 and 5.9 days.
+The reported $v\sin{i}=35.8\pm1.1$ km/s would yield an $R_\star \sin{i}$ =
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/TESS_S26_trend.png}
+    \caption{Stellar lightcurve modulation observed in TESS Sector 26.
+The stellar surface pattern speed appears to have a slightly longer period than the exoplanet orbit, causing the transit to occur earlier in the phase of the modulation upon each orbit.}
+    \label{fig:TESSmodulation}
+\end{figure}
 
@@
 \end{deluxetable*}
-
-\authorcomment1{Todo: Figure of TESS Transit}
 
@@
     \label{fig:stellar_periodogram}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/planetary_periodogram.png}
-    \caption{Periodogram of the stellar variation coupled with the planetary transit signal of the flux. }
-    \label{fig:planetary_periodogram}
 \end{figure}

### 2022-11-15 paper/paper1/ms.tex
Compute Rsini constraints

@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{../../figures/Gaia_HAT_P_67_AB.png}
+    \includegraphics[width=\linewidth]{figures/Gaia_HAT_P_67_AB.png}
     \caption{HR Diagram of F star HAT-P-67A with its assumed M-dwarf main sequence companion HAT-P-67B.
@@
 During the exoplanet orbit fitting, we fit the TESS lightcurve modulation with a quasiperiodic Gaussian Process (GP) model using \citep{celerite} \citep{celerite1,celerite2}.
-The GP model fit to the entire composite lightcurve yields a period of 4.68 days; when fit to individual sectors alone the periods hover around 5.9 days.
+The GP model fit to the entire composite lightcurve yields a period of 4.7 days; when fit to individual sectors alone the periods hover around 5.9 days.
 
-If we assume the TESS modulation signal is attributable to stellar activity, we obtain a rotation period $P_\mathrm{rot}$ between 4.7 and 5.9 days.
-The reported $v\sin{i}=35.8\pm1.1$ km/s would yield an $R_\star \sin{i}$ =
+If we attribute the TESS modulation signal to stellar activity, we obtain a rotation period $P_\mathrm{rot}$ between 4.7 and 5.9 days.
+\citet{2017AJ....153..211Z} reported a $v\sin{i}=35.8\pm1.1$ km/s, or possibly as $v\sin{i}=30\pm1.1$ km/s if macroturbulence were included.
+We obtain a geometric constraint on $2.85< R_\star \sin{i} (R_\odot) < 4.2 $.
+These constraints are consistent with  the 1-$\sigma$ range of $2.0 < R_\star (R_\odot) < 3.2$ provided in \citet{2017AJ....153..211Z} from different isochrones and orbit fits, and assuming a near-edge-on orbital inclination.
+The Gaia \emph{DR3}-derived distance is 8\% greater than the \emph{Gaia} DR1 estimate used in \citet{2017AJ....153..211Z}, which would tend to increase the radius estimate by 16\% to match the observed SED in isochrone-fitting.
+We would therefore expect an $R_\star$ range closer to $2.5-3.14 R_\odot$, where we have dropped the 1-$\sigma$ uncertainties which had included the less certain Gaia DR 1 parallax and its uncertain correction terms.
 

### 2022-11-15 paper/paper1/ms.tex

@@
 
-Ideally we seek the pixel-to-pixel substructured spectrum of the helium exosphere, corrected for all the conceivable instrumental, telluric, and stellar contamination artifacts.
-In practice, these corrections are incomplete and so some care is needed to assess the extent of contamination.
-We experimented with a range of pre-processing and analysis techniques to quantify the accuracy and precision of our HPF spectra.
-
 \subsection{TESS Light Curve}
 
-\subsubsection{Revised exoplanet parameters with exoplanet framework}
+\subsubsection{Revised exoplanet orbital parameters}
 We assembled a composite lightcurve by stitching TESS Sectors 24, 26, 51, 52, 53, which were reduced with the default SPOC pipeline \citep{2020RNAAS...4..201C}, and lightly post-processed with \texttt{lightkurve} \citep{geert_barentsen_2019_2565212}.
@@
 The TESS Sector 26 lightcurve exhibits a weak $\sim3\;$ppt peak-to-valley out-of-transit modulation on timescales comparable to the exoplanet orbit.
-TESS Sectors 51-53 do not show as conspicuous a modulation signal as does Sector 26.
+TESS Sectors 51-53 do not show as conspicuous a modulation signal.
 Figure \ref{fig:TESSmodulation} shows this modulation in the minimally processed TESS lightcurve.
@@
 \citet{2017AJ....153..211Z} reported a $v\sin{i}=35.8\pm1.1$ km/s, or possibly as $v\sin{i}=30\pm1.1$ km/s if macroturbulence were included.
-We obtain a geometric constraint on $2.85< R_\star \sin{i} (R_\odot) < 4.2 $.
-These constraints are consistent with  the 1-$\sigma$ range of $2.0 < R_\star (R_\odot) < 3.2$ provided in \citet{2017AJ....153..211Z} from different isochrones and orbit fits, and assuming a near-edge-on orbital inclination.
-The Gaia \emph{DR3}-derived distance is 8\% greater than the \emph{Gaia} DR1 estimate used in \citet{2017AJ....153..211Z}, which would tend to increase the radius estimate by 16\% to match the observed SED in isochrone-fitting.
-We would therefore expect an $R_\star$ range closer to $2.5-3.14 R_\odot$, where we have dropped the 1-$\sigma$ uncertainties which had included the less certain Gaia DR 1 parallax and its uncertain correction terms.
+We obtain a combined geometric constraint $2.85< R_\star \sin{i} (R_\odot) < 4.2 $.
+The lower end of these constraints are consistent with  the 1-$\sigma$ range of $2.0 < R_\star (R_\odot) < 3.2$ provided in \citet{2017AJ....153..211Z} from different isochrones and orbit fits, and assuming a near-edge-on orbital inclination.
+The Gaia \emph{DR3}-derived distance is 8\% greater than the \emph{Gaia} DR1 estimate used in \citet{2017AJ....153..211Z}; the revised larger distance would tend to increase the radius estimate by 16\% to match the observed SED in isochrone-fitting.
+We would therefore expect an isochrone-deived $R_\star$ range closer to $2.5-3.14 R_\odot$, where we have dropped the 1-$\sigma$ uncertainties which had included the less certain Gaia DR 1 parallax and its uncertain correction terms.
 
@@
 
-\subsection{HPF analysis with \texttt{muler} }
+\subsection{HPF analysis}
+Ideally we seek the pixel-to-pixel substructured spectrum of the helium exosphere, corrected for all the conceivable instrumental, telluric, and stellar contamination artifacts.
+In practice, these corrections are incomplete and so some care is needed to assess the extent of contamination.
+We experimented with a range of pre-processing and analysis techniques to quantify the accuracy and precision of our HPF spectra.
 
@@
 The sky fiber and target fiber have slightly different throughputs and illumination properties so the sky fiber must be scaled prior to subtraction from the target spectrum.
-On average the target fiber sees $93\%$ of the flux of the sky reference fiber, and in detail this ratio depends on wavelength.
+On average the target fiber sees $93\%$ of the flux of the sky reference fiber, and in detail this ratio depends on wavelength, and to-some-extent season.
 We quantified the wavelength dependence by acquiring calibration observations of blank sky in both the target and sky fiber.
 We applied this wavelength-based scale factor to each target spectrum's associated reference sky fiber to achieve near-imperceptible sky-line residuals.
-A few lines exhibit residuals which may arise from slight differences in the local atmospheric conditions between the target and sky fiber.
+A few lines exhibit residuals which may arise from genuine differences in the local atmospheric conditions between the target and sky fiber.
 
@@
 
-We flatten the spectral to continuum indices near the He 10830 features and compute the equivalent width (EW) defined over the spectral region \censorbox{xx,xxx}$-$\censorbox{xx,xxx} shown in Figure \censorbox{XX}.
+The sky-subtraction, telluric masking, barycentric correction, and all of our other standard pre-processing steps are implemented in the open-source Python interface \texttt{muler} \citep{2022JOSS....7.4302G}.
 
-The sky-subtraction, telluric masking, barycentric correction, and all of our other standard pre-processing steps are implemented in a new open-source Python interface \texttt{muler}\footnote{\url{https://github.com/OttoStruve/muler/}} (Gully-Santiago \emph{et al.}, submitted).
+Figure X shows
 

### 2022-11-15 paper/paper1/ms.tex
Add HPF figure

@@
 
-Figure X shows
+Figure \ref{fig:HPF2022campaign} shows a zoom-in on the He 10830 region of interest.
 
-\authorcomment1{Add overplots of He and Ca II.}
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/HAT-P-67_2022_clean.png}
+    \caption{HPF spectrum of HAT-P-67 around the spring 2022 campaign.
+We see conspicuous absorption during and immediately preceding the transit, but not immediately after.
+The continuum normalization indices are shown by the vertical blue shaded region and the region used for computing EW is shown in the faint gray vertical band.}
+    \label{fig:HPF2022campaign}
+\end{figure}
 
-\subsection{EW Uncertainty quantification with MCMC}
-We assessed the uncertainty in our equivalent fit Gaussian line profiles to the He 10830 line with \texttt{emcee} \citep{foreman13}.
+%\subsection{EW Uncertainty quantification with MCMC}
+%We assessed the uncertainty in our equivalent fit Gaussian line profiles to the He 10830 line with \texttt{emcee} \citep{foreman13}.
 The model consists of a straight-line trend with a Gaussian absorption line.
 It has five parameters: the straight-line trend slope $m$ and offset $b$, and the Gaussian amplitude $A$, center wavelength $\mu$, and width $w$.
-
-We computed the equivalent width with the closed-form integral:
-
-\begin{gather}
-    W_\lambda=\frac{Aw}{m \mu + b}\cdot\sqrt{2\pi}
-\end{gather}
-
-Ultimately the MCMC method was highly accurate but imprecise, and was replaced in favor of \emph{data-driven} methods.
 
@@
 \end{deluxetable*}
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/stellar_periodogram.png}
-    \caption{Periodogram of solely the stellar variation of the flux. }
-    \label{fig:stellar_periodogram}
-\end{figure}
 

### 2022-11-15 paper/paper1/ms.tex
a little prose, some figures in place

@@
 Figure \ref{fig:TESSmodulation} shows this modulation in the minimally processed TESS lightcurve.
-During the exoplanet orbit fitting, we fit the TESS lightcurve modulation with a quasiperiodic Gaussian Process (GP) model using \citep{celerite} \citep{celerite1,celerite2}.
+During the exoplanet orbit fitting, we fit the TESS lightcurve modulation with a quasiperiodic Gaussian Process (GP) model using \texttt{celerite} \citep{celerite1,celerite2}.
 The GP model fit to the entire composite lightcurve yields a period of 4.7 days; when fit to individual sectors alone the periods hover around 5.9 days.
@@
     ~~~$T_c$ (${\rm BTJD}$)  \dotfill    & $-1038.61533_{-0.00064}^{+0.00076}$ & 1958.08059$\pm$0.00032 & 1958.07933 & z \\
-    ~~~$T_{14}$ (hours)  \dotfill    & $6.9888 \pm 0.046$ & x & 7.0636 & z \\
-    ~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ & x & y & z \\
-    ~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ & x & y & z \\
-    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ & x & 0.08231 & z \\
+    ~~~$T_{14}$ (hours)  \dotfill    & $6.9888 \pm 0.046$ &  & 7.0636 & z \\
+    ~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ &  &  & z \\
+    ~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ &  &  & z \\
+    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ &  & 0.08231 & z \\
     ~~~$b \equiv a \cos i/\rstar$
-    \dotfill    & $0.12_{-0.08}^{+0.12}$ & x & 0.45616 & z \\
-    ~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ & x & y & z \\
+    \dotfill    & $0.12_{-0.08}^{+0.12}$ &  & 0.45616 & z \\
+    ~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ &  &  & z \\
     \enddata
@@
 
-%\subsection{EW Uncertainty quantification with MCMC}
-%We assessed the uncertainty in our equivalent fit Gaussian line profiles to the He 10830 line with \texttt{emcee} \citep{foreman13}.
-The model consists of a straight-line trend with a Gaussian absorption line.
-It has five parameters: the straight-line trend slope $m$ and offset $b$, and the Gaussian amplitude $A$, center wavelength $\mu$, and width $w$.
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/HAT_P_67b_Helium10830EW_byCampaign.png}
+    \caption{Time series EW lightcurve of Helium absorption in HAT-P-67b.  The system exhibits a characteristic absorption leading up to transit, followed by a sharp decline after transit passage.  }
+    \label{fig:HPFtimeseries}
+\end{figure}
 
-Table \ref{tab:sample_properties} lists the bulk physical properties for HAT-P-67.
-
-\begin{deluxetable*}{ccccc}[!ht]
-    \tablecaption{Stellar properties \label{tab:sample_properties}}
-    \tablehead{
-        \colhead{$T_{\mathrm{eff}}$ (K)} & \colhead{$\log{g}$} & \colhead{RV (km/s)} & \colhead{V sin(i) (km/s)} & \colhead{Reference}}
-    \startdata
-    $6406^{+65}_{-61}$ & $3.854^{+0.014}_{-0.023}$ & -1.4 $\pm$ 0.5 & 35.8 $\pm$ 1.1 & \cite{2017AJ....153..211Z}\\
-    \enddata
-\end{deluxetable*}
-
-\subsection{HPF MCMC}
-The methodology used to fit the HPF spectra was the Markov chain Monte Carlo (MCMC).
-After deblazing and normalizing the spectrum, we used a Gaussian line to fit the spectra with five parameters: width, center wavelength, amplitude, slope, and offset.
-We focused on each sub-region of the spectrum by cutting of data outside of the $99.9\%-100.1\%*line$ threshold to create a better fit for the data.
-This threshold was determined as a result of which line we were looking at.
-The generative model consists of a straight-line trend with a Gaussian subtracted from it.
-The continuum of the spectrum was given by $continuum=m(\lambda-\lambda_{int})+b$ and the Gaussian fit was subtracted off of the continuum to get the absorption line fit.
-After applying values to the five parameters for the generative model, we improved our fitting with the MCMC process.
-We computed the log likelihood of the guessing parameters to determine a quality of fit metric.
-From there, we ran MCMC with the package \textit{emcee} at 5000 steps for the five parameters.
-After thinning out and discarding the last 1000 steps, we gathered the final draws for the given parameters with their corresponding uncertainties.
-
-\subsection{HPF Equivalent Width Determination}
-In addition to the MCMC method, we verified the precision of our numbers through another fitting method.
-While the MCMC method produced an accurate result, it lacked the precision required.
-Thus, we chose to analyze the data again with the summation method.
-
-After collecting the new parameters, we then calculated the equivalent width of the corresponding line with the formula $EW=\sqrt{2\pi}\frac{Aw}{m(\mu-line)+b}$.
-We then calculated the mean and standard deviation of the equivalent width.
-\subsection{Contemporaneous Stellar Activity Quantification}
-
-\input{tables/ew_table.tex}
+\subsection{Calcium IR Triplet lines}
 
 \section{Results}
-\subsection{Detection of Helium with Orbital Phase}
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/TESS_EW_HAT-P-67.jpg}
-    \caption{A boat.}
-    \label{fig:boat1}
-\end{figure}
-We can see that there is indeed a helium signature that arises when the planet is in transit with its host star.
-\subsection{Stellar Activity (non)detection versus Equivalent Width}
-There is a likelihood that a portion of the exoplanet emission spectra originates from stellar activity.
-Thus, we must identify which stellar features mimic a helium signature.
-Such features can be narrowed down to the star's radial velocity, star spots, and faculae.
+
+\subsection{Geometry of the Escaping Exosphere}
+Helium absorption occurs before the planet is in-transit, indicating a \emph{leading} tail escaping the planet. We see excess as early as 30\% of the orbital path, or about 130 planetary radii.
+
 \subsection{Star Planet Interaction}
-Characterizing a host star's stellar environment is of utmost importance if we want to understand how exoplanet atmospheres are affected.
-While cool dwarfs generate high irradiation in the ultraviolet and stellar winds, the sub-giant category
 \subsection{Gas Motion Relative to Planet}
 \subsection{Parker Winds Model}
-\subsubsection{p-winds model failure}
-\subsection{Geometry of the Escaping Exosphere}
-We can depict the transit of HAT-P-67b from the orbital phase versus equivalent width plot.
-The plot exhibits helium absorption occurring before the planet is in-transit.
-We can attribute this shallow increase in the equivalent width to the shape of the helium exosphere.
-Because the absorption gradually increases, we created a leading tail that begins transit 2 days before the planet does.
-As a result, we mold the shape of the helium exosphere to mimic the irregular absorption with constraints on the velocity and length
 
@@
 \subsection{Hot Spot Scenario}
-Using the contemporaneous TESS lightcurve, we notice that there is a 0.2\% flux variation.
-Assuming that this increase in flux is due to a hot spot with a contrast of 200\%, the hot spot must have a radius that is 12.49 times that of the radius of the Earth.
-Assuming that the mass loss rate of the planet is its mass over 10 billion years, we can assume that this hot spot is not caused by in falling mass from the planetary envelope as the mass is not enough to cause a 0.2\% modulation in the flux.
+The TESS 0.2\% flux variation could hypothetically arise from the foot-print of a star-planet interaction.
+Assuming that this increase in flux is due to a hot spot with a contrast of 200\% the ambient photosphere in the TESS bandpass, the hot spot would have a modest 5\% coverage fraction.
+Thermal radiation from gravitational infall alone cannot explain the luminosity of this spot, so it would have to stem from a non-thermal cause.
 
 \subsection{Tidal Locking Calculation}
-From section 3.3.1, we determined the rotational period of the star from contemporaneous TESS data. Given the orbital period of the planet, we concluded that the system is tidally locked.
+The similarity of the rotation period with the orbital period suggests the star-planet system may be tidally locked.
 
 \subsection{Mass Loss Rate}
-Parker wind models, such as those implemented in the Python tool p-winds, are incapable of accurately measuring mass loss rates for systems as extreme as HAT-P-67.
-Instead, we must constrain the mass loss rate to the mass of the planet over the course of the age of the universe.
-The resulting value is $2.045*10^{12}$ g/s.
-
-The first scenario is where the mass from the exosphere falls onto the surface of the star.
-The TESS lightkurve for this system exhibits a reoccurring 0.2\% increase in the flux that is not attributable to the planet’s transit.
-Assuming that this modulation is due to a hot spot on the stellar surface, we conclude that gravitational potential energy alone is not sufficient to increase the flux by such an amount.
-Larger mass loss rates could cause brighter hotspots, but this would cause the planet to disappear entirely over its lifetime, which is unphysical.
+A steady state mass loss rate greater than $2\times10^{12}$ g/s would erode the planet over the age of the stellar system.
 
@@
 \subsection{Limits of Stellar Activity Metrics}
-\authorcomment1{3D Heat Map Interpolation figure that mimics MacLeod paper}
 \subsection{Comparison to Other Systems}
-\authorcomment1{Parameter plot with HAT-P-67 system with others from exoplanet archive}
 \section{Conclusions}
-
-Reiteration here.
 
@@
     \texttt{seaborn} \citep{waskom14},
-    \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A},
-    \texttt{muler} (Gully-Santiago et al., submitted),
+    \texttt{astropy} \citep{2022ApJ...935..167A},
+    \texttt{muler} \citep{2022JOSS....7.4302G},
     \texttt{telfit} \citep{2014AJ....148...53G},

### 2022-11-16 paper/paper1/ms.tex
Add some prose about HPF observations

@@
 
-The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R, 2007PASP..119..556S} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands.
-We observed HAT-P-67b with HPF in-transit on 2020 April 28, 2020 May 22, and 2020 June 15 and out-of-transit on a total of \censorbox{xx} other nights.
+The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands.
+We observed HAT-P-67 with HPF on a total of 26 unique nights.
+The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of HAT-P-67 to about 1 hour ``tracks'', compared to conventional steerable telescopes that can conduct point-and-stare observations for hours.
+We organized the observations into four campaigns to coincide with HAT-P-67b transits on 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.
+These in-transit nights had 12-18 exposures per HET track, with integration times between 5-8.5 minutes.
+These campaigns were designed to acquire out-of-transit observations one and two nights before and after transit, weather and schedule permitting.
+These out-of-transit observations typically received 4 or fewer individual exposures.
+Additionally we acquired random-in-phase observations using low priority ``P4'' time.
+
+Finally, the observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.
+The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836$\AA$, but the core and blue line wings appear pristine.
 
@@
 
-Figure \ref{fig:HPF2022campaign} shows a zoom-in on the He 10830 region of interest.
+Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 region of interest, with all 128 observations overlaid.
+We see a variability in the Helium line of up to 10\%, which is not seen in other adjacent stellar lines.
+The feature width spans about 3 $\AA~$, too broad to originate from the much narrower telluric lines.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/HAT_P_67b_He_spectrum.png}
+    \caption{Overlay of all 128 individual HPF exposures of HAT-P-67, spanning 2020-2022.
+Variability is seen in the Helium 10833 $\AA$ band, denoted by the vertical orange shaded band, but not in the adjacent regions.
+These snapshot spectra were barycentric corrected, and continuum flattened to the regions in the blue vertical bands.
+Sharp telluric absorption lines have been masked in regions near 10835 and 10837.5 $\AA$.}
+    \label{fig:HPFheliumOverview}
+\end{figure}
 
@@
     \includegraphics[width=\linewidth]{figures/HAT-P-67_2022_clean.png}
-    \caption{HPF spectrum of HAT-P-67 around the spring 2022 campaign.
-We see conspicuous absorption during and immediately preceding the transit, but not immediately after.
-The continuum normalization indices are shown by the vertical blue shaded region and the region used for computing EW is shown in the faint gray vertical band.}
+    \caption{HPF spectra of HAT-P-67 from the April/May 2022 campaign.  We see conspicuous absorption during and immediately preceding the transit, but not immediately after.}
     \label{fig:HPF2022campaign}

### 2022-11-21 paper/paper1/ms.tex
Add an observation log to the paper, may add/remove columns later...
Some text about the HPF observations

@@
 The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands.
-We observed HAT-P-67 with HPF on a total of 26 unique nights.
-The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of HAT-P-67 to about 1 hour ``tracks'', compared to conventional steerable telescopes that can conduct point-and-stare observations for hours.
+We observed HAT-P-67 with HPF on a total of 39 unique nights.
+The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of HAT-P-67 to less than 1 hour ``tracks'' for a fixed range of hour angles before and after the meridian; whereas conventional steerable telescopes can conduct point-and-stare observations for hours, HET cannot.
 We organized the observations into four campaigns to coincide with HAT-P-67b transits on 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.
-These in-transit nights had 12-18 exposures per HET track, with integration times between 5-8.5 minutes.
+These in-transit nights had up to exposures per HET track, with integration times between 5-8.5 minutes.
+Table \ref{tabHPFLog} summarizes the log of observations.
 These campaigns were designed to acquire out-of-transit observations one and two nights before and after transit, weather and schedule permitting.
@@
 
-Finally, the observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.
+The observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.
 The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836$\AA$, but the core and blue line wings appear pristine.
 
-\input{tables/observations_flat_table.tex}
+Only 19 out of the 39 nights possess A0V telluric calibration standard stars.  These standard stars, when available, we used to spot-check our masking procedure.
+
+\begin{deluxetable*}{lrrrccr}
+    \tablewidth{0pc}
+    \tabletypesize{\scriptsize}
+    \tablecaption{
+        HPF Observation Log
+        \label{tabHPFLog}
+    }
+    \tablehead{
+        \colhead{Date}   &
+        \colhead{Track} &
+        \colhead{Transit?} &
+        \colhead{BTJD} &
+        \colhead{$N_\mathrm{exp}$} &
+        \colhead{$t_\mathrm{exp}$} &
+        \colhead{$\phi$}\\
+        \colhead{}   &
+        \colhead{} &
+        \colhead{} &
+        \colhead{(days)} &
+        \colhead{} &
+        \colhead{(s)} &
+        \colhead{$\in(-0.5, 0.5)$}
+    }
+    \startdata
+    \input{tables/observation_log.tex}
+    \enddata
+\end{deluxetable*}
 

### 2022-11-28 paper/paper1/ms.tex
Paper text tweaks

@@
 \begin{abstract}
-    We aim to understand how exoplanet atmospheres evolve across age, stellar irradiation environments, planet properties, and---for extremely close-in exoplanets---direct star-planet interaction (SPI) such as stellar winds, tidal forces, and magnetic interactions.
-The scarcity of exoplanet atmosphere measurements across a range of stellar properties has limited our ability to complete this picture.
-
-    The Helium Exospheres program with the Habitable Zone Planet Finder (HPF) spectrograph on the Hobby Eberly Telescope (HET) in West Texas has targeted 23 exoplanet systems over two years.
-Here, we present a study of HAT-P-67, an F subgiant hosting a low density planet with 0.3 $M_{\mathrm{Jup}}$ and 2.1 $R_{\mathrm{Jup}}$ on a close-in 4.8 day orbit.
-The high energy radiation environment should provide a uniquely harsh testing ground for examining atmospheric escape.
-The planet shows prominent in-transit absorption in the He 10830 \AA~ triplet and infrared Ca II 8542 \AA~ triplet across 20 visits over the course of a year including in- and out-of-transit spectroscopy.
-We identify the rotational period of HAT-P-67 to be 5.417 days by using contemporaneous data from the Transiting Exoplanet Survey Satellite (TESS).
-We consider multiple interpretations of the HPF and TESS observations.
-First, the period measured by TESS may be the rotational period of the star and thus, the star and planet are nearly-tidally locked.
-On the other hand, the period measured by TESS may result from SPI-induced hot spots on the surface that follow the magnetic field lines linked to the planet's orbital period.
-Finally, we consider the possibility of stellar surface inhomogeneity contaminating the He and Ca II transit signals.
+    To be overhauled...
 \end{abstract}
@@
 
-Exoplanets possess a dynamic range of atmospheric properties far beyond what we have seen in our own Solar System.
-Extreme radiation effects, atmospheric erosion, and unexpected chemistry must exist, but collecting examples of these phenomena remains at the edge of the possible today.
-The minuscule signal strengths of atmospheric shells has hidden all but the most conspicuous phenomena.
-Helium 10830 \AA has emerged as the most conspicuous exosphere indicator, enabling ground-based detection with high-resolution near-infrared (IR) spectrographs.
+\authorcomment1{Todo: Intro topics-- atmospheric escape, variety of exoplanets, extremes, photoevaporation, Fulton Gap, Helium 10830 backgorund, etc...}
+
+%Exoplanet atmospheres must exhibit an unimaginable dynamic range in physical and chemical properties, spanning familiar life-sustaining worlds to uninhabitable toxic wastelands.
+Most systems exhibit signals too weak to register with current instruments, so our understanding of the variety of exoplanet atmospheres has been built on a foundation of comparative studies \citep{2016Natur.529...59S}, population studies \citep{2017AJ....154..109F}, and theoretical understanding.
+Extreme atmospheres offer the benefit of being more conspicuous, while challenging the limits of the imagination and motivating new directions for building theory.
 
@@
 HAT-P-67 is an F type sub-giant with the Saturn-sized planet HAT-P-67b.
-HAT-P-67b stands out for a few reasons.
-It has a relatively low surface gravity, which could make it amenable to rapid atmospheric mass loss.
+HAT-P-67b has a low surface gravity, which makes it amenable to rapid atmospheric mass loss.
 It orbits an evolved star, which means its instellation may have increased as the star's size has grown.
@@
 
-The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands.
-We observed HAT-P-67 with HPF on a total of 39 unique nights.
-The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of HAT-P-67 to less than 1 hour ``tracks'' for a fixed range of hour angles before and after the meridian; whereas conventional steerable telescopes can conduct point-and-stare observations for hours, HET cannot.
-We organized the observations into four campaigns to coincide with HAT-P-67b transits on 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.
-These in-transit nights had up to exposures per HET track, with integration times between 5-8.5 minutes.
+The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands at spectral resolving power $R=55,000$.
+The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of HAT-P-67 to less than 1 hour ``tracks'' for a fixed range of hour angles before (east track) and after (west track) transiting the meridian.
+Whereas conventional steerable telescopes could conduct cintinuous point-and-stare observations of HAT-P-67 for hours, HET cannot.
+In practice, this limitation means that in-transit and out-of-transit were rarely possible on the same night.
+Instead, we organized the observations into four campaigns to coincide with HAT-P-67b transits on the nights beginning 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.
+These in-transit nights had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.
+We obtained out-of-transit baseline observations up to 2 nights before and after the transit, plus random-in-phase low priority P4 queue-filler observations.
+These out-of-transit observations typically received 4 or fewer individual exposures.
+We observed HAT-P-67 with HPF for a total 41 visits on 39 unique nights, with two of those nights observing both an east and a west track.
 Table \ref{tabHPFLog} summarizes the log of observations.
-These campaigns were designed to acquire out-of-transit observations one and two nights before and after transit, weather and schedule permitting.
-These out-of-transit observations typically received 4 or fewer individual exposures.
-Additionally we acquired random-in-phase observations using low priority ``P4'' time.
 
 The observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.
-The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836$\AA$, but the core and blue line wings appear pristine.
+The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836$\AA$, but the core and blue line wings appear relatively pristine.
 
-Only 19 out of the 39 nights possess A0V telluric calibration standard stars.  These standard stars, when available, we used to spot-check our masking procedure.
+Only 19 out of the 39 nights possess A0V telluric calibration standard stars.  These standard stars, when available, were used to spot-check our telluric mitigation strategy.
 
@@
 We retrieved ground-based photometry with the \emph{All-Sky Automated Survey for Supernovae} (ASAS-SN) using the Sky-Portal \citep{shappee14,2017PASP..129j4502K}.
+The precision of ASAS-SN was too low to perceive stellar variability, and so the photometry is not presented further.
 
 \subsection{DASCH}
-We searched for observations of HAT-P-67 in other archives.
-It appears in the Harvard Plate Archive, with 5809 measurements digitized through DASCH \censorbox{citation}, spanning over 120 years of coarse photometric monitoring.
+HAT-P-67 appears in the Harvard Plate Archive, with 5809 measurements digitized through DASCH, spanning over 120 years of coarse photometric monitoring.
 In principle these datasets could inform long-term variability trends such as stellar cycles.
 In practice the 0.15 magnitude jitter appears too coarse to perceive any genuine astrophysical variability, with no conspicuous trend seen.
-We can therefore place a relatively mild constraint that the star is stable at the $30\%$ level over periods of tens of years.
+We can therefore place a relatively mild constraint that the star is stable at the $30\%$ level over periods of tens to hundreds of years.
 
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/Gaia_HAT_P_67_AB.png}
-    \caption{HR Diagram of F star HAT-P-67A with its assumed M-dwarf main sequence companion HAT-P-67B.
+%\begin{figure}
+%    \includegraphics[width=\linewidth]{figures/Gaia_HAT_P_67_AB.png}
+%    \caption{HR Diagram of F star HAT-P-67A with its assumed M-dwarf main sequence companion HAT-P-67B.
 The density of stars comes from the \emph{Kepler} prime field estimated by \citet{2020AJ....160..108B} using \emph{Gaia DR2}.}
-    \label{fig:gaiaHRD}
-\end{figure}
+%    \label{fig:gaiaHRD}
+%\end{figure}
 
@@
 We obtained a best fit orbital period of $4.81011$ days, non-zero eccentricity of 0.19, an impact parameter of 0.46, planet-to-star radius of 0.0823, transit depth of 0.74\%, and $T_0$ of 1958.07933 in BTJD.
-We did not attempt MCMC sampling to quantify degeneracy among these parameters, and we suspect that the transit is adequately modeled by a circular orbit.
+These properties are consistent with the previously reported values from \citet{2017AJ....153..211Z}.
 Figure \ref{fig:transit} shows the best-fit orbit overlaid on the detrended TESS lightcurve.
-Table \ref{tabOrbit} lists a previous orbit determination and solutions reported here.
+Table \ref{tabOrbit} lists one of the previous orbit determinations and solution reported here.
 
@@
 If we attribute the TESS modulation signal to stellar activity, we obtain a rotation period $P_\mathrm{rot}$ between 4.7 and 5.9 days.
-\citet{2017AJ....153..211Z} reported a $v\sin{i}=35.8\pm1.1$ km/s, or possibly as $v\sin{i}=30\pm1.1$ km/s if macroturbulence were included.
+\citet{2017AJ....153..211Z} estimated $v\sin{i}=35.8\pm1.1$ km/s, or lower ($v\sin{i}=30\pm1.1$ km/s) if macroturbulence was accounted for.
 We obtain a combined geometric constraint $2.85< R_\star \sin{i} (R_\odot) < 4.2 $.
@@
 We would therefore expect an isochrone-deived $R_\star$ range closer to $2.5-3.14 R_\odot$, where we have dropped the 1-$\sigma$ uncertainties which had included the less certain Gaia DR 1 parallax and its uncertain correction terms.
+For a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius, revising the already-low density of HAT-P-67 even lower.
 
@@
 Ideally we seek the pixel-to-pixel substructured spectrum of the helium exosphere, corrected for all the conceivable instrumental, telluric, and stellar contamination artifacts.
-In practice, these corrections are incomplete and so some care is needed to assess the extent of contamination.
+In practice, these corrections are incomplete.
 We experimented with a range of pre-processing and analysis techniques to quantify the accuracy and precision of our HPF spectra.
@@
 The sky fiber and target fiber have slightly different throughputs and illumination properties so the sky fiber must be scaled prior to subtraction from the target spectrum.
-On average the target fiber sees $93\%$ of the flux of the sky reference fiber, and in detail this ratio depends on wavelength, and to-some-extent season.
+On average the target fiber sees $93\%$ of the flux of the sky reference fiber, and at the few percent level this ratio depends on wavelength and season.
 We quantified the wavelength dependence by acquiring calibration observations of blank sky in both the target and sky fiber.
@@
 We shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W} as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A}.
-
 The sky-subtraction, telluric masking, barycentric correction, and all of our other standard pre-processing steps are implemented in the open-source Python interface \texttt{muler} \citep{2022JOSS....7.4302G}.
 
-Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 region of interest, with all 128 observations overlaid.
-We see a variability in the Helium line of up to 10\%, which is not seen in other adjacent stellar lines.
+Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 region of interest, with all 153 individual exposures overlaid.
+We see a variability in the Helium line of up to 10\%, much greater than the $<1\%$ pixel-to-pixel variation.
 The feature width spans about 3 $\AA~$, too broad to originate from the much narrower telluric lines.

### 2022-11-28 paper/paper1/ms.tex
writing the analysis

@@
 We observed HAT-P-67 with HPF for a total 41 visits on 39 unique nights, with two of those nights observing both an east and a west track.
+The total on-source integration time exceeds 13.8 hours.
 Table \ref{tabHPFLog} summarizes the log of observations.
@@
 We shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W} as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A}.
-The sky-subtraction, telluric masking, barycentric correction, and all of our other standard pre-processing steps are implemented in the open-source Python interface \texttt{muler} \citep{2022JOSS....7.4302G}.
+We flattened the spectra to two pre-selected continuum indices highlighted as vertical blue bands in Figure \ref{fig:HPFheliumOverview}.
+The sky-subtraction, telluric masking, barycentric correction, flattening, and all of our other standard pre-processing steps were carried out in the open-source Python interface \texttt{muler} \citep{2022JOSS....7.4302G}.
 
@@
 We see a variability in the Helium line of up to 10\%, much greater than the $<1\%$ pixel-to-pixel variation.
-The feature width spans about 3 $\AA~$, too broad to originate from the much narrower telluric lines.
+The feature width spans about 3 $\AA~$, comparable to the stellar rotationally lines too broad to originate from the much narrower telluric lines.
 
@@
 
+The 13.8 hours of exposure, combined with HAT-P-67b's short ($P\sim4.8$ day) period, means that a large fraction of the orbit has been collected, with some phases (especially near transit) heavily sampled, and some other out-of-transit phases sampled only sparsely.
+We constructed a 2-D intensity phase scan, binning in phase and wavelength, and spanning the entire orbit of HAT-P-67.
+Figure \ref{fig:HPFphase2D} overlays the planet's approximately $\pm150\;$km/s orbital Doppler velocity, with the stellar rest frame velocity demarcated by the vertical line.
+The vanishing $<36$ m/s reflex motion of the star is imperceptible at this scale.
+The horizontal dashed lines indicate the transit ingress, midcenter, and egress.
+
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/HAT-P-67_2022_clean.png}
-    \caption{HPF spectra of HAT-P-67 from the April/May 2022 campaign.  We see conspicuous absorption during and immediately preceding the transit, but not immediately after.}
-    \label{fig:HPF2022campaign}
+    \includegraphics[width=\linewidth]{figures/phase_2D_diagram.png}
+    \caption{Phase scan of intensity for HAT-P-67.
+The spectrum flux intensity shows significant in-transit absorption during and before the transit.
+Telluric lines redward of the line center have been masked.
+An unmasked telluric line near 10825 $\AA$ can be seen.}
+    \label{fig:HPFphase2D}
 \end{figure}
+
+A large absorption signal can be seen preceding transit ingress, with some significant absorption evident before $-0.2$ in phase.
+We construct a fractional residual absorption spectrum by subtracting off and re-normalizing to the non-varying baseline.
+We define the non-varying baseline spectrum as the average over phases $0.3-0.5$, which exhibited stable spectra with the lease absorption.
+Figure \ref{fig:HPFscanResid} shows a conspicuous view of the Helium absorption of HAT-P-67b.
+Significant absorption can be seen as a few percent at $-0.37$ in phase, rising to 10\% just before and during transit.
+The egress drop off is extremely sharp, with almost no absorption directly after transit.
+
+The absorption resides mostly near the stellar zero restframe velocity reference.
+As mentioned previously, the telluric masking near 10836 $\AA$ censors our view of the existence (or not) of any redshifted lobe in this region.
+A more careful treatment of the telluric absorption could rescue some of the data in this region.
+
+Finally, a tentative much weaker post-egress bifurcation into blue-shifted absorption and redshifted emission may exist near 0.1 in phase.
+The signal appears at or just above the noise level, but is shared among tens of pixels.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/phase_2D_diagram_resid.png}
+    \caption{Absorption depth phase scan over the entire HAT-P-67b orbit from 41 visits with HPF.  }
+    \label{fig:HPFscanResid}
+\end{figure}
+
+%\begin{figure}
+%    \includegraphics[width=\linewidth]{figures/HAT-P-67_2022_clean.png}
+%    \caption{HPF spectra of HAT-P-67 from the April/May 2022 campaign.  We see conspicuous absorption during and immediately preceding the transit, but not immediately after.}
+%    \label{fig:HPF2022campaign}
+%\end{figure}
 
@@
 
-\subsection{Calcium IR Triplet lines}
+\subsection{Calcium IR Triplet and other line diagnostics}
+We examined the Calcium IR Triplet lines (Ca IRT) for evidence of variability.
+No variation was seen in these features, which were pre-processed in the same way as the Helium feature.
+Figure \ref{x} shows a similar phase plot as Figure \ref{fig:HPFscanResid}, adapted to the line at
 

### 2022-12-01 paper/paper1/ms.tex
Some figures and text around the 2D heatmap scans

@@
 No variation was seen in these features, which were pre-processed in the same way as the Helium feature.
-Figure \ref{x} shows a similar phase plot as Figure \ref{fig:HPFscanResid}, adapted to the line at
+Figure \ref{fig:CaPhaseScan} shows a similar phase plot as Figure \ref{fig:HPFscanResid}, adapted to the line at 8662 $\AA$.
+We see no conspicuous variability at this or any of the other Ca IRT lines.
+We also found no detectable variability in the Pa$\delta$ line at 10050 $\AA$, nor other deep lines at 10330 $\AA$ and elsewhere.
+Helium 10830 appears to be the only conspicuously variable line in the HPF spectrum.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/Ca8662_phase_2D_diagram_resid.png}
+    \caption{Non-detection of variability in the Calcium IR Triplet line at 8862 $\AA$.  No other HPF lines appear to show any variability.}
+    \label{fig:CaPhaseScan}
+\end{figure}
+
+\subsection{Velocity substructure}
+Figure \ref{fig:HeliumScanZoom} shows a zoom-in of the in-transit portion of the absorption residual scan.  The scan exhibits some velocity substructure.  At transit ingress, the absorption
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/phase_2D_diagram_zoom.png}
+    \caption{A zoom-in of the in-transit and post-transit phase scan for the Helium 10830 triplet.  Some velocity substructure may be seen.}
+    \label{fig:HeliumScanZoom}
+\end{figure}
 

### 2023-01-05 paper/formulae/HAT-P-67 Formula/main.tex
back of the envelope calculations

% file: fonts.tex
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsfonts}
\usepackage{amsmath, amssymb, graphics, setspace}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[legalpaper, margin=1in]{geometry}
\usepackage[caption=false]{subfig}

\newcommand{\mathsym}[1]{{}}
\newcommand{\unicode}[1]{{}}

\title{HAT-P-67 Calculations}
\author{ag68874}
\date{2/1/2022}

\begin{document}

\maketitle

\section{Free Fall}
Let's solve the free-fall problem where we throw a rock from HAT-P-67b onto its host star.
$$PE_1+KE_1=PE_2+KE_2$$
Using conservation of energy,
$$PE_1+0=0+KE_2$$
$$mgh=\frac{1}{2}mv^2$$
$$v=\sqrt{2gh}$$
In this case, $h=a-r$, which is this semi-major axis of the planetary system minus the radius of the star (as the in-falling mass lands on the surface of the star).
$$v=\sqrt{2g(a-r)}=\sqrt{2g(0.06505\:au-1.842283*10^9m)}=\sqrt{2g(9731341489\:m-1.842283*10^9m)}$$
We must calculate the new $g$ for the star with the formula
$$g=\frac{GM}{r^2}=\frac{(6.67*10^{-11}Nm^2)(2.56968*10^{30}kg)}{(1.842283*10^9m)^2}=50.50\:m/s^2$$
Using this new constant $g$, we get
$$v=\sqrt{2g(a-r)}=\sqrt{2g(7.88905849*10^9m)}=\sqrt{2(50.50\:m/s^2)(7.889*10^9m)}=892633.7771\:m/s=8.926*10^5m/s$$

\section{Hot Spots}
We know that the planet transiting the star reduces the total flux by 0.7\%. The planet has a radius of 23.37 Earth radii. We can use this information to calculate the size of a hot spot needed to create a 0.2\% increase in the flux.

$$A_p=\pi r_p^2=\pi (1.49057*10^8m)^2=6.980*10^{16}m^2$$
$$\frac{A_p}{f_p}=\frac{A_h}{f_h}$$
$$\frac{6.980*10^{16}m^2}{0.7\%}=\frac{A_h}{0.2\%}$$
$$A_h=1.994*10^{16}m^2$$
$$r_h=\sqrt{\frac{A_h}{\pi}}=\sqrt{\frac{1.994*10^{16}m^2}{\pi}}=79668683.5\:m=7.967*10^7m$$

This is about 12.49 Earth radii. So, in order to have a flux increase of 0.2\%, you must have a hot spot with a radius that is 12.49 times the radius of Earth.

\subsection{Contrast}
Contrast defines the amount of light that shines through a spot on the surface of the star. A contrast of 0\% translates to a dark spot, where the flux decreases by 0.2\%. A contrast of 100\% translates to a spot with flux output equal to that of the rest of the stellar surface. For a contrast of 200\%, the flux increases by 0.2\% and translates to a hot spot.

\section{Mass Loss Rate}
Let's assume that the mass loss rate of the planet is the mass of the planet per 10 billion years. That gives us a value of

$$\frac{108\:M_\oplus}{10^{10}\:yr}=\frac{6.45*10^{26}kg}{10^{10}\:yr}=6.45*10^{16}\:kg/yr$$
$$\frac{6.45*10^{16}\:kg}{year}*\frac{1000\:g}{kg}*\frac{year}{365\:days}*\frac{day}{24\:hr}*\frac{hr}{60\:min}*\frac{min}{60\:s}=2.045*10^{12}g/s$$

Converting this to an energy per unit time, we get
$$E=mgh=(2.045*10^{9}kg)(50.5\:m/s^2)(7.889*10^9m)=8.148*10^{20}J$$
$$E/time={8.148*10^{20}\:J/s}=8.148*10^{20}W$$
$$\frac{1\:W}{2.613*10^{-27}L_\odot}=\frac{8.148*10^{20}W}{L}$$
$$L=2.129*10^{-6}L_\odot$$

The luminosity of the host star is given as $1.0298 \log(L_\odot)$.

\section{Tidal Locking}
Let's use the formula for tidal locking to determine if our system is tidally locked. First, let's see if the planet is tidally locked by the star: 
$$t_{\text{lock}} \approx \frac{\omega a^6 I Q}{3 G m_p^2 k_2 R^5}$$

We can use a more simplified version of the prior equation where we assume the satellite is spherical.

$$t_{lock}\approx 6\frac{a^6 R_p\mu}{m_pm_s^2}*10^{10}\:year$$
$$t_{lock}\approx \frac{6(9.731*10^9\:m)^6 (1.491*10^8\:m)(3*10^{10}\: Nm^{-2})}{(6.45*10^{26}kg)(2.570*10^{30}kg)^2}*10^{10}\:year$$
$$=53.5\:years$$

While this value may be off by a large magnitude, it is nowhere close to a million years. The age of the system is much greater than $t_{lock}$, so the planet is tidally locked to the star.

Now let's see if the host star is tidally locked by the planet:
$$t_{lock}\approx \frac{6(9.731*10^9\:m)^6 (1.842*10^9\:m)(3*10^{10}\: Nm^{-2})}{(6.45*10^{26}kg)^2(2.570*10^{30}kg)}*10^{10}\:year$$
$$=2.633*10^6\:years\approx 2.6 \text{ million years}$$

\section{Scale Height}
We will now calculate the scale height of our planet's atmosphere. We will assume a mean molecular weight equal to that of Saturn, which is $\mu=2.07$.

Solving for gravity we get
$$g=\frac{GM}{r^2}=\frac{(6.67*10^{-11}Nm^2)(6.45*10^{26}\:kg)}{(1.49057*10^8\:m)^2}=1.919\:m/s^2$$
$$H=\frac{kT}{\mu m_H g}=\frac{(1.38 \times 10^{-23} \frac{J}{K})(400\:K)}{(1.66 \times 10^{-27} kg)(2.07)(1.919\:m/s^2)}=837.116\:km$$

For a phase of 0.2, we have a length scale of $1.223*10^{10}m$. Converting this to scale heights, we get:
$$\frac{1.223*10^{7}km}{837.116\:km}=14,609 \text{ scale heights}$$
\end{document}

### 2023-02-07 paper/paper1/ms.tex
Switch to Modern format for the paper for now
Writing prose for the introduction

@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[modern]{aastex631}
 \bibliographystyle{aasjournal}
@@
 
-\authorcomment1{Todo: Intro topics-- atmospheric escape, variety of exoplanets, extremes, photoevaporation, Fulton Gap, Helium 10830 backgorund, etc...}
+Atmospheric escape appears to be a compulsory phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5-2.0~$R_\oplus$ planets in the California-Kepler survey \citep{2017AJ....154..109F}.
+The two physical mechanisms for this fleeting interlude between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G}.
+Whatever the cause, some large fraction of planets must undergo atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations.
 
-%Exoplanet atmospheres must exhibit an unimaginable dynamic range in physical and chemical properties, spanning familiar life-sustaining worlds to uninhabitable toxic wastelands.
-Most systems exhibit signals too weak to register with current instruments, so our understanding of the variety of exoplanet atmospheres has been built on a foundation of comparative studies \citep{2016Natur.529...59S}, population studies \citep{2017AJ....154..109F}, and theoretical understanding.
-Extreme atmospheres offer the benefit of being more conspicuous, while challenging the limits of the imagination and motivating new directions for building theory.
+The most amenable observing configuration involves transit spectroscopy in one of three key atomic transitions: Ly~$\alpha$, \ion{He}{1} 10833 \AA, or H~$\alpha$...
 
-At least 8 systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
+Enough uncertainty exists in the tradeoffs among physical mechanisms, system ages, and timescales to make it unclear whether any given exoplanet will be actively undergoing atmospheric escape.
+The most favorable conditions may include certain commonalities: close-in, low surface gravity exoplanets with a strategically chosen radius range.
+The 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of descending to their final state.
+Alternatively, inflated Hot Jupiters could be so dramatically ablated as to overcome the somewhat stronger potential well.
+Significant gains in understanding can therefore be expected from observational studies sampling the extremes of the exoplanet distribution.
+
+8 systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
 

### 2023-02-07 paper/paper1/ms.tex
Retool the introduction

@@
 The two physical mechanisms for this fleeting interlude between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G}.
-Whatever the cause, some large fraction of planets must undergo atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations.
-
-The most amenable observing configuration involves transit spectroscopy in one of three key atomic transitions: Ly~$\alpha$, \ion{He}{1} 10833 \AA, or H~$\alpha$...
+Whatever the cause, some large fraction of planets must undergo atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations such as transiting planets.
 
 Enough uncertainty exists in the tradeoffs among physical mechanisms, system ages, and timescales to make it unclear whether any given exoplanet will be actively undergoing atmospheric escape.
-The most favorable conditions may include certain commonalities: close-in, low surface gravity exoplanets with a strategically chosen radius range.
+The most favorable traits may include close-in, low surface gravity exoplanets within a strategically chosen radius range.
 The 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of descending to their final state.
@@
 
-8 systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
+Candidates for detection should be observable in one of three atomic lines.
+Ly~$\alpha$, \ion{He}{1} 10833 \AA, and H~$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}.
+Ly $\alpha$ can exhibit strong atmospheric escape signals, but instellar medium \ion{H}{1} absorption censors its low-velocity linecore.
+\ion{He}{1} 10833 \AA offers significant advantages over Ly~$\alpha$, and has resulted in 8 systems with detections to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
+These detections exhibit a range of signal strengths, as high as 10$\%$ transit depths.
+Measurements at high spectral resolution have been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.
 
-Here we present a study of the exosphere of HAT-P-67b.
-HAT-P-67 is an F type sub-giant with the Saturn-sized planet HAT-P-67b.
-HAT-P-67b has a low surface gravity, which makes it amenable to rapid atmospheric mass loss.
-It orbits an evolved star, which means its instellation may have increased as the star's size has grown.
-The star appears close to the star, making it conceivable that star-planet interactions could be at play.
-These and other reasons make HAT-P-67b a unique laboratory for measuring the properties of exospheres and their interactions with their host stars.
-The system appears to consist of a binary with an M dwarf companion HAT-P-67B separated by $9\farcs0$.
+Here we present a study of the exosphere of \object{HAT-P-67 b}, an inflated hot Saturn orbiting an F type sub-giant\footnote{The system appears to consist of a binary with an M dwarf companion HAT-P-67B separated on-sky by $9\farcs0$ \citep{2019MNRAS.490.5088M}.
+The IAU naming convention would demand HAT-P-67Ab.
+We simply drop the A designation for notational simplicity, since the wide companion will not factor into our analysis.} at a distance of 0.06 AU \citep{2017AJ....153..211Z}.
+The strong insolation combined with \object{HAT-P-67 b}'s low surface gravity makes it an excellent candidate for strong atmospheric mass loss.
+It orbits an evolved star, opening the prospect for the planet's insolation to have increased over time as the star grew.
+These and other reasons make \object{HAT-P-67 b} a predestined laboratory for measuring the properties of exospheres at the extreme.
 

### 2023-02-07 paper/paper1/ms.tex
Re-reading and fixing the analysis section

@@
 Ly $\alpha$ can exhibit strong atmospheric escape signals, but instellar medium \ion{H}{1} absorption censors its low-velocity linecore.
-\ion{He}{1} 10833 \AA offers significant advantages over Ly~$\alpha$, and has resulted in 8 systems with detections to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
+\ion{He}{1} 10833 \AA~ offers significant advantages over Ly~$\alpha$, and has resulted in 8 systems with detections to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
 These detections exhibit a range of signal strengths, as high as 10$\%$ transit depths.
@@
 
-The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands at spectral resolving power $R=55,000$.
-The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of HAT-P-67 to less than 1 hour ``tracks'' for a fixed range of hour angles before (east track) and after (west track) transiting the meridian.
-Whereas conventional steerable telescopes could conduct cintinuous point-and-stare observations of HAT-P-67 for hours, HET cannot.
-In practice, this limitation means that in-transit and out-of-transit were rarely possible on the same night.
-Instead, we organized the observations into four campaigns to coincide with HAT-P-67b transits on the nights beginning 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.
+The Habitable Zone Planet Finder Spectrograph \citep[HPF;][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET;][]{1998SPIE.3352...34R} operates in the near-IR from $8100-12800~$\AA~ spanning the \textit{z}, \textit{Y}, and \textit{J} bands at spectral resolving power $R=55,000$.
+The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of \object{HAT-P-67} to less than 1 hour ``tracks'' for a fixed range of hour angles before (east track) and after (west track) the star transits the meridian.
+Whereas conventional steerable telescopes could conduct continuous point-and-stare observations of \object{HAT-P-67} for hours, HET cannot.
+In practice, this limitation means that in-transit and out-of-transit observational phases were rarely possible on the same night.
+Instead, we organized the observations into four campaigns to coincide with \object{HAT-P-67 b} transits on the nights beginning 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.
 These in-transit nights had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.
@@
 The observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.
-The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836$\AA$, but the core and blue line wings appear relatively pristine.
+The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836 \AA, but the core and blue line wings appear relatively pristine.
 
@@
 We searched for observations of HAT-P-67 in public archives.
-It has one $R\sim8000$ spectrum from the Intermediate Dispersion Spectrograph on the INT, centered near 4000 $\AA$.
+It has one $R\sim8000$ spectrum from the Intermediate Dispersion Spectrograph on the INT, centered near 4000 \AA.
 It has 26 photometry points from \emph{Pan-STARRS} spread across its 5 filters.
@@
 The northern source does not appear in ESO archives, nor the Gemini Archive, and it is not publicly accessible in the Zwicky Transient Factory (ZTF) archive.
-It was not targeted by Spitzer or Hubble.
+It was not targeted by \emph{Spitzer} or \emph{Hubble}.
 
@@
 We fit a Keplerian orbit model to the TESS lightcurve using the \texttt{exoplanet} framework \citep{exoplanet:joss}.
-We obtained a best fit orbital period of $4.81011$ days, non-zero eccentricity of 0.19, an impact parameter of 0.46, planet-to-star radius of 0.0823, transit depth of 0.74\%, and $T_0$ of 1958.07933 in BTJD.
-These properties are consistent with the previously reported values from \citet{2017AJ....153..211Z}.
+We obtained a best fit orbital period of $4.81011$ days, non-zero eccentricity of 0.19, an impact parameter of 0.46, planet-to-star radius ratio of 0.0823, transit depth of 0.74\%, and $T_0$ of 1958.07933 in BTJD.
+These properties are consistent with the previously reported values from \citet{2017AJ....153..211Z} and the updated ephemeris of \citet{2022ApJS..259...62I}.
 Figure \ref{fig:transit} shows the best-fit orbit overlaid on the detrended TESS lightcurve.
@@
 \citet{2017AJ....153..211Z} estimated $v\sin{i}=35.8\pm1.1$ km/s, or lower ($v\sin{i}=30\pm1.1$ km/s) if macroturbulence was accounted for.
-We obtain a combined geometric constraint $2.85< R_\star \sin{i} (R_\odot) < 4.2 $.
-The lower end of these constraints are consistent with  the 1-$\sigma$ range of $2.0 < R_\star (R_\odot) < 3.2$ provided in \citet{2017AJ....153..211Z} from different isochrones and orbit fits, and assuming a near-edge-on orbital inclination.
+We obtain a combined geometric constraint $2.85< R_\star \sin{i}  < 4.2 $ in units of $R_\odot$.
+The lower end of these constraints is consistent with  the 1-$\sigma$ range of $2.0 < R_\star < 3.2$ provided in \citet{2017AJ....153..211Z} from different isochrones and orbit fits, and assuming a near-equator-on orbital inclination.
 The Gaia \emph{DR3}-derived distance is 8\% greater than the \emph{Gaia} DR1 estimate used in \citet{2017AJ....153..211Z}; the revised larger distance would tend to increase the radius estimate by 16\% to match the observed SED in isochrone-fitting.
-We would therefore expect an isochrone-deived $R_\star$ range closer to $2.5-3.14 R_\odot$, where we have dropped the 1-$\sigma$ uncertainties which had included the less certain Gaia DR 1 parallax and its uncertain correction terms.
+We would therefore expect an isochrone-derived $R_\star$ range closer to $2.5-3.14 R_\odot$, where we have dropped the 1-$\sigma$ uncertainties which had included the less certain Gaia DR 1 parallax and its uncertain correction terms.
 For a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius, revising the already-low density of HAT-P-67 even lower.
@@
     ~~~$T_{14}$ (hours)  \dotfill    & $6.9888 \pm 0.046$ &  & 7.0636 & z \\
-    ~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ &  &  & z \\
-    ~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ &  &  & z \\
+    %~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ &  &  & z \\
+    %~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ &  &  & z \\
     ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ &  & 0.08231 & z \\
@@
     \dotfill    & $0.12_{-0.08}^{+0.12}$ &  & 0.45616 & z \\
-    ~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ &  &  & z \\
+    %~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ &  &  & z \\
     \enddata
@@
 \subsection{HPF analysis}
-Ideally we seek the pixel-to-pixel substructured spectrum of the helium exosphere, corrected for all the conceivable instrumental, telluric, and stellar contamination artifacts.
-In practice, these corrections are incomplete.
-We experimented with a range of pre-processing and analysis techniques to quantify the accuracy and precision of our HPF spectra.
-
 The raw 2D echellograms were reduced with the \texttt{Goldilocks} package\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}}, which outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb (LFC).
@@
 We masked spectral regions predicted to have significant telluric lines with a template generated by \texttt{telfit} \citep{2014AJ....148...53G}.
-We shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W} as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A}.
+We shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W} as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A,2022ApJ...935..167A}.
 We flattened the spectra to two pre-selected continuum indices highlighted as vertical blue bands in Figure \ref{fig:HPFheliumOverview}.
@@
 We see a variability in the Helium line of up to 10\%, much greater than the $<1\%$ pixel-to-pixel variation.
-The feature width spans about 3 $\AA~$, comparable to the stellar rotationally lines too broad to originate from the much narrower telluric lines.
+The feature width spans about 3~\AA, comparable to the stellar rotationally broadened lines and too broad to originate from the much narrower telluric lines.
 
@@
     \caption{Overlay of all 128 individual HPF exposures of HAT-P-67, spanning 2020-2022.
-Variability is seen in the Helium 10833 $\AA$ band, denoted by the vertical orange shaded band, but not in the adjacent regions.
+Variability is seen in the \ion{He}{1} 10833 \AA~ triplet, denoted by the vertical orange shaded band, but not in the adjacent regions.
 These snapshot spectra were barycentric corrected, and continuum flattened to the regions in the blue vertical bands.
@@
 
-The 13.8 hours of exposure, combined with HAT-P-67b's short ($P\sim4.8$ day) period, means that a large fraction of the orbit has been collected, with some phases (especially near transit) heavily sampled, and some other out-of-transit phases sampled only sparsely.
-We constructed a 2-D intensity phase scan, binning in phase and wavelength, and spanning the entire orbit of HAT-P-67.
+The 13.8 hours of exposure, combined with \object{HAT-P-67 b}'s short ($P\sim4.8$ day) period, means that a large fraction of the orbit has been collected, with some phases (especially near transit) heavily sampled, and some other out-of-transit phases sampled only sparsely.
+We constructed a 2-D intensity phase scan, binning in phase and wavelength, and spanning the entire orbit of \object{HAT-P-67 b}.
 Figure \ref{fig:HPFphase2D} overlays the planet's approximately $\pm150\;$km/s orbital Doppler velocity, with the stellar rest frame velocity demarcated by the vertical line.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/phase_2D_diagram.png}
+    \includegraphics[width=0.8\linewidth]{figures/phase_2D_diagram.png}
     \caption{Phase scan of intensity for HAT-P-67.
@@
 Telluric lines redward of the line center have been masked.
-An unmasked telluric line near 10825 $\AA$ can be seen.}
+An unmasked telluric line near 10825 \AA~ can be seen.}
     \label{fig:HPFphase2D}
@@
 We construct a fractional residual absorption spectrum by subtracting off and re-normalizing to the non-varying baseline.
-We define the non-varying baseline spectrum as the average over phases $0.3-0.5$, which exhibited stable spectra with the lease absorption.
-Figure \ref{fig:HPFscanResid} shows a conspicuous view of the Helium absorption of HAT-P-67b.
+We define the non-varying baseline spectrum as the average over phases $0.3-0.5$, which exhibited stable spectra with the least absorption.
+Figure \ref{fig:HPFscanResid} shows a conspicuous view of the Helium absorption of \object{HAT-P-67 b}.
 Significant absorption can be seen as a few percent at $-0.37$ in phase, rising to 10\% just before and during transit.
@@
 The absorption resides mostly near the stellar zero restframe velocity reference.
-As mentioned previously, the telluric masking near 10836 $\AA$ censors our view of the existence (or not) of any redshifted lobe in this region.
+As mentioned previously, the telluric masking near 10836 \AA~ censors our view of the existence (or not) of any redshifted lobe in this region.
 A more careful treatment of the telluric absorption could rescue some of the data in this region.
@@
 \subsection{Calcium IR Triplet and other line diagnostics}
-We examined the Calcium IR Triplet lines (Ca IRT) for evidence of variability.
+We examined the \ion{Ca}{2} IR Triplet lines (Ca IRT) for evidence of variability.
 No variation was seen in these features, which were pre-processed in the same way as the Helium feature.
-Figure \ref{fig:CaPhaseScan} shows a similar phase plot as Figure \ref{fig:HPFscanResid}, adapted to the line at 8662 $\AA$.
+Figure \ref{fig:CaPhaseScan} shows a similar phase plot as Figure \ref{fig:HPFscanResid}, adapted to the line at 8662 \AA.
 We see no conspicuous variability at this or any of the other Ca IRT lines.
-We also found no detectable variability in the Pa$\delta$ line at 10050 $\AA$, nor other deep lines at 10330 $\AA$ and elsewhere.
-Helium 10830 appears to be the only conspicuously variable line in the HPF spectrum.
+We also found no detectable variability in the Pa$\delta$ line at 10050 \AA, nor other deep lines at 10330 \AA and elsewhere.
+\ion{He}{1} 10833 appears to be the only conspicuously variable line in the HPF spectrum.
 

### 2023-02-08 paper/paper1/ms.tex
Add prose about atmospheric escape

@@
 
+We also assembled a comparison sample of about 1000 lightcurves to interpret the  prevalence of lightcurve modulation and stellar activity among broadly F subgiant-like stars.
+We selected sources based on \emph{Gaia} DR3 $T_\mathrm{eff}$ estimates and similar $\log{g}$,  and availability of at least one sector of TESS 2-minute cadence data\footnote{The requirement to have 2-minute cadence data---a data reduction convenience---may include biases stemming from the pre-selection of TESS targets, but it is not clear whether such a pre-selection would favor more or less stellar activity}.
+We also visually spot-checked these lightcurves to understand artifacts and windowing effects.
+
 \subsection{ASAS-SN}
@@
 For a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius, revising the already-low density of HAT-P-67 even lower.
+
+\subsubsection{Lightcurve modulation amplitude}
+Finally, we computed the peak-to-valley modulation for the 1000-lightcurve comparison sample, defined as the difference between the 90$^{th}$ to 10$^{th}$ percentile of each normalized TESS lightcurve.
+We find that most lightcurves are consistent with negligible astrophysical variability and/or variability predominated by instrumental artifacts.
+Nevertheless, \object{HAT-P-67 b}'s 0.36$\%$ lightcurve modulation was slightly larger than the typical comparison source, ranking in the 87$^{th}$ percentile of the ensemble.
+However the higher-modulation sources exhibited 3-5$\times$ the level of modulation seen in \object{HAT-P-67 b}, whereas \object{HAT-P-67 b} was only about 0.5$\times$ above the median.
 
@@
 \subsection{Velocity substructure}
-Figure \ref{fig:HeliumScanZoom} shows a zoom-in of the in-transit portion of the absorption residual scan.  The scan exhibits some velocity substructure.  At transit ingress, the absorption
+Figure \ref{fig:HeliumScanZoom} shows a zoom-in of the in-transit portion of the absorption residual scan.
+The scan appears to exhibit some velocity substructure.
+At transit ingress, the absorption appears more centrally concentrated near the vertical 10833 \AA~ line.
+The line depth gets slightly shallower with a slight redshift approaching transit midcenter.
 
@@
     \includegraphics[width=\linewidth]{figures/phase_2D_diagram_zoom.png}
-    \caption{A zoom-in of the in-transit and post-transit phase scan for the Helium 10830 triplet.  Some velocity substructure may be seen.}
+    \caption{A zoom-in of the in-transit and post-transit phase scan for the Helium 10830 triplet.  Some velocity substructure may be apparent.}
     \label{fig:HeliumScanZoom}
@@
 
-\section{Results}
+\section{Atmospheric Escape}
 
-\subsection{Geometry of the Escaping Exosphere}
-Helium absorption occurs before the planet is in-transit, indicating a \emph{leading} tail escaping the planet. We see excess as early as 30\% of the orbital path, or about 130 planetary radii.
+\subsection{Size and geometry of atmospheric escape}
+Helium absorption occurs predominantly before the planet is in-transit, indicating a \emph{leading} tail escaping the planet.
+The excess occurs as early as 30\% of the orbital path.
+That large fraction of an orbit translates to about 0.1 AU, 130 planetary radii, and well outside of the Roche Lobe, with its Hill radius of merely 2.6 planetary radii.
+We are therefore primarily detecting gas that is entirely unbound from the planet.
+The leading gas tail does not appear to accelerate, neither blue-shifting nor redshifting.
+The bulk of the detectable unbound gas may therefore follow its own Keplerian trajectory at a slightly shorter period orbit.
+Such a scenario may arise from preferential emission on the planet dayside, and other hypotheticals that we discussion in Section \ref{secDiscuss}.
 
-\subsection{Star Planet Interaction}
-\subsection{Gas Motion Relative to Planet}
-\subsection{Parker Winds Model}
+We
 
-\section{Discussion}
-\subsection{Hot Spot Scenario}
-The TESS 0.2\% flux variation could hypothetically arise from the foot-print of a star-planet interaction.
+\section{Discussion} \label{secDiscuss}
+%\subsection{Hot Spot Scenario}
+%The TESS 0.2\% flux variation could hypothetically arise from the foot-print of a star-planet interaction.
 Assuming that this increase in flux is due to a hot spot with a contrast of 200\% the ambient photosphere in the TESS bandpass, the hot spot would have a modest 5\% coverage fraction.
@@
 
-\subsection{Tidal Locking Calculation}
-The similarity of the rotation period with the orbital period suggests the star-planet system may be tidally locked.
+%\subsection{Tidal Locking Calculation}
+%The similarity of the rotation period with the orbital period suggests the star-planet system may be tidally locked.
 
-\subsection{Mass Loss Rate}
-A steady state mass loss rate greater than $2\times10^{12}$ g/s would erode the planet over the age of the stellar system.
+%\subsection{Mass Loss Rate}
+%A steady state mass loss rate greater than $2\times10^{12}$ g/s would erode the planet over the age of the stellar system.
 
-\subsection{Confinement to Stellar Wind}
-\subsection{Limits of Stellar Activity Metrics}
-\subsection{Comparison to Other Systems}
+%\subsection{Confinement to Stellar Wind}
+%\subsection{Limits of Stellar Activity Metrics}
+%\subsection{Comparison to Other Systems}
 \section{Conclusions}

### 2023-02-08 paper/paper1/ms.tex
a nice piece of prose about the vertical extent of the gas

@@
 The leading gas tail does not appear to accelerate, neither blue-shifting nor redshifting.
-The bulk of the detectable unbound gas may therefore follow its own Keplerian trajectory at a slightly shorter period orbit.
-Such a scenario may arise from preferential emission on the planet dayside, and other hypotheticals that we discussion in Section \ref{secDiscuss}.
+The bulk of the detectable unbound gas may therefore follow its own Keplerian trajectory at a slightly shorter period orbit, pulling away from the planet parallel to the orbital path.
+Such a scenario may arise from preferential emission on the planet dayside, and other hypotheticals that we discuss in Section \ref{secDiscuss}.
 
-We
+The out-of-transit excess exhibits approximately the same line width as the stellar lines, which are rotationally broadened by a $v\sin{i}$ of 30-35 km/s \citep{2017AJ....153..211Z}.
+The large size of the gas stream overfills the transit chord, which means both the advancing blue side and receding red side of the rotating star are nearly continuously obscured in this spin-orbit-aligned system \citep{2017AJ....153..211Z}.
+The planet transits near the Stellar equator \citep{2017AJ....153..211Z}, meaning the transit chord covers about 10$\%$ of the projected stellar surface area.
+Hypothetically a nearly 100$\%$ opaque optically thick stream of gas covering only the transit chord could reproduce the observed 10$\%$ absorption excess.
+Alternatively---and more likely---an optically thin gas stream has some additional vertical extent perpendicular to the plane of orbit, which would act to overfill the entire projected stellar disk.
+Assume the gas has a spatially uniform optical depth of about 0.1 would reproduce the 10\% absorption excess.
+
+The stream must have a finite vertical extent
 

### 2023-02-08 paper/paper1/ms.tex
Greater depth at ingress

@@
 Alternatively---and more likely---an optically thin gas stream has some additional vertical extent perpendicular to the plane of orbit, which would act to overfill the entire projected stellar disk.
-Assume the gas has a spatially uniform optical depth of about 0.1 would reproduce the 10\% absorption excess.
+Assuming the gas has a spatially uniform optical depth of about 0.1 would reproduce the 10\% absorption excess.
 
-The stream must have a finite vertical extent
+The excess absorption appears deepest and with the narrowest line width at the moment of ingress.
+Gas overfilling the stellar disk does not contribute to the excess absorption, and so the ratio of the vertical component of the intial velocity of the gas (perpendicular to the orbital plane) to the Keplerian shear controls how much time a given gas parcel has before it leaves the projected orbital chord.
 

### 2023-02-10 paper/paper1/ms.tex

--- 2023-02-08 paper/paper1/ms.tex
@@
 The bulk of the detectable unbound gas may therefore follow its own Keplerian trajectory at a slightly shorter period orbit, pulling away from the planet parallel to the orbital path.
-Such a scenario may arise from preferential emission on the planet dayside, and other hypotheticals that we discuss in Section \ref{secDiscuss}.
+Such a scenario may arise from preferential emission on the planet dayside, or other configurations that we discuss in Section \ref{secDiscuss}.
 
@@
 Alternatively---and more likely---an optically thin gas stream has some additional vertical extent perpendicular to the plane of orbit, which would act to overfill the entire projected stellar disk.
-Assume the gas has a spatially uniform optical depth of about 0.1 would reproduce the 10\% absorption excess.
+Assuming the gas has a spatially uniform optical depth of about 0.1 would reproduce the 10\% absorption excess.
 
-The stream must have a finite vertical extent
+\subsection{Inapplicability of the Parker Wind model}
+As mentioned, most of the excess we see resides outside the Roche Lobe,  extended emissions
 

### 2023-02-10 paper/paper1/ms.tex
Add partial list of authors and affiliations, alphabetically

@@
 
+%% ---------------------------------------------------------------------
+%% Affiliations
+\newcommand{\PSUAA}{Department of Astronomy \& Astrophysics, 525 Davey Laboratory, The Pennsylvania State University, University Park, PA, 16802, USA}
+\newcommand{\PSUCEHW}{Center for Exoplanets and Habitable Worlds, 525 Davey Laboratory, The Pennsylvania State University, University Park, PA, 16802, USA}
+\newcommand{\Princeton}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+\newcommand{\RUSSELL}{Henry Norris Russell Fellow}
+\newcommand{\CFA}{Center for Astrophysics $\vert$ Harvard $\&$ Smithsonian, 60 Garden Street, MS-16, Cambridge, MA 02138, USA}
+\newcommand{\UTAustin}{Department of Astronomy, The University of Texas at Austin, 2515 Speedway, Austin, TX 78712, USA}
+\newcommand{\MCDonald}{McDonald Observatory and Department of Astronomy, The University of Texas at Austin, 2515 Speedway, Austin, TX 78712, USA}
+\newcommand{\UTSpace}{Center for Planetary Systems Habitability, The University of Texas at Austin, 2515 Speedway, Austin, TX 78712, USA}
+\newcommand{\Amsterdam}{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, NL-1098 XH Amsterdam, The Netherlands}
+\newcommand{\UCSC}{Department of Astronomy \& Astrophysics, University of California, Santa Cruz, 1156 High St, Santa Cruz, CA 95064, USA}
+
+% -------------------------------------------------------
+
 \begin{document}
@@
 
-\title{Atmospheric escape and star-planet-interaction in the HAT-P-67 b system}
+\title{A large leading tail of atmospheric escape in the HAT-P-67 b system}
 
-\author{TBD}
-\affiliation{TBD}
+\author[0000-0002-4020-3457]{Michael Gully-Santiago}
+\affil{\UTAustin}
+
+\author[0000-0003-2649-2288]{Brendan P. Bowler}
+\affiliation{\UTAustin}
+
+\author[0000-0001-9662-3496]{William D. Cochran}
+\affil{\MCDonald}
+\affil{\UTSpace}
+
+\author[0000-0002-1846-196X]{Aishwarya Ganesh}
+\affil{\UTAustin}
+
+\author[0000-0001-9811-568X]{Adam L. Kraus}
+\affil{\UTAustin}
+
+\author[0000-0001-9626-0613]{Daniel M. Krolikowski}
+\affil{\UTAustin}
+
+\author[0000-0003-2152-9248]{Jessica Luna}
+\affil{\UTAustin}
+
+\author[0000-0002-1417-8024]{Morgan MacLeod}
+\affiliation{\CFA}
+
+\author[0000-0001-9596-7983]{Suvrath Mahadevan}
+\affil{\PSUAA}
+\affil{\PSUCEHW}
+
+\author[0000-0002-4404-0456]{Caroline V. Morley}
+\affil{\UTAustin}
+
+\author[0000-0001-8720-5612]{Joe P.\ Ninan}
+\affil{\PSUAA}
+\affil{\PSUCEHW}
+
+\author[0000-0002-9584-6476]{Antonija Oklop{\v{c}}i{\'c}}
+\affil{\Amsterdam}
+
+\author[0000-0001-7409-5688]{Guðmundur Stefánsson}
+\affil{\Princeton}
+\affil{\RUSSELL}
+
+\author[0000-0001-6532-6755]{Quang H. Tran}
+\affiliation{\UTAustin}
+
+\author[0000-0002-3726-4881]{Zhoujian Zhang}\thanks{NASA Sagan Fellow}
+\affiliation{\UCSC}
+
+% and more...
+
+\collaboration{1}{HPF Helium Exospheres Collaboration}
 
@@
 
-Atmospheric escape appears to be a compulsory phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5-2.0~$R_\oplus$ planets in the California-Kepler survey \citep{2017AJ....154..109F}.
-The two physical mechanisms for this fleeting interlude between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G}.
+Atmospheric escape appears to be a compulsory phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5-2.0~$R_\oplus$ planets \citep{2017AJ....154..109F}.
+The two physical mechanisms for this rapid transition between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G}.
 Whatever the cause, some large fraction of planets must undergo atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations such as transiting planets.

### 2023-02-10 paper/paper1/ms.tex
Main insight of the paper, I think--- Ohmic Dissipation could fuel runaway Roche Lobe overflow we are seeing

@@
 %From: http://arxiv.org/format/1512.00483
-%\input{setup}
-%\input{mgs_setup}
 
@@
 \newcommand{\ljup}{\ensuremath{L_{\rm J}}}
-\newcommand{\teffjup}{\ensuremath{T_{eff,{\rm J}}}}
 \newcommand{\rhojup}{\ensuremath{\rho_{\rm J}}}
@@
 
-%\begin{figure}
-%    \includegraphics[width=\linewidth]{figures/Gaia_HAT_P_67_AB.png}
-%    \caption{HR Diagram of F star HAT-P-67A with its assumed M-dwarf main sequence companion HAT-P-67B.
-The density of stars comes from the \emph{Kepler} prime field estimated by \citet{2020AJ....160..108B} using \emph{Gaia DR2}.}
-%    \label{fig:gaiaHRD}
-%\end{figure}
-
 \subsection{TESS Light Curve}
@@
     ~~~$T_{14}$ (hours)  \dotfill    & $6.9888 \pm 0.046$ &  & 7.0636 & z \\
-    %~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ &  &  & z \\
-    %~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ &  &  & z \\
     ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ &  & 0.08231 & z \\
@@
     \dotfill    & $0.12_{-0.08}^{+0.12}$ &  & 0.45616 & z \\
-    %~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ &  &  & z \\
     \enddata
@@
 
-%\begin{figure}
-%    \includegraphics[width=\linewidth]{figures/HAT-P-67_2022_clean.png}
-%    \caption{HPF spectra of HAT-P-67 from the April/May 2022 campaign.  We see conspicuous absorption during and immediately preceding the transit, but not immediately after.}
-%    \label{fig:HPF2022campaign}
-%\end{figure}
-
 \begin{figure}
@@
 
+\subsection{The timescale of gas motion}
+The The density and ionization properties of this material only permit its observation during the 1.5 days immediately after its release.
+
 \section{Discussion} \label{secDiscuss}
+
+\subsection{Physical mechanisms for atmospheric escape}
+\object{HAT-P-67 b} exhibits both dramatic atmospheric escape and significant radius inflation.
+Ohmic dissipation stands out as a physical mechanism that could be responsible for both of these attributes.
+\citet{2011ApJ...738....1B} showed that ohmic heating acts to inflate hot Jupiters, with low mass hot Jupiters overflowing their Roche lobes and leading to evaporation on Gyr timescales.
+The ohmic heating scenario requires only on a modest planetary magnetic field and enough photoionization to ionize some modest fraction of neutral metals.
+The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K, well matched to HAT-P-67 b's $\sim$1900 K.
+The inflation timescale goes as (Eq.
+20 in \citet{2011ApJ...738....1B}):
+\begin{equation}
+    \tau_{\textit{infl}}\sim \left(\frac{0.01}{\epsilon} \right) \left(\frac{M}{M_{J}}\right)^2 \left(\frac{R_{J}}{R}\right)^3 \left(\frac{1500 \textrm{K}}{T_\mathrm{eff}}\right)^4 \textrm{Gyr}.
+\end{equation}
+
+\noindent yielding an incredibly short 5 Myr timescale for HAT-P-67 b, assuming a typical $\epsilon\sim0.01$.
+The order of magnitude of this inflation timescale is so fleetingly short that HAT-P-67 b must be firmly in the runaway stage of inflation, growing in surface area and proportionally fueling the ohmic dissipation mechanism.
+This runaway Roche lobe overflow would explain the large leading tail as the byproduct of such profound mass loss as to create an orbit-filling torus of material.
+
 %\subsection{Hot Spot Scenario}

### 2023-02-14 paper/paper1/ms.tex
Discussion sections

@@
 
-\subsection{Size and geometry of atmospheric escape}
+\subsection{Size and geometry of outflow}
 Helium absorption occurs predominantly before the planet is in-transit, indicating a \emph{leading} tail escaping the planet.
@@
 This runaway Roche lobe overflow would explain the large leading tail as the byproduct of such profound mass loss as to create an orbit-filling torus of material.
+
+\subsection{Cause for stellar modulation}
+The \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $p=4.8-5.2$ days, and with some sectors exhibiting lower amplitudes of modulation.
+The baseline interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8 day orbital period of planet b.
+The cause for such orbital and rotational synchronization would then ostensibly be tides.
+We examine the prospect of tides in the next subsection.
+
+Instead, the exteme mass loss and credibility of the ohmic diffusion model motivates the prospect of star-planet-interaction (SPI) that we consider now.
+In this scenario, the magnetic field of the planet permeates the space between the star and planet.
+Magnetic perturbations propagate via planetary magnetic fields with the Alfv\'en speed.
+The planet can interact with the star if the Alfv\'en speed exceeds the stellar wind speed controling the bulk motion of intervening medium.
+The magnetic field of the planet is not known, but the ohmic dissipation mechanism favors a limited range in the magnetic field strength: large enough to cause significant dissipative energy generation, but not too large to shut down motion entirely.
+\citet{2011ApJ...738....1B} estimate this range as between about 1-30 Gauss.
+With
+
+A few observations disfavor this interpretation.  First, the non-detection of variability in the \ion{Ca}{2} H and K lines and H~$\alpha$ lines.
+
+\subsection{Timescale for tidal synchronization}
 

### 2023-02-14 paper/paper1/ms.tex
anticipating a merge conflict

@@
 \subsection{Cause for stellar modulation}
-The \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $p=4.8-5.2$ days, and with some sectors exhibiting lower amplitudes of modulation.
-The baseline interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8 day orbital period of planet b.
+The \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $p=4.8-5.2$ days.
+Some sectors exhibit lower amplitudes.
+The conventional interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8 day orbital period of planet b.
 The cause for such orbital and rotational synchronization would then ostensibly be tides.
@@
 
-Instead, the exteme mass loss and credibility of the ohmic diffusion model motivates the prospect of star-planet-interaction (SPI) that we consider now.
+Alternatively, the exteme mass loss and credibility of the ohmic diffusion model motivates the prospect of Star Planet Magnetic Interaction (SPMI) that we consider now.
 In this scenario, the magnetic field of the planet permeates the space between the star and planet.
@@
 The planet can interact with the star if the Alfv\'en speed exceeds the stellar wind speed controling the bulk motion of intervening medium.
-The magnetic field of the planet is not known, but the ohmic dissipation mechanism favors a limited range in the magnetic field strength: large enough to cause significant dissipative energy generation, but not too large to shut down motion entirely.
-\citet{2011ApJ...738....1B} estimate this range as between about 1-30 Gauss.
-With
+The magnetic field of the planet is not known, but the ohmic dissipation mechanism favors a limited range in the magnetic field strength: large enough to cause significant dissipative energy generation, but not too large to shut down charged particle motion entirely.
+\citet{2011ApJ...738....1B} estimate this range as between about 1-30~G.
 

### 2023-02-14 paper/paper1/ms.tex
working on the same document on two computers asynchronously... oops

--- 2023-02-14 paper/paper1/ms.tex
@@
 \citet{2017AJ....153..211Z} estimated $v\sin{i}=35.8\pm1.1$ km/s, or lower ($v\sin{i}=30\pm1.1$ km/s) if macroturbulence was accounted for.
-We obtain a combined geometric constraint $2.85< R_\star \sin{i}  < 4.2 $ in units of $R_\odot$.
-The lower end of these constraints is consistent with  the 1-$\sigma$ range of $2.0 < R_\star < 3.2$ provided in \citet{2017AJ....153..211Z} from different isochrones and orbit fits, and assuming a near-equator-on orbital inclination.
+Assuming a stellar radius of 2.1-2.7 $R_\odot$, we obtain combined geometric constraint $3.0 < \frac{P_\mathrm{rot}}{\sin{i}}  < 4.5 $ days.
+This range is close to---but slightly lower than---the TESS modulation period.
 The Gaia \emph{DR3}-derived distance is 8\% greater than the \emph{Gaia} DR1 estimate used in \citet{2017AJ....153..211Z}; the revised larger distance would tend to increase the radius estimate by 16\% to match the observed SED in isochrone-fitting.
@@
 \citet{2011ApJ...738....1B} estimate this range as between about 1-30 Gauss.
-With
+Such a modest planetary field appears adequate to maintain a magnetosphere \citep{2019ApJ...881..136S}.
 
-A few observations disfavor this interpretation.  First, the non-detection of variability in the \ion{Ca}{2} H and K lines and H~$\alpha$ lines.
+The non-detection of variability in the \ion{Ca}{2} H and K lines and H~$\alpha$ lines appears to disfavor this SPMI interpretation.
 

### 2023-02-14 paper/paper1/ms.tex

--- 2023-02-14 paper/paper1/ms.tex
@@
 
-A few observations disfavor this interpretation.  First, the non-detection of variability in the \ion{Ca}{2} H and K lines and H~$\alpha$ lines.
+The non-detection of variability in the \ion{Ca}{2} H and K lines and H~$\alpha$ lines appears to disfavor this SPMI interpretation.
 

### 2023-02-14 paper/paper1/ms.tex
tiny prose

@@
 \subsection{TESS Light Curve}
-HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS][]{2014SPIE.9143E..20R} in Sectors 24, 26, 51, 52, 53 with 2-minute cadence, and in Sector 25 with 30-minute (FFI) cadence.
+HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS,][]{2014SPIE.9143E..20R} in Sectors 24, 26, 51, 52, 53 with 2-minute cadence, and in Sector 25 with 30-minute (FFI) cadence.
 The Sector 25 FFI data appeared malformed, possibly due to problems with pipeline CCD smear correction, and was disregarded.
@@
 
+\subsection{Keck HIRES}
+We retrieved 22 epochs of archival \emph{Keck HIRES} spectra via the Keck Observatory Archive (KOA).
+Of these, 19 were acquired through the iodine cell as reported by \citet{2017AJ....153..211Z}, providing RV orbit constraints.
+Only 8 were acquired with the B5 decker, with the rest through the C2 decker.
+The 14\arcsec slit height of the C2 decker appears to cause order overlap in \ion{Ca}{2} H and K lines, which contaminated the spectral extraction.
+The 3.5\farcs B2 deck   Most of the spectra were acquired with the C2 decker
+
 \subsection{Velocity substructure}
@@
 \begin{acknowledgements}
+
+    This material is based upon work supported by the National Aeronautics and Space Administration under Grant Number 80NSSC20K0257 for the XRP program issued through the Science Mission Directorate.
+
+    Based on observations obtained with the Hobby-Eberly Telescope (HET), which is a joint project of the University of Texas at Austin, the Pennsylvania State University, Ludwig-Maximillians-Universitaet Muenchen, and Georg-August Universitaet Goettingen.
+The HET is named in honor of its principal benefactors, William P.
+Hobby and Robert E.
+Eberly.
+
+    These results are based on observations obtained with the Habitable-zone Planet Finder Spectrograph on the HET.
+The HPF team acknowledges support from NSF grants AST-1006676, AST-1126413, AST-1310885, AST-1517592, AST-1310875, ATI 2009889, ATI-2009982, AST-2108512, and the NASA Astrobiology Institute (NNA09DA76A) in the pursuit of precision radial velocities in the NIR.
+The HPF team also acknowledges support from the Heising-Simons Foundation via grant 2017-0494.
+
+    This paper includes data collected with the TESS mission, obtained from the MAST data archive at the Space Telescope Science Institute (STScI).
+Funding for the TESS mission is provided by the NASA Explorer Program.
+STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5–26555.
+
+    This research has made use of the Keck Observatory Archive (KOA), which is operated by the W.
+M.
+Keck Observatory and the NASA Exoplanet Science Institute (NExScI), under contract with the National Aeronautics and Space Administration.
+
     This research has made use of NASA's Astrophysics Data System.

### 2023-02-15 paper/paper1/ms.tex
Add a new TESS overview figure

@@
 %From: http://arxiv.org/format/1512.00483
+
+\newcommand{\hatp}{\object{HAT-P-67}}
+\newcommand{\hatpb}{\object{HAT-P-67 b}}
 
@@
 \newcommand{\UCSC}{Department of Astronomy \& Astrophysics, University of California, Santa Cruz, 1156 High St, Santa Cruz, CA 95064, USA}
-
 % -------------------------------------------------------
@@
 
-\begin{deluxetable*}{lrrrccr}
+\begin{deluxetable}{lccrchr}
     \tablewidth{0pc}
@@
         \colhead{$N_\mathrm{exp}$} &
-        \colhead{$t_\mathrm{exp}$} &
+        \nocolhead{$t_\mathrm{exp}$} &
         \colhead{$\phi$}\\
@@
         \colhead{} &
-        \colhead{(s)} &
+        \nocolhead{(s)} &
         \colhead{$\in(-0.5, 0.5)$}
@@
     \enddata
-\end{deluxetable*}
+    \tablecomments{All exposure times were 308.85~s except for observations from 2020-07-21 to 2021-03-30, which were 511.20~s.}
+\end{deluxetable}
 
-\subsection{TESS Light Curve}
+\subsection{TESS Light Curves}
 HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS,][]{2014SPIE.9143E..20R} in Sectors 24, 26, 51, 52, 53 with 2-minute cadence, and in Sector 25 with 30-minute (FFI) cadence.
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.7\linewidth]{figures/TESS_HAT-P-67b_overview.png}
+    \caption{Overview of all available TESS Sectors showing 24 full or partial transits with 34 visits with HPF (vertical gray bars), 7 of which coincide with transits, and the rest sample out-of-transit phase.
+The 8 HPF visits between BTJD 2050 and 2690 are not shown.}
+    \label{fig:TESSoverview}
+\end{figure*}
+
 \section{Analysis}
@@
 \subsection{TESS Light Curve}
-
+Previously, \hatp transits had only been detected with \emph{HATNet} \citep{2004PASP..116..266B} and followed up with KeplerCam on the FLWO 1.2 m telescope.
+These ground-based photometers were not intended to measure, and did not detect, long term stellar variability signals.
+We therefore examined the \emph{TESS} lightcurves for out-of-transit photometric variability.
 \subsubsection{Revised exoplanet orbital parameters}
@@
 These properties are consistent with the previously reported values from \citet{2017AJ....153..211Z} and the updated ephemeris of \citet{2022ApJS..259...62I}.
+Figure \ref{fig:TESSoverview} shows an overview of all the TESS Sectors demarcated with the epochs of HPF measurements.
 Figure \ref{fig:transit} shows the best-fit orbit overlaid on the detrended TESS lightcurve.
@@
 However the higher-modulation sources exhibited 3-5$\times$ the level of modulation seen in \object{HAT-P-67 b}, whereas \object{HAT-P-67 b} was only about 0.5$\times$ above the median.
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/TESS_S26_trend.png}
-    \caption{Stellar lightcurve modulation observed in TESS Sector 26.
-The stellar surface pattern speed appears to have a slightly longer period than the exoplanet orbit, causing the transit to occur earlier in the phase of the modulation upon each orbit.}
-    \label{fig:TESSmodulation}
-\end{figure}
 
@@
 Of these, 19 were acquired through the iodine cell as reported by \citet{2017AJ....153..211Z}, providing RV orbit constraints.
-Only 8 were acquired with the B5 decker, with the rest through the C2 decker.
-The 14\arcsec slit height of the C2 decker appears to cause order overlap in \ion{Ca}{2} H and K lines, which contaminated the spectral extraction.
-The 3.5\farcs B2 deck   Most of the spectra were acquired with the C2 decker
+The 14\arcsec~ slit height of the C2 decker appears to cause order overlap in \ion{Ca}{2} H and K lines, which contaminated the spectral extraction for 14 of the 22 spectra.
+The 3\farcs5 B2 decker allowed the faithful extraction of this region for 6 spectra.
+The
 

### 2023-02-16 paper/paper1/ms.tex
Thinking about vsini and planet motion
some tiny prose

@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/best_fit_orbit.png}
-    \caption{Best fit orbit overlaid on the composite TESS lightcurve.  The 1 ppt TESS precision improves upon the ground-based detection and refining the orbital properties and ephemerides.}
-    \label{fig:transit}
-\end{figure}
-
 \subsubsection{Stellar rotation rate from periodogram analysis}
@@
 For a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius, revising the already-low density of HAT-P-67 even lower.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/best_fit_orbit.png}
+    \caption{Best fit orbit overlaid on the composite TESS lightcurve.}
+    \label{fig:transit}
+\end{figure}
 
@@
 The 14\arcsec~ slit height of the C2 decker appears to cause order overlap in \ion{Ca}{2} H and K lines, which contaminated the spectral extraction for 14 of the 22 spectra.
-The 3\farcs5 B2 decker allowed the faithful extraction of this region for 6 spectra.
-The
+The 3\farcs5 B2 decker allowed the faithful extraction of this region for 6 spectra, which exhibit no perceptible \ion{Ca}{2} H and K variability.
+The H~$\alpha$ region similarly exhibited no perceptible variability.
+The timing of these spectra coincidentally missed the orbital phases ($-0.3$ to $+0.03$) where we see the greatest \ion{He}{1} 10833 \AA~ absorption excess, leaving open the possibility that detectable H~$\alpha$ absorption could be present at more favorable orbital phases.
+New spectra or a more careful extraction of the archival C2 decker spectra would be needed.
 

### 2023-03-02 paper/paper1/ms.tex
paper section on 1D parker winds

@@
 
+\section{1D Parker wind models}
+The dramatic leading tail of atmospheric escape suggests an underlying 6-dimensionality (3 space dimensions and 3 velocity dimensions), coupled with stellar wind \citep{2022ApJ...926..226M} may be needed to depict the problem faithfully.
+MHD simulations are needed.
+Here we explore one-dimensional (1D) models, which offer ease of interpretation and rapid calculation.
+We employ the open-source \texttt{p-winds} code \citep{2022A&A...659A..62D}, which implements a transonic 1D Parker wind model with radiative transfer of the Helium 10830 triplet \citep{2018ApJ...855L..11O,2020A&A...636A..13L}.
+
+The predicted Helium ionization depends sensitively on the XUV flux \citep{2019ApJ...881..133O}.
+Few XUV measurements exist for F stars, with the F7IV-V \object[tau Boo]{$\tau$ Boo} serving as the closest analog \citep{2011A&A...532A...6S}.
+\hatp resides closer to the Kraft break than does \object[tau Boo]{$\tau$ Boo}, which may be associated with rapid changes in the stellar wind and other atmospheric changes leading to much lower XUV flux.
+We explore incident XUV fluxes of $100\times$ higher and lower than \object[tau Boo]{$\tau$ Boo} to gauge the sensitivity.
+Figure XX shows the range of conceivable XUV SEDs.
+
+Figure XX shows the 1D wind velocity and density computed with \texttt{p-winds}, assuming the baseline planet properties, a characteristic exosphere temperature of $T\sim10^4$ K, and including tidal gravity.
+
 \section{Discussion} \label{secDiscuss}

### 2023-03-03 paper/paper1/ms.tex
Adding some pwinds figures, to be revised

@@
 The predicted Helium ionization depends sensitively on the XUV flux \citep{2019ApJ...881..133O}.
-Few XUV measurements exist for F stars, with the F7IV-V \object[tau Boo]{$\tau$ Boo} serving as the closest analog \citep{2011A&A...532A...6S}.
-\hatp resides closer to the Kraft break than does \object[tau Boo]{$\tau$ Boo}, which may be associated with rapid changes in the stellar wind and other atmospheric changes leading to much lower XUV flux.
-We explore incident XUV fluxes of $100\times$ higher and lower than \object[tau Boo]{$\tau$ Boo} to gauge the sensitivity.
-Figure XX shows the range of conceivable XUV SEDs.
+Ideally we would have a measurement of the XUV spectrum of \hatp, but the limited facilities and distance of the source preclude these challenging observations.
+Instead we constructed panchromatic X-ray to visible SEDs by scaling and stitching together synthetic spectra to provide a range of high and low $L_X/L_\mathrm{bol}$.
+We chose a 6400 K PHOENIX \citep{husser13} solar metallicity photospheric specrtral template with $\log{g}=3.5$, scaled to the solid angle seen by \hatpb.
+The F7IV-V \object[tau Boo]{$\tau$ Boo} serves as the closest analog \citep{2011A&A...532A...6S} with synthetic x-ray coronal spectra available.
+But \hatp resides closer to the Kraft break than does \object[tau Boo]{$\tau$ Boo}.
+The move to hotter F stars may be associated with rapid changes in the stellar wind and other atmospheric changes leading to the prospect of much lower XUV flux.
+So it is not clear to what extent the \object[tau Boo]{$\tau$ Boo} x-ray spectrum resembles that of \hatp.
+We scaled the synthetic SED of \object[tau Boo]{$\tau$ Boo} retrieved from X-exoplanets \citep{2011A&A...532A...6S} so that the integral of ground-state ionizing photons ($\lambda<504\AA$) exhibited $L_X/L_\mathrm{bol} \in [10^{-7}, 10^{-5}]$.
+Figure \ref{fig:XUV} shows two conceivable SEDs with a high and low radiation hardness.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/XUV_flux_schematic.png}
+    \caption{Synthetic XUV radiation scenarios for \hatpb.  }
+    \label{fig:XUV}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/pwinds_1D_higXUV_t1p2Gyr.png}
+    \caption{Simulated 1D Parker wind model of Helium absorption in \hatpb.
+The spectrum was generated with a mass loss rate of $1.7\times10^{13}$ g/s, exosphere gas temperature of 9100 K, and with the high XUV spectrum ($L_x/L_\mathrm{bol}=10^{-4}$) shown in Figure \ref{fig:XUV}.
+The line depth and width broadly agrees with the width observed in HPF.}
+    \label{fig:pwinds}
+\end{figure}
 

### 2023-03-06 paper/paper1/ms.tex
Prose on 1D Parker wind models.

@@
 
-\subsection{Inapplicability of the Parker Wind model}
-As mentioned, most of the excess we see resides outside the Roche Lobe,  extended emissions
-
-\subsection{The timescale of gas motion}
-The The density and ionization properties of this material only permit its observation during the 1.5 days immediately after its release.
-
-\section{1D Parker wind models}
-The dramatic leading tail of atmospheric escape suggests an underlying 6-dimensionality (3 space dimensions and 3 velocity dimensions), coupled with stellar wind \citep{2022ApJ...926..226M} may be needed to depict the problem faithfully.
-MHD simulations are needed.
+\section{1D Parker wind models and mass loss rates}
+The dramatic leading tail of atmospheric escape suggests that more complicated 3D hydrodymaic simulations coupled with stellar wind \citep{2022ApJ...926..226M} may be needed to depict the geometry faithfully.
 Here we explore one-dimensional (1D) models, which offer ease of interpretation and rapid calculation.
@@
 Instead we constructed panchromatic X-ray to visible SEDs by scaling and stitching together synthetic spectra to provide a range of high and low $L_X/L_\mathrm{bol}$.
-We chose a 6400 K PHOENIX \citep{husser13} solar metallicity photospheric specrtral template with $\log{g}=3.5$, scaled to the solid angle seen by \hatpb.
-The F7IV-V \object[tau Boo]{$\tau$ Boo} serves as the closest analog \citep{2011A&A...532A...6S} with synthetic x-ray coronal spectra available.
-But \hatp resides closer to the Kraft break than does \object[tau Boo]{$\tau$ Boo}.
-The move to hotter F stars may be associated with rapid changes in the stellar wind and other atmospheric changes leading to the prospect of much lower XUV flux.
-So it is not clear to what extent the \object[tau Boo]{$\tau$ Boo} x-ray spectrum resembles that of \hatp.
+We chose a 6400 K PHOENIX \citep{husser13} solar metallicity photospheric spectral template with $\log{g}=3.5$, scaled to the solid angle seen by \hatpb.
+The F7IV-V \object[tau Boo]{$\tau$ Boo} serves as the closest analog with synthetic x-ray coronal spectra available \citep{2011A&A...532A...6S}.
+But \hatp resides closer to the Kraft break than does \object[tau Boo]{$\tau$ Boo}, and the move to hotter F stars may be associated with rapid changes in the stellar wind and other atmospheric changes leading to the prospect of much lower XUV luminosity for \hatp.
+So there remains significant uncertainty about the applicability of the \object[tau Boo]{$\tau$ Boo} x-ray spectrum to \hatp.
 We scaled the synthetic SED of \object[tau Boo]{$\tau$ Boo} retrieved from X-exoplanets \citep{2011A&A...532A...6S} so that the integral of ground-state ionizing photons ($\lambda<504\AA$) exhibited $L_X/L_\mathrm{bol} \in [10^{-7}, 10^{-5}]$.
@@
 \end{figure}
+
+The SED shows two key features.
+First the corona model does not extend all the way to 2600 $\AA$ photons capable of ionizing out of the 2 $^3$S Helium metastable state.
+This apparent deficit probably does not matter because the F spectral type obtains most of its NUV photons ($\lambda\sim2600\AA$) from the Wein side of the photospheric spectrum, so the hardness of the radiation stems mostly from the assumptions of the corona flux level.
+The wavelength-dependent cross section for absorption (not shown) is largest just blueward of the ionization thresholds, so the differences in the spectrum between 504 $\AA$ and 1000 $\AA$ have relatively little impact on the overall ionization out of the metastable state.
+
+Equipped with these three SEDs of differing radiation hardness, we explored different mass loss rates and exosphere temperatures.
+Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 7\times10^{13}$ g/s, and $T_0=9100$~K.
+The model spectrum exhibits approximately the same line width and depth as our HPF observations, making it a plausible solution.
+The model-dependent line profile (\emph{i.e.
+width and depth}) is degenerate with XUV flux, $\dot{M}$, and $T_0$.
+We were able to replicate the line profile with mass loss rates as high as \censorbox{X}, assuming \censorbox{Y}, or as low as \censorbox{Z} assuming \censorbox{W}.
 
@@
 \citet{2011ApJ...738....1B} showed that ohmic heating acts to inflate hot Jupiters, with low mass hot Jupiters overflowing their Roche lobes and leading to evaporation on Gyr timescales.
-The ohmic heating scenario requires only on a modest planetary magnetic field and enough photoionization to ionize some modest fraction of neutral metals.
-The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K, well matched to HAT-P-67 b's $\sim$1900 K.
-The inflation timescale goes as (Eq.
+The Ohmic heating scenario requires only on a modest planetary magnetic field ($\sim$1 G) and enough photoionization to ionize some modest fraction of neutral metals.
+The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K \citep{2011ApJ...738....1B}, well matched to HAT-P-67 b's $\sim$1900 K.
+A plausible scaling law relationship approximate to an order-of-magnitude predicts an inflation timescales (Eq.
 20 in \citet{2011ApJ...738....1B}):
@@
 
-\noindent yielding an incredibly short 5 Myr timescale for HAT-P-67 b, assuming a typical $\epsilon\sim0.01$.
-The order of magnitude of this inflation timescale is so fleetingly short that HAT-P-67 b must be firmly in the runaway stage of inflation, growing in surface area and proportionally fueling the ohmic dissipation mechanism.
-This runaway Roche lobe overflow would explain the large leading tail as the byproduct of such profound mass loss as to create an orbit-filling torus of material.
+\noindent yielding an incredibly short 5 Myr timescale for \hatpb, assuming a typical $\epsilon\sim0.01$.
+The order of magnitude of this inflation timescale is so fleetingly short that \hatpb must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
+
+\subsection{Photoevaporation}
+The prospect of Ohmic dissipation does not preclude the possibility that other mass loss drivers are at play.
+Photoevaporation should simultaneously drive heating of the upper layers in the atmosphere, reinforcing the mass loss associated with Ohmic dissipation.
+It is not clear which effect predominates.
 
@@
 
-\subsection{Timescale for tidal synchronization}
+%\subsection{Timescale for tidal synchronization}
 
@@
     \texttt{jupyter} \citep{Kluyver2016jupyter},
+    \texttt{p-winds}, \citep{2022A&A...659A..62D}
 }

### 2023-03-06 paper/paper1/ms.tex
text of constraining the mass loss rate

@@
 
-\section{1D Parker wind models and mass loss rates}
+\subsection{1D Parker wind models and mass loss rates}\label{pwinds}
 The dramatic leading tail of atmospheric escape suggests that more complicated 3D hydrodymaic simulations coupled with stellar wind \citep{2022ApJ...926..226M} may be needed to depict the geometry faithfully.
@@
 Equipped with these three SEDs of differing radiation hardness, we explored different mass loss rates and exosphere temperatures.
-Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 7\times10^{13}$ g/s, and $T_0=9100$~K.
-The model spectrum exhibits approximately the same line width and depth as our HPF observations, making it a plausible solution.
-The model-dependent line profile (\emph{i.e.
-width and depth}) is degenerate with XUV flux, $\dot{M}$, and $T_0$.
-We were able to replicate the line profile with mass loss rates as high as \censorbox{X}, assuming \censorbox{Y}, or as low as \censorbox{Z} assuming \censorbox{W}.
+Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 7\times10^{13}$ g/s, and $T_0=9100$~K, with the high XUV spectrum ($L_x/L_\mathrm{bol}=10^{-4}$).
+The model spectrum exhibits approximately the same line width and depth as our HPF observations, making it a conceivable solution.
+
+At least a few shortcomings limit the applicability of this 1D Parker wind model.
+First, the model-dependent line profile (\emph{i.e.
+width and depth}) is degenerate with XUV flux, $\dot{M}$, and $T_0$, and so a range of these parameters can be fine-tuned to obtain a large range of mass loss rates consistent with the data and our limited understanding of the XUV flux.
+Second, the 1D model breaks down when attempting to explain the inherently 3D leading tail geometry.
+We discuss these two and other model-dependent interpretations in Section \ref{secDiscuss}.
 
@@
 
-Figure XX shows the 1D wind velocity and density computed with \texttt{p-winds}, assuming the baseline planet properties, a characteristic exosphere temperature of $T\sim10^4$ K, and including tidal gravity.
-
 \section{Discussion} \label{secDiscuss}
 
-\subsection{Physical mechanisms for atmospheric escape}
+\subsection{Ohmic Dissipation and runaway escape}
 \object{HAT-P-67 b} exhibits both dramatic atmospheric escape and significant radius inflation.
@@
     \tau_{\textit{infl}}\sim \left(\frac{0.01}{\epsilon} \right) \left(\frac{M}{M_{J}}\right)^2 \left(\frac{R_{J}}{R}\right)^3 \left(\frac{1500 \textrm{K}}{T_\mathrm{eff}}\right)^4 \textrm{Gyr}.
+\label{eqInflate}
 \end{equation}
@@
 The order of magnitude of this inflation timescale is so fleetingly short that \hatpb must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
+
+\subsection{Constraining mass loss rate}
+A 5 Myr inflation timescale would imply an instantaneous $\dot{M}_\mathrm{infl}\sim10^{15}$ g/s, about 50 times larger than the 1D Parker wind model mass loss rate of $\dot{M}_\mathrm{1D}\sim2\times10^{13}$.
+Here we enumerate all of uncertainties that go into assessing mass loss rates to show that some in-between mass loss rate may be plausible.
+
+First, the scaling law arguments that produced Equation \ref{eqInflate} (Eq.
+20 of \citet{2011ApJ...738....1B}) were only proposed as order of magnitude estimates not to be taken too faithfully.
+So a $10\times$ higher inflation timescale of 50 Myr would yield $\dot{M}_\mathrm{infl}\sim10^{14}$ g/s, still a very large mass loss rate, but only a factor of 5 away from the baseline 1D model.
+Order unity uncertainties in the Ohmic dissipation efficiency $\epsilon$ may also contribute.
+
+As mentioned in Section \ref{pwinds}, inferring the mass loss rate from observations is strongly model dependent, as seen in \censorbox{cite e.g.
+S.V.
+papers}.
+In particular, the uncertain XUV-to-NUV flux ratio introduces a large degeneracy in
+
+the observations indicate a 3D geometry of the outflow-- a preference for escaping material to overtake the planet along the orbital path.  Once the The 1D Parker wind models for high mass loss rates
+During the moment of the planet transit midcenter ($\phi=0.0$), the subsolar point on the planet dayside will have material be preferrentially removed from the line-of-sight
 

### 2023-03-06 paper/paper1/ms.tex
experimenting with p-winds to explore mass loss rates

@@
 papers}.
-In particular, the uncertain XUV-to-NUV flux ratio introduces a large degeneracy in
+The XUV flux, exosphere temperature $T_0$, and $\dot{M}$ are all at least partially degenerate.
+In particular, the uncertain XUV-to-NUV flux ratio confounds the interpretation of the observed Helium signal.
+Even the ``high XUV'' scenario in Figure \ref{fig:XUV} does not have enough ground-state ionizing photons to penetrate to within 5 $R_p$ of the planet surface.
+This means that at best only 1 in $10^{6}$ Helium atoms participate in the observability of the Helium metastable triplet lines in the baseline 1D Parker wind model.
+Turning down the XUV flux makes the signal even less observable.
+A larger mass loss rate would be needed to explain the same observed HPF Helium absorption, if say only 1 in $10^{7}$ helium atoms are populating the metastable state.
+
+Finally, the entire premise of the Parker wind model may be unjustified due to the inherently 3D geometry of the leading tail.
+In the next section we critically examine the assumptions in the 1D Parker wind model.
+
+\subsection{Critical examination of the Parker Wind model}
+An even more existential limit arises when we consider the assumptions of the isothermal Parker wind model, and the extreme geometry of \hatpb.
+Figure \ref{fig:murrayClaySchematic} shows a schematic modeled after Figure 8 from \citet{2009ApJ...693...23M}.
+The point at which the gas velocity exceeds the sound speed, the so-called sonic point, resides at 1.2 $R_p$, a mere $\sim9$ atmospheric scale heights from the planet surface.
+The smallness of this radius can be understood from the significant effect of tidal gravity and the .
+The pressure level here would be in the fractions of a millibar level, with an atmospheric temperature $\le T_\mathrm{eq}\sim10^3$~K and not yet the $T\sim10^4$~K exosphere range.
+Depending on the mass loss rate, the transition from primarily neutral to primarily ionized plasma may occur outside or inside the sonic radius.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/murray_clay_schematic_v0p1.png}
+    \caption{Schematic of the relevant length scales in a stratified atmosphere, modeled after Figure 8 from \citet{2009ApJ...693...23M}.
+The sonic point resides at a mere 2 atmospheric scale heights, and well below the photoionization level of Hydrogen, raising the possibility that the supersonic flow begins neutral and becomes ionized later on.}
+    \label{fig:murrayClaySchematic}
+\end{figure}
+
+Eventually, for very large mass loss rates, the width of the line begins to grow.
 

### 2023-03-07 paper/paper1/ms.tex
Some text on Orbital shear

@@
 
+\subsection{Causes for the leading tail}
+Several physical phenomena could give rise to a leading tail geometry.  Here we explore two leading candidates: orbital shear and stellar wind confinement.
+
+Figure \ref{fig:KeplerianShear} shows an illustration of Keplerian shear adapted to the system properties of \hatpb.
+In this scenario, the wind launches primarily from the dayside, with relatively little or no wind launched from the nightside.
+The wind initially launches radially from the planet, with the strongest wind located near the sub-stellar point, the line connecting the planet to star along the vertical axis in the figure.
+Inefficient heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemi-spherical shape, more like a bulb or torpedo.
+The gas increasingly experiences the star's Keplerian potential past the Roche lobe, accelerating in the direction of orbital motion, $+x$.
+The accelerating column eventually overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.
+
+Stellar wind confinement...
+
+\begin{figure}
+    \includegraphics[width=0.8\linewidth]{figures/KeplerianShear_v0p3.png}
+    \caption{Schematic of Keplerian orbital shear.
+Locations outside the Roche lobe experience orbital shear from the Keplerian potential.
+A wind launched primarily from the dayside will tend to form a leading tail.}
+    \label{fig:KeplerianShear}
+\end{figure}
+
 \subsection{Critical examination of the Parker Wind model}
+
+\begin{figure*}[t]
+    \includegraphics[width=\linewidth]{figures/murray_clay_schematic_v0p2.png}
+    \caption{Schematic of the relevant length scales in a stratified atmosphere, modeled after Figure 8 from \citet{2009ApJ...693...23M}.
+The sonic point resides at a mere 2 atmospheric scale heights, and well below the photoionization level of Hydrogen, raising the possibility that the supersonic flow begins neutral and becomes ionized later on.}
+    \label{fig:murrayClaySchematic}
+\end{figure*}
+
 An even more existential limit arises when we consider the assumptions of the isothermal Parker wind model, and the extreme geometry of \hatpb.
@@
 Depending on the mass loss rate, the transition from primarily neutral to primarily ionized plasma may occur outside or inside the sonic radius.
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/murray_clay_schematic_v0p1.png}
-    \caption{Schematic of the relevant length scales in a stratified atmosphere, modeled after Figure 8 from \citet{2009ApJ...693...23M}.
-The sonic point resides at a mere 2 atmospheric scale heights, and well below the photoionization level of Hydrogen, raising the possibility that the supersonic flow begins neutral and becomes ionized later on.}
-    \label{fig:murrayClaySchematic}
-\end{figure}
-
-Eventually, for very large mass loss rates, the width of the line begins to grow.
-
-the observations indicate a 3D geometry of the outflow-- a preference for escaping material to overtake the planet along the orbital path.  Once the The 1D Parker wind models for high mass loss rates
-During the moment of the planet transit midcenter ($\phi=0.0$), the subsolar point on the planet dayside will have material be preferrentially removed from the line-of-sight
 

### 2023-03-07 paper/paper1/ms.tex
Orbital shear versus stellar wind confinement, remove junk text

@@
 
-Stellar wind confinement...
-
 \begin{figure}
@@
 \end{figure}
+
+Stellar wind confinement arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.
+A trailing tail may be present, but would not undergo the same boost in density, and would be rapidly carried away by the stellar wind.
+This asymmetry could yield the appearance of a leading tail even if mass loss proceeds isotropically, or the asymmetry could be reinforced by an additional dayside/nightside asymmetry.
+Examples of this asymmetry can be seen in 3D MHD modeling of WASP 107~b \citep{2022ApJ...926..226M}.
 
@@
 \end{figure*}
-
-An even more existential limit arises when we consider the assumptions of the isothermal Parker wind model, and the extreme geometry of \hatpb.
-Figure \ref{fig:murrayClaySchematic} shows a schematic modeled after Figure 8 from \citet{2009ApJ...693...23M}.
-The point at which the gas velocity exceeds the sound speed, the so-called sonic point, resides at 1.2 $R_p$, a mere $\sim9$ atmospheric scale heights from the planet surface.
-The smallness of this radius can be understood from the significant effect of tidal gravity and the .
-The pressure level here would be in the fractions of a millibar level, with an atmospheric temperature $\le T_\mathrm{eq}\sim10^3$~K and not yet the $T\sim10^4$~K exosphere range.
-Depending on the mass loss rate, the transition from primarily neutral to primarily ionized plasma may occur outside or inside the sonic radius.
 

### 2023-03-07 paper/paper1/ms.tex
Move text around
Ohmic Dissipation as the cause of lack of inflated sub Saturns

@@
 
+\subsection{Photoevaporation}
+The prospect of Ohmic dissipation does not preclude the possibility that other mass loss drivers are at play.
+Photoevaporation should simultaneously drive heating of the upper layers in the atmosphere, reinforcing the mass loss associated with Ohmic dissipation.
+It is not clear which effect predominates.
+
 \subsection{Constraining mass loss rate}
@@
 
-\subsection{Critical examination of the Parker Wind model}
-
 \begin{figure*}[t]
@@
 
-\subsection{Photoevaporation}
-The prospect of Ohmic dissipation does not preclude the possibility that other mass loss drivers are at play.
-Photoevaporation should simultaneously drive heating of the upper layers in the atmosphere, reinforcing the mass loss associated with Ohmic dissipation.
-It is not clear which effect predominates.
+\subsection{The Ohmic Dissipation Cliff: Evaporative annihilation as the cause of a lack of sub-Saturns}
+The Ohmic dissipation mechanism predicts a rapid inflation timescale leading to the complete evaporation of hot Saturns.
+The Ohmic dissipation mechanism made two key observable predictions.
+The Ohmic dissipation heating should become less efficient as irradiation increased past an equilibrium temperature of about 2000 K.
+Second, hot Saturns should should runaway evaporation, whereas hot Jupiters should reach equilibrium---albeit inflated---radii after Gyr timescales.
+Both of these outcomes predated data that could adequately validate them, and these outcomes differ from the behavior of other heating mechanisms, such as photoevaporation or tides.
+
+\citet{2018AJ....155..214T} statistically favored Ohmic dissipation based on evidence for a turnover in the heating efficiency of hot Jupiters in a sample of 281 Giant planets.
+Futhermore, \citet{2018AJ....155..214T} also highlighted the lack of inflated sub-Saturns as an anomaly: the observational capability exist to detect such sources in large numbers and yet they were not found.
+
+This dearth of hot-Saturns has persisted into the \emph{TESS} era.
+Figure XX highlights the region of highly irradiated close-in planets with $N=$\censor{x} planets accessed through the NASA Exoplanet Archive \censor{cite NExScI}.
+\hatpb occupies a relative void in this region.
+
+The observation that \hatpb---the only hot Saturn searched for atmospheric escape to date---exhibits mass loss indicative of a terminal fate leads us to a natural explanation for the dearth of inflated hot Saturns.
+The inflationary lifetime of this class is so short that observing planets of this class is unlikely.
+\hatpb appears to be one of the rare planets that we happen to catch a glimpse of before it has been completely annihilated.
+
+We therefore attribute this cliff in the $m_p$ vs $R_p$ diagram to Ohmic dissipation.
+\citet{2018AJ....155..214T} emphasized the positive feedback loop as a cause for the lack of sub-Saturns, and noted an alternative interpretation-- mass-dependent migration segregation.
+While both scenarios are conceivable, the evidence of strong evaporation of \hatpb favors the evaporation scenario.
+Futhermore, the runaway evaporation of hot-Saturns was naturally predicted by the Ohmic dissipation mechanism, whereas mass-dependent migration has only been developed as a post-diction.
+
+We predict that the few other inflated hot-Saturn \hatpb-analogs should also show evidence for atmospheric escape.
+These sources make excellent targets for \ion{He}{1} 10830 observations, and other atmospheric escape diagnostics.
+The key figure-of-merit can be distilled to $\tau_\mathrm{infl}$, and ignoring the $\epsilon$ term.
+Following \censor{Kempton} et al we define a Helium Spectroscopy Metric (HSM) defined as...
 

### 2023-03-09 paper/paper1/ms.tex
Add the Thorngren & Fortney reference
Ignore the Murray-Clay schematic, we probably will not use it

@@
 
-\begin{figure*}[t]
-    \includegraphics[width=\linewidth]{figures/murray_clay_schematic_v0p2.png}
-    \caption{Schematic of the relevant length scales in a stratified atmosphere, modeled after Figure 8 from \citet{2009ApJ...693...23M}.
+%\begin{figure*}[t]
+%    \includegraphics[width=\linewidth]{figures/murray_clay_schematic_v0p2.png}
+%    \caption{Schematic of the relevant length scales in a stratified atmosphere, modeled after Figure 8 from \citet{2009ApJ...693...23M}.
 The sonic point resides at a mere 2 atmospheric scale heights, and well below the photoionization level of Hydrogen, raising the possibility that the supersonic flow begins neutral and becomes ionized later on.}
-    \label{fig:murrayClaySchematic}
-\end{figure*}
+%    \label{fig:murrayClaySchematic}
+%\end{figure*}
 

### 2023-03-09 paper/paper1/ms.tex
Revising the introduction

@@
 Atmospheric escape appears to be a compulsory phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5-2.0~$R_\oplus$ planets \citep{2017AJ....154..109F}.
-The two physical mechanisms for this rapid transition between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G}.
+The leading candidate physical mechanisms for this rapid transition between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G}.
 Whatever the cause, some large fraction of planets must undergo atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations such as transiting planets.
+At least 28 examples have been seen to date \citep{2022arXiv221116243D}.
 
-Enough uncertainty exists in the tradeoffs among physical mechanisms, system ages, and timescales to make it unclear whether any given exoplanet will be actively undergoing atmospheric escape.
-The most favorable traits may include close-in, low surface gravity exoplanets within a strategically chosen radius range.
-The 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of descending to their final state.
-Alternatively, inflated Hot Jupiters could be so dramatically ablated as to overcome the somewhat stronger potential well.
-Significant gains in understanding can therefore be expected from observational studies sampling the extremes of the exoplanet distribution.
+Uncertainty in system ages, evaporation timescales, and dominating physical mechanisms, degrade our ability to foretell if any given planet will exhibit ongoing signature of atmospheric escape.
+Episodic stellar wind gusts and other forms of cosmic variance could also subdue atmospheric escape, even when we expect it.
+The 48 published non-detections of atmospheric escape \citep{2022arXiv221116243D} encode these natural whims in a way that we have not yet disentangled.
+Nevertheless, we can boost our chances of witnessing active and significant atmospheric escape by tailoring our survey to sources with our notions of favorable traits.
+These traits may include close-in, low surface gravity exoplanets within a strategically chosen radius range.
+The 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of eroding to their final rocky state.
+Alternatively, inflated Hot Jupiters could be so dramatically ablated as to overcome the somewhat stronger potential well and facilitating hydrodynamic flows.
+Significant gains in understanding can therefore be expected from observational studies sampling the extremes of the exoplanet distributions.
 
-Candidates for detection should be observable in one of three atomic lines.
+Candidates for detection should usually be observable in one of three atomic lines.
 Ly~$\alpha$, \ion{He}{1} 10833 \AA, and H~$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}.
 Ly $\alpha$ can exhibit strong atmospheric escape signals, but instellar medium \ion{H}{1} absorption censors its low-velocity linecore.
-\ion{He}{1} 10833 \AA~ offers significant advantages over Ly~$\alpha$, and has resulted in 8 systems with detections to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
+\ion{He}{1} 10833 \AA~ offers significant advantages over Ly~$\alpha$, and has resulted in at least 14 systems with detections to date, including \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
 These detections exhibit a range of signal strengths, as high as 10$\%$ transit depths.

### 2023-03-09 paper/paper1/ms.tex
Add text about Ohmic dissipation and inflated hot Saturns to the introduction

@@
 
-Uncertainty in system ages, evaporation timescales, and dominating physical mechanisms, degrade our ability to foretell if any given planet will exhibit ongoing signature of atmospheric escape.
-Episodic stellar wind gusts and other forms of cosmic variance could also subdue atmospheric escape, even when we expect it.
-The 48 published non-detections of atmospheric escape \citep{2022arXiv221116243D} encode these natural whims in a way that we have not yet disentangled.
-Nevertheless, we can boost our chances of witnessing active and significant atmospheric escape by tailoring our survey to sources with our notions of favorable traits.
+Uncertainty in system ages, evaporation timescales, and dominating physical mechanisms, degrade our ability to foretell if any given planet will exhibit ongoing signatures of atmospheric escape.
+Episodic stellar wind gusts and other forms of cosmic variance could also subdue atmospheric escape, even where we expect it most.
+The 48 published non-detections of atmospheric escape \citep{2022arXiv221116243D} must encode these natural whims in a way that we have not yet disentangled.
+Nevertheless, we can boost our chances of witnessing active and significant atmospheric escape by targeting sources with favorable traits.
 These traits may include close-in, low surface gravity exoplanets within a strategically chosen radius range.
@@
 
-Candidates for detection should usually be observable in one of three atomic lines.
-Ly~$\alpha$, \ion{He}{1} 10833 \AA, and H~$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}.
-Ly $\alpha$ can exhibit strong atmospheric escape signals, but instellar medium \ion{H}{1} absorption censors its low-velocity linecore.
-\ion{He}{1} 10833 \AA~ offers significant advantages over Ly~$\alpha$, and has resulted in at least 14 systems with detections to date, including \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
-These detections exhibit a range of signal strengths, as high as 10$\%$ transit depths.
-Measurements at high spectral resolution have been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.
+Inflated hot Saturns stand out as an especially extreme category that should exhibit mass loss.
+Their low gravitational potentials should let go of their atmospheres more easily than their more steadfast Hot Jupiter counterparts.
+Their lower gravity yields larger atmospheric scale heights making them easier to detect in transmission spectroscopy.
+And their large transit depths and short periods should make them easy to detect in large numbers, like Hot Jupiters.
+
+But inflated hot Saturns are rare \citep{2018AJ....155..214T}.
+The cause for their underabundance remains an open question, with two leading candidate explanations.
+Tidal migration mechanisms may be mass-dependent in such a way as to proceed efficiently for Hot Jupiters, but inefficiently for the lower mass hot Saturns.
+In this scenario, sub-Saturn mass planets never make it to the close-in orbital separations that would lead to their conditions needed for inflation in the first place.
+
+Alternatively---and most consequentially for atmospheric escape---another explanation may prevail.
+Inflated hot Saturns may effectively migrate to close-in orbital separations, but once they arrive the intense irradation overheats the planet, leading to runaway inflation and ultimately complete disintegration.
+The atmosphere overflows its Roche lobe, the potential well softens, the Roche lobe shrinks, and a positive feedback loop ensues.
+The mass loss increases expoentially.
+In this scenario, the inflationary half-life may be so short as to lead to a low probability of observing members in the class, and hence the apparent lack of inflated sub-Saturns.
+
+\citet{2011ApJ...738....1B} predicted runaway inflation of hot Saturns as a consequence of the Ohmic dissipation mechanism.  Ohmic dissipation
+
+\citet{2018AJ....155..214T} stated these two explanations for the lack of sub-Saturns, without a way to distinguish which one was at play.
+
+This inflationary scenario would predict a profound mass loss rate for inflated hot Saturns.  If the planet is inflated, it is already in the runaway mass loss phase.
 
@@
 These and other reasons make \object{HAT-P-67 b} a predestined laboratory for measuring the properties of exospheres at the extreme.
+
+Candidates for detection should usually be observable in one of three atomic lines.
+Ly~$\alpha$, \ion{He}{1} 10833 \AA, and H~$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}.
+Ly $\alpha$ can exhibit strong atmospheric escape signals, but instellar medium \ion{H}{1} absorption censors its low-velocity linecore.
+\ion{He}{1} 10833 \AA~ offers significant advantages over Ly~$\alpha$, and has resulted in at least 14 systems with detections to date, including \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
+These detections exhibit a range of signal strengths, as high as 10$\%$ transit depths.
+Measurements at high spectral resolution have been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}
 

### 2023-03-09 paper/paper1/ms.tex
Introduction threads the story now

@@
 These traits may include close-in, low surface gravity exoplanets within a strategically chosen radius range.
-The 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of eroding to their final rocky state.
-Alternatively, inflated Hot Jupiters could be so dramatically ablated as to overcome the somewhat stronger potential well and facilitating hydrodynamic flows.
-Significant gains in understanding can therefore be expected from observational studies sampling the extremes of the exoplanet distributions.
+For example, the 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of eroding to their final rocky state.
 
 Inflated hot Saturns stand out as an especially extreme category that should exhibit mass loss.
-Their low gravitational potentials should let go of their atmospheres more easily than their more steadfast Hot Jupiter counterparts.
+Their low gravitational potentials should let go of their atmospheres more readily than their steadfast Hot Jupiter counterparts.
 Their lower gravity yields larger atmospheric scale heights making them easier to detect in transmission spectroscopy.
@@
 Alternatively---and most consequentially for atmospheric escape---another explanation may prevail.
-Inflated hot Saturns may effectively migrate to close-in orbital separations, but once they arrive the intense irradation overheats the planet, leading to runaway inflation and ultimately complete disintegration.
-The atmosphere overflows its Roche lobe, the potential well softens, the Roche lobe shrinks, and a positive feedback loop ensues.
-The mass loss increases expoentially.
+Inflated hot Saturns may effectively migrate to close-in orbital separations, but once they arrive, the intense irradation overheats the planet.
+This heating leads to runaway inflation and ultimately complete disintegration.
 In this scenario, the inflationary half-life may be so short as to lead to a low probability of observing members in the class, and hence the apparent lack of inflated sub-Saturns.
 
-\citet{2011ApJ...738....1B} predicted runaway inflation of hot Saturns as a consequence of the Ohmic dissipation mechanism.  Ohmic dissipation
+\citet{2011ApJ...738....1B} predicted runaway inflation of hot Saturns as a consequence of the Ohmic dissipation mechanism.
+Here, a lightly ionized atmosphere experiences drag in a planetary magnetic field, weakly coupling the stellar incident energy into the planetary interior.
+\citet{2018AJ....155..214T} proposed these two explanations for the lack of sub-Saturns, while statistically favoring Ohmic dissipation as the mechanism responsible for inflating Hot Jupiters.
+Ohmic dissipation does not preclude the existence and role of other heating mechanisms---such as photoevaporation and tidal heating---but it does stand out has having made these predictions before data were widely available to test these predictions.
 
-\citet{2018AJ....155..214T} stated these two explanations for the lack of sub-Saturns, without a way to distinguish which one was at play.
+The runaway inflation scenario could yield a profound mass loss rate for inflated hot Saturns, possibly much larger than we have seen in previous systems.
+The ability to detect that mass loss hinges on their observability in spectral tracers.
+Ly~$\alpha$, \ion{He}{1} 10833 \AA, and H~$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}, but each of these has its own limitations.
+Ly $\alpha$ can suffer from instellar medium \ion{H}{1} absorption censoring its low-velocity linecore, for example.
+Here we focus on \ion{He}{1} 10833 \AA~, which offers some advantages over Ly~$\alpha$.
+In particular, metastable Helium's ability to be observed at high spectral resolution from the ground has been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.
+\ion{H}{1} has resulted in at least 14 systems with detections, including \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
+To date, no inflated hot Saturns appear to have been examined, neither in Helium nor other tracers \emph{c.f.} Figure \censorbox{figure X}.
 
-This inflationary scenario would predict a profound mass loss rate for inflated hot Saturns.  If the planet is inflated, it is already in the runaway mass loss phase.
-
-Here we present a study of the exosphere of \object{HAT-P-67 b}, an inflated hot Saturn orbiting an F type sub-giant\footnote{The system appears to consist of a binary with an M dwarf companion HAT-P-67B separated on-sky by $9\farcs0$ \citep{2019MNRAS.490.5088M}.
-The IAU naming convention would demand HAT-P-67Ab.
-We simply drop the A designation for notational simplicity, since the wide companion will not factor into our analysis.} at a distance of 0.06 AU \citep{2017AJ....153..211Z}.
+Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, an inflated hot Saturn orbiting an F type sub-giant at an orbital separation of 0.06 AU \citep{2017AJ....153..211Z}.
 The strong insolation combined with \object{HAT-P-67 b}'s low surface gravity makes it an excellent candidate for strong atmospheric mass loss.
-It orbits an evolved star, opening the prospect for the planet's insolation to have increased over time as the star grew.
-These and other reasons make \object{HAT-P-67 b} a predestined laboratory for measuring the properties of exospheres at the extreme.
-
-Candidates for detection should usually be observable in one of three atomic lines.
-Ly~$\alpha$, \ion{He}{1} 10833 \AA, and H~$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}.
-Ly $\alpha$ can exhibit strong atmospheric escape signals, but instellar medium \ion{H}{1} absorption censors its low-velocity linecore.
-\ion{He}{1} 10833 \AA~ offers significant advantages over Ly~$\alpha$, and has resulted in at least 14 systems with detections to date, including \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
-These detections exhibit a range of signal strengths, as high as 10$\%$ transit depths.
-Measurements at high spectral resolution have been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}
+It orbits an evolved star, opening the prospect for ``re-inflation'' as the planet's insolation increased over time as the star expanded.
+Its status as a rare inflated Hot Saturn make \object{HAT-P-67 b} a promising laboratory for testing the inflationary predictions of the Ohmic dissipation mechanism.
 
@@
 \subsection{Gaia DR3}
+The stellar system consists of a binary with an M dwarf companion HAT-P-67B separated on-sky by $9\farcs0$ \citep{2019MNRAS.490.5088M}.
+The IAU naming convention would demand HAT-P-67A\emph{b} to refer to the planet.
 HAT-P-67A (\emph{Gaia DR3 1358614983131339392}) has a parallax of $2.69\pm0.01$ mas in \emph{Gaia} DR3, placing it at about 372$\pm$1.4 pc, slightly farther than previously estimated by \citet{2017AJ....153..211Z} using Gaia DR1.
@@
 Its wide companion HAT-P-67B (\emph{Gaia DR3 1358614983131339904}) \citep{2019MNRAS.490.5088M} has statistically identical parallax ($2.58\pm0.05$) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
+Hereafter, we simply drop the A designation for notational simplicity, since the wide companion will not factor into our analysis.
 

### 2023-03-09 paper/paper1/ms.tex
Gotta run because it might rain and I biked today

@@
 
-\newcommand{\hatp}{\object{HAT-P-67}}
+\newcommand{\hatp}{\object{HAT-P-67}~}
 \newcommand{\hatpb}{\object{HAT-P-67 b}}
@@
 Nevertheless, we can boost our chances of witnessing active and significant atmospheric escape by targeting sources with favorable traits.
-These traits may include close-in, low surface gravity exoplanets within a strategically chosen radius range.
-For example, the 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of eroding to their final rocky state.
+These intrinsic or extrinsic factors may include close proximity to host star, low surface gravity, and high energy incident radiation.
+For example, the small planet radius gap between 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of eroding to their final rocky state.
 
@@
 The cause for their underabundance remains an open question, with two leading candidate explanations.
-Tidal migration mechanisms may be mass-dependent in such a way as to proceed efficiently for Hot Jupiters, but inefficiently for the lower mass hot Saturns.
-In this scenario, sub-Saturn mass planets never make it to the close-in orbital separations that would lead to their conditions needed for inflation in the first place.
+Tidal migration mechanisms may be mass-dependent in such a way as to proceed efficiently for Jupiter-mass planets, but inefficiently for the lower mass Saturns.
+In this scenario, sub-Saturn mass planets never make it to the close-in orbital separations that would lead to the conditions needed for inflation in the first place.
 
@@
 Here, a lightly ionized atmosphere experiences drag in a planetary magnetic field, weakly coupling the stellar incident energy into the planetary interior.
-\citet{2018AJ....155..214T} proposed these two explanations for the lack of sub-Saturns, while statistically favoring Ohmic dissipation as the mechanism responsible for inflating Hot Jupiters.
-Ohmic dissipation does not preclude the existence and role of other heating mechanisms---such as photoevaporation and tidal heating---but it does stand out has having made these predictions before data were widely available to test these predictions.
+\citet{2018AJ....155..214T} recognized the above two explanations for the lack of sub-Saturns, while statistically favoring Ohmic dissipation as the mechanism responsible for inflating Hot Jupiters.
+Ohmic dissipation does not preclude the existence and role of other heating mechanisms---such as photoevaporation and tidal heating---but it does stand out has having made these predictions before data were widely available to test them.
 
 The runaway inflation scenario could yield a profound mass loss rate for inflated hot Saturns, possibly much larger than we have seen in previous systems.
-The ability to detect that mass loss hinges on their observability in spectral tracers.
+The ability to detect that conceivable mass loss hinges on its observability in spectral tracers.
 Ly~$\alpha$, \ion{He}{1} 10833 \AA, and H~$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}, but each of these has its own limitations.
@@
 \ion{H}{1} has resulted in at least 14 systems with detections, including \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
-To date, no inflated hot Saturns appear to have been examined, neither in Helium nor other tracers \emph{c.f.} Figure \censorbox{figure X}.
+To date, no inflated hot Saturns appear to have been examined, neither in Helium nor other tracers \emph{c.f.} Figure \ref{fig:instellation}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figures/HAT-P-67b_radius_valley.png}
+    \caption{Overview of exoplanet size versus instellation.
+Inflated Hot Jupiters appear as the cluster of sources larger than Jupiter and receiving up to 100 to 10,000 $\times$ as much insolation.
+The pixel bins reflect the observed density of over 5000 planets accessed from the NASA Exoplanet Archive.
+The star symbol shows the inflated position of \hatpb.}
+    \label{fig:instellation}
+\end{figure}
 
@@
 The strong insolation combined with \object{HAT-P-67 b}'s low surface gravity makes it an excellent candidate for strong atmospheric mass loss.
-It orbits an evolved star, opening the prospect for ``re-inflation'' as the planet's insolation increased over time as the star expanded.
-Its status as a rare inflated Hot Saturn make \object{HAT-P-67 b} a promising laboratory for testing the inflationary predictions of the Ohmic dissipation mechanism.
+It orbits an evolved star, opening the prospect for ``re-inflation'' as the planet's insolation increased over time with the star's expansion.
+Its status as a rare inflated Hot Saturn make \object{HAT-P-67 b} a promising laboratory, including but not limited to, testing the inflationary predictions of the Ohmic dissipation mechanism.
 
@@
 These in-transit nights had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.
-We obtained out-of-transit baseline observations up to 2 nights before and after the transit, plus random-in-phase low priority P4 queue-filler observations.
+We obtained out-of-transit baseline observations up to 2 nights before and after the transit, plus random-in-phase low priority ``P4'' queue-filler observations.
 These out-of-transit observations typically received 4 or fewer individual exposures.
@@
 We retrieved ground-based photometry with the \emph{All-Sky Automated Survey for Supernovae} (ASAS-SN) using the Sky-Portal \citep{shappee14,2017PASP..129j4502K}.
-The precision of ASAS-SN was too low to perceive stellar variability, and so the photometry is not presented further.
+The precision of ASAS-SN was too low to perceive stellar variability, and so we can place a relatively uninformative limit of $<5\%$ stellar variability on years-long timescales.
 
 \subsection{DASCH}
-HAT-P-67 appears in the Harvard Plate Archive, with 5809 measurements digitized through DASCH, spanning over 120 years of coarse photometric monitoring.
+\hatp appears in the Harvard Plate Archive, with 5809 measurements digitized through DASCH, spanning over 120 years of coarse photometric monitoring.
 In principle these datasets could inform long-term variability trends such as stellar cycles.
 In practice the 0.15 magnitude jitter appears too coarse to perceive any genuine astrophysical variability, with no conspicuous trend seen.
-We can therefore place a relatively mild constraint that the star is stable at the $30\%$ level over periods of tens to hundreds of years.
+We can therefore place a relatively mild constraint that the star is stable at the $\sim30\%$ level over periods of tens to hundreds of years.
 
@@
 The IAU naming convention would demand HAT-P-67A\emph{b} to refer to the planet.
-HAT-P-67A (\emph{Gaia DR3 1358614983131339392}) has a parallax of $2.69\pm0.01$ mas in \emph{Gaia} DR3, placing it at about 372$\pm$1.4 pc, slightly farther than previously estimated by \citet{2017AJ....153..211Z} using Gaia DR1.
-Its coarse Gaia-based estimates for RV and Doppler broadening are consistent with the more precise values published in \citet{2017AJ....153..211Z}.
-Its wide companion HAT-P-67B (\emph{Gaia DR3 1358614983131339904}) \citep{2019MNRAS.490.5088M} has statistically identical parallax ($2.58\pm0.05$) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
+HAT-P-67A (\emph{Gaia DR3 1358614983131339392}) has a parallax of $2.69\pm0.01$ mas in \emph{Gaia} DR3, placing it at about 372$\pm$1.4 pc, slightly farther than previously estimated by \citet{2017AJ....153..211Z} using \emph{Gaia} DR1.
+Its coarse \emph{Gaia}-based estimates for RV and Doppler broadening are consistent with the more precise values published in \citet{2017AJ....153..211Z}.
+Its wide companion HAT-P-67B (\emph{Gaia DR3 1358614983131339904}) \citep{2019MNRAS.490.5088M} has statistically identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
 Hereafter, we simply drop the A designation for notational simplicity, since the wide companion will not factor into our analysis.
@@
 \subsection{Other archives}
-We searched for observations of HAT-P-67 in public archives.
-It has one $R\sim8000$ spectrum from the Intermediate Dispersion Spectrograph on the INT, centered near 4000 \AA.
+\hatp has one $R\sim8000$ spectrum from the Intermediate Dispersion Spectrograph on the INT, centered near 4000 \AA.
 It has 26 photometry points from \emph{Pan-STARRS} spread across its 5 filters.
@@
 \subsection{TESS Light Curve}
-Previously, \hatp transits had only been detected with \emph{HATNet} \citep{2004PASP..116..266B} and followed up with KeplerCam on the FLWO 1.2 m telescope.
-These ground-based photometers were not intended to measure, and did not detect, long term stellar variability signals.
+Previously, \hatp transits had only been detected with \emph{HATNet} \citep{2004PASP..116..266B} and followed up with KeplerCam on the FLWO 1.2 m telescope \citep{2017AJ....153..211Z}.
+These ground-based photometers were not intended to measure long term stellar variability signals.
 We therefore examined the \emph{TESS} lightcurves for out-of-transit photometric variability.

### 2023-03-14 paper/paper1/ms.tex
Text describing the MCMC fitting, probably too verbose

@@
 
+% We will probably delete all of this in favor of fitting just the static-subtracted strategy, and merely stating the Si internal precision.
+We estimated bulk characteristics of the spectral line by fitting a pair of Voigt profiles to the 10828$-$10838 \AA region.
+The blue Voigt profile was intended to fit the Si line centered at 10830 \AA, acting as static control sample.
+The red line initialized at 10833 \AA was intended to aglomerate all three components of the metastable triplet into a single feature, consistent with their appearance in Figure \ref{fig:HPFheliumOverview}.
+The model constructed in this way has a total of 8 parameters: amplitude $A$, location $\lambda_c$, Gaussian width $\sigma$, and Lorentzian width $\gamma$ for each of the two pseudo-lines.
+This phenomenological choice was intended not to match the underlying substructure of the line, but instead merely to match the bulk characteristics in the region of interest.
+The choice of Voigt profiles---as opposed to simple Gaussians---provides enough model flexibility to make up for possible deficiencies in the continuum assignment and line shapes.
+
+The individual fits to the Si line show a line center position of typically $X\pm z$.
+The weighted mean of all 152 spectra shows a mean of $Y\pm w$.
+In contrast, the Helium 10833 bulk feature shows a phase-dependent velocity shift.
+The out-of-transit phases exhibit \censor{XX}, consistent with the stellar \ion{He}{1} rest frame zero velocity.
+The extended ingress and in-transit phases exhibit a blueshift of \censor{xpmz}.
+
+The model constructed in this way smears the apparent shift, since the static underlying stellar spectrum tends to dilute the dynamic portion of the line.
+So we repeated the line fitting by subtracting off a model of the out-of-transit stellar spectrum.
+While any interpolation strategy would work, we chose to a Gaussian Process GP model \censor{cite DFM}.
+This GP strategy has the advantage of providing principled uncertainty bands, useful for quantifying our confidence in putative weak signals in the presence of correlations.
+
 The absorption resides mostly near the stellar zero restframe velocity reference.

### 2023-03-16 paper/paper1/ms.tex
Revise and put in numbers for the excess absorption bulk characteristics

--- 2023-03-09 paper/paper1/ms.tex
@@
 
-The absorption resides mostly near the stellar zero restframe velocity reference.
+% Describe construction of residual spectra
+
+We estimated bulk characteristics of the Helium lines by fitting a Gaussian line profile to the 10828$-$10838 \AA region of the residual spectra.
+The single line initialized at 10833 \AA was intended to aglomerate all three components of the metastable triplet into a single feature, consistent with their appearance in Figure \ref{fig:HPFheliumOverview}.
+The model constructed in this way has a total of 4 parameters: amplitude $A$, location $\lambda_c$, Gaussian width $\sigma$, and constant offset.
+We repeated a similar process for the nearby Si line at 10830~\AA as a control sample.
+
+The full-width at half maximum (FWHM) of the feature is about 1.8-2.6~\AA, equivalent to a line-of-sight velocity distribution in the range of 50-75~km/s.
+Individual fits to the He feature show a typical line center uncertainty $\pm0.1$~\AA or better, when confidently detected.
+The out-of-transit phases exhibit a line center position of 10833.4~\AA, consistent with the stellar \ion{He}{1} rest frame zero velocity.
+The excess absorption resides slightly blueward of the stellar zero restframe velocity reference.
 As mentioned previously, the telluric masking near 10836 \AA~ censors our view of the existence (or not) of any redshifted lobe in this region.
 A more careful treatment of the telluric absorption could rescue some of the data in this region.
+The excess detections exhibit a bulk blueshift of up to 30~km/s.
 
-Finally, a tentative much weaker post-egress bifurcation into blue-shifted absorption and redshifted emission may exist near 0.1 in phase.
-The signal appears at or just above the noise level, but is shared among tens of pixels.
+The excess absorption spectrum exhibits an increasing line-of-sight velocity distribution as the planet transits, going from 60~km/s at ingress, up to 100 km/s at egress.
+
+Finally, we detect a much weaker but still significant post-egress blue-shifted absorption.
+This lobe appears to decrease linearly in wavelength, corresponding to a characteristic blueshift increasing from near zero at transit midpoint to 80~km/s 12 hours after transit.
+It exhibits a slightly lower line-of-sight velocity distribution of 50 km/s, about half of the peak during transit.
 

### 2023-03-17 paper/paper1/ms.tex
Add a figure modeled after Thorngren & Fortney 2018 Fig 2, updated with TESS

@@
 
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/tf2018_fig2_update2023_HAT.png}
+    \caption{Mass-radius trends for inflated hot sub-Saturns and hot Jupiters, form modeled after Figure 2 from \citet{2018AJ....155..214T} and updated with NASA Exoplanet Archive confirmed planets.
+The trend lines show mass-radius relationship for equilibrium temperatures of 500, 1000, 1250, 1500, and 2000 K, assuming the mean composition and mean heating efficiency from the original figure.
+HAT-P-67~b stands alones as occupying the ``Ohmic Dissipation Ridge'', defined by the lack of inflated sub-Saturns.}
+    \label{fig:murrayClaySchematic}
+\end{figure}
+
 This dearth of hot-Saturns has persisted into the \emph{TESS} era.

### 2023-03-17 paper/paper1/ms.tex
Small amount of text added.

@@
 The trend lines show mass-radius relationship for equilibrium temperatures of 500, 1000, 1250, 1500, and 2000 K, assuming the mean composition and mean heating efficiency from the original figure.
-HAT-P-67~b stands alones as occupying the ``Ohmic Dissipation Ridge'', defined by the lack of inflated sub-Saturns.}
+HAT-P-67~b stands alones as occupying the ``Ohmic Dissipation Ridge'', defined by the lack of inflated sub-Saturns, and explained by short lifetimes form runaway inflation and mass loss.}
     \label{fig:murrayClaySchematic}

### 2023-03-22 paper/paper1/ms.tex
Minor tweaks from printout

@@
 Whatever the cause, some large fraction of planets must undergo atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations such as transiting planets.
-At least 28 examples have been seen to date \citep{2022arXiv221116243D}.
+Such signals have been searched for and increasingly found, with at least 28 detections to date \citep{2022arXiv221116243D}.
 
 Uncertainty in system ages, evaporation timescales, and dominating physical mechanisms, degrade our ability to foretell if any given planet will exhibit ongoing signatures of atmospheric escape.
-Episodic stellar wind gusts and other forms of cosmic variance could also subdue atmospheric escape, even where we expect it most.
+Episodic stellar wind gusts and other forms of astrophysical variance could also subdue the appearance of atmospheric escape, even where we expect it most.
 The 48 published non-detections of atmospheric escape \citep{2022arXiv221116243D} must encode these natural whims in a way that we have not yet disentangled.
-Nevertheless, we can boost our chances of witnessing active and significant atmospheric escape by targeting sources with favorable traits.
+Nevertheless, we can boost our chances of witnessing active and significant atmospheric escape by targeting sources that seem predisposed to loss.
 These intrinsic or extrinsic factors may include close proximity to host star, low surface gravity, and high energy incident radiation.
-For example, the small planet radius gap between 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of eroding to their final rocky state.
+The small planet radius gap between 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of eroding to their final rocky state.
 
-Inflated hot Saturns stand out as an especially extreme category that should exhibit mass loss.
+Inflated hot Saturns stand out as another especially extreme category that should exhibit mass loss.
 Their low gravitational potentials should let go of their atmospheres more readily than their steadfast Hot Jupiter counterparts.
@@
 The ability to detect that conceivable mass loss hinges on its observability in spectral tracers.
-Ly~$\alpha$, \ion{He}{1} 10833 \AA, and H~$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}, but each of these has its own limitations.
-Ly $\alpha$ can suffer from instellar medium \ion{H}{1} absorption censoring its low-velocity linecore, for example.
-Here we focus on \ion{He}{1} 10833 \AA~, which offers some advantages over Ly~$\alpha$.
+Ly$\alpha$, \ion{He}{1} 10833 \AA, and H$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}, but each of these has its own limitations.
+Ly $\alpha$ can suffer from interstellar medium \ion{H}{1} absorption censoring its low-velocity linecore, for example.
+Here we focus on \ion{He}{1} 10833 \AA, which offers some advantages over Ly$\alpha$.
 In particular, metastable Helium's ability to be observed at high spectral resolution from the ground has been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.
 \ion{H}{1} has resulted in at least 14 systems with detections, including \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
-To date, no inflated hot Saturns appear to have been examined, neither in Helium nor other tracers \emph{c.f.} Figure \ref{fig:instellation}.
+To date, no inflated hot Saturns appear to have been examined, neither in Helium nor other tracers (\emph{c.f.} Figure \ref{fig:instellation}).
 
@@
 Instead, we organized the observations into four campaigns to coincide with \object{HAT-P-67 b} transits on the nights beginning 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.
-These in-transit nights had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.
-We obtained out-of-transit baseline observations up to 2 nights before and after the transit, plus random-in-phase low priority ``P4'' queue-filler observations.
-These out-of-transit observations typically received 4 or fewer individual exposures.
-We observed HAT-P-67 with HPF for a total 41 visits on 39 unique nights, with two of those nights observing both an east and a west track.
+These campaigns have out-of-transit observations at least one night before and one night after, and often two nights on either side of the transit.
+Two more transits were obtained in 2022 June-July without the visits immediately before and after.
+The in-transit nights had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.
+We also obtained random-in-phase low priority ``P4'' queue-filler observations.
+These out-of-transit snapshot observations typically received 4 or fewer individual exposures.
+We observed HAT-P-67 with HPF for a total 41 visits on 39 unique nights, with two of those nights observing both an east and a west HET track.
 The total on-source integration time exceeds 13.8 hours.
@@
 We also assembled a comparison sample of about 1000 lightcurves to interpret the  prevalence of lightcurve modulation and stellar activity among broadly F subgiant-like stars.
-We selected sources based on \emph{Gaia} DR3 $T_\mathrm{eff}$ estimates and similar $\log{g}$,  and availability of at least one sector of TESS 2-minute cadence data\footnote{The requirement to have 2-minute cadence data---a data reduction convenience---may include biases stemming from the pre-selection of TESS targets, but it is not clear whether such a pre-selection would favor more or less stellar activity}.
+We selected sources based on \emph{Gaia} DR3 $T_\mathrm{eff}$ estimates and similar $\log{g}$,  and availability of at least one sector of TESS 2-minute cadence data.
 We also visually spot-checked these lightcurves to understand artifacts and windowing effects.
@@
 The stellar system consists of a binary with an M dwarf companion HAT-P-67B separated on-sky by $9\farcs0$ \citep{2019MNRAS.490.5088M}.
-The IAU naming convention would demand HAT-P-67A\emph{b} to refer to the planet.
 HAT-P-67A (\emph{Gaia DR3 1358614983131339392}) has a parallax of $2.69\pm0.01$ mas in \emph{Gaia} DR3, placing it at about 372$\pm$1.4 pc, slightly farther than previously estimated by \citet{2017AJ....153..211Z} using \emph{Gaia} DR1.
@@
 Its wide companion HAT-P-67B (\emph{Gaia DR3 1358614983131339904}) \citep{2019MNRAS.490.5088M} has statistically identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
+The IAU naming convention would demand HAT-P-67A\emph{b} to refer to the planet.
 Hereafter, we simply drop the A designation for notational simplicity, since the wide companion will not factor into our analysis.

### 2023-03-22 paper/paper1/ms.tex
Negligible corrections for Gaia DR3 bias and uncertainty

@@
 \subsection{Gaia DR3}
-The stellar system consists of a binary with an M dwarf companion HAT-P-67B separated on-sky by $9\farcs0$ \citep{2019MNRAS.490.5088M}.
-HAT-P-67A (\emph{Gaia DR3 1358614983131339392}) has a parallax of $2.69\pm0.01$ mas in \emph{Gaia} DR3, placing it at about 372$\pm$1.4 pc, slightly farther than previously estimated by \citet{2017AJ....153..211Z} using \emph{Gaia} DR1.
+The stellar system consists of a binary with an M dwarf companion HAT-P-67B (\emph{Gaia DR3 1358614983131339904}) separated on-sky by $9\farcs0$ \citep{2019MNRAS.490.5088M}.
+HAT-P-67A (\emph{Gaia DR3 1358614983131339392}) has a parallax of $2.69\pm0.01$ mas in \emph{Gaia} DR3, placing it at about 372$\pm$1.4 pc.
+Minor corrections to the parallax uncertainty \citep{2021MNRAS.506.2269E} and bias \citep{2021A&A...649A...4L} appear negligible for the system properties.
+The DR3 parallax places the system slightly farther than previously estimated by \citet{2017AJ....153..211Z} using \emph{Gaia} DR1-derived parallax of $2.92\pm0.23$, which included bias and  .
 Its coarse \emph{Gaia}-based estimates for RV and Doppler broadening are consistent with the more precise values published in \citet{2017AJ....153..211Z}.
-Its wide companion HAT-P-67B (\emph{Gaia DR3 1358614983131339904}) \citep{2019MNRAS.490.5088M} has statistically identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
+Its wide companion HAT-P-67B  \citep{2019MNRAS.490.5088M} has statistically identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
 The IAU naming convention would demand HAT-P-67A\emph{b} to refer to the planet.

### 2023-03-22 paper/paper1/ms.tex
More prose editing

@@
 
-\subsection{Gaia DR3}
+\subsection{Gaia DR3}\label{gaiadr3}
 The stellar system consists of a binary with an M dwarf companion HAT-P-67B (\emph{Gaia DR3 1358614983131339904}) separated on-sky by $9\farcs0$ \citep{2019MNRAS.490.5088M}.
 HAT-P-67A (\emph{Gaia DR3 1358614983131339392}) has a parallax of $2.69\pm0.01$ mas in \emph{Gaia} DR3, placing it at about 372$\pm$1.4 pc.
-Minor corrections to the parallax uncertainty \citep{2021MNRAS.506.2269E} and bias \citep{2021A&A...649A...4L} appear negligible for the system properties.
-The DR3 parallax places the system slightly farther than previously estimated by \citet{2017AJ....153..211Z} using \emph{Gaia} DR1-derived parallax of $2.92\pm0.23$, which included bias and  .
+Minor corrections to the parallax uncertainty \citep{2021MNRAS.506.2269E} and bias \citep{2021A&A...649A...4L} appear negligible for the $G=9.98$ source.
+The DR3 parallax places the system about 8.7\% farther than previously estimated by \citet{2017AJ....153..211Z}, which adopted a \emph{Gaia} DR1-informed parallax of $2.92\pm0.23$ mas, including a $-0.325$ mas bias term from \citep{2016ApJ...831L...6S}.
 Its coarse \emph{Gaia}-based estimates for RV and Doppler broadening are consistent with the more precise values published in \citet{2017AJ....153..211Z}.
-Its wide companion HAT-P-67B  \citep{2019MNRAS.490.5088M} has statistically identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
+Its wide companion HAT-P-67B  \citep{2019MNRAS.490.5088M} has nearly identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
 The IAU naming convention would demand HAT-P-67A\emph{b} to refer to the planet.
 Hereafter, we simply drop the A designation for notational simplicity, since the wide companion will not factor into our analysis.
+Finally, for a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius, systematically decreasing the estimate for the already-low density of HAT-P-67 by 30\%.
 
@@
 We therefore examined the \emph{TESS} lightcurves for out-of-transit photometric variability.
+The revised precision and continuous coverage of \emph{TESS} can refine the orbital solution.
+
 \subsubsection{Revised exoplanet orbital parameters}
@@
 
-The TESS Sector 26 lightcurve exhibits a weak $\sim3\;$ppt peak-to-valley out-of-transit modulation on timescales comparable to the exoplanet orbit.
+The TESS Sector 26 lightcurve exhibits a weak $\sim$3 ppt peak-to-valley out-of-transit modulation on timescales comparable to the exoplanet orbit.
 TESS Sectors 51-53 do not show as conspicuous a modulation signal.
-Figure \ref{fig:TESSmodulation} shows this modulation in the minimally processed TESS lightcurve.
-During the exoplanet orbit fitting, we fit the TESS lightcurve modulation with a quasiperiodic Gaussian Process (GP) model using \texttt{celerite} \citep{celerite1,celerite2}.
+Figure \ref{fig:TESSoverview} shows this modulation in the minimally processed TESS lightcurve.
+We fit the TESS lightcurve modulation with a quasiperiodic Gaussian Process (GP) model using \texttt{celerite} \citep{celerite1,celerite2}.
 The GP model fit to the entire composite lightcurve yields a period of 4.7 days; when fit to individual sectors alone the periods hover around 5.9 days.
@@
 If we attribute the TESS modulation signal to stellar activity, we obtain a rotation period $P_\mathrm{rot}$ between 4.7 and 5.9 days.
-\citet{2017AJ....153..211Z} estimated $v\sin{i}=35.8\pm1.1$ km/s, or lower ($v\sin{i}=30\pm1.1$ km/s) if macroturbulence was accounted for.
-Assuming a stellar radius of 2.1-2.7 $R_\odot$, we obtain combined geometric constraint $3.0 < \frac{P_\mathrm{rot}}{\sin{i}}  < 4.5 $ days.
-This range is close to---but slightly lower than---the TESS modulation period.
-The Gaia \emph{DR3}-derived distance is 8\% greater than the \emph{Gaia} DR1 estimate used in \citet{2017AJ....153..211Z}; the revised larger distance would tend to increase the radius estimate by 16\% to match the observed SED in isochrone-fitting.
-We would therefore expect an isochrone-derived $R_\star$ range closer to $2.5-3.14 R_\odot$, where we have dropped the 1-$\sigma$ uncertainties which had included the less certain Gaia DR 1 parallax and its uncertain correction terms.
-For a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius, revising the already-low density of HAT-P-67 even lower.
+We can constrain the expected rotation period based on radius estimates from isochrone fitting, stellar rotation rate from $v\sin{i}$, and the observation of $i\sim90^\circ$ from orbit fitting and Doppler tomography \citep{2017AJ....153..211Z}.
+We adopt a high limit of $v\sin{i}=35.8\pm1.1$ km/s and a lower $v\sin{i}=30\pm1.1$ km/s value if macroturbulence is accounted for.
+We increase the previously derived stellar radius of 2.1-2.7 $R_\odot$ by 8.7\% to match the greater Gaia \emph{DR3} distance (\S \ref{gaiadr3}).
+We obtain a wide range of $3.2 < P_\mathrm{rot}  < 4.9 $ days, which may be typical for F stars that have not yet evolved too far into the sub-giant branch \citep{2022ApJ...930....7A}.
+The geometrical constraint includes the 4.7 day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9 day per-Sector fits.
 

### 2023-03-22 paper/paper1/ms.tex
Revisiting the stellar rotation constraints including Gaia radius

@@
 Hereafter, we simply drop the A designation for notational simplicity, since the wide companion will not factor into our analysis.
-Finally, for a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius, systematically decreasing the estimate for the already-low density of HAT-P-67 by 30\%.
 
@@
 \section{Analysis}
+
+\subsection{Gaia DR3}
+\citet{2017AJ....153..211Z} previously derived stellar radius estimates of 2.1-2.7 $R_\odot$ through Spectral Energy Distribution (SED) isochrone fitting as part of a joint orbit fit.
+We systematically increase those stellar radius estimates by 8.7\% to match the greater Gaia \emph{DR3} distance (\S \ref{gaiadr3}).
+For a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius.
+This update systematically decreases the estimate for the already-low density of HAT-P-67 by 28\%, to a mere 0.035 g$\;$cm$^{-3}$, albeit with significant uncertainties from the weak mass constraint, and from the model dependence of multiple orbit fits.
 
@@
 
-If we attribute the TESS modulation signal to stellar activity, we obtain a rotation period $P_\mathrm{rot}$ between 4.7 and 5.9 days.
-We can constrain the expected rotation period based on radius estimates from isochrone fitting, stellar rotation rate from $v\sin{i}$, and the observation of $i\sim90^\circ$ from orbit fitting and Doppler tomography \citep{2017AJ....153..211Z}.
-We adopt a high limit of $v\sin{i}=35.8\pm1.1$ km/s and a lower $v\sin{i}=30\pm1.1$ km/s value if macroturbulence is accounted for.
-We increase the previously derived stellar radius of 2.1-2.7 $R_\odot$ by 8.7\% to match the greater Gaia \emph{DR3} distance (\S \ref{gaiadr3}).
-We obtain a wide range of $3.2 < P_\mathrm{rot}  < 4.9 $ days, which may be typical for F stars that have not yet evolved too far into the sub-giant branch \citep{2022ApJ...930....7A}.
-The geometrical constraint includes the 4.7 day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9 day per-Sector fits.
+If we attribute this TESS modulation signal to stellar activity, we obtain a rotation period $P_\mathrm{rot}$ between 4.7 and 5.9 days.
+We can constrain the expected rotation period based on our revised stellar radius estimate, stellar rotation rate from $v\sin{i}$, and the observation of $i\sim90^\circ$ from orbit fitting and Doppler tomography \citep{2017AJ....153..211Z}.
+We adopt a high limit of $v\sin{i}=35.8\pm1.1$ km/s and a lower $v\sin{i}=30.9\pm2$ km/s value if macroturbulence is accounted for.
+We obtain a range of $3.2 < P_\mathrm{rot}  < 4.8 $ days.
+This range may be typical for F stars that have not yet evolved too far into the sub-giant branch \citep{2022ApJ...930....7A}.
+The geometrical constraint includes the 4.7 day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9 day per-Sector fits, slightly preferring the lower 4.7 day modulation as the stellar rotation period.
+The 5.9 day value would require a stellar radius over 3.2$R_\odot$, which appears consistent with only an eccentric orbit model combined with the Geneva isochrone \citep{2017AJ....153..211Z}.
 

### 2023-03-22 paper/paper1/ms.tex
Revising text from paper edits

@@
 \subsubsection{Lightcurve modulation amplitude}
-Finally, we computed the peak-to-valley modulation for the 1000-lightcurve comparison sample, defined as the difference between the 90$^{th}$ to 10$^{th}$ percentile of each normalized TESS lightcurve.
-We find that most lightcurves are consistent with negligible astrophysical variability and/or variability predominated by instrumental artifacts.
-Nevertheless, \object{HAT-P-67 b}'s 0.36$\%$ lightcurve modulation was slightly larger than the typical comparison source, ranking in the 87$^{th}$ percentile of the ensemble.
-However the higher-modulation sources exhibited 3-5$\times$ the level of modulation seen in \object{HAT-P-67 b}, whereas \object{HAT-P-67 b} was only about 0.5$\times$ above the median.
+We computed the peak-to-valley modulation for the 1000-source \emph{TESS} comparison sample, defined as the difference between the 90$^{th}$ to 10$^{th}$ percentile of each normalized \emph{TESS} lightcurve.
+Most lightcurves appear consistent with negligible astrophysical variability and/or variability predominated by instrumental artifacts.
+\object{HAT-P-67}'s 0.36$\%$ lightcurve modulation ranked in the 87$^{th}$ percentile of the ensemble, about 0.5$\times$ above the median.
+Sources more variable than HAT-P-67 exhibited 3-5$\times$ its amplitude of modulation.
 
@@
 \subsection{HPF analysis}
-The raw 2D echellograms were reduced with the \texttt{Goldilocks} package\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}}, which outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb (LFC).
-The observations were acquired with the LFC turned off, so this unilluminated spectrum was discarded.
+The raw 2D echellograms were reduced with the \texttt{Goldilocks} package\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}}, which outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb \citep[LFC,][]{2019Optic...6..233M}.
+The observations were usually acquired with the LFC turned off, so this unilluminated spectrum was discarded.
 
-The sky fiber and target fiber have slightly different throughputs and illumination properties so the sky fiber must be scaled prior to subtraction from the target spectrum.
-On average the target fiber sees $93\%$ of the flux of the sky reference fiber, and at the few percent level this ratio depends on wavelength and season.
+The sky fiber and target fiber have slightly different throughputs and illumination properties, with the target fiber receiving $93\%$ of the flux of the sky reference fiber on average.
+This ratio depends on wavelength and season at the few percent level.
 We quantified the wavelength dependence by acquiring calibration observations of blank sky in both the target and sky fiber.
@@
 
-Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 region of interest, with all 153 individual exposures overlaid.
+Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 region of interest, with all 152 individual exposures overlaid.
 We see a variability in the Helium line of up to 10\%, much greater than the $<1\%$ pixel-to-pixel variation.
-The feature width spans about 3~\AA, comparable to the stellar rotationally broadened lines and too broad to originate from the much narrower telluric lines.
+The feature width spans about 3~\AA.
 
@@
 
-The 13.8 hours of exposure, combined with \object{HAT-P-67 b}'s short ($P\sim4.8$ day) period, means that a large fraction of the orbit has been collected, with some phases (especially near transit) heavily sampled, and some other out-of-transit phases sampled only sparsely.
-We constructed a 2-D intensity phase scan, binning in phase and wavelength, and spanning the entire orbit of \object{HAT-P-67 b}.
-Figure \ref{fig:HPFphase2D} overlays the planet's approximately $\pm150\;$km/s orbital Doppler velocity, with the stellar rest frame velocity demarcated by the vertical line.
+The 13.8 hours of exposure, combined with \object{HAT-P-67 b}'s short ($P\sim4.8$ day) period, means that a large fraction of the orbit has been collected, with some phases (especially near transit) heavily sampled, and some other out-of-transit phases sampled more sparsely.
+For visualization purposes, we constructed a 2-D intensity phase scan, binning in phase and wavelength, and spanning the entire orbit of \object{HAT-P-67 b}.
+Figure \ref{fig:HPFscanResid} overlays the planet's approximately $\pm150\;$km/s orbital Doppler velocity, with the stellar rest frame velocity demarcated by the vertical line.
 The vanishing $<36$ m/s reflex motion of the star is imperceptible at this scale.
-The horizontal dashed lines indicate the transit ingress, midcenter, and egress.
+The horizontal dashed lines indicate the moments of transit ingress (-0.03), midcenter (0.0), and egress (+0.03).
 
-\begin{figure}
-    \includegraphics[width=0.8\linewidth]{figures/phase_2D_diagram.png}
-    \caption{Phase scan of intensity for HAT-P-67.
-The spectrum flux intensity shows significant in-transit absorption during and before the transit.
-Telluric lines redward of the line center have been masked.
-An unmasked telluric line near 10825 \AA~ can be seen.}
-    \label{fig:HPFphase2D}
-\end{figure}
-
+The in-transit phases exhibit over 10\% excess absorption peaks.
 A large absorption signal can be seen preceding transit ingress, with some significant absorption evident before $-0.2$ in phase.
@@
 We define the non-varying baseline spectrum as the average over phases $0.3-0.5$, which exhibited stable spectra with the least absorption.
-Figure \ref{fig:HPFscanResid} shows a conspicuous view of the Helium absorption of \object{HAT-P-67 b}.
-Significant absorption can be seen as a few percent at $-0.37$ in phase, rising to 10\% just before and during transit.
-The egress drop off is extremely sharp, with almost no absorption directly after transit.
+Figure \ref{fig:HPFscanResid} shows that significant absorption can be seen as a few percent at $-0.37$ in phase, rising to 10\% just before and during transit.
+The egress drop off is extremely sharp, with almost no excess absorption directly after transit.
 
@@
 
-We estimated bulk characteristics of the Helium lines by fitting a Gaussian line profile to the 10828$-$10838 \AA region of the residual spectra.
-The single line initialized at 10833 \AA was intended to aglomerate all three components of the metastable triplet into a single feature, consistent with their appearance in Figure \ref{fig:HPFheliumOverview}.
+We estimated bulk characteristics of the Helium lines by fitting a Gaussian line profile to the 10828$-$10838 \AA~region of the residual spectra.
+The single line initialized at 10833 \AA~ was intended to aglomerate all three components of the metastable triplet into a single feature, consistent with their appearance in Figure \ref{fig:HPFheliumOverview}.
 The model constructed in this way has a total of 4 parameters: amplitude $A$, location $\lambda_c$, Gaussian width $\sigma$, and constant offset.
-We repeated a similar process for the nearby Si line at 10830~\AA as a control sample.
+We repeated a similar process for the nearby Si line at 10830 \AA~as a control sample.
 
+Excess is confidently detected at \censor{X} phases at \censor{Z}$\sigma$.
 The full-width at half maximum (FWHM) of the feature is about 1.8-2.6~\AA, equivalent to a line-of-sight velocity distribution in the range of 50-75~km/s.
-Individual fits to the He feature show a typical line center uncertainty $\pm0.1$~\AA or better, when confidently detected.
+Individual fits to the He feature show a typical line center uncertainty $\pm0.1$~\AA~ or better.
 The out-of-transit phases exhibit a line center position of 10833.4~\AA, consistent with the stellar \ion{He}{1} rest frame zero velocity.
@@
 We see no conspicuous variability at this or any of the other Ca IRT lines.
-We also found no detectable variability in the Pa$\delta$ line at 10050 \AA, nor other deep lines at 10330 \AA and elsewhere.
+We also found no detectable variability in the Pa$\delta$ line at 10050 \AA, nor other deep lines at 10330 \AA~ and elsewhere.
 \ion{He}{1} 10833 appears to be the only conspicuously variable line in the HPF spectrum.
@@
 The 3\farcs5 B2 decker allowed the faithful extraction of this region for 6 spectra, which exhibit no perceptible \ion{Ca}{2} H and K variability.
-The H~$\alpha$ region similarly exhibited no perceptible variability.
-The timing of these spectra coincidentally missed the orbital phases ($-0.3$ to $+0.03$) where we see the greatest \ion{He}{1} 10833 \AA~ absorption excess, leaving open the possibility that detectable H~$\alpha$ absorption could be present at more favorable orbital phases.
+The H$\alpha$ region exhibited no perceptible variability, but the timing of these spectra coincidentally missed the orbital phases ($-0.3$ to $+0.03$) where we see the greatest \ion{He}{1} 10833 \AA~ absorption excess, leaving open the possibility that detectable H$\alpha$ absorption could be present at more favorable orbital phases.
 New spectra or a more careful extraction of the archival C2 decker spectra would be needed.
@@
 \subsection{Velocity substructure}
-Figure \ref{fig:HeliumScanZoom} shows a zoom-in of the in-transit portion of the absorption residual scan.
+Figure \ref{fig:HeliumScanZoom} shows a zoom-in of the in-transit portion of the Helium excess absorption scan, overlaid with line center positions.
 The scan appears to exhibit some velocity substructure.
@@
 The line depth gets slightly shallower with a slight redshift approaching transit midcenter.
+\authorcomment1{Add more text here and revise figure.}
 

### 2023-03-22 paper/paper1/ms.tex
Minor edits

@@
 We are therefore primarily detecting gas that is entirely unbound from the planet.
-The leading gas tail does not appear to accelerate, neither blue-shifting nor redshifting.
+The leading gas tail does not appear to accelerate, with only a modest blueshift.
 The bulk of the detectable unbound gas may therefore follow its own Keplerian trajectory at a slightly shorter period orbit, pulling away from the planet parallel to the orbital path.
@@
 
-The out-of-transit excess exhibits approximately the same line width as the stellar lines, which are rotationally broadened by a $v\sin{i}$ of 30-35 km/s \citep{2017AJ....153..211Z}.
 The large size of the gas stream overfills the transit chord, which means both the advancing blue side and receding red side of the rotating star are nearly continuously obscured in this spin-orbit-aligned system \citep{2017AJ....153..211Z}.
@@
 We chose a 6400 K PHOENIX \citep{husser13} solar metallicity photospheric spectral template with $\log{g}=3.5$, scaled to the solid angle seen by \hatpb.
-The F7IV-V \object[tau Boo]{$\tau$ Boo} serves as the closest analog with synthetic x-ray coronal spectra available \citep{2011A&A...532A...6S}.
-But \hatp resides closer to the Kraft break than does \object[tau Boo]{$\tau$ Boo}, and the move to hotter F stars may be associated with rapid changes in the stellar wind and other atmospheric changes leading to the prospect of much lower XUV luminosity for \hatp.
-So there remains significant uncertainty about the applicability of the \object[tau Boo]{$\tau$ Boo} x-ray spectrum to \hatp.
+The F7IV-V \object[tau Boo]{$\tau$ Boo} serves as the closest analog with available synthetic x-ray coronal spectra \citep{2011A&A...532A...6S}.
+But \hatp resides closer to the Kraft break than does \object[tau Boo]{$\tau$ Boo}, and the move to hotter F stars may be associated with weakening of the stellar wind and other atmospheric changes leading to the prospect of much lower XUV luminosity for HAT-P-67.
+So there remains significant uncertainty about the applicability of the \object[tau Boo]{$\tau$ Boo} XUV spectrum to HAT-P-67.
 We scaled the synthetic SED of \object[tau Boo]{$\tau$ Boo} retrieved from X-exoplanets \citep{2011A&A...532A...6S} so that the integral of ground-state ionizing photons ($\lambda<504\AA$) exhibited $L_X/L_\mathrm{bol} \in [10^{-7}, 10^{-5}]$.
@@
 
-The SED shows two key features.
-First the corona model does not extend all the way to 2600 $\AA$ photons capable of ionizing out of the 2 $^3$S Helium metastable state.
-This apparent deficit probably does not matter because the F spectral type obtains most of its NUV photons ($\lambda\sim2600\AA$) from the Wein side of the photospheric spectrum, so the hardness of the radiation stems mostly from the assumptions of the corona flux level.
-The wavelength-dependent cross section for absorption (not shown) is largest just blueward of the ionization thresholds, so the differences in the spectrum between 504 $\AA$ and 1000 $\AA$ have relatively little impact on the overall ionization out of the metastable state.
+The SED shows that the corona model does not extend all the way to 2600 \AA~photons capable of ionizing out of the 2 $^3$S Helium metastable state.
+This apparent deficit should be negligible, since the F spectral type obtains most of its NUV photons ($\lambda\sim2600$ \AA) from the Wein side of the photospheric spectrum, so the hardness of the radiation stems mostly from the assumptions of the corona flux level.
+The wavelength-dependent cross section for absorption (not shown) is largest just blueward of the ionization thresholds, so the differences in the spectrum between 504 and 1000 \AA~ have relatively little impact on the overall ionization out of the metastable state.
 

### 2023-03-27 paper/paper1/ms.tex
Revising text from written notes

@@
 width and depth}) is degenerate with XUV flux, $\dot{M}$, and $T_0$, and so a range of these parameters can be fine-tuned to obtain a large range of mass loss rates consistent with the data and our limited understanding of the XUV flux.
+These known degeneracies have been pointed out previously \citep{2022AJ....164..234V,2019ApJ...881..133O}, but the problem for \hatpb~ appears somewhat more acute since XUV data are scarce for F-type stars near the Kraft break.
 Second, the 1D model breaks down when attempting to explain the inherently 3D leading tail geometry.
@@
 \object{HAT-P-67 b} exhibits both dramatic atmospheric escape and significant radius inflation.
-Ohmic dissipation stands out as a physical mechanism that could be responsible for both of these attributes.
-\citet{2011ApJ...738....1B} showed that ohmic heating acts to inflate hot Jupiters, with low mass hot Jupiters overflowing their Roche lobes and leading to evaporation on Gyr timescales.
-The Ohmic heating scenario requires only on a modest planetary magnetic field ($\sim$1 G) and enough photoionization to ionize some modest fraction of neutral metals.
-The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K \citep{2011ApJ...738....1B}, well matched to HAT-P-67 b's $\sim$1900 K.
-A plausible scaling law relationship approximate to an order-of-magnitude predicts an inflation timescales (Eq.
+Ohmic dissipation stands out as a physical mechanism that could be responsible for both of these oustanding attributes.
+\citet{2011ApJ...738....1B} showed that Ohmic heating acts to inflate hot Jupiters, with planets $\lesssim 0.5 M_\mathrm{Jup}$ overflowing their Roche lobes and leading to evaporation on Gyr timescales.
+The Ohmic heating scenario requires only a modest planetary magnetic field ($\gtrsim$1 G) and enough photoionization to ionize some modest fraction of neutral metals, such as the low ionization species of \ion{Na}{1} and \ion{K}{1}.
+The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K \citep{2011ApJ...738....1B}, where the ionization is strong enough to cause an effective drag, but not so strong as to halt motion altogether.
+The predicted range matches HAT-P-67 b's $\sim$1900 K.
+A plausible scaling law relationship approximate to an order-of-magnitude predicts an inflation timescale (Eq.
 20 in \citet{2011ApJ...738....1B}):
@@
 \noindent yielding an incredibly short 5 Myr timescale for \hatpb, assuming a typical $\epsilon\sim0.01$.
-The order of magnitude of this inflation timescale is so fleetingly short that \hatpb must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
-
-\subsection{Photoevaporation}
-The prospect of Ohmic dissipation does not preclude the possibility that other mass loss drivers are at play.
-Photoevaporation should simultaneously drive heating of the upper layers in the atmosphere, reinforcing the mass loss associated with Ohmic dissipation.
-It is not clear which effect predominates.
+The order of magnitude of this inflation timescale is so fleetingly short that \hatpb~ must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
+We therefore propose that \hatpb~ represents the first and only known example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic Dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
 
@@
 So a $10\times$ higher inflation timescale of 50 Myr would yield $\dot{M}_\mathrm{infl}\sim10^{14}$ g/s, still a very large mass loss rate, but only a factor of 5 away from the baseline 1D model.
-Order unity uncertainties in the Ohmic dissipation efficiency $\epsilon$ may also contribute.
+Factors of a few uncertainties in the Ohmic dissipation efficiency $\epsilon$ may also contribute.
 
-As mentioned in Section \ref{pwinds}, inferring the mass loss rate from observations is strongly model dependent, as seen in \censorbox{cite e.g.
-S.V.
-papers}.
-The XUV flux, exosphere temperature $T_0$, and $\dot{M}$ are all at least partially degenerate.
+As mentioned in Section \ref{pwinds}, inferring the mass loss rate from observations is strongly model dependent.
+The ionization fraction profile, exosphere temperature $T_0$, and $\dot{M}$ are all at least partially degenerate.
 In particular, the uncertain XUV-to-NUV flux ratio confounds the interpretation of the observed Helium signal.
-Even the ``high XUV'' scenario in Figure \ref{fig:XUV} does not have enough ground-state ionizing photons to penetrate to within 5 $R_p$ of the planet surface.
+Even the ``high XUV'' scenario in Figure \ref{fig:XUV} does not have enough ground-state ionizing photons to penetrate to within 5 $R_p$ of the planet surface, in a 1D Parker wind model.
 This means that at best only 1 in $10^{6}$ Helium atoms participate in the observability of the Helium metastable triplet lines in the baseline 1D Parker wind model.
@@
 
-Finally, the entire premise of the Parker wind model may be unjustified due to the inherently 3D geometry of the leading tail.
-In the next section we critically examine the assumptions in the 1D Parker wind model.
+\subsection{Photoevaporation}
+The prospect of Ohmic dissipation does not preclude the possibility that other mass loss drivers are at play.
+Photoevaporation \citep{2009ApJ...693...23M} could simultaneously drive heating of the upper layers in the atmosphere, driving a hydrodynamic wind and reinforcing the mass loss associated with Ohmic dissipation.
+It is not clear \emph{a-priori} which effect predominates.
 
-\subsection{Causes for the leading tail}
-Several physical phenomena could give rise to a leading tail geometry.  Here we explore two leading candidates: orbital shear and stellar wind confinement.
+Photoevaporation stands out as a potential cause of dayside/nightside differences in mass loss, with the greatest supersonic motions stemming from the sub-solar point on the planetary dayside, and merely sonic motion originating on the nightside and near the dayside terminator \citep{2009ApJ...693...23M}.
+Such a scenario is illustrated in Figure \ref{fig:KeplerianShear}.
+We discuss how dayside/nightside differences could explain the leading tail in the next section.
+
+\subsection{Causes for the leading tail} \label{secLeading}
+Several physical phenomena could give rise to a leading tail geometry.  Here we explore the predominant two physical effects: orbital shear and stellar wind confinement.
 
@@
 The wind initially launches radially from the planet, with the strongest wind located near the sub-stellar point, the line connecting the planet to star along the vertical axis in the figure.
-Inefficient heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemi-spherical shape, more like a bulb or torpedo.
+Inefficient heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemi-spherical shape, but more like a bulb or torpedo.
 The gas increasingly experiences the star's Keplerian potential past the Roche lobe, accelerating in the direction of orbital motion, $+x$.
@@
 
-Stellar wind confinement arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.
-A trailing tail may be present, but would not undergo the same boost in density, and would be rapidly carried away by the stellar wind.
+Stellar wind confinement \citep{2022ApJ...926..226M} arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.
+A trailing tail may also be present, but would not undergo the same boost in density, and would be rapidly carried away by the stellar wind.
 This asymmetry could yield the appearance of a leading tail even if mass loss proceeds isotropically, or the asymmetry could be reinforced by an additional dayside/nightside asymmetry.
 Examples of this asymmetry can be seen in 3D MHD modeling of WASP 107~b \citep{2022ApJ...926..226M}.
+
+The overall observation of a leading tail comports with either of these two physical mechanisms, and both could be at play in \hatpb.
+Here we discuss how the observed line profiles of the gas motions could be interpreted in these two paradigms.
 
@@
 
-\subsection{The Ohmic Dissipation Cliff: Evaporative annihilation as the cause of a lack of sub-Saturns}
-The Ohmic dissipation mechanism predicts a rapid inflation timescale leading to the complete evaporation of hot Saturns.
+\section{The Ohmic Dissipation Cliff}
+\subsection{Evaporative annihilation as the cause of a lack of sub-Saturns}
 The Ohmic dissipation mechanism made two key observable predictions.
-The Ohmic dissipation heating should become less efficient as irradiation increased past an equilibrium temperature of about 2000 K.
-Second, hot Saturns should should runaway evaporation, whereas hot Jupiters should reach equilibrium---albeit inflated---radii after Gyr timescales.
+Heating efficiency should initially increase as a function of equilibrium temperature, then degrade as irradiation exceeds equilibrium temperatures of about 2000 K.
+Second, hot Saturns ($\lesssim0.5 M_\mathrm{Jup}$) should undergo runaway evaporation, whereas hot Jupiters ($\gtrsim 1 M_\mathrm{Jup}$) should reach equilibrium---albeit inflated---radii after Gyr timescales.
 Both of these outcomes predated data that could adequately validate them, and these outcomes differ from the behavior of other heating mechanisms, such as photoevaporation or tides.
+When applied to an ensemble of planet systems, the Ohmic dissipation mechanism would expect a dearth of inflated hot Saturns.
 
 \citet{2018AJ....155..214T} statistically favored Ohmic dissipation based on evidence for a turnover in the heating efficiency of hot Jupiters in a sample of 281 Giant planets.
-Futhermore, \citet{2018AJ....155..214T} also highlighted the lack of inflated sub-Saturns as an anomaly: the observational capability exist to detect such sources in large numbers and yet they were not found.
+Futhermore, \citet{2018AJ....155..214T} also highlighted the lack of inflated sub-Saturns as an anomaly: by that time, the observational capability existed to detect such sources in large numbers and yet they were not found.
 
@@
 HAT-P-67~b stands alones as occupying the ``Ohmic Dissipation Ridge'', defined by the lack of inflated sub-Saturns, and explained by short lifetimes form runaway inflation and mass loss.}
-    \label{fig:murrayClaySchematic}
+    \label{fig:ThornFortUpdated}
 \end{figure}
@@
 This dearth of hot-Saturns has persisted into the \emph{TESS} era.
-Figure XX highlights the region of highly irradiated close-in planets with $N=$\censor{x} planets accessed through the NASA Exoplanet Archive \censor{cite NExScI}.
-\hatpb occupies a relative void in this region.
+Figure \ref{ThornFortUpdated} highlights the region of highly irradiated close-in planets with $N>5000$ planets accessed through the NASA Exoplanet Archive \censor{cite NExScI}.
+\hatpb~ occupies a relative void in this region.
 
 The observation that \hatpb---the only hot Saturn searched for atmospheric escape to date---exhibits mass loss indicative of a terminal fate leads us to a natural explanation for the dearth of inflated hot Saturns.
-The inflationary lifetime of this class is so short that observing planets of this class is unlikely.
-\hatpb appears to be one of the rare planets that we happen to catch a glimpse of before it has been completely annihilated.
+The inflationary lifetime of hot Saturns is so short that observing planets of this class is unlikely.
+\hatpb~ appears to be one of the rare planets that we happen to catch a glimpse of before it has been completely annihilated.
+The lack of inflated hot Saturns is analogous to the small planet radius gap \citep{2017AJ....154..109F}, with Ohmic dissipation and replacing core-powered mass loss as the heating mechanism, and photoevaporation remaining a contender.
 
@@
 
+    This research has made use of the NASA Exoplanet Archive, which is operated by the California Institute of Technology, under contract with the National Aeronautics and Space Administration under the Exoplanet Exploration Program.
+
     This research has made use of NASA's Astrophysics Data System.
@@
 
-\facilities{HET (HPF), TESS, ASAS}
+\facilities{HET (HPF), TESS, ASAS, Exoplanet Archive}
 

### 2023-03-28 paper/paper1/ms.tex
Some text, including a new table

@@
 This dearth of hot-Saturns has persisted into the \emph{TESS} era.
-Figure \ref{ThornFortUpdated} highlights the region of highly irradiated close-in planets with $N>5000$ planets accessed through the NASA Exoplanet Archive \censor{cite NExScI}.
+Figure \ref{fig:ThornFortUpdated} highlights the region of highly irradiated close-in planets with $N>5000$ planets accessed through the NASA Exoplanet Archive.
 \hatpb~ occupies a relative void in this region.
@@
 \hatpb~ appears to be one of the rare planets that we happen to catch a glimpse of before it has been completely annihilated.
-The lack of inflated hot Saturns is analogous to the small planet radius gap \citep{2017AJ....154..109F}, with Ohmic dissipation and replacing core-powered mass loss as the heating mechanism, and photoevaporation remaining a contender.
+The lack of inflated hot Saturns is analogous to the small planet radius gap \citep{2017AJ....154..109F}, with Ohmic dissipation and replacing core-powered mass loss as a heating mechanism, and photoevaporation at play.
 
@@
 \citet{2018AJ....155..214T} emphasized the positive feedback loop as a cause for the lack of sub-Saturns, and noted an alternative interpretation-- mass-dependent migration segregation.
-While both scenarios are conceivable, the evidence of strong evaporation of \hatpb favors the evaporation scenario.
+While both scenarios are conceivable, the evidence of strong evaporation of \hatpb~ favors the evaporation scenario.
 Futhermore, the runaway evaporation of hot-Saturns was naturally predicted by the Ohmic dissipation mechanism, whereas mass-dependent migration has only been developed as a post-diction.
 
-We predict that the few other inflated hot-Saturn \hatpb-analogs should also show evidence for atmospheric escape.
-These sources make excellent targets for \ion{He}{1} 10830 observations, and other atmospheric escape diagnostics.
-The key figure-of-merit can be distilled to $\tau_\mathrm{infl}$, and ignoring the $\epsilon$ term.
-Following \censor{Kempton} et al we define a Helium Spectroscopy Metric (HSM) defined as...
+\subsection{Predictions}
+
+As seen in Figure \ref{fig:ThornFortUpdated}, \hatpb has few other known analogs.
+The closest analogues appear both smaller and more massive.
+Nevertheless, we predict that these few other inflated hot-Saturn \hatpb-analogs should also show evidence for atmospheric escape, albeit likely at a lesser scale.
+These sources make excellent targets for \ion{He}{1} 10830 observations, and/or other atmospheric escape diagnostics.
+The key figure-of-merit can be distilled to $\tau_\mathrm{infl}$, and setting the $\epsilon$ term to unity (Eq.
+\ref{eqInflate}).
+Following \citet{2018PASP..130k4401K} we define a Helium Spectroscopy Metric (HeSM):
+
+\begin{eqnarray}
+    \mathrm{HeSM} = \tau_\mathrm{infl} \label{HeSM}
+\end{eqnarray}
+
+\begin{deluxetable}{lLLCR}
+    \tablewidth{0pc}
+    \tabletypesize{\scriptsize}
+    \tablecaption{
+        Coarse Inflation Timescales for hot Jupiters
+        \label{tabHeSM}
+    }
+    \tablehead{
+        \colhead{Planet}   &
+        \colhead{Mass} &
+        \colhead{Radius} &
+        \colhead{Eq. Temp.} &
+        \colhead{$\tau_\mathrm{infl}$} \\
+        \colhead{}   &
+        \colhead{$M_\mathrm{Jup}$} &
+        \colhead{$R_\mathrm{Jup}$}   &
+        \colhead{K} &
+        \colhead{Myr}
+    }
+    \startdata
+    \input{tables/tab_HeSM.tex}
+    \enddata
+    \tablecomments{Inflation timescale assumes $\epsilon=0.01$.}
+\end{deluxetable}
+
+As emphasized, there are significant uncertainties in the inflation timescale, but its order-of-magnitude value gives us a way to prioritize target selection, since these may be the sources most amenable to detection of atmospheric escape.
+Table \ref{tabHeSM} lists $15$ candidates that have nominal lifetimes less than about 40 Myr.
 

### 2023-03-30 paper/paper1/ms.tex
Prose

@@
 \hatpb~ appears to be one of the rare planets that we happen to catch a glimpse of before it has been completely annihilated.
-The lack of inflated hot Saturns is analogous to the small planet radius gap \citep{2017AJ....154..109F}, with Ohmic dissipation and replacing core-powered mass loss as a heating mechanism, and photoevaporation at play.
+The lack of inflated hot Saturns is analogous to the small planet radius gap \citep{2017AJ....154..109F}, with Ohmic dissipation replacing core-powered mass loss as a heating mechanism, and with photoevaporation still at play.
 
-We therefore attribute this cliff in the $m_p$ vs $R_p$ diagram to Ohmic dissipation.
+We therefore attribute this cliff in the $M_p$ vs $R_p$ diagram to Ohmic dissipation.
 \citet{2018AJ....155..214T} emphasized the positive feedback loop as a cause for the lack of sub-Saturns, and noted an alternative interpretation-- mass-dependent migration segregation.
@@
 
-\subsection{Predictions}
+\begin{figure}[t]
+    \includegraphics[width=\linewidth]{figures/tf2018_fig2_theory.png}
+    \caption{Ohmic dissipation runaway inflation timescale in the exoplanet mass-radius diagram.
+Individual planets with confident mass and radius detections are shown as small black dots.
+Helium non-detections are shown in red squares with all detections of atmospheric escape coming from \citet{2022arXiv221116243D}.
+\hatpb~ resides in a sparsely populated region with a vanishingly short inflationary timescale, making it unstable to runaway evaporation with large mass loss expected.}
+    \label{fig:tf2018_theory}
+\end{figure}
 
-As seen in Figure \ref{fig:ThornFortUpdated}, \hatpb has few other known analogs.
-The closest analogues appear both smaller and more massive.
-Nevertheless, we predict that these few other inflated hot-Saturn \hatpb-analogs should also show evidence for atmospheric escape, albeit likely at a lesser scale.
+As seen in Figure \ref{fig:ThornFortUpdated}, \hatpb~ has few other known analogs.
+Figure \ref{fig:tf2018_theory} illustrates why: the inflationary lifetime for planets with comparable mass, radius, and $T_\mathrm{eq}$ is exceptionally short, and so they are rare.
+We constructed the $\tau_\mathrm{infl}$ contours in the following way.
+We censored the $\tau_\mathrm{infl}$ to regions in the mass-radius plane where numerical simulations of Ohmic dissipation resulted in runaway inflation \citet{2011ApJ...738....1B}.
+We interpolate the $T_\mathrm{eq}$ trendlines from Fig.
+\ref{fig:ThornFortUpdated} to compute $\tau_\mathrm{infl}$ from Equation\ref{eqInflate}, including the best fit Gaussian prescription for $\hat{\epsilon_G}$ from Eq.
+34 of \citet{2018AJ....155..214T}.
+This trend should exhibit significant uncertainty owing to the order-of-magnitude nature of the scaling relation, source-to-source scatter in $\hat{\epsilon}_G$, and to what extent $\hat{\epsilon}_G$ applies for planets less than $0.5 M_\mathrm{Jup}$, which were excluded in the derivation of $\hat{\epsilon}_G$ owing to their scarcity.
+Nevertheless, this contour appears to match the bulk trends: the bulk locus of planets reside in either the non-inflationary, stable scenario, or the inflationary-yet-stable scenario.
+A relatively few $\sim$dozens of planets approach the ``cosmic shoreline'' of inflationary lifetimes in the tens of Myr.
+The detection of atmospheric escape along this frontier (green circles in Figure \ref{fig:tf2018_theory}) support this interpretation.
+More observations and theoretical modeling of atmospheric escape along this ridge could help better understand its realized versus expected shape.
+
+\subsection{HAT-P-67b analogues}
+
+The key figure-of-merit can be distilled to $\tau_\mathrm{infl}$, whic can be thought of as an atmospheric escape metric \citep{2018PASP..130k4401K} for inflated planets in the shaded regime of Figure \ref{fig:tf2018_theory}.
+Table \ref{tabHeSM} presents the rank-ordered list of planets by this metric, indicating that they are mostly smaller and more massive than \hatpb.
+Only KELT-11~b shows a shorter nominal inflationary timescale than \hatpb, owing to its low mass and equilibrium temperature residing closer to the peak of $\epsilon_G(T\mathrm{eq})$.
+We predict that these few other inflated \hatpb-analogs should show evidence for significant atmospheric escape, comparable to what we see for \hatpb.
 These sources make excellent targets for \ion{He}{1} 10830 observations, and/or other atmospheric escape diagnostics.
-The key figure-of-merit can be distilled to $\tau_\mathrm{infl}$, and setting the $\epsilon$ term to unity (Eq.
-\ref{eqInflate}).
-Following \citet{2018PASP..130k4401K} we define a Helium Spectroscopy Metric (HeSM):
-
-\begin{eqnarray}
-    \mathrm{HeSM} = \tau_\mathrm{infl} \label{HeSM}
-\end{eqnarray}
+As emphasized, there are significant uncertainties in the inflation timescale, but at least its order-of-magnitude value gives us a quantitative and justified way to prioritize target selection.
 
@@
 \end{deluxetable}
-
-As emphasized, there are significant uncertainties in the inflation timescale, but its order-of-magnitude value gives us a way to prioritize target selection, since these may be the sources most amenable to detection of atmospheric escape.
-Table \ref{tabHeSM} lists $15$ candidates that have nominal lifetimes less than about 40 Myr.
 

### 2023-04-03 paper/paper1/ms.tex
Re-arrange Sec 5.4 to 5.1
Reinflation discussion

@@
 
-\section{Discussion} \label{secDiscuss}
+\section{Causal Interpretations} \label{secDiscuss}
+
+\subsection{Causes for the leading tail} \label{secLeading}
+Several physical phenomena could give rise to a leading tail geometry.  Here we explore the predominant two physical effects: orbital shear and stellar wind confinement.
+
+Figure \ref{fig:KeplerianShear} shows an illustration of Keplerian shear adapted to the system properties of \hatpb.
+In this scenario, the wind launches primarily from the dayside, with relatively little or no wind launched from the nightside.
+The wind initially launches radially from the planet, with the strongest wind located near the sub-stellar point, the line connecting the planet to star along the vertical axis in the figure.
+Inefficient heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemi-spherical shape, but more like a bulb or torpedo.
+The gas increasingly experiences the star's Keplerian potential past the Roche lobe, accelerating in the direction of orbital motion, $+x$.
+The accelerating column eventually overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.
+
+\begin{figure}
+    \includegraphics[width=0.8\linewidth]{figures/KeplerianShear_v0p3.png}
+    \caption{Schematic of Keplerian orbital shear.
+Locations outside the Roche lobe experience orbital shear from the Keplerian potential.
+A wind launched primarily from the dayside will tend to form a leading tail.}
+    \label{fig:KeplerianShear}
+\end{figure}
+
+Stellar wind confinement \citep{2022ApJ...926..226M} arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.
+A trailing tail may also be present, but would not undergo the same boost in density, and would be rapidly carried away by the stellar wind.
+This asymmetry could yield the appearance of a leading tail even if mass loss proceeds isotropically, or the asymmetry could be reinforced by an additional dayside/nightside asymmetry.
+Examples of this asymmetry can be seen in 3D MHD modeling of WASP 107~b \citep{2022ApJ...926..226M}.
+
+The overall observation of a leading tail comports with either of these two physical mechanisms, and both could be at play in \hatpb.
+Here we discuss how the observed line profiles of the gas motions could be interpreted in these two paradigms.
 
@@
 
-\subsection{Causes for the leading tail} \label{secLeading}
-Several physical phenomena could give rise to a leading tail geometry.  Here we explore the predominant two physical effects: orbital shear and stellar wind confinement.
-
-Figure \ref{fig:KeplerianShear} shows an illustration of Keplerian shear adapted to the system properties of \hatpb.
-In this scenario, the wind launches primarily from the dayside, with relatively little or no wind launched from the nightside.
-The wind initially launches radially from the planet, with the strongest wind located near the sub-stellar point, the line connecting the planet to star along the vertical axis in the figure.
-Inefficient heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemi-spherical shape, but more like a bulb or torpedo.
-The gas increasingly experiences the star's Keplerian potential past the Roche lobe, accelerating in the direction of orbital motion, $+x$.
-The accelerating column eventually overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.
-
-\begin{figure}
-    \includegraphics[width=0.8\linewidth]{figures/KeplerianShear_v0p3.png}
-    \caption{Schematic of Keplerian orbital shear.
-Locations outside the Roche lobe experience orbital shear from the Keplerian potential.
-A wind launched primarily from the dayside will tend to form a leading tail.}
-    \label{fig:KeplerianShear}
-\end{figure}
-
-Stellar wind confinement \citep{2022ApJ...926..226M} arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.
-A trailing tail may also be present, but would not undergo the same boost in density, and would be rapidly carried away by the stellar wind.
-This asymmetry could yield the appearance of a leading tail even if mass loss proceeds isotropically, or the asymmetry could be reinforced by an additional dayside/nightside asymmetry.
-Examples of this asymmetry can be seen in 3D MHD modeling of WASP 107~b \citep{2022ApJ...926..226M}.
-
-The overall observation of a leading tail comports with either of these two physical mechanisms, and both could be at play in \hatpb.
-Here we discuss how the observed line profiles of the gas motions could be interpreted in these two paradigms.
-
 %\begin{figure*}[t]
@@
 
-\section{The Ohmic Dissipation Cliff}
+\subsection{Reinflation}
+Evolved stars increase in size, delivering greater insolation to planets at a fixed separation.
+The heightened equilibrium temperature can cause mature planets to inflate, a phenomenon known as \emph{reinflation}.
+Such re-inflated hot planets around red giant stars have been recently found by \emph{TESS} \citep{2022AJ....163..120G,2023arXiv230306728G}, though not all planets around evolved stars appear to re-inflate \citep{2022AJ....163...53S}.
+
+\citet{2017AJ....153..211Z} estimate that \hatpb~receives about twice the incident flux as a Zero Age Main Sequence (ZAMS) \hatp.
+A doubling of insolation would place the young \hatpb~at a 20\% lower equilibrium temperature of 1600 K.
+Perversely, the $\epsilon_G(T_\mathrm{eq})$ may tend to \emph{decrease} over time since the heating efficiency appears to peak at 2.5\% at 1600 K \citep{2018AJ....155..214T}, and reduce to about 1\% at 1900 K.
+So it's possible that the inflation timescale would remain relatively unchanged over the planet lifetime, despite a doubling of incident radiation.
+Uncertainties in the applicability of these trends to hot Saturns leaves the prospect of reinflation as an open question.
+
 \subsection{Evaporative annihilation as the cause of a lack of sub-Saturns}

### 2023-04-04 paper/paper1/ms.tex
Move spectral non-detections section to appendix

@@
 
-Inflated hot Saturns stand out as another especially extreme category that should exhibit mass loss.
+Inflated hot Saturns stand out as an especially extreme category that should exhibit mass loss.
 Their low gravitational potentials should let go of their atmospheres more readily than their steadfast Hot Jupiter counterparts.
@@
 \citet{2011ApJ...738....1B} predicted runaway inflation of hot Saturns as a consequence of the Ohmic dissipation mechanism.
-Here, a lightly ionized atmosphere experiences drag in a planetary magnetic field, weakly coupling the stellar incident energy into the planetary interior.
+Here, lightly ionized atmospheric flows induce drag in a planetary magnetic field, weakly coupling the stellar incident energy into the planetary interior.
 \citet{2018AJ....155..214T} recognized the above two explanations for the lack of sub-Saturns, while statistically favoring Ohmic dissipation as the mechanism responsible for inflating Hot Jupiters.
@@
 The ability to detect that conceivable mass loss hinges on its observability in spectral tracers.
-Ly$\alpha$, \ion{He}{1} 10833 \AA, and H$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}, but each of these has its own limitations.
+Ly$\alpha$, \ion{He}{1} 10833 \AA, and H$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2022arXiv221116243D,2023MNRAS.518.4357O}, but each of these has its own limitations.
 Ly $\alpha$ can suffer from interstellar medium \ion{H}{1} absorption censoring its low-velocity linecore, for example.
@@
 In particular, metastable Helium's ability to be observed at high spectral resolution from the ground has been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.
-\ion{H}{1} has resulted in at least 14 systems with detections, including \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
-To date, no inflated hot Saturns appear to have been examined, neither in Helium nor other tracers (\emph{c.f.} Figure \ref{fig:instellation}).
+\ion{He}{1} has resulted in at least 14 systems with detections, including \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
+An observational picture of mass loss in hot Saturns appears to be lacking, at least in part due to their intrinsic rarity.
 
@@
     \includegraphics[width=\linewidth]{figures/HAT-P-67b_radius_valley.png}
-    \caption{Overview of exoplanet size versus instellation.
-Inflated Hot Jupiters appear as the cluster of sources larger than Jupiter and receiving up to 100 to 10,000 $\times$ as much insolation.
+    \caption{Overview of exoplanet demographics.
 The pixel bins reflect the observed density of over 5000 planets accessed from the NASA Exoplanet Archive.
-The star symbol shows the inflated position of \hatpb.}
+Detections of atmospheric escape are common among large planets with strong instellation.
+\hatpb---among the most inflated planets known---is an outlier.}
     \label{fig:instellation}
@@
 
-Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, an inflated hot Saturn orbiting an F type sub-giant at an orbital separation of 0.06 AU \citep{2017AJ....153..211Z}.
-The strong insolation combined with \object{HAT-P-67 b}'s low surface gravity makes it an excellent candidate for strong atmospheric mass loss.
-It orbits an evolved star, opening the prospect for ``re-inflation'' as the planet's insolation increased over time with the star's expansion.
+Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, an inflated hot Saturn orbiting an F type sub-giant at an orbital separation of 0.06 AU and a 4.8 day orbital period \citep{2017AJ....153..211Z}.
+Its strong insolation ($T_\mathrm{eq}\sim1900\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
+It orbits an evolved star, opening the prospect for ``re-inflation'' \citep{2022AJ....163...53S,2022AJ....163..120G,2023arXiv230306728G} as the planet's insolation increased over time with the star's expansion.
 Its status as a rare inflated Hot Saturn make \object{HAT-P-67 b} a promising laboratory, including but not limited to, testing the inflationary predictions of the Ohmic dissipation mechanism.
@@
 The observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.
-The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836 \AA, but the core and blue line wings appear relatively pristine.
+The small BERV still means the redward Helium linewing has significant telluric contamination between 10834$-$10836 \AA, but the core and blue line wings appear relatively pristine.
 
-Only 19 out of the 39 nights possess A0V telluric calibration standard stars.  These standard stars, when available, were used to spot-check our telluric mitigation strategy.
+Only 19 out of the 39 nights possess A0V telluric calibration standard stars.  These standard stars, when available, were used to spot-check our telluric masking.
 
@@
 Minor corrections to the parallax uncertainty \citep{2021MNRAS.506.2269E} and bias \citep{2021A&A...649A...4L} appear negligible for the $G=9.98$ source.
-The DR3 parallax places the system about 8.7\% farther than previously estimated by \citet{2017AJ....153..211Z}, which adopted a \emph{Gaia} DR1-informed parallax of $2.92\pm0.23$ mas, including a $-0.325$ mas bias term from \citep{2016ApJ...831L...6S}.
+The DR3 parallax places the system about 8.7\% farther than previously estimated by \citet{2017AJ....153..211Z}, which adopted a \emph{Gaia} DR1-informed parallax of $2.92\pm0.23$ mas, including a systematic $-0.325$ mas bias term \citep{2016ApJ...831L...6S}.
 Its coarse \emph{Gaia}-based estimates for RV and Doppler broadening are consistent with the more precise values published in \citet{2017AJ....153..211Z}.
 Its wide companion HAT-P-67B  \citep{2019MNRAS.490.5088M} has nearly identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
-The IAU naming convention would demand HAT-P-67A\emph{b} to refer to the planet.
+The IAU naming convention would demand HAT-P-67A\emph{b} to refer to the planet, which orbits the primary.
 Hereafter, we simply drop the A designation for notational simplicity, since the wide companion will not factor into our analysis.
@@
 It was not targeted by \emph{Spitzer} or \emph{Hubble}.
+Overall the system appears relative unstudied outside of the discovery paper.
 
@@
     \includegraphics[width=0.7\linewidth]{figures/TESS_HAT-P-67b_overview.png}
-    \caption{Overview of all available TESS Sectors showing 24 full or partial transits with 34 visits with HPF (vertical gray bars), 7 of which coincide with transits, and the rest sample out-of-transit phase.
+    \caption{Overview of all available TESS Sectors showing 24 full or partial transits with 34 visits with HPF (vertical gray bars), 7 of which coincide with transits.
+The rest of the visits sample out-of-transit phases.
 The 8 HPF visits between BTJD 2050 and 2690 are not shown.}
@@
 \subsection{TESS Light Curve}
-Previously, \hatp transits had only been detected with \emph{HATNet} \citep{2004PASP..116..266B} and followed up with KeplerCam on the FLWO 1.2 m telescope \citep{2017AJ....153..211Z}.
+Previously, \hatpb~transits had only been detected with \emph{HATNet} \citep{2004PASP..116..266B} and followed up with KeplerCam on the FLWO 1.2 m telescope \citep{2017AJ....153..211Z}.
 These ground-based photometers were not intended to measure long term stellar variability signals.
@@
 TESS Sectors 51-53 do not show as conspicuous a modulation signal.
-Figure \ref{fig:TESSoverview} shows this modulation in the minimally processed TESS lightcurve.
+The ebb and flow of the modulation can be seen in the minimally processed TESS lightcurve in Figure \ref{fig:TESSoverview}.
 We fit the TESS lightcurve modulation with a quasiperiodic Gaussian Process (GP) model using \texttt{celerite} \citep{celerite1,celerite2}.
@@
 This range may be typical for F stars that have not yet evolved too far into the sub-giant branch \citep{2022ApJ...930....7A}.
-The geometrical constraint includes the 4.7 day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9 day per-Sector fits, slightly preferring the lower 4.7 day modulation as the stellar rotation period.
+The geometrical constraint comports with the 4.7 day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9 day per-Sector fits, slightly preferring the lower 4.7 day modulation as the stellar rotation period.
 The 5.9 day value would require a stellar radius over 3.2$R_\odot$, which appears consistent with only an eccentric orbit model combined with the Geneva isochrone \citep{2017AJ....153..211Z}.
@@
 
-\subsection{HPF analysis}
+\subsection{HPF analysis I: RV fitting}
+\authorcomment1{Insert Quang's work here}
+
+\subsection{HPF analysis II: \ion{He}{1} 10833 \AA}
 The raw 2D echellograms were reduced with the \texttt{Goldilocks} package\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}}, which outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb \citep[LFC,][]{2019Optic...6..233M}.
@@
 We quantified the wavelength dependence by acquiring calibration observations of blank sky in both the target and sky fiber.
-We applied this wavelength-based scale factor to each target spectrum's associated reference sky fiber to achieve near-imperceptible sky-line residuals.
+We applied this wavelength-based scale factor to each target spectrum's associated reference sky fiber to achieve near-imperceptible sky-line subtraction residuals.
 A few lines exhibit residuals which may arise from genuine differences in the local atmospheric conditions between the target and sky fiber.
@@
 
-We estimated bulk characteristics of the Helium lines by fitting a Gaussian line profile to the 10828$-$10838 \AA~region of the residual spectra.
+We estimated bulk characteristics of the Helium excess absorption feature by fitting a Gaussian line profile to the 10828$-$10838 \AA~region of the residual spectra.
 The single line initialized at 10833 \AA~ was intended to aglomerate all three components of the metastable triplet into a single feature, consistent with their appearance in Figure \ref{fig:HPFheliumOverview}.
@@
 Finally, we detect a much weaker but still significant post-egress blue-shifted absorption.
-This lobe appears to decrease linearly in wavelength, corresponding to a characteristic blueshift increasing from near zero at transit midpoint to 80~km/s 12 hours after transit.
+This lobe appears to decrease linearly in wavelength, corresponding to a characteristic blueshift increasing from near zero at transit midpoint to 80~km/s at 12 hours after transit.
 It exhibits a slightly lower line-of-sight velocity distribution of 50 km/s, about half of the peak during transit.
+
+We examined other spectral lines using the same methodology as above, finding no detectable variability in the \ion{Ca}{2} infrared triplet, Hydrogen lines, or other neutral metal lines.
+We show some of the diagnostic plots for these non-detections in Appendix Section \ref{}.
 
@@
     \label{fig:HPFtimeseries}
-\end{figure}
-
-\subsection{Calcium IR Triplet and other line diagnostics}
-We examined the \ion{Ca}{2} IR Triplet lines (Ca IRT) for evidence of variability.
-No variation was seen in these features, which were pre-processed in the same way as the Helium feature.
-Figure \ref{fig:CaPhaseScan} shows a similar phase plot as Figure \ref{fig:HPFscanResid}, adapted to the line at 8662 \AA.
-We see no conspicuous variability at this or any of the other Ca IRT lines.
-We also found no detectable variability in the Pa$\delta$ line at 10050 \AA, nor other deep lines at 10330 \AA~ and elsewhere.
-\ion{He}{1} 10833 appears to be the only conspicuously variable line in the HPF spectrum.
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/Ca8662_phase_2D_diagram_resid.png}
-    \caption{Non-detection of variability in the Calcium IR Triplet line at 8862 $\AA$.  No other HPF lines appear to show any variability.}
-    \label{fig:CaPhaseScan}
 \end{figure}
@@
 
+\section{Spectral variability non-detections}
+\subsection{Calcium IR Triplet and other line diagnostics}
+We examined the \ion{Ca}{2} IR Triplet lines (Ca IRT) for evidence of variability.
+No variation was seen in these features, which were pre-processed in the same way as the Helium feature.
+Figure \ref{fig:CaPhaseScan} shows a similar phase plot as Figure \ref{fig:HPFscanResid}, adapted to the line at 8662 \AA.
+We see no conspicuous variability at this or any of the other Ca IRT lines.
+We also found no detectable variability in the Pa$\delta$ line at 10050 \AA, nor other deep lines at 10330 \AA~ and elsewhere.
+\ion{He}{1} 10833 appears to be the only conspicuously variable line in the HPF spectrum.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/Ca8662_phase_2D_diagram_resid.png}
+    \caption{Non-detection of variability in the Calcium IR Triplet line at 8862 $\AA$.  No other HPF lines appear to show any variability.}
+    \label{fig:CaPhaseScan}
+\end{figure}
+
 \begin{acknowledgements}

### 2023-04-04 paper/paper1/ms.tex
First pass through written edits

@@
 That large fraction of an orbit translates to about 0.1 AU, 130 planetary radii, and well outside of the Roche Lobe, with its Hill radius of merely 2.6 planetary radii.
-We are therefore primarily detecting gas that is entirely unbound from the planet.
+We are unambiguously detecting Roche lobe overlow, gas that is entirely unbound from the planet.
 The leading gas tail does not appear to accelerate, with only a modest blueshift.
@@
 The F7IV-V \object[tau Boo]{$\tau$ Boo} serves as the closest analog with available synthetic x-ray coronal spectra \citep{2011A&A...532A...6S}.
-But \hatp resides closer to the Kraft break than does \object[tau Boo]{$\tau$ Boo}, and the move to hotter F stars may be associated with weakening of the stellar wind and other atmospheric changes leading to the prospect of much lower XUV luminosity for HAT-P-67.
+But \hatp resides closer to the Kraft break than does \object[tau Boo]{$\tau$ Boo}, and the move to hotter F stars may be associated with weakening of the stellar wind and other atmospheric changes leading to the prospect of much lower XUV luminosity for HAT-P-67 \citep{2022ApJ...930....7A}.
 So there remains significant uncertainty about the applicability of the \object[tau Boo]{$\tau$ Boo} XUV spectrum to HAT-P-67.
@@
 
-Equipped with these three SEDs of differing radiation hardness, we explored different mass loss rates and exosphere temperatures.
+Equipped with these two SEDs of differing radiation hardness, we explored different mass loss rates and exosphere temperatures.
 Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 7\times10^{13}$ g/s, and $T_0=9100$~K, with the high XUV spectrum ($L_x/L_\mathrm{bol}=10^{-4}$).
-The model spectrum exhibits approximately the same line width and depth as our HPF observations, making it a conceivable solution.
+This mass loss rate would imply a mass loss rate timescale of $\sim$500 Myr.
+The model spectrum exhibits approximately the same line width and depth as our HPF observations, making it a conceivable solution, albeit one of many.
 
@@
 The accelerating column eventually overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.
+The mass loss has to be large enough to shield the material in order to make it observable in the metastable \ion{He}{1} 10833 \AA triplet.
 
@@
 The predicted range matches HAT-P-67 b's $\sim$1900 K.
-A plausible scaling law relationship approximate to an order-of-magnitude predicts an inflation timescale (Eq.
-20 in \citet{2011ApJ...738....1B}):
+A plausible scaling law relationship approximate to an order-of-magnitude predicts an inflation timescale, Eq.
+20 in \citet{2011ApJ...738....1B}:
 \begin{equation}
@@
 \noindent yielding an incredibly short 5 Myr timescale for \hatpb, assuming a typical $\epsilon\sim0.01$.
-The order of magnitude of this inflation timescale is so fleetingly short that \hatpb~ must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
-We therefore propose that \hatpb~ represents the first and only known example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic Dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
+The order of magnitude of this inflation timescale is so fleetingly short that---according to this scenario---\hatpb~must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
+We therefore propose that \hatpb~ represents the first example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic Dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
 
@@
 
-First, the scaling law arguments that produced Equation \ref{eqInflate} (Eq.
-20 of \citet{2011ApJ...738....1B}) were only proposed as order of magnitude estimates not to be taken too faithfully.
+First, the scaling law arguments that produced Equation \ref{eqInflate} were only proposed as order of magnitude estimates not to be taken too faithfully.
 So a $10\times$ higher inflation timescale of 50 Myr would yield $\dot{M}_\mathrm{infl}\sim10^{14}$ g/s, still a very large mass loss rate, but only a factor of 5 away from the baseline 1D model.
@@
 
-Photoevaporation stands out as a potential cause of dayside/nightside differences in mass loss, with the greatest supersonic motions stemming from the sub-solar point on the planetary dayside, and merely sonic motion originating on the nightside and near the dayside terminator \citep{2009ApJ...693...23M}.
+Photoevaporation stands out as a potential cause of dayside/nightside differences in mass loss, with the greatest supersonic motions stemming from the sub-solar point on the planetary dayside, and merely sonic motion prevailing in latitudinal zonal bands.
+The effect may be boosted if dayside/nightside energy transport proceeds inefficiently \citep{2009ApJ...693...23M}.
 Such a scenario is illustrated in Figure \ref{fig:KeplerianShear}.
-We discuss how dayside/nightside differences could explain the leading tail in the next section.
-
-%\begin{figure*}[t]
-%    \includegraphics[width=\linewidth]{figures/murray_clay_schematic_v0p2.png}
-%    \caption{Schematic of the relevant length scales in a stratified atmosphere, modeled after Figure 8 from \citet{2009ApJ...693...23M}.
-The sonic point resides at a mere 2 atmospheric scale heights, and well below the photoionization level of Hydrogen, raising the possibility that the supersonic flow begins neutral and becomes ionized later on.}
-%    \label{fig:murrayClaySchematic}
-%\end{figure*}
 
@@
 Heating efficiency should initially increase as a function of equilibrium temperature, then degrade as irradiation exceeds equilibrium temperatures of about 2000 K.
-Second, hot Saturns ($\lesssim0.5 M_\mathrm{Jup}$) should undergo runaway evaporation, whereas hot Jupiters ($\gtrsim 1 M_\mathrm{Jup}$) should reach equilibrium---albeit inflated---radii after Gyr timescales.
+Second, hot Saturns ($\lesssim0.5 M_\mathrm{Jup}$) should undergo runaway evaporation, whereas hot Jupiters ($\gtrsim 1 M_\mathrm{Jup}$) should reach stable equilibrium---albeit inflated---radii after Gyr timescales.
 Both of these outcomes predated data that could adequately validate them, and these outcomes differ from the behavior of other heating mechanisms, such as photoevaporation or tides.
@@
 
-The observation that \hatpb---the only hot Saturn searched for atmospheric escape to date---exhibits mass loss indicative of a terminal fate leads us to a natural explanation for the dearth of inflated hot Saturns.
+The observation that \hatpb---the most inflated hot Saturn searched for atmospheric escape to date---exhibits mass loss indicative of a terminal fate leads us to a natural explanation for the dearth of inflated hot Saturns.
 The inflationary lifetime of hot Saturns is so short that observing planets of this class is unlikely.
@@
 
-As seen in Figure \ref{fig:ThornFortUpdated}, \hatpb~ has few other known analogs.
+As seen in Figure \ref{fig:ThornFortUpdated}, \hatpb~has few other known analogs.
 Figure \ref{fig:tf2018_theory} illustrates why: the inflationary lifetime for planets with comparable mass, radius, and $T_\mathrm{eq}$ is exceptionally short, and so they are rare.
@@
 We interpolate the $T_\mathrm{eq}$ trendlines from Fig.
-\ref{fig:ThornFortUpdated} to compute $\tau_\mathrm{infl}$ from Equation\ref{eqInflate}, including the best fit Gaussian prescription for $\hat{\epsilon_G}$ from Eq.
+\ref{fig:ThornFortUpdated} to compute $\tau_\mathrm{infl}$ from Equation \ref{eqInflate}, including the best fit Gaussian prescription for $\hat{\epsilon}_G$ from Eq.
 34 of \citet{2018AJ....155..214T}.
@@
 
-\subsection{HAT-P-67b analogues}
+\subsection{HAT-P-67 b analogues}
 
-The key figure-of-merit can be distilled to $\tau_\mathrm{infl}$, whic can be thought of as an atmospheric escape metric \citep{2018PASP..130k4401K} for inflated planets in the shaded regime of Figure \ref{fig:tf2018_theory}.
+The key figure-of-merit can be distilled to $\tau_\mathrm{infl}$, whic can be thought of as an atmospheric escape spectroscopy metric \citep{2018PASP..130k4401K} for inflated planets in the shaded regime of Figure \ref{fig:tf2018_theory}.
 Table \ref{tabHeSM} presents the rank-ordered list of planets by this metric, indicating that they are mostly smaller and more massive than \hatpb.
-Only KELT-11~b shows a shorter nominal inflationary timescale than \hatpb, owing to its low mass and equilibrium temperature residing closer to the peak of $\epsilon_G(T\mathrm{eq})$.
+Only KELT-11~b shows a shorter nominal inflationary timescale than \hatpb, owing to its low mass and equilibrium temperature residing closer to the peak of $\epsilon_G(T_\mathrm{eq})$.
 We predict that these few other inflated \hatpb-analogs should show evidence for significant atmospheric escape, comparable to what we see for \hatpb.
@@
 
+\section{Discussion}
 \subsection{Cause for stellar modulation}
-The \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $p=4.8-5.2$ days.
+As discussed in Section \censor{x}, the \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $p=4.7-5.9$ days.
 Some sectors exhibit lower amplitudes.
@@
 
-Alternatively, the exteme mass loss and credibility of the ohmic diffusion model motivates the prospect of Star Planet Magnetic Interaction (SPMI) that we consider now.
+Alternatively, the exteme mass loss and credibility of the Ohmic dissipation model motivates the prospect of Star Planet Magnetic Interaction (SPMI) that we consider now.
 In this scenario, the magnetic field of the planet permeates the space between the star and planet.
@@
 
-%\subsection{Timescale for tidal synchronization}
-
-%\subsection{Hot Spot Scenario}
-%The TESS 0.2\% flux variation could hypothetically arise from the foot-print of a star-planet interaction.
-Assuming that this increase in flux is due to a hot spot with a contrast of 200\% the ambient photosphere in the TESS bandpass, the hot spot would have a modest 5\% coverage fraction.
-Thermal radiation from gravitational infall alone cannot explain the luminosity of this spot, so it would have to stem from a non-thermal cause.
-
-%\subsection{Tidal Locking Calculation}
-%The similarity of the rotation period with the orbital period suggests the star-planet system may be tidally locked.
-
-%\subsection{Mass Loss Rate}
-%A steady state mass loss rate greater than $2\times10^{12}$ g/s would erode the planet over the age of the stellar system.
-
-%\subsection{Confinement to Stellar Wind}
-%\subsection{Limits of Stellar Activity Metrics}
-%\subsection{Comparison to Other Systems}
 \section{Conclusions}
@@
 \appendix
-%\section{HPF spectra post-processing}
-%\label{methods-details}
 
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/Ca8662_phase_2D_diagram_resid.png}
+\begin{figure}[b]
+    \includegraphics[width=0.5\linewidth]{figures/Ca8662_phase_2D_diagram_resid.png}
     \caption{Non-detection of variability in the Calcium IR Triplet line at 8862 $\AA$.  No other HPF lines appear to show any variability.}

### 2023-04-11 paper/paper1/ms.tex
Add revised properties from HPF/TESS fit from Quang Tran
Some text for the RV fitting and orbit determination

@@
 \newcommand{\vmic}{\ensuremath{v_{\rm mic}}}
+\newcommand{\ms}{\ensuremath{\rm m\,s^{-1}}}
 % Activity index R'_HK
@@
 \newcommand{\mpl}{\ensuremath{M_{p}}}
+\newcommand{\kms}{\ensuremath{\rm km\,s^{-1}}}
 \newcommand{\lpl}{\ensuremath{L_{p}}}
@@
 
-\begin{deluxetable*}{lrrrh}
-    \tablewidth{0pc}
-    \tabletypesize{\scriptsize}
-    \tablecaption{
-        Revised orbital and planetary parameters
-        \label{tabOrbit}
-    }
-    \tablehead{
-        \colhead{Parameter}   &
-        \colhead{Zhou et al. 2017} &
-        \colhead{Ivshina \& Winn 2022} &
-        \colhead{This Work} &
-        \nocolhead{Alternate}
-    }
-    \startdata
-    %%
-    ~~~$P$ (days)             \dotfill    & $4.8101025_{-3.3\times 10^{-7}}^{+4.3\times 10^{-7}}$ & 4.8101046$\pm1.7\times10^{-6}$ & 4.81011 & z \\
-    ~~~$T_c$ (${\rm BTJD}$)  \dotfill    & $-1038.61533_{-0.00064}^{+0.00076}$ & 1958.08059$\pm$0.00032 & 1958.07933 & z \\
-    ~~~$T_{14}$ (hours)  \dotfill    & $6.9888 \pm 0.046$ &  & 7.0636 & z \\
-    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ &  & 0.08231 & z \\
-    ~~~$b \equiv a \cos i/\rstar$
-    \dotfill    & $0.12_{-0.08}^{+0.12}$ &  & 0.45616 & z \\
-    \enddata
-\end{deluxetable*}
+\input{tables/revise_props_tbl.tex}
 
 \subsection{HPF analysis I: RV fitting}
-\authorcomment1{Insert Quang's work here}
+
+We reduced and analyzed the HPF data first for the purpose of orbit fitting via precision radial velocity measurements following the procedures described in \citet{2021AJ....161..173T} and updated for joint lightcurve and RV fits \citep{2022AJ....163..225T}.
+Here we included the new TESS lightcurves, and the existing Keck HIRES points reported in Table 3 of \citet{2017AJ....153..211Z}.
+The HPF points exhibited an RV jitter of $\sim164\kms$, a few times larger than the typical Keck HIRES measurements.
+So even though the HPF points were more numerous, their marginal value for RV orbit determination was subdued owing to the lower RV information content in the near-IR for this relatively rapidly rotating F star.
+Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$, slightly decreasing the uncertainty compared to the previous $1\sigma$ limit.
+Table \ref{tabOrbit} lists the revised properties, with minor differences from the existing values.
+Notably our fit does not jointly model the Doppler tomographic signals reported in \citep{2017AJ....153..211Z}, which would further constrain the impact parameter.
+Additionally our input $\rstar$ was slightly lower than the best fit value derived from \emph{Gaia DR3} and SED fitting.
+\authorcomment1{Quang Tran: please verify and revise.}
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/HAT-P-67b_rv.pdf}
+    \caption{RV orbit fit including both HPF and Keck HIRES data points.}
+    \label{fig:RVfit}
+\end{figure}
 

### 2023-04-11 paper/paper1/ms.tex
Add MIST evolutionary tracks

@@
 
-\subsection{Gaia DR3}
+\subsection{Gaia DR3}\label{gaiaDR3}
 \citet{2017AJ....153..211Z} previously derived stellar radius estimates of 2.1-2.7 $R_\odot$ through Spectral Energy Distribution (SED) isochrone fitting as part of a joint orbit fit.
@@
 
+\subsection{Revised system evolutionary state}
+As discussed in Section \ref{gaiaDR3}, the slightly increased distance and radius implies a slightly more luminous host star than previously estimated.
+Figure \ref{fig:evolTracks} shows evolutionary tracks using the solar-metallicity MESA \citep{2011ApJS..192....3P,2013ApJS..208....4P,2015ApJS..220...15P} Isochrones and Stellar Tracks \citep[MIST;]{2016ApJS..222....8D,2016ApJ...823..102C} for \hatp.
+The tracks show that a 1.8 Gyr, 1.64 $M_\odot$ \hatp~ could be at the end of its main sequence lifetime (teal track), yielding a gradual rise in incident radiation to \hatpb.
+Alternatively, a 1.54 $M_\odot$ evolutionary track would send \hatp~ along the subgiant branch at an age over 2.2 Gyr, with a rapid 50\% increase in luminosity, potentially leading to ``re-inflation'' of the planet \citep{2021ApJ...909L..16T}.
+Either evolutionary track appears consistent with the observed SED, stellar surface gravity, and available constraints from spectral fitting.
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.7\linewidth]{figures/MIST_tracks_HATP.png}
+    \caption{MIST evolutionary model tracks for \hatp.  The $T_\mathrm{eff}$ and luminosity of \hatp~ (gray circle) are consistent with either the late main sequence or recently evolved subgiant.}
+    \label{fig:evolTracks}
+\end{figure*}
+
 \subsection{HPF analysis I: RV fitting}
@@
 Here we included the new TESS lightcurves, and the existing Keck HIRES points reported in Table 3 of \citet{2017AJ....153..211Z}.
-The HPF points exhibited an RV jitter of $\sim164\kms$, a few times larger than the typical Keck HIRES measurements.
+The HPF points exhibited an RV jitter of $\sim164\;\kms$, a few times larger than the typical Keck HIRES measurements.
 So even though the HPF points were more numerous, their marginal value for RV orbit determination was subdued owing to the lower RV information content in the near-IR for this relatively rapidly rotating F star.
@@
 \subsection{HPF analysis II: \ion{He}{1} 10833 \AA}
-The raw 2D echellograms were reduced with the \texttt{Goldilocks} package\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}}, which outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb \citep[LFC,][]{2019Optic...6..233M}.
+The preparation for analyzing the Helium feature followed a similar but slightly different procedure than that used for the RV, namely we used \texttt{Goldilocks}\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}} for 2D echellogram reduction.
+This tool outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb \citep[LFC,][]{2019Optic...6..233M}.
 The observations were usually acquired with the LFC turned off, so this unilluminated spectrum was discarded.
@@
 
-\citet{2017AJ....153..211Z} estimate that \hatpb~receives about twice the incident flux as a Zero Age Main Sequence (ZAMS) \hatp.
+\citet{2017AJ....153..211Z} estimated that \hatpb~received about twice the incident flux as a Zero Age Main Sequence (ZAMS) \hatp.
 A doubling of insolation would place the young \hatpb~at a 20\% lower equilibrium temperature of 1600 K.
@@
 So it's possible that the inflation timescale would remain relatively unchanged over the planet lifetime, despite a doubling of incident radiation.
-Uncertainties in the applicability of these trends to hot Saturns leaves the prospect of reinflation as an open question.
 

### 2023-04-11 paper/paper1/ms.tex
Countervailing of reinflation scenarios

@@
 
-\subsection{Revised system evolutionary state}
+\subsection{Revised system evolutionary state}\label{secMISTtracks}
 As discussed in Section \ref{gaiaDR3}, the slightly increased distance and radius implies a slightly more luminous host star than previously estimated.
@@
 
-\citet{2017AJ....153..211Z} estimated that \hatpb~received about twice the incident flux as a Zero Age Main Sequence (ZAMS) \hatp.
+\citet{2017AJ....153..211Z} estimated that \hatpb~received about twice the incident flux as a Zero Age Main Sequence (ZAMS) \hatp, based on comparison to the Geneva isochrones.
+In Section \ref{secMISTtracks} MIST evolutionary tracks showed two equally plausible states: the tail-end of the main sequence or a recently evolved sub-giant.
+Figure X employs these tracks to assess what the impact on \hatpb~could be, assuming that the orbital location has not changed over the system lifetime (\emph{i.e.} star-planet or planet-planet migration has been negligible).
+The second panel from the top illustrates a countervailing effect: the decrease in Ohmic dissipation heating efficiency, $\epsilon$, could counteract the increase of stellar flux, assuming the functional form for $\hat{\epsilon}_G$ described by \citet{2018AJ....155..214T}.
+Together the effects nearly cancel when computing the inflationary lifetimes, yielding nearly identical curves in the bottom panel.
+The third panel recreates the numerically computed curve for $0.5\;M_\mathrm{Jup}$, $T_\mathrm{eq}=$1800 K from \citep{2011ApJ...738....1B}, which should be considered as representative since it was not necessarily tailored to the evolutionary history of \hatpb.
+Nevertheless, the similarly of curve is remarkable since it arrives at approximately the correct planet radius at the right age.
+The modeled mass is slightly higher than, but consistent with the RV-measured mass, and could imply a large and increasing mass loss rate over its lifetime.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/reinflation_MIST.png}
+    \caption{Conceivable evolutionary scenarios for \hatpb.
+The planet equilibrium temperature increases as the stellar luminosity gradually increases on the main sequence.
+The Ohmic dissipation model makes predictions for runaway inflation, depending on the incident stellar flux.
+The heuristic scaling relation for inflation timescale predicts unusually small values in this extreme regime, but illustrates the countervailing effects of the top two panels.}
+    \label{fig:OhmicInflate}
+\end{figure}
+
 A doubling of insolation would place the young \hatpb~at a 20\% lower equilibrium temperature of 1600 K.

### 2023-04-13 paper/paper1/ms.tex
Paper edits from written text

@@
 
-Atmospheric escape appears to be a compulsory phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5-2.0~$R_\oplus$ planets \citep{2017AJ....154..109F}.
+Atmospheric escape appears to be a compulsory phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5$-$2.0~$R_\oplus$ planets \citep{2017AJ....154..109F}.
 The leading candidate physical mechanisms for this rapid transition between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G}.
-Whatever the cause, some large fraction of planets must undergo atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations such as transiting planets.
+Whatever the cause, some large fraction of planets must undergo transformative atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations such as transiting planets.
 Such signals have been searched for and increasingly found, with at least 28 detections to date \citep{2022arXiv221116243D}.
@@
 These intrinsic or extrinsic factors may include close proximity to host star, low surface gravity, and high energy incident radiation.
-The small planet radius gap between 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of eroding to their final rocky state.
+The small planet radius gap between 1.5$-$2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of eroding to their final rocky state.
 
@@
 \citet{2018AJ....155..214T} recognized the above two explanations for the lack of sub-Saturns, while statistically favoring Ohmic dissipation as the mechanism responsible for inflating Hot Jupiters.
-Ohmic dissipation does not preclude the existence and role of other heating mechanisms---such as photoevaporation and tidal heating---but it does stand out has having made these predictions before data were widely available to test them.
+Therefore Ohmic dissipation stands out as a leading physical mechanism unifying several observations.
+Ohmic dissipation does not preclude the existence and role of other heating mechanisms---such as photoevaporation and tidal heating---but it does stand out has having made successful predictions before data were widely available to test them.
 
-The runaway inflation scenario could yield a profound mass loss rate for inflated hot Saturns, possibly much larger than we have seen in previous systems.
+A runaway inflation scenario implies an inevitable and profound mass loss rate for inflated hot Saturns.
+The planet's atmosphere overflows its Roche lobe at an ever increasing pace, yielding instantaneous mass loss rates possibly much larger than we have seen in previous long-term stable systems.
 The ability to detect that conceivable mass loss hinges on its observability in spectral tracers.
@@
 Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, an inflated hot Saturn orbiting an F type sub-giant at an orbital separation of 0.06 AU and a 4.8 day orbital period \citep{2017AJ....153..211Z}.
-Its strong insolation ($T_\mathrm{eq}\sim1900\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
-It orbits an evolved star, opening the prospect for ``re-inflation'' \citep{2022AJ....163...53S,2022AJ....163..120G,2023arXiv230306728G} as the planet's insolation increased over time with the star's expansion.
+Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
+It orbits a possibly evolved subgiant, opening the prospect for ``re-inflation'' \citep{2022AJ....163...53S,2022AJ....163..120G,2023arXiv230306728G} as the planet's insolation increased with the star's rapid luminosity increase.
+The tidal gravity of the nearby massive host star may accelerate mass loss rates even further \citep{2007A&A...472..329E}.
 Its status as a rare inflated Hot Saturn make \object{HAT-P-67 b} a promising laboratory, including but not limited to, testing the inflationary predictions of the Ohmic dissipation mechanism.
@@
 These campaigns have out-of-transit observations at least one night before and one night after, and often two nights on either side of the transit.
-Two more transits were obtained in 2022 June-July without the visits immediately before and after.
+Two more transits were obtained in 2022 June-July without the accompanying visits immediately before and after.
 The in-transit nights had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.
@@
 
-The observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.
+The observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature \citep{2022ApJ...939L..11S}.
 The small BERV still means the redward Helium linewing has significant telluric contamination between 10834$-$10836 \AA, but the core and blue line wings appear relatively pristine.
 
-Only 19 out of the 39 nights possess A0V telluric calibration standard stars.  These standard stars, when available, were used to spot-check our telluric masking.
+Only 19 out of the 39 nights possess A0V telluric calibration standard stars.  These standard stars were used to spot-check our telluric masking.
 
@@
 
-\subsection{ASAS-SN}
-We retrieved ground-based photometry with the \emph{All-Sky Automated Survey for Supernovae} (ASAS-SN) using the Sky-Portal \citep{shappee14,2017PASP..129j4502K}.
-The precision of ASAS-SN was too low to perceive stellar variability, and so we can place a relatively uninformative limit of $<5\%$ stellar variability on years-long timescales.
-
-\subsection{DASCH}
-\hatp appears in the Harvard Plate Archive, with 5809 measurements digitized through DASCH, spanning over 120 years of coarse photometric monitoring.
-In principle these datasets could inform long-term variability trends such as stellar cycles.
-In practice the 0.15 magnitude jitter appears too coarse to perceive any genuine astrophysical variability, with no conspicuous trend seen.
-We can therefore place a relatively mild constraint that the star is stable at the $\sim30\%$ level over periods of tens to hundreds of years.
-
 \subsection{Gaia DR3}\label{gaiadr3}
@@
 Its coarse \emph{Gaia}-based estimates for RV and Doppler broadening are consistent with the more precise values published in \citet{2017AJ....153..211Z}.
-Its wide companion HAT-P-67B  \citep{2019MNRAS.490.5088M} has nearly identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
+The wide companion HAT-P-67B has nearly identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
 The IAU naming convention would demand HAT-P-67A\emph{b} to refer to the planet, which orbits the primary.
 Hereafter, we simply drop the A designation for notational simplicity, since the wide companion will not factor into our analysis.
+
+\subsection{ASAS-SN, DASCH, and ZTF}
+We retrieved ground-based photometry with the \emph{All-Sky Automated Survey for Supernovae} (ASAS-SN) using the Sky-Portal \citep{shappee14,2017PASP..129j4502K}.
+The precision of ASAS-SN was too low to perceive stellar variability, and so we can place a relatively uninformative limit of $<5\%$ stellar variability on years-long timescales.
+
+Similarly, \hatp appears in the Harvard Plate Archive, with 5809 measurements digitized through the Digital Access to a Sky Century at Harvard (DASCH) program, spanning over 120 years of coarse photometric monitoring.
+In principle these datasets could inform long-term variability trends such as stellar cycles.
+In practice the 0.15 magnitude jitter appears too coarse to perceive any genuine astrophysical variability, with no conspicuous trend seen.
+We can therefore place a relatively mild constraint that the star is stable at the $\sim30\%$ level over periods of tens to hundreds of years.
+
+HAT-P-67A was saturated in ZTF, but the M-dwarf companion HAT-P-67B had up to thousands of visits across several years.
+The data quality appeared too poor to perceive any genuine astrophysical variability, with the indication of some lunar background signals in the periodogram.
 
@@
 The other archival observations have been previously reported by \citet{2017AJ....153..211Z}, including Keck HIRES, Keck NIRC2, and WIYN High-Resolution Infrared Camera.
-The northern source does not appear in ESO archives, nor the Gemini Archive, and it is not publicly accessible in the Zwicky Transient Factory (ZTF) archive.
-It was not targeted by \emph{Spitzer} or \emph{Hubble}.
 Overall the system appears relative unstudied outside of the discovery paper.

### 2023-04-17 paper/paper1/ms.tex
Run text through grammarly

@@
 Nevertheless, we can boost our chances of witnessing active and significant atmospheric escape by targeting sources that seem predisposed to loss.
-These intrinsic or extrinsic factors may include close proximity to host star, low surface gravity, and high energy incident radiation.
+These intrinsic or extrinsic factors may include proximity to the host star, low surface gravity, and high energy incident radiation.
 The small planet radius gap between 1.5$-$2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of eroding to their final rocky state.
@@
 The cause for their underabundance remains an open question, with two leading candidate explanations.
-Tidal migration mechanisms may be mass-dependent in such a way as to proceed efficiently for Jupiter-mass planets, but inefficiently for the lower mass Saturns.
+Tidal migration mechanisms may be mass-dependent in such a way as to proceed efficiently for Jupiter-mass planets, but inefficiently for the lower-mass Saturns.
 In this scenario, sub-Saturn mass planets never make it to the close-in orbital separations that would lead to the conditions needed for inflation in the first place.
@@
 Alternatively---and most consequentially for atmospheric escape---another explanation may prevail.
-Inflated hot Saturns may effectively migrate to close-in orbital separations, but once they arrive, the intense irradation overheats the planet.
+Inflated hot Saturns may effectively migrate to close-in orbital separations, but once they arrive, the intense irradiation overheats the planet.
 This heating leads to runaway inflation and ultimately complete disintegration.
@@
 Therefore Ohmic dissipation stands out as a leading physical mechanism unifying several observations.
-Ohmic dissipation does not preclude the existence and role of other heating mechanisms---such as photoevaporation and tidal heating---but it does stand out has having made successful predictions before data were widely available to test them.
+Ohmic dissipation does not preclude the existence and role of other heating mechanisms---such as photoevaporation and tidal heating---but it does stand out as having made successful predictions before data were widely available to test them.
 
 A runaway inflation scenario implies an inevitable and profound mass loss rate for inflated hot Saturns.
-The planet's atmosphere overflows its Roche lobe at an ever increasing pace, yielding instantaneous mass loss rates possibly much larger than we have seen in previous long-term stable systems.
+The planet's atmosphere overflows its Roche lobe at an ever-increasing pace, yielding instantaneous mass loss rates possibly much larger than we have seen in previous long-term stable systems.
 The ability to detect that conceivable mass loss hinges on its observability in spectral tracers.
 Ly$\alpha$, \ion{He}{1} 10833 \AA, and H$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2022arXiv221116243D,2023MNRAS.518.4357O}, but each of these has its own limitations.
-Ly $\alpha$ can suffer from interstellar medium \ion{H}{1} absorption censoring its low-velocity linecore, for example.
+Ly $\alpha$ can suffer from interstellar medium \ion{H}{1} absorption censoring its low-velocity line core, for example.
 Here we focus on \ion{He}{1} 10833 \AA, which offers some advantages over Ly$\alpha$.
@@
 The pixel bins reflect the observed density of over 5000 planets accessed from the NASA Exoplanet Archive.
-Detections of atmospheric escape are common among large planets with strong instellation.
+Detections of atmospheric escape are common among large planets with strong insolation.
 \hatpb---among the most inflated planets known---is an outlier.}
@@
 
-Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, an inflated hot Saturn orbiting an F type sub-giant at an orbital separation of 0.06 AU and a 4.8 day orbital period \citep{2017AJ....153..211Z}.
+Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, an inflated hot Saturn orbiting an F type sub-giant at an orbital separation of 0.06 AU and a 4.8-day orbital period \citep{2017AJ....153..211Z}.
 Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
@@
 The tidal gravity of the nearby massive host star may accelerate mass loss rates even further \citep{2007A&A...472..329E}.
-Its status as a rare inflated Hot Saturn make \object{HAT-P-67 b} a promising laboratory, including but not limited to, testing the inflationary predictions of the Ohmic dissipation mechanism.
+Its status as a rare inflated Hot Saturn makes \object{HAT-P-67 b} a promising laboratory, including but not limited to, testing the inflationary predictions of the Ohmic dissipation mechanism.
 
@@
 In practice, this limitation means that in-transit and out-of-transit observational phases were rarely possible on the same night.
-Instead, we organized the observations into four campaigns to coincide with \object{HAT-P-67 b} transits on the nights beginning 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.
+Instead, we organized the observations into four campaigns to coincide with \object{HAT-P-67 b} transits on the nights beginning 2020 April 28, 2020; May 22, 2020; June 15, 2020; and 2022 April 28.
 These campaigns have out-of-transit observations at least one night before and one night after, and often two nights on either side of the transit.
@@
 The in-transit nights had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.
-We also obtained random-in-phase low priority ``P4'' queue-filler observations.
+We also obtained random-in-phase low-priority ``P4'' queue-filler observations.
 These out-of-transit snapshot observations typically received 4 or fewer individual exposures.
-We observed HAT-P-67 with HPF for a total 41 visits on 39 unique nights, with two of those nights observing both an east and a west HET track.
+We observed HAT-P-67 with HPF for a total of 41 visits on 39 unique nights, with two of those nights observing both an east and a west HET track.
 The total on-source integration time exceeds 13.8 hours.
@@
 
-The observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature \citep{2022ApJ...939L..11S}.
-The small BERV still means the redward Helium linewing has significant telluric contamination between 10834$-$10836 \AA, but the core and blue line wings appear relatively pristine.
+The observation schedule was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature \citep{2022ApJ...939L..11S}.
+The small BERV still means the redward Helium line wing has significant telluric contamination between 10834$-$10836 \AA, but the core and blue line wings appear relatively pristine.
 
@@
 Its coarse \emph{Gaia}-based estimates for RV and Doppler broadening are consistent with the more precise values published in \citet{2017AJ....153..211Z}.
-The wide companion HAT-P-67B has nearly identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with projected separation of about 3400 AU.
+The wide companion HAT-P-67B has nearly identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with a projected separation of about 3400 AU.
 The IAU naming convention would demand HAT-P-67A\emph{b} to refer to the planet, which orbits the primary.
@@
 We retrieved ground-based photometry with the \emph{All-Sky Automated Survey for Supernovae} (ASAS-SN) using the Sky-Portal \citep{shappee14,2017PASP..129j4502K}.
-The precision of ASAS-SN was too low to perceive stellar variability, and so we can place a relatively uninformative limit of $<5\%$ stellar variability on years-long timescales.
+The precision of ASAS-SN was too low to perceive stellar variability, so we can place a relatively uninformative limit of $<5\%$ stellar variability on years-long timescales.
 
 Similarly, \hatp appears in the Harvard Plate Archive, with 5809 measurements digitized through the Digital Access to a Sky Century at Harvard (DASCH) program, spanning over 120 years of coarse photometric monitoring.
-In principle these datasets could inform long-term variability trends such as stellar cycles.
-In practice the 0.15 magnitude jitter appears too coarse to perceive any genuine astrophysical variability, with no conspicuous trend seen.
+In principle, these datasets could inform long-term variability trends such as stellar cycles.
+In practice, the 0.15 magnitude jitter appears too coarse to perceive any genuine astrophysical variability, with no conspicuous trend seen.
 We can therefore place a relatively mild constraint that the star is stable at the $\sim30\%$ level over periods of tens to hundreds of years.
@@
 The other archival observations have been previously reported by \citet{2017AJ....153..211Z}, including Keck HIRES, Keck NIRC2, and WIYN High-Resolution Infrared Camera.
-Overall the system appears relative unstudied outside of the discovery paper.
+Overall the system appears relatively unstudied outside of the discovery paper.
 
@@
 For a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius.
-This update systematically decreases the estimate for the already-low density of HAT-P-67 by 28\%, to a mere 0.035 g$\;$cm$^{-3}$, albeit with significant uncertainties from the weak mass constraint, and from the model dependence of multiple orbit fits.
+This update systematically decreases the estimate for the already-low density of HAT-P-67 by 28\%, to a mere 0.035 g$\;$cm$^{-3}$, albeit with significant uncertainties from the weak mass constraint.
 
@@
 Previously, \hatpb~transits had only been detected with \emph{HATNet} \citep{2004PASP..116..266B} and followed up with KeplerCam on the FLWO 1.2 m telescope \citep{2017AJ....153..211Z}.
-These ground-based photometers were not intended to measure long term stellar variability signals.
-We therefore examined the \emph{TESS} lightcurves for out-of-transit photometric variability.
+These ground-based photometers were not intended to measure long-term stellar variability signals.
+We, therefore, examined the \emph{TESS} lightcurves for out-of-transit photometric variability.
 The revised precision and continuous coverage of \emph{TESS} can refine the orbital solution.
@@
 Figure \ref{fig:transit} shows the best-fit orbit overlaid on the detrended TESS lightcurve.
-Table \ref{tabOrbit} lists one of the previous orbit determinations and solution reported here.
+Table \ref{tabOrbit} lists one of the previous orbit determinations and the orbital solution reported here.
 
@@
 We fit the TESS lightcurve modulation with a quasiperiodic Gaussian Process (GP) model using \texttt{celerite} \citep{celerite1,celerite2}.
-The GP model fit to the entire composite lightcurve yields a period of 4.7 days; when fit to individual sectors alone the periods hover around 5.9 days.
+The GP model fit to the entire composite lightcurve yields a 4.7-day period; when fit to individual sectors alone the periods hover around 5.9 days.
 
@@
 This range may be typical for F stars that have not yet evolved too far into the sub-giant branch \citep{2022ApJ...930....7A}.
-The geometrical constraint comports with the 4.7 day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9 day per-Sector fits, slightly preferring the lower 4.7 day modulation as the stellar rotation period.
-The 5.9 day value would require a stellar radius over 3.2$R_\odot$, which appears consistent with only an eccentric orbit model combined with the Geneva isochrone \citep{2017AJ....153..211Z}.
+The geometrical constraint comports with the 4.7-day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9-day per-Sector fits, slightly preferring the lower 4.7-day modulation as the stellar rotation period.
+The 5.9-day value would require a stellar radius over 3.2$R_\odot$, which appears consistent with only an eccentric orbit model combined with the Geneva isochrone \citep{2017AJ....153..211Z}.
 
@@
 \subsection{Revised system evolutionary state}\label{secMISTtracks}
-As discussed in Section \ref{gaiaDR3}, the slightly increased distance and radius implies a slightly more luminous host star than previously estimated.
+As discussed in Section \ref{gaiaDR3}, the slightly increased distance and radius imply a slightly more luminous host star than previously estimated.
 Figure \ref{fig:evolTracks} shows evolutionary tracks using the solar-metallicity MESA \citep{2011ApJS..192....3P,2013ApJS..208....4P,2015ApJS..220...15P} Isochrones and Stellar Tracks \citep[MIST;]{2016ApJS..222....8D,2016ApJ...823..102C} for \hatp.
@@
 
-We reduced and analyzed the HPF data first for the purpose of orbit fitting via precision radial velocity measurements following the procedures described in \citet{2021AJ....161..173T} and updated for joint lightcurve and RV fits \citep{2022AJ....163..225T}.
-Here we included the new TESS lightcurves, and the existing Keck HIRES points reported in Table 3 of \citet{2017AJ....153..211Z}.
+We reduced and analyzed the HPF data first for orbit fitting via precision radial velocity (PRV) measurements following the procedures described in \citet{2021AJ....161..173T} and updated for joint lightcurve and RV fits \citep{2022AJ....163..225T}.
+Here we included the new TESS lightcurves and the existing Keck HIRES points reported in Table 3 of \citet{2017AJ....153..211Z}.
 The HPF points exhibited an RV jitter of $\sim164\;\kms$, a few times larger than the typical Keck HIRES measurements.
@@
 Table \ref{tabOrbit} lists the revised properties, with minor differences from the existing values.
-Notably our fit does not jointly model the Doppler tomographic signals reported in \citep{2017AJ....153..211Z}, which would further constrain the impact parameter.
-Additionally our input $\rstar$ was slightly lower than the best fit value derived from \emph{Gaia DR3} and SED fitting.
+Notably, our fit does not jointly model the Doppler tomographic signals reported in \citep{2017AJ....153..211Z}, which would further constrain the impact parameter.
+Additionally, our input $\rstar$ was slightly lower than the best-fit value derived from \emph{Gaia DR3} and SED fitting.
 \authorcomment1{Quang Tran: please verify and revise.}
@@
 \subsection{HPF analysis II: \ion{He}{1} 10833 \AA}
-The preparation for analyzing the Helium feature followed a similar but slightly different procedure than that used for the RV, namely we used \texttt{Goldilocks}\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}} for 2D echellogram reduction.
+The preparation for analyzing the Helium feature followed a similar but slightly different procedure than that used for the RV, namely, we used \texttt{Goldilocks}\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}} for 2D echellogram reduction.
 This tool outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb \citep[LFC,][]{2019Optic...6..233M}.
@@
 We applied this wavelength-based scale factor to each target spectrum's associated reference sky fiber to achieve near-imperceptible sky-line subtraction residuals.
-A few lines exhibit residuals which may arise from genuine differences in the local atmospheric conditions between the target and sky fiber.
+A few lines exhibit residuals that may arise from genuine differences in the local atmospheric conditions between the target and sky fiber.
 
@@
 Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 region of interest, with all 152 individual exposures overlaid.
-We see a variability in the Helium line of up to 10\%, much greater than the $<1\%$ pixel-to-pixel variation.
+We see variability in the Helium line of up to 10\%, much greater than the $<1\%$ pixel-to-pixel variation.
 The feature width spans about 3~\AA.
@@
 The vanishing $<36$ m/s reflex motion of the star is imperceptible at this scale.
-The horizontal dashed lines indicate the moments of transit ingress (-0.03), midcenter (0.0), and egress (+0.03).
+The horizontal dashed lines indicate the moments of transit ingress (-0.03), mid-center (0.0), and egress (+0.03).
 
@@
 Figure \ref{fig:HPFscanResid} shows that significant absorption can be seen as a few percent at $-0.37$ in phase, rising to 10\% just before and during transit.
-The egress drop off is extremely sharp, with almost no excess absorption directly after transit.
+The egress drop-off is extremely sharp, with almost no excess absorption directly after transit.
 
@@
 We estimated bulk characteristics of the Helium excess absorption feature by fitting a Gaussian line profile to the 10828$-$10838 \AA~region of the residual spectra.
-The single line initialized at 10833 \AA~ was intended to aglomerate all three components of the metastable triplet into a single feature, consistent with their appearance in Figure \ref{fig:HPFheliumOverview}.
+The single line initialized at 10833 \AA~ was intended to agglomerate all three components of the metastable triplet into a single feature, consistent with their appearance in Figure \ref{fig:HPFheliumOverview}.
 The model constructed in this way has a total of 4 parameters: amplitude $A$, location $\lambda_c$, Gaussian width $\sigma$, and constant offset.
@@
 At transit ingress, the absorption appears more centrally concentrated near the vertical 10833 \AA~ line.
-The line depth gets slightly shallower with a slight redshift approaching transit midcenter.
+The line depth gets slightly shallower with a slight redshift approaching transit mid-center.
 \authorcomment1{Add more text here and revise figure.}
@@
 That large fraction of an orbit translates to about 0.1 AU, 130 planetary radii, and well outside of the Roche Lobe, with its Hill radius of merely 2.6 planetary radii.
-We are unambiguously detecting Roche lobe overlow, gas that is entirely unbound from the planet.
+We are unambiguously detecting Roche lobe overflow, gas that is entirely unbound from the planet.
 The leading gas tail does not appear to accelerate, with only a modest blueshift.
@@
 \subsection{1D Parker wind models and mass loss rates}\label{pwinds}
-The dramatic leading tail of atmospheric escape suggests that more complicated 3D hydrodymaic simulations coupled with stellar wind \citep{2022ApJ...926..226M} may be needed to depict the geometry faithfully.
+The dramatic leading tail of atmospheric escape suggests that more complicated 3D hydrodynamic simulations coupled with stellar wind \citep{2022ApJ...926..226M} may be needed to depict the geometry faithfully.
 Here we explore one-dimensional (1D) models, which offer ease of interpretation and rapid calculation.
@@
 The predicted Helium ionization depends sensitively on the XUV flux \citep{2019ApJ...881..133O}.
-Ideally we would have a measurement of the XUV spectrum of \hatp, but the limited facilities and distance of the source preclude these challenging observations.
-Instead we constructed panchromatic X-ray to visible SEDs by scaling and stitching together synthetic spectra to provide a range of high and low $L_X/L_\mathrm{bol}$.
+Ideally, we would have a measurement of the XUV spectrum of \hatp, but the limited facilities and distance of the source preclude these challenging observations.
+Instead, we constructed panchromatic X-ray to visible SEDs by scaling and stitching together synthetic spectra to provide a range of high and low $L_X/L_\mathrm{bol}$.
 We chose a 6400 K PHOENIX \citep{husser13} solar metallicity photospheric spectral template with $\log{g}=3.5$, scaled to the solid angle seen by \hatpb.
@@
 We scaled the synthetic SED of \object[tau Boo]{$\tau$ Boo} retrieved from X-exoplanets \citep{2011A&A...532A...6S} so that the integral of ground-state ionizing photons ($\lambda<504\AA$) exhibited $L_X/L_\mathrm{bol} \in [10^{-7}, 10^{-5}]$.
-Figure \ref{fig:XUV} shows two conceivable SEDs with a high and low radiation hardness.
+Figure \ref{fig:XUV} shows two conceivable SEDs with high and low radiation hardness.
 
@@
 
-The SED shows that the corona model does not extend all the way to 2600 \AA~photons capable of ionizing out of the 2 $^3$S Helium metastable state.
+The SED shows that the XUV corona model does not extend redward to 2600 \AA~photons capable of ionizing out of the 2 $^3$S Helium metastable state.
 This apparent deficit should be negligible, since the F spectral type obtains most of its NUV photons ($\lambda\sim2600$ \AA) from the Wein side of the photospheric spectrum, so the hardness of the radiation stems mostly from the assumptions of the corona flux level.
@@
 The spectrum was generated with a mass loss rate of $1.7\times10^{13}$ g/s, exosphere gas temperature of 9100 K, and with the high XUV spectrum ($L_x/L_\mathrm{bol}=10^{-4}$) shown in Figure \ref{fig:XUV}.
-The line depth and width broadly agrees with the width observed in HPF.}
+The line depth and width broadly agree with those observed in HPF.}
     \label{fig:pwinds}
@@
 In this scenario, the wind launches primarily from the dayside, with relatively little or no wind launched from the nightside.
-The wind initially launches radially from the planet, with the strongest wind located near the sub-stellar point, the line connecting the planet to star along the vertical axis in the figure.
-Inefficient heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemi-spherical shape, but more like a bulb or torpedo.
+The wind initially launches radially from the planet, with the strongest wind located near the sub-stellar point, the line connecting the planet to the star along the vertical axis in the figure.
+Inefficient heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemispherical shape, but more like a bulb or torpedo.
 The gas increasingly experiences the star's Keplerian potential past the Roche lobe, accelerating in the direction of orbital motion, $+x$.
 The accelerating column eventually overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.
-The mass loss has to be large enough to shield the material in order to make it observable in the metastable \ion{He}{1} 10833 \AA triplet.
+The mass loss has to be large enough to shield the material to make it observable in the metastable \ion{He}{1} 10833 \AA triplet.
 
@@
 \object{HAT-P-67 b} exhibits both dramatic atmospheric escape and significant radius inflation.
-Ohmic dissipation stands out as a physical mechanism that could be responsible for both of these oustanding attributes.
+Ohmic dissipation stands out as a physical mechanism that could be responsible for both of these outstanding attributes.
 \citet{2011ApJ...738....1B} showed that Ohmic heating acts to inflate hot Jupiters, with planets $\lesssim 0.5 M_\mathrm{Jup}$ overflowing their Roche lobes and leading to evaporation on Gyr timescales.
@@
 The order of magnitude of this inflation timescale is so fleetingly short that---according to this scenario---\hatpb~must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
-We therefore propose that \hatpb~ represents the first example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic Dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
+We, therefore, propose that \hatpb~ represents the first example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic Dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
 
@@
 A 5 Myr inflation timescale would imply an instantaneous $\dot{M}_\mathrm{infl}\sim10^{15}$ g/s, about 50 times larger than the 1D Parker wind model mass loss rate of $\dot{M}_\mathrm{1D}\sim2\times10^{13}$.
-Here we enumerate all of uncertainties that go into assessing mass loss rates to show that some in-between mass loss rate may be plausible.
+Here we enumerate uncertainties that go into assessing mass loss rates to show that some in-between mass loss rate may be plausible.
 
@@
 In particular, the uncertain XUV-to-NUV flux ratio confounds the interpretation of the observed Helium signal.
-Even the ``high XUV'' scenario in Figure \ref{fig:XUV} does not have enough ground-state ionizing photons to penetrate to within 5 $R_p$ of the planet surface, in a 1D Parker wind model.
+Even the ``high XUV'' scenario in Figure \ref{fig:XUV} does not have enough ground-state ionizing photons to penetrate to within 5 $R_p$ of the planet's surface, in a 1D Parker wind model.
 This means that at best only 1 in $10^{6}$ Helium atoms participate in the observability of the Helium metastable triplet lines in the baseline 1D Parker wind model.
@@
 \subsection{Reinflation}
-Evolved stars increase in size, delivering greater insolation to planets at a fixed separation.
-The heightened equilibrium temperature can cause mature planets to inflate, a phenomenon known as \emph{reinflation}.
+Evolved stars increase in luminosity, delivering greater insolation to planets at a fixed separation.
+The heightened equilibrium temperature can cause mature planets to inflate, the phenomenon known as \emph{reinflation}.
 Such re-inflated hot planets around red giant stars have been recently found by \emph{TESS} \citep{2022AJ....163..120G,2023arXiv230306728G}, though not all planets around evolved stars appear to re-inflate \citep{2022AJ....163...53S}.
@@
 The third panel recreates the numerically computed curve for $0.5\;M_\mathrm{Jup}$, $T_\mathrm{eq}=$1800 K from \citep{2011ApJ...738....1B}, which should be considered as representative since it was not necessarily tailored to the evolutionary history of \hatpb.
-Nevertheless, the similarly of curve is remarkable since it arrives at approximately the correct planet radius at the right age.
+Nevertheless, the similarity of the curve is remarkable since it arrives at approximately the correct planet radius at the right age.
 The modeled mass is slightly higher than, but consistent with the RV-measured mass, and could imply a large and increasing mass loss rate over its lifetime.
@@
     \caption{Conceivable evolutionary scenarios for \hatpb.
-The planet equilibrium temperature increases as the stellar luminosity gradually increases on the main sequence.
+The planet's equilibrium temperature increases as the stellar luminosity gradually increases on the main sequence.
 The Ohmic dissipation model makes predictions for runaway inflation, depending on the incident stellar flux.
-The heuristic scaling relation for inflation timescale predicts unusually small values in this extreme regime, but illustrates the countervailing effects of the top two panels.}
+The heuristic scaling relation for the inflation timescale predicts unusually small values in this extreme regime but illustrates the countervailing effects of the top two panels.}
     \label{fig:OhmicInflate}
@@
 \citet{2018AJ....155..214T} statistically favored Ohmic dissipation based on evidence for a turnover in the heating efficiency of hot Jupiters in a sample of 281 Giant planets.
-Futhermore, \citet{2018AJ....155..214T} also highlighted the lack of inflated sub-Saturns as an anomaly: by that time, the observational capability existed to detect such sources in large numbers and yet they were not found.
+Furthermore, \citet{2018AJ....155..214T} also highlighted the lack of inflated sub-Saturns as an anomaly: by that time, the observational capability existed to detect such sources in large numbers and yet they were not found.
 
@@
     \caption{Mass-radius trends for inflated hot sub-Saturns and hot Jupiters, form modeled after Figure 2 from \citet{2018AJ....155..214T} and updated with NASA Exoplanet Archive confirmed planets.
-The trend lines show mass-radius relationship for equilibrium temperatures of 500, 1000, 1250, 1500, and 2000 K, assuming the mean composition and mean heating efficiency from the original figure.
-HAT-P-67~b stands alones as occupying the ``Ohmic Dissipation Ridge'', defined by the lack of inflated sub-Saturns, and explained by short lifetimes form runaway inflation and mass loss.}
+The trend lines show the mass-radius relationship for equilibrium temperatures of 500, 1000, 1250, 1500, and 2000 K, assuming the mean composition and mean heating efficiency from the original figure.
+HAT-P-67~b stands alone as occupying the ``Ohmic Dissipation Ridge'', defined by the lack of inflated sub-Saturns, and explained by short lifetimes from runaway inflation and mass loss.}
     \label{fig:ThornFortUpdated}
@@
 
-This dearth of hot-Saturns has persisted into the \emph{TESS} era.
+This dearth of hot Saturns has persisted into the \emph{TESS} era.
 Figure \ref{fig:ThornFortUpdated} highlights the region of highly irradiated close-in planets with $N>5000$ planets accessed through the NASA Exoplanet Archive.
@@
 The inflationary lifetime of hot Saturns is so short that observing planets of this class is unlikely.
-\hatpb~ appears to be one of the rare planets that we happen to catch a glimpse of before it has been completely annihilated.
+\hatpb~ appears to be one of the rare planets that we happen to catch a glimpse of before it has been annihilated.
 The lack of inflated hot Saturns is analogous to the small planet radius gap \citep{2017AJ....154..109F}, with Ohmic dissipation replacing core-powered mass loss as a heating mechanism, and with photoevaporation still at play.
 
-We therefore attribute this cliff in the $M_p$ vs $R_p$ diagram to Ohmic dissipation.
-\citet{2018AJ....155..214T} emphasized the positive feedback loop as a cause for the lack of sub-Saturns, and noted an alternative interpretation-- mass-dependent migration segregation.
+We, therefore, attribute this cliff in the $M_p$ vs $R_p$ diagram to Ohmic dissipation.
+\citet{2018AJ....155..214T} emphasized the positive feedback loop as a cause for the lack of sub-Saturns and noted an alternative interpretation-- mass-dependent migration segregation.
 While both scenarios are conceivable, the evidence of strong evaporation of \hatpb~ favors the evaporation scenario.
-Futhermore, the runaway evaporation of hot-Saturns was naturally predicted by the Ohmic dissipation mechanism, whereas mass-dependent migration has only been developed as a post-diction.
+Furthermore, the runaway evaporation of hot Saturns was naturally predicted by the Ohmic dissipation mechanism, whereas mass-dependent migration has only been developed as a post-diction.
 
@@
 This trend should exhibit significant uncertainty owing to the order-of-magnitude nature of the scaling relation, source-to-source scatter in $\hat{\epsilon}_G$, and to what extent $\hat{\epsilon}_G$ applies for planets less than $0.5 M_\mathrm{Jup}$, which were excluded in the derivation of $\hat{\epsilon}_G$ owing to their scarcity.
-Nevertheless, this contour appears to match the bulk trends: the bulk locus of planets reside in either the non-inflationary, stable scenario, or the inflationary-yet-stable scenario.
+Nevertheless, this contour appears to match the bulk trends: planets tend to reside in either the non-inflationary, stable locus or the inflationary-yet-stable locus.
 A relatively few $\sim$dozens of planets approach the ``cosmic shoreline'' of inflationary lifetimes in the tens of Myr.
-The detection of atmospheric escape along this frontier (green circles in Figure \ref{fig:tf2018_theory}) support this interpretation.
+The detection of atmospheric escape along this frontier (green circles in Figure \ref{fig:tf2018_theory}) supports this interpretation.
 More observations and theoretical modeling of atmospheric escape along this ridge could help better understand its realized versus expected shape.
@@
 
-The key figure-of-merit can be distilled to $\tau_\mathrm{infl}$, whic can be thought of as an atmospheric escape spectroscopy metric \citep{2018PASP..130k4401K} for inflated planets in the shaded regime of Figure \ref{fig:tf2018_theory}.
+The key figure-of-merit can be distilled to $\tau_\mathrm{infl}$, which can be thought of as an atmospheric escape spectroscopy metric \citep{2018PASP..130k4401K} for inflated planets in the shaded regime of Figure \ref{fig:tf2018_theory}.
 Table \ref{tabHeSM} presents the rank-ordered list of planets by this metric, indicating that they are mostly smaller and more massive than \hatpb.
@@
     \tablecaption{
-        Coarse Inflation Timescales for hot Jupiters
+        Coarse Inflation Timescales for Hot Jupiters
         \label{tabHeSM}
@@
 Some sectors exhibit lower amplitudes.
-The conventional interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8 day orbital period of planet b.
-The cause for such orbital and rotational synchronization would then ostensibly be tides.
+The conventional interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8-day orbital period of planet b.
+The cause for such orbital and rotational synchronization would then ostensibly be star-planet tidal interactions.
 We examine the prospect of tides in the next subsection.
 
-Alternatively, the exteme mass loss and credibility of the Ohmic dissipation model motivates the prospect of Star Planet Magnetic Interaction (SPMI) that we consider now.
-In this scenario, the magnetic field of the planet permeates the space between the star and planet.
+Alternatively, the extreme mass loss and credibility of the Ohmic dissipation model motivate the prospect of Star Planet Magnetic Interaction (SPMI) that we consider now.
+In this scenario, the magnetic field of the planet permeates the space between the star and the planet.
 Magnetic perturbations propagate via planetary magnetic fields with the Alfv\'en speed.
-The planet can interact with the star if the Alfv\'en speed exceeds the stellar wind speed controling the bulk motion of intervening medium.
+The planet can interact with the star if the Alfv\'en speed exceeds the stellar wind speed controlling the bulk motion of the intervening medium.
 The magnetic field of the planet is not known, but the ohmic dissipation mechanism favors a limited range in the magnetic field strength: large enough to cause significant dissipative energy generation, but not too large to shut down charged particle motion entirely.

### 2023-04-19 paper/paper1/ms.tex
minor

@@
 
-\subsection{Gaia DR3}\label{gaiaDR3}
+\subsection{Gaia DR3}\label{analysisgaiaDR3}
 \citet{2017AJ....153..211Z} previously derived stellar radius estimates of 2.1-2.7 $R_\odot$ through Spectral Energy Distribution (SED) isochrone fitting as part of a joint orbit fit.
@@
 
-\subsubsection{Stellar rotation rate from periodogram analysis}
+\subsubsection{Stellar rotation rate from periodogram analysis}\label{TESSmodulation}
 
@@
 \subsection{Revised system evolutionary state}\label{secMISTtracks}
-As discussed in Section \ref{gaiaDR3}, the slightly increased distance and radius imply a slightly more luminous host star than previously estimated.
-Figure \ref{fig:evolTracks} shows evolutionary tracks using the solar-metallicity MESA \citep{2011ApJS..192....3P,2013ApJS..208....4P,2015ApJS..220...15P} Isochrones and Stellar Tracks \citep[MIST;]{2016ApJS..222....8D,2016ApJ...823..102C} for \hatp.
+As discussed in Section \ref{analysisgaiaDR3}, the slightly increased distance and radius imply a slightly more luminous host star than previously estimated.
+Figure \ref{fig:evolTracks} shows evolutionary tracks using the solar-metallicity MESA \citep{2011ApJS..192....3P,2013ApJS..208....4P,2015ApJS..220...15P} Isochrones and Stellar Tracks \citep[MIST;][]{2016ApJS..222....8D,2016ApJ...823..102C} for HAT-P-67.
 The tracks show that a 1.8 Gyr, 1.64 $M_\odot$ \hatp~ could be at the end of its main sequence lifetime (teal track), yielding a gradual rise in incident radiation to \hatpb.
@@
 Either evolutionary track appears consistent with the observed SED, stellar surface gravity, and available constraints from spectral fitting.
+
 \begin{figure*}
@@
 
-Excess is confidently detected at \censor{X} phases at \censor{Z}$\sigma$.
+Excess is confidently detected at from phases $-$0.3 to $+$0.03.
 The full-width at half maximum (FWHM) of the feature is about 1.8-2.6~\AA, equivalent to a line-of-sight velocity distribution in the range of 50-75~km/s.
@@
 \section{Discussion}
+\subsection{Orbital constraints}
+We premised our joint \emph{TESS} lightcurve and HPF RV time series orbit fit on a circular orbit.
+
 \subsection{Cause for stellar modulation}
-As discussed in Section \censor{x}, the \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $p=4.7-5.9$ days.
+As discussed in Section \ref{TESSmodulation}, the \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $P=4.7-5.9$ days.
 Some sectors exhibit lower amplitudes.

### 2023-04-19 paper/paper1/ms.tex
Add text about sub Saturn runaway to the intro

@@
 Alternatively---and most consequentially for atmospheric escape---another explanation may prevail.
-Inflated hot Saturns may effectively migrate to close-in orbital separations, but once they arrive, the intense irradiation overheats the planet.
+Inflated hot Saturns may either form \emph{in-situ} or effectively migrate to close-in orbital separations \citep{2018ARA&A..56..175D}, but once they arrive, the intense irradiation overheats the planet.
 This heating leads to runaway inflation and ultimately complete disintegration.
-In this scenario, the inflationary half-life may be so short as to lead to a low probability of observing members in the class, and hence the apparent lack of inflated sub-Saturns.
+In this scenario, the inflationary half-life may be so short as to lead to a low probability of observing members in the class among the overall population, and hence the apparent lack of inflated sub-Saturns.
 
@@
 \citet{2018AJ....155..214T} recognized the above two explanations for the lack of sub-Saturns, while statistically favoring Ohmic dissipation as the mechanism responsible for inflating Hot Jupiters.
-Therefore Ohmic dissipation stands out as a leading physical mechanism unifying several observations.
-Ohmic dissipation does not preclude the existence and role of other heating mechanisms---such as photoevaporation and tidal heating---but it does stand out as having made successful predictions before data were widely available to test them.
+Therefore Ohmic dissipation stands out as a leading physical mechanism for inflation and mass loss.
 
-A runaway inflation scenario implies an inevitable and profound mass loss rate for inflated hot Saturns.
-The planet's atmosphere overflows its Roche lobe at an ever-increasing pace, yielding instantaneous mass loss rates possibly much larger than we have seen in previous long-term stable systems.
+Recently, \citet{2023ApJ...945L..36T} showed that hot Saturns can undergo catastrophic erosion by stellar X-ray and Extreme UV (XUV) photoevaporative mass loss.
+Planets with densities less than $\sim$1 g~cm$^{-3}$ achieve mass loss rates of up to $10^3$ $M_\oplus /$Gyr setting up a positive feedback loop: the planet increases in radius, overflowing its Roche lobe, fueling greater mass loss, and increasing in radius even further.
+This vicious cycle systematically depopulates the mass-radius plane with a cliff defined by the $\sim$1 g~cm$^{-3}$ dividing line.
+
+A runaway inflation scenario predicts an inevitable and profound mass loss rate for inflated hot Saturns.
+As the planet's atmosphere overflows its Roche lobe at an ever-increasing pace instantaneous mass loss rates may exceed those previously seen in atmospheric escape measurements to date.
+
 The ability to detect that conceivable mass loss hinges on its observability in spectral tracers.
@@
 Ly $\alpha$ can suffer from interstellar medium \ion{H}{1} absorption censoring its low-velocity line core, for example.
-Here we focus on \ion{He}{1} 10833 \AA, which offers some advantages over Ly$\alpha$.
+Here we focus on \ion{He}{1} 10833 \AA, which offers some advantages.
 In particular, metastable Helium's ability to be observed at high spectral resolution from the ground has been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.
@@
 Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
+Its $\sim$0.05 g~cm$^-3$ density places it below the 1.0 g~cm$^-3$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.
 It orbits a possibly evolved subgiant, opening the prospect for ``re-inflation'' \citep{2022AJ....163...53S,2022AJ....163..120G,2023arXiv230306728G} as the planet's insolation increased with the star's rapid luminosity increase.
-The tidal gravity of the nearby massive host star may accelerate mass loss rates even further \citep{2007A&A...472..329E}.
-Its status as a rare inflated Hot Saturn makes \object{HAT-P-67 b} a promising laboratory, including but not limited to, testing the inflationary predictions of the Ohmic dissipation mechanism.
+The tidal gravity of the nearby massive host star may accelerate mass loss rates even further \citep{2007A&A...472..329E,2023ApJ...945L..36T}.
+Its status as a rare inflated Hot Saturn makes \object{HAT-P-67 b} a promising laboratory, including testing the runaway inflationary predictions of Ohmic dissipation and XUV photoevaporation.
 
@@
 
-Excess is confidently detected at from phases $-$0.3 to $+$0.03.
+Excess is confidently detected from phases $-$0.3 to $+$0.03.
 The full-width at half maximum (FWHM) of the feature is about 1.8-2.6~\AA, equivalent to a line-of-sight velocity distribution in the range of 50-75~km/s.

### 2023-04-19 paper/paper1/ms.tex
Revisions

@@
 As the planet's atmosphere overflows its Roche lobe at an ever-increasing pace instantaneous mass loss rates may exceed those previously seen in atmospheric escape measurements to date.
+These planets therefore make excellent targets for direct measurement of atmospheric escape.
 
@@
 Either evolutionary track appears consistent with the observed SED, stellar surface gravity, and available constraints from spectral fitting.
+We therefore adopt a MIST-based 2$\pm$0.2 Gyr age for the system, in-between the previous Geneva and Dartmouth-based scenarios.
 
@@
 These snapshot spectra were barycentric corrected, and continuum flattened to the regions in the blue vertical bands.
-Sharp telluric absorption lines have been masked in regions near 10835 and 10837.5 $\AA$.}
+Sharp telluric absorption lines have been masked in regions near 10835 and 10837.5 \AA.}
     \label{fig:HPFheliumOverview}
@@
 The accelerating column eventually overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.
-The mass loss has to be large enough to shield the material to make it observable in the metastable \ion{He}{1} 10833 \AA triplet.
+The mass loss has to be large enough to shield the material to make it observable in the metastable \ion{He}{1} 10833 \AA~triplet.
 
@@
 The overall observation of a leading tail comports with either of these two physical mechanisms, and both could be at play in \hatpb.
-Here we discuss how the observed line profiles of the gas motions could be interpreted in these two paradigms.
+Next we discuss how the observed line profiles of the gas motions could be interpreted in these two paradigms.
+
+\subsection{Interpretation of velocity structure}
+\authorcomment1{Describe the velocity structure}
 
@@
 The Ohmic heating scenario requires only a modest planetary magnetic field ($\gtrsim$1 G) and enough photoionization to ionize some modest fraction of neutral metals, such as the low ionization species of \ion{Na}{1} and \ion{K}{1}.
-The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K \citep{2011ApJ...738....1B}, where the ionization is strong enough to cause an effective drag, but not so strong as to halt motion altogether.
-The predicted range matches HAT-P-67 b's $\sim$1900 K.
-A plausible scaling law relationship approximate to an order-of-magnitude predicts an inflation timescale, Eq.
+The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K \citep{2011ApJ...738....1B,2012ApJ...745..138M,2016ApJ...819..116G,2018AJ....155..214T,2022A&A...658L...7K}, where the ionization is strong enough to cause an effective drag without being so strong that magnetic braking slows the planetary wind.
+HAT-P-67 b's $\sim$2000 K sits to the higher end, but still in a region of high Ohmic dissipation heating efficiency.
+A proposed order-of-magnitude scaling law predicts an inflation timescale, Eq.
 20 in \citet{2011ApJ...738....1B}:
+
 \begin{equation}
@@
 
-\noindent yielding an incredibly short 5 Myr timescale for \hatpb, assuming a typical $\epsilon\sim0.01$.
+\noindent yielding an incredibly short $<$5 Myr timescale for \hatpb, assuming a typical $\epsilon\sim0.01$.
 The order of magnitude of this inflation timescale is so fleetingly short that---according to this scenario---\hatpb~must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
-We, therefore, propose that \hatpb~ represents the first example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic Dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
+Under this interpretation, \hatpb~ would represent an example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic Dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
+
+Caveats abound.
+Chiefly, numerical simulations \citep{2013ApJ...763...13W} and analytic theory \citep{2016ApJ...819..116G} indicate that Ohmic dissipation can stall the contraction of hot Jupiters, but cannot easily ``re-inflate'' them after having undergone a traditional cooling curve.
+Heat transfer from the atmosphere to a cooled core simply proceeds too slowly, on order of tens of Gyr \citep{2016ApJ...819..116G}.
+This path dependence to Ohmic dissipation would restrict the allowed evolutionary histories of \hatpb, to have arrived to its current location within a few to tens of Myr.
+This short time window prefers a physical mechanism such as disk migration, which would be faster than secular eccentric migration with an outer companion.
+\emph{In-situ} formation of a hot Saturn at these close-in separations may be implausible \citep{2018ARA&A..56..175D}.
+Other caveats like unknowns in planetary magnetic fields, zonal band geometries, and dayside/nightside temperature differences make it impossible to uniqely prescribe Ohmic dissipation.
+Several factors may be at play \citep{2021A&A...645A..79S}.
+
+\subsection{XUV Photoevaporation}
+XUV photoevaporation heats the upper layers in the atmosphere, driving a hydrodynamic wind \citep{2009ApJ...693...23M}.
+
+Photoevaporation stands out as a potential cause of dayside/nightside differences in mass loss, with the greatest supersonic motions stemming from the sub-solar point on the planetary dayside, and merely sonic motion prevailing in latitudinal zonal bands.
+The effect may be boosted if dayside/nightside energy transport proceeds inefficiently \citep{2009ApJ...693...23M}.
+Such a scenario is illustrated in Figure \ref{fig:KeplerianShear}.
 
@@
 A larger mass loss rate would be needed to explain the same observed HPF Helium absorption, if say only 1 in $10^{7}$ helium atoms are populating the metastable state.
-
-\subsection{Photoevaporation}
-The prospect of Ohmic dissipation does not preclude the possibility that other mass loss drivers are at play.
-Photoevaporation \citep{2009ApJ...693...23M} could simultaneously drive heating of the upper layers in the atmosphere, driving a hydrodynamic wind and reinforcing the mass loss associated with Ohmic dissipation.
-It is not clear \emph{a-priori} which effect predominates.
-
-Photoevaporation stands out as a potential cause of dayside/nightside differences in mass loss, with the greatest supersonic motions stemming from the sub-solar point on the planetary dayside, and merely sonic motion prevailing in latitudinal zonal bands.
-The effect may be boosted if dayside/nightside energy transport proceeds inefficiently \citep{2009ApJ...693...23M}.
-Such a scenario is illustrated in Figure \ref{fig:KeplerianShear}.
 

### 2023-04-19 paper/paper1/ms.tex
OD vs XUV

@@
 \citet{2011ApJ...738....1B} showed that Ohmic heating acts to inflate hot Jupiters, with planets $\lesssim 0.5 M_\mathrm{Jup}$ overflowing their Roche lobes and leading to evaporation on Gyr timescales.
-The Ohmic heating scenario requires only a modest planetary magnetic field ($\gtrsim$1 G) and enough photoionization to ionize some modest fraction of neutral metals, such as the low ionization species of \ion{Na}{1} and \ion{K}{1}.
-The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K \citep{2011ApJ...738....1B,2012ApJ...745..138M,2016ApJ...819..116G,2018AJ....155..214T,2022A&A...658L...7K}, where the ionization is strong enough to cause an effective drag without being so strong that magnetic braking slows the planetary wind.
+The Ohmic heating scenario requires only a modest planetary magnetic field ($\gtrsim$1 G) and an equilibrium temperature great enough to thermally ionize some modest fraction of neutral metals, such as the low ionization species of \ion{Na}{1} and \ion{K}{1}.
+The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K \citep{2011ApJ...738....1B,2012ApJ...745..138M,2016ApJ...819..116G,2018AJ....155..214T,2022A&A...658L...7K}, where the conductivity is strong enough to cause an effective drag without being so strong that magnetic braking slows the planetary wind.
 HAT-P-67 b's $\sim$2000 K sits to the higher end, but still in a region of high Ohmic dissipation heating efficiency.
@@
 \noindent yielding an incredibly short $<$5 Myr timescale for \hatpb, assuming a typical $\epsilon\sim0.01$.
+At Roche lobe overflow, a 5 Myr inflation timescale would imply an instantaneous $\dot{M}_\mathrm{infl}\sim10^{15}$ g/s.
 The order of magnitude of this inflation timescale is so fleetingly short that---according to this scenario---\hatpb~must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
@@
 
-Caveats abound.
+A few caveats complicate the unambiguous causal interpretation of Ohmic dissipation.
 Chiefly, numerical simulations \citep{2013ApJ...763...13W} and analytic theory \citep{2016ApJ...819..116G} indicate that Ohmic dissipation can stall the contraction of hot Jupiters, but cannot easily ``re-inflate'' them after having undergone a traditional cooling curve.
@@
 \emph{In-situ} formation of a hot Saturn at these close-in separations may be implausible \citep{2018ARA&A..56..175D}.
-Other caveats like unknowns in planetary magnetic fields, zonal band geometries, and dayside/nightside temperature differences make it impossible to uniqely prescribe Ohmic dissipation.
-Several factors may be at play \citep{2021A&A...645A..79S}.
+Other caveats like unknowns in planetary magnetic fields, zonal band geometries, and dayside/nightside temperature differences make it impossible to uniqely prescribe Ohmic dissipation, and instead several additional factors may also be at play \citep{2021A&A...645A..79S}.
 
@@
 XUV photoevaporation heats the upper layers in the atmosphere, driving a hydrodynamic wind \citep{2009ApJ...693...23M}.
+The combined effects of photoevaporation, anomalous heating, and tidal gravity are predicted to have especially drastic outcomes for inflated hot Saturns \citep{2023ApJ...945L..36T}, where the low densities lead to large mass loss rates.
 

### 2023-04-19 paper/paper1/ms.tex
Add a bunch of text about XUV photoevaporation of hot Saturns

@@
 \noindent yielding an incredibly short $<$5 Myr timescale for \hatpb, assuming a typical $\epsilon\sim0.01$.
-At Roche lobe overflow, a 5 Myr inflation timescale would imply an instantaneous $\dot{M}_\mathrm{infl}\sim10^{15}$ g/s.
 The order of magnitude of this inflation timescale is so fleetingly short that---according to this scenario---\hatpb~must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
 Under this interpretation, \hatpb~ would represent an example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic Dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
+At Roche lobe overflow, a 5 Myr inflation timescale may imply an instantaneous $\dot{M}_\mathrm{infl}>10^{3}$ M$_\oplus$/Gyr.
 
@@
 XUV photoevaporation heats the upper layers in the atmosphere, driving a hydrodynamic wind \citep{2009ApJ...693...23M}.
-The combined effects of photoevaporation, anomalous heating, and tidal gravity are predicted to have especially drastic outcomes for inflated hot Saturns \citep{2023ApJ...945L..36T}, where the low densities lead to large mass loss rates.
-
-Photoevaporation stands out as a potential cause of dayside/nightside differences in mass loss, with the greatest supersonic motions stemming from the sub-solar point on the planetary dayside, and merely sonic motion prevailing in latitudinal zonal bands.
+Photoevaporation stands out as offering a natural cause of the observed leading tail attributable to dayside/nightside differences in mass loss: the greatest supersonic motions arise from the sub-solar point on the planetary dayside.
 The effect may be boosted if dayside/nightside energy transport proceeds inefficiently \citep{2009ApJ...693...23M}.
@@
 
+The combined effects of photoevaporation, anomalous heating, and tidal gravity are predicted to have especially drastic outcomes for inflated hot Saturns \citep{2023ApJ...945L..36T} such as \hatp, where the low densities lead to large mass loss rates:
+
+\begin{equation}
+    \dot{M} = \frac{3}{4}\frac{\eta F_\mathrm{XUV}}{G K_t \rho_\mathrm{XUV}}\label{thorn23Mdot}.
+\end{equation}
+
+Assuming $\log{L_\mathrm{XUV}/L_\mathrm{bol}}=-4.2$, we would expect \hatpb~ to exhibit $\dot{M}\sim10^2$ M$_\oplus$/Gyr.
+At a current $M\sim95\;$M$_\oplus$ and an accelerating mass loss rate, its lifetime would measure in the $\sim$100 Myr range.
+The \citet{2023ApJ...945L..36T} simulations focused on 0.75-1.25 $M_\odot$ host stars; the higher mass $\sim$1.6 $M_\odot$ \hatp would deliver greater tidal gravity for a given semi-major axis, and possibly lower $\log{L_\mathrm{XUV}/L_\mathrm{bol}}$ compared to more active G stars.
+Nevertheless, we can project the time series trends in their Figures 3 and 4 to recreate a qualitative history and fate of \hatpb~ under the assumptions of XUV photoevaporation.
+Broadly, the planet would have started with an initial mass up to 50$\%$ more massive than it is now, with $R\sim\;$1.4 $R_\mathrm{Jup}$, for an initial density of $\sim$0.2 g/cm$^-3$.
+It would lose mass at a rate of tens of Earth masses per Gyr for its 1 Gyr lifetime, expanding modestly until it reaches the critical $\sim$0.1 g/cm$^-3$ threshold, at which point the mass loss rate increases to its current value.
+Having lost a significant portion of its mass, its orbit expands to conserve angular momentum.
+It will last only tens of Myr in its current state before losing almost all of its envelope and settling as a $5-15$ M$_\oplus$ core with a final radius of 0.2$-$0.3 R$_\mathrm{Jup}$.
+
 \subsection{Constraining mass loss rate}
-A 5 Myr inflation timescale would imply an instantaneous $\dot{M}_\mathrm{infl}\sim10^{15}$ g/s, about 50 times larger than the 1D Parker wind model mass loss rate of $\dot{M}_\mathrm{1D}\sim2\times10^{13}$.
-Here we enumerate uncertainties that go into assessing mass loss rates to show that some in-between mass loss rate may be plausible.
+The theory-inspired mass loss rates above correspond to 1D Parker wind \ion{He}{1} feature depths and widths similar to what we observe, as evinced in Figure \ref{fig:pwinds}, with $\dot{M}_\mathrm{1D}\sim100$ M$_\oplus$/Gyr.
+\authorcomment1{To be continued--- interpret this congruence}.
 

### 2023-04-20 paper/paper1/ms.tex
Neat new figures on centroids

@@
 \subsection{Velocity substructure}
-Figure \ref{fig:HeliumScanZoom} shows a zoom-in of the in-transit portion of the Helium excess absorption scan, overlaid with line center positions.
+Figure \ref{fig:HeliumZoom} shows a zoom-in of the in-transit portion of the Helium excess absorption scan, overlaid with line center positions.
 The scan appears to exhibit some velocity substructure.
@@
 
+%\begin{figure}
+%    \includegraphics[width=\linewidth]{figures/centroid_inset10833.png}
+%    \caption{A zoom-in of the line centroid positions of the  10830 triplet feature relative to the planet rest frame.}
+%    \label{fig:HeliumZoom}
+%\end{figure}
+
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/phase_2D_diagram_zoom.png}
-    \caption{A zoom-in of the in-transit and post-transit phase scan for the Helium 10830 triplet.  Some velocity substructure may be apparent.}
-    \label{fig:HeliumScanZoom}
+    \centering
+    \subfloat{\includegraphics[width=5cm]{figures/centroid_overview10833.png} }
+    \hskip-3em
+    \subfloat{\includegraphics[width=4cm]{figures/centroid_inset10833.png}}
+    \caption{Line centroid positions of the  10830 triplet.
+\emph{left}: The overview panel shows a slight blueshift relative to the stellar restframe, and a weak excess blueshift trend after planet egress.
+\emph{right:} The detailed zoom-in of the in-transit phase shows a redshift relative to the planet restframe at ingress and a blueshift relative to the planet restframe near egress.
+The line-of-sight velocity distribution of 2-3 \AA means that the gas distribution exhibits both advancing and receding lobes at all phases other than post-egress.}
+    \label{fig:example}
 \end{figure}

### 2023-04-24 paper/paper1/ms.tex
compress figures, tables and text to eliminate whitespace

@@
 
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.98\linewidth]{figures/TESS_HAT-P-67b_overview.png}
+    \caption{Overview of all available TESS Sectors showing 24 full or partial transits with 34 visits with HPF (vertical gray bars), 7 of which coincide with transits.
+The rest of the visits sample out-of-transit phases.
+The 8 HPF visits between BTJD 2050 and 2690 are not shown.
+Note the large time breaks between some consecutive panels, which correspond roughly to the duration of a TESS sector.}
+    \label{fig:TESSoverview}
+\end{figure*}
+
 \subsection{Gaia DR3}\label{gaiadr3}
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.7\linewidth]{figures/TESS_HAT-P-67b_overview.png}
-    \caption{Overview of all available TESS Sectors showing 24 full or partial transits with 34 visits with HPF (vertical gray bars), 7 of which coincide with transits.
-The rest of the visits sample out-of-transit phases.
-The 8 HPF visits between BTJD 2050 and 2690 are not shown.}
-    \label{fig:TESSoverview}
-\end{figure*}
-
 \section{Analysis}
@@
 This update systematically decreases the estimate for the already-low density of HAT-P-67 by 28\%, to a mere 0.035 g$\;$cm$^{-3}$, albeit with significant uncertainties from the weak mass constraint.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/best_fit_orbit.png}
+    \caption{Best fit orbit overlaid on the composite TESS lightcurve.}
+    \label{fig:transit}
+\end{figure}
 
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/best_fit_orbit.png}
-    \caption{Best fit orbit overlaid on the composite TESS lightcurve.}
-    \label{fig:transit}
-\end{figure}
-
 \subsubsection{Lightcurve modulation amplitude}
@@
 \subsection{HPF analysis I: RV fitting}
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/HAT-P-67b_rv.pdf}
+    \caption{RV orbit fit including both HPF and Keck HIRES data points.}
+    \label{fig:RVfit}
+\end{figure}
 
@@
 \authorcomment1{Quang Tran: please verify and revise.}
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/HAT-P-67b_rv.pdf}
-    \caption{RV orbit fit including both HPF and Keck HIRES data points.}
-    \label{fig:RVfit}
-\end{figure}
 
@@
 The horizontal dashed lines indicate the moments of transit ingress (-0.03), mid-center (0.0), and egress (+0.03).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/HAT_P_67b_Helium10830EW_byCampaign.png}
+    \caption{Time series EW lightcurve of Helium absorption in HAT-P-67b.  The system exhibits a characteristic absorption leading up to transit, followed by a sharp decline after transit passage.  }
+    \label{fig:HPFtimeseries}
+\end{figure}
 
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/HAT_P_67b_Helium10830EW_byCampaign.png}
-    \caption{Time series EW lightcurve of Helium absorption in HAT-P-67b.  The system exhibits a characteristic absorption leading up to transit, followed by a sharp decline after transit passage.  }
-    \label{fig:HPFtimeseries}
-\end{figure}
-
 \subsection{Keck HIRES}
@@
     \subfloat{\includegraphics[width=4cm]{figures/centroid_inset10833.png}}
-    \caption{Line centroid positions of the  10830 triplet.
+    \caption{Line centroid positions of the  \ion{He}{1} 10830 \AA~ feature.
 \emph{left}: The overview panel shows a slight blueshift relative to the stellar restframe, and a weak excess blueshift trend after planet egress.
 \emph{right:} The detailed zoom-in of the in-transit phase shows a redshift relative to the planet restframe at ingress and a blueshift relative to the planet restframe near egress.
-The line-of-sight velocity distribution of 2-3 \AA means that the gas distribution exhibits both advancing and receding lobes at all phases other than post-egress.}
+The line-of-sight velocity distribution of 2-3 \AA~ means that the gas distribution exhibits both advancing and receding lobes at all phases other than post-egress.}
     \label{fig:example}
@@
         \colhead{Radius} &
-        \colhead{Eq. Temp.} &
+        \colhead{$T_\mathrm{eq}$} &
         \colhead{$\tau_\mathrm{infl}$} \\
@@
     \enddata
-    \tablecomments{Inflation timescale assumes $\epsilon=0.01$.}
+    %\tablecomments{Inflation timescale assumes $\epsilon=0.01$.}  Not true, we use the empirical estimate
 \end{deluxetable}

### 2023-04-24 paper/paper1/ms.tex
More figure re-arranging
Add text to the velocity substructure analysis section.

@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.98\linewidth]{figures/MIST_only_HATP.png}
+    \caption{MIST evolutionary model tracks for \hatp.  The $T_\mathrm{eff}$ and luminosity of \hatp~ (gray circle) are consistent with either the late main sequence or recently evolved subgiant.}
+    \label{fig:evolTracks}
+\end{figure}
+
 \subsection{Revised system evolutionary state}\label{secMISTtracks}
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.7\linewidth]{figures/MIST_tracks_HATP.png}
-    \caption{MIST evolutionary model tracks for \hatp.  The $T_\mathrm{eff}$ and luminosity of \hatp~ (gray circle) are consistent with either the late main sequence or recently evolved subgiant.}
-    \label{fig:evolTracks}
-\end{figure*}
-
-\subsection{HPF analysis I: RV fitting}
 \begin{figure}
@@
 \end{figure}
+
+\subsection{HPF analysis I: RV fitting}
 
@@
 Additionally, our input $\rstar$ was slightly lower than the best-fit value derived from \emph{Gaia DR3} and SED fitting.
-\authorcomment1{Quang Tran: please verify and revise.}
+%\authorcomment1{Quang Tran: please verify and revise.}
 
@@
 
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/phase_2D_diagram_resid.png}
+    \caption{Absorption depth phase scan over the entire HAT-P-67b orbit from 41 visits with HPF.  }
+    \label{fig:HPFscanResid}
+\end{figure}
+
 Excess is confidently detected from phases $-$0.3 to $+$0.03.
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/phase_2D_diagram_resid.png}
-    \caption{Absorption depth phase scan over the entire HAT-P-67b orbit from 41 visits with HPF.  }
-    \label{fig:HPFscanResid}
-\end{figure}
-
 \subsection{Keck HIRES}
@@
 \subsection{Velocity substructure}
-Figure \ref{fig:HeliumZoom} shows a zoom-in of the in-transit portion of the Helium excess absorption scan, overlaid with line center positions.
-The scan appears to exhibit some velocity substructure.
-At transit ingress, the absorption appears more centrally concentrated near the vertical 10833 \AA~ line.
-The line depth gets slightly shallower with a slight redshift approaching transit mid-center.
-\authorcomment1{Add more text here and revise figure.}
+Figure \ref{fig:centroids} shows the centroid positions of the Helium excess feature.
+The bulk velocity drifts of the planet outflow can be seen with a few conspicuous trends.
+The pre-transit phases ($-0.3$ - $+0.03$) show a slight tendency towards blueshift relative to stellar restframe, with an accelerating blueshift from phases ($-0.3$ - $-0.15$), albeit with some visit-to-visit scatter.
+The post-transit observations ($+0.03$ - $+0.015$) exhibit weak-albeit-significant equivalent widths, as denoted by their smaller marker size.
+The centroids dramatically accelerate to larger bulk blueshifts, as low as 10831 \AA.
 
-%\begin{figure}
-%    \includegraphics[width=\linewidth]{figures/centroid_inset10833.png}
-%    \caption{A zoom-in of the line centroid positions of the  10830 triplet feature relative to the planet rest frame.}
-%    \label{fig:HeliumZoom}
-%\end{figure}
+The densely sampled in-transit phases are shown as a zoomed-in, oversized inset.
+Here we can see the planetary rest frame as the dotted line cutting across the panel.
+At the moment of planet ingress, the centroids exhibit a redshifted absorption relative to the planet restframe.
+Measurements from April 2022 and May 2020 transits partially overlap in phase coverage while yielding slightly different line centroid locations.
+Both visits appear consistent with near-zero restframe velocity.
+The May 2020 visit shows a slight trend towards alignment with the planet restframe.
+The April 2020 and June 2020 partial transits sampled phases close to planet egress, with a clear blueshift relative to both the star and planet.
+
+Overall this pattern of velocity centroids appears consistent with the majority of the gas rapidly obeying the stellar restframe, but with a large spread in the line-of-sight velocity distribution as we would expect from a range of launch angles.
+We revisit the interpretations and caveats for this substructure in the Discussion section.
 
@@
 The line-of-sight velocity distribution of 2-3 \AA~ means that the gas distribution exhibits both advancing and receding lobes at all phases other than post-egress.}
-    \label{fig:example}
+    \label{fig:centroids}
 \end{figure}

### 2023-04-24 paper/paper1/ms.tex
Interpreting the velocity structure

@@
 We examined other spectral lines using the same methodology as above, finding no detectable variability in the \ion{Ca}{2} infrared triplet, Hydrogen lines, or other neutral metal lines.
-We show some of the diagnostic plots for these non-detections in Appendix Section \ref{}.
+We show some of the diagnostic plots for these non-detections in Appendix Section \ref{appendixSec}.
 
@@
 The bulk velocity drifts of the planet outflow can be seen with a few conspicuous trends.
-The pre-transit phases ($-0.3$ - $+0.03$) show a slight tendency towards blueshift relative to stellar restframe, with an accelerating blueshift from phases ($-0.3$ - $-0.15$), albeit with some visit-to-visit scatter.
-The post-transit observations ($+0.03$ - $+0.015$) exhibit weak-albeit-significant equivalent widths, as denoted by their smaller marker size.
+The pre-transit phases ($-0.3$ to $+0.03$) show a slight tendency towards blueshift relative to stellar restframe, with an accelerating blueshift from phases $-0.3$ to $-0.15$, albeit with some visit-to-visit scatter.
+The post-transit observations ($+0.03$ to $+0.015$) exhibit weak-albeit-significant equivalent widths, as denoted by their smaller marker size.
 The centroids dramatically accelerate to larger bulk blueshifts, as low as 10831 \AA.
@@
 Overall this pattern of velocity centroids appears consistent with the majority of the gas rapidly obeying the stellar restframe, but with a large spread in the line-of-sight velocity distribution as we would expect from a range of launch angles.
-We revisit the interpretations and caveats for this substructure in the Discussion section.
+We revisit the interpretations and caveats for this substructure in the next sections.
 
@@
 That large fraction of an orbit translates to about 0.1 AU, 130 planetary radii, and well outside of the Roche Lobe, with its Hill radius of merely 2.6 planetary radii.
-We are unambiguously detecting Roche lobe overflow, gas that is entirely unbound from the planet.
-The leading gas tail does not appear to accelerate, with only a modest blueshift.
-The bulk of the detectable unbound gas may therefore follow its own Keplerian trajectory at a slightly shorter period orbit, pulling away from the planet parallel to the orbital path.
-Such a scenario may arise from preferential emission on the planet dayside, or other configurations that we discuss in Section \ref{secDiscuss}.
+We are detecting Roche lobe overflow, gas that is entirely unbound from the planet.
+The bulk of the detectable unbound gas may be understood as following its own Keplerian trajectory at a slightly shorter period orbit, pulling away from the planet parallel to the orbital path.
+Such a scenario may arise from preferential emission on the planet dayside.
 
@@
 We scaled the synthetic SED of \object[tau Boo]{$\tau$ Boo} retrieved from X-exoplanets \citep{2011A&A...532A...6S} so that the integral of ground-state ionizing photons ($\lambda<504\AA$) exhibited $L_X/L_\mathrm{bol} \in [10^{-7}, 10^{-5}]$.
-Figure \ref{fig:XUV} shows two conceivable SEDs with high and low radiation hardness.
+Figure \ref{fig:XUV} shows two conceivable SEDs with these high and low radiation hardness.
 
@@
 Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 7\times10^{13}$ g/s, and $T_0=9100$~K, with the high XUV spectrum ($L_x/L_\mathrm{bol}=10^{-4}$).
-This mass loss rate would imply a mass loss rate timescale of $\sim$500 Myr.
-The model spectrum exhibits approximately the same line width and depth as our HPF observations, making it a conceivable solution, albeit one of many.
+This mass loss rate would imply a characteristic lifetime of $\sim$500 Myr.
+The model spectrum exhibits approximately the same line width and depth as our HPF observations, making it a conceivable scenario among a family of partially degnerate solutions.
 
@@
 Second, the 1D model breaks down when attempting to explain the inherently 3D leading tail geometry.
-We discuss these two and other model-dependent interpretations in Section \ref{secDiscuss}.
 
@@
 Figure \ref{fig:KeplerianShear} shows an illustration of Keplerian shear adapted to the system properties of \hatpb.
-In this scenario, the wind launches primarily from the dayside, with relatively little or no wind launched from the nightside.
-The wind initially launches radially from the planet, with the strongest wind located near the sub-stellar point, the line connecting the planet to the star along the vertical axis in the figure.
-Inefficient heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemispherical shape, but more like a bulb or torpedo.
+In this shear-dominated scenario, the planetary wind launches primarily from the dayside, with relatively little or no wind launched from the nightside.
+The planet wind initially launches radially outward from the exobase, with the strongest wind located near the sub-stellar point, the line connecting the planet to the star along the vertical axis in the figure.
+Inefficient grazing incidence heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemispherical shape, but more concentration along the star-planet line.
 The gas increasingly experiences the star's Keplerian potential past the Roche lobe, accelerating in the direction of orbital motion, $+x$.
@@
 Stellar wind confinement \citep{2022ApJ...926..226M} arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.
-A trailing tail may also be present, but would not undergo the same boost in density, and would be rapidly carried away by the stellar wind.
+A trailing tail may also be present, but would not undergo the same boost in density, and would be rapidly carried away alongside the stellar wind.
 This asymmetry could yield the appearance of a leading tail even if mass loss proceeds isotropically, or the asymmetry could be reinforced by an additional dayside/nightside asymmetry.
@@
 
-The overall observation of a leading tail comports with either of these two physical mechanisms, and both could be at play in \hatpb.
-Next we discuss how the observed line profiles of the gas motions could be interpreted in these two paradigms.
+The overall observation of a leading tail comports with either of these two physical mechanisms, and we suspect both are at play in \hatpb.
+Both cases appear needed to create the conditions of high enough column density to populate the \ion{He}{1} metastable triplet to detectable levels while imbuing the velocity substructure that we see.
+Here we interpret the bulk velocity substructure in Figure \ref{fig:centroids} under a combination of the two.
+We attribute the pre-transit arc to stellar wind acceleration.
+The stellar wind is initially too weak to plow the dense escaping gas until a separation of 60-130 planetary radii ($+0.15$ orbital phase), the inflection point in an enormous bow shock.
+Gas at these separations has had enough time to diffuse, both out of the orbital plane and to slightly larger radii shells, in turn lowering the column density along the line-of-sight.
+The lower column density provides both fewer Helium atoms to participate in absorption, and less overall NUV shielding, leading to greater fractional ionization and further depopulation of the \ion{He}{1} metastable state.
 
-\subsection{Interpretation of velocity structure}
-\authorcomment1{Describe the velocity structure}
+The weak post-egress tail can be understood as follows.
+A weak nightside mass loss means that there is both less overall column density and less NUV photoionization shielding, subduing the overall \ion{He}{1} metastable state's signal strength.
+The blueshift arises from the Keplerian shear that lags the planet, and the ever-blueshifting centroid represents the stellar wind's greater ability to carry away the lower total inertia of less nightside material.
+
+In order to examine the in-transit velocity structure, we have to consider the interplay of a two subtle geometrical effects.
+First, the planet's Roche lobe is small enough (2.7 $R_\mathrm{p}$) that the majority of the projected stellar disk should be filled with gas unbound from the planet, even at the time of mid-transit.
+In other words, only a small fraction of the \ion{He}{1} excess signal would be expected to trace the planet's motion, as opposed to the hypothetical in-transit signal for WASP-107~b that definitively traces out the planet's orbital path \citep{2022ApJ...926..226M}.
+
+Second, the star's non-negligible rotational velocity sets up a configuration analogous to Doppler Tomography in the Rossiter-McLaughlin (RM) effect, but distinct in a subtle way.
+Whereas traditional Doppler Tomography treats the scanning reticle as an opaque planetary disk, here the reticle resembles a transmissive filter with a wavelength center and width that varies in space and time.
+We can understand this transmissive Doppler tomography effect through an example of a pathological limiting case.
+Imagine the escaping atmsosphere were concentrated in a 50\% transmissive cylinder coming out of the orbital plane, as in an idealized transparent bipolar outflow.
+This cyclinder would possess the planet's bulk velocity of about $-30$ km/s at the moment of transit ingress, placing the locus of absorption at about 10832.4 \AA.
+But the absorptive cylinder would intercept a finite range of stellar limb velocities, broadening the apparent width of the absorption line.
 
@@
 
-\section{Spectral variability non-detections}
+\section{Spectral variability non-detections} \label{appendixSec}
 \subsection{Calcium IR Triplet and other line diagnostics}

### 2023-04-24 paper/paper1/ms.tex
Ignore the second-order effect

@@
 Whereas traditional Doppler Tomography treats the scanning reticle as an opaque planetary disk, here the reticle resembles a transmissive filter with a wavelength center and width that varies in space and time.
-We can understand this transmissive Doppler tomography effect through an example of a pathological limiting case.
+We rank this effect as second-order and ignore it for now.
+%%We can understand this transmissive Doppler tomography effect through an example of a pathological limiting case.
 Imagine the escaping atmsosphere were concentrated in a 50\% transmissive cylinder coming out of the orbital plane, as in an idealized transparent bipolar outflow.

### 2023-04-25 paper/paper1/ms.tex
Add new figure and adjust the observation log table

@@
         \colhead{Track} &
-        \colhead{Transit?} &
+        \colhead{Desc.} &
         \colhead{BTJD} &
@@
         \nocolhead{(s)} &
-        \colhead{$\in(-0.5, 0.5)$}
+        \colhead{}
     }
@@
     \enddata
-    \tablecomments{All exposure times were 308.85~s except for observations from 2020-07-21 to 2021-03-30, which were 511.20~s.}
+    \tablecomments{All exposure times were 308.85~s except for observations from 2020-07-21 to 2021-03-30, which were 511.20~s.
+Column 2 describes the HET ``track'', restricted to either East (E) or West (W).
+The thresholds for the prepositional description in Column 3 is defined in the text.
+Column 5 is the normalized phase $\phi \in(-0.5, 0.5)$, with zero at midtransit.}
 \end{deluxetable}
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/pwinds_1D_higXUV_t1p2Gyr.png}
+    \includegraphics[width=\linewidth]{figures/pwinds_data_overlay.png}
     \caption{Simulated 1D Parker wind model of Helium absorption in \hatpb.
-The spectrum was generated with a mass loss rate of $1.7\times10^{13}$ g/s, exosphere gas temperature of 9100 K, and with the high XUV spectrum ($L_x/L_\mathrm{bol}=10^{-4}$) shown in Figure \ref{fig:XUV}.
-The line depth and width broadly agree with those observed in HPF.}
+The spectrum was generated with a mass loss rate of $10^{13}$ g/s, exosphere gas temperature of 9100 K, and with an XUV luminosity $L_x/L_\mathrm{bol}=10^{-5}$ intermediate between those shown in Figure \ref{fig:XUV}.
+The lines have about the same  equivalent width, while additional unmodeled velocity dispersion of the gas can explain differences between the line shapes of model and data.
+Overall the 1D models may be too simplistic to represent the inherently 3D structure of the outflow.}
     \label{fig:pwinds}
@@
 The theory-inspired mass loss rates above correspond to 1D Parker wind \ion{He}{1} feature depths and widths similar to what we observe, as evinced in Figure \ref{fig:pwinds}, with $\dot{M}_\mathrm{1D}\sim100$ M$_\oplus$/Gyr.
-\authorcomment1{To be continued--- interpret this congruence}.
+%\authorcomment1{To be continued--- interpret this congruence}.
 

### 2023-05-08 paper/paper1/ms.tex
uncomitted changes to draft

@@
     \includegraphics[width=0.98\linewidth]{figures/MIST_only_HATP.png}
-    \caption{MIST evolutionary model tracks for \hatp.  The $T_\mathrm{eff}$ and luminosity of \hatp~ (gray circle) are consistent with either the late main sequence or recently evolved subgiant.}
+    \caption{MIST evolutionary model tracks for HAT-P-67.  The $T_\mathrm{eff}$ and luminosity of \hatp (gray circle) are consistent with either the late main sequence or recently evolved subgiant.}
     \label{fig:evolTracks}
@@
 Equipped with these two SEDs of differing radiation hardness, we explored different mass loss rates and exosphere temperatures.
-Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 7\times10^{13}$ g/s, and $T_0=9100$~K, with the high XUV spectrum ($L_x/L_\mathrm{bol}=10^{-4}$).
-This mass loss rate would imply a characteristic lifetime of $\sim$500 Myr.
-The model spectrum exhibits approximately the same line width and depth as our HPF observations, making it a conceivable scenario among a family of partially degnerate solutions.
+Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 10^{13}$ g/s, and $T_0=9100$~K, with the a medium XUV spectrum ($L_x/L_\mathrm{bol}=10^{-5}$).
+This mass loss rate would imply a characteristic lifetime of $\sim$2000 Myr.
+The model spectrum exhibits approximately the same equivalent width as our HPF observations, making it a hypothetical scenario among a family of partially degnerate solutions.
 

### 2023-05-09 paper/paper1/ms.tex
Corrections from printed document

@@
 \usepackage{booktabs}
+\usepackage{xcolor}
 \usepackage{censor}
@@
 Atmospheric escape appears to be a compulsory phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5$-$2.0~$R_\oplus$ planets \citep{2017AJ....154..109F}.
-The leading candidate physical mechanisms for this rapid transition between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G}.
+The leading candidate physical mechanisms for this rapid transition between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2013ApJ...776....2L,2017ApJ...847...29O} a=nd core-powered mass loss \citep{2019MNRAS.487...24G}.
 Whatever the cause, some large fraction of planets must undergo transformative atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations such as transiting planets.
@@
 This heating leads to runaway inflation and ultimately complete disintegration.
-In this scenario, the inflationary half-life may be so short as to lead to a low probability of observing members in the class among the overall population, and hence the apparent lack of inflated sub-Saturns.
+In this scenario, the inflationary half-life may be so short as to lead to a low probability of observing members in the class among the overall population, and hence the apparent lack of inflated sub-Saturns \citep{2023ApJ...945L..36T}.
 
 \citet{2011ApJ...738....1B} predicted runaway inflation of hot Saturns as a consequence of the Ohmic dissipation mechanism.
-Here, lightly ionized atmospheric flows induce drag in a planetary magnetic field, weakly coupling the stellar incident energy into the planetary interior.
-\citet{2018AJ....155..214T} recognized the above two explanations for the lack of sub-Saturns, while statistically favoring Ohmic dissipation as the mechanism responsible for inflating Hot Jupiters.
+Here, lightly thermally ionized atmospheric flows induce drag in a planetary magnetic field, weakly coupling the stellar incident energy into the planetary interior.
+\citet{2018AJ....155..214T} recognized the above two hypotheses for the lack of sub-Saturns, while statistically favoring Ohmic dissipation as the mechanism responsible for inflating Hot Jupiters.
 Therefore Ohmic dissipation stands out as a leading physical mechanism for inflation and mass loss.
@@
 A runaway inflation scenario predicts an inevitable and profound mass loss rate for inflated hot Saturns.
-As the planet's atmosphere overflows its Roche lobe at an ever-increasing pace instantaneous mass loss rates may exceed those previously seen in atmospheric escape measurements to date.
-These planets therefore make excellent targets for direct measurement of atmospheric escape.
+As the planet's atmosphere overflows its Roche lobe at an ever-increasing pace instantaneous mass loss rates may exceed $\dot{M}>10^{13}$, about 10$\times$ larger than those previously seen in atmospheric escape measurements to date \citep{2022arXiv221116243D}.
+Inflated hot Saturns therefore make excellent targets for direct measurement of atmospheric escape.
 
-The ability to detect that conceivable mass loss hinges on its observability in spectral tracers.
-Ly$\alpha$, \ion{He}{1} 10833 \AA, and H$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2022arXiv221116243D,2023MNRAS.518.4357O}, but each of these has its own limitations.
+Large mass loss alone does not guarantee detectability.
+The ability to detect even immense mass loss hinges on its observability in spectral tracers.
+Ly$\alpha$, \ion{He}{1} 10833 \AA, and H$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2022arXiv221116243D,2023MNRAS.518.4357O}, but each of these has its own observational limitations.
 Ly $\alpha$ can suffer from interstellar medium \ion{H}{1} absorption censoring its low-velocity line core, for example.
@@
 
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/tf2018_fig2_update2023_HAT.png}
+    \caption{Mass-radius trends for inflated hot sub-Saturns and hot Jupiters, form modeled after Figure 2 from \citet{2018AJ....155..214T} and updated with NASA Exoplanet Archive confirmed planets.
+The trend lines show the mass-radius relationship for equilibrium temperatures of 500, 1000, 1250, 1500, and 2000 K, assuming the mean composition and mean heating efficiency from the original figure.
+HAT-P-67~b stands alone in a region defined by the lack of inflated sub-Saturns, and explained by short lifetimes from runaway inflation and mass loss.}
+    \label{fig:ThornFortUpdated}
+\end{figure}
+
 Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, an inflated hot Saturn orbiting an F type sub-giant at an orbital separation of 0.06 AU and a 4.8-day orbital period \citep{2017AJ....153..211Z}.
 Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
-Its $\sim$0.05 g~cm$^-3$ density places it below the 1.0 g~cm$^-3$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.
-It orbits a possibly evolved subgiant, opening the prospect for ``re-inflation'' \citep{2022AJ....163...53S,2022AJ....163..120G,2023arXiv230306728G} as the planet's insolation increased with the star's rapid luminosity increase.
-The tidal gravity of the nearby massive host star may accelerate mass loss rates even further \citep{2007A&A...472..329E,2023ApJ...945L..36T}.
-Its status as a rare inflated Hot Saturn makes \object{HAT-P-67 b} a promising laboratory, including testing the runaway inflationary predictions of Ohmic dissipation and XUV photoevaporation.
+Its $\sim$0.05 g~cm$^{-3}$ density places it below the 1.0 g~cm$^{-3}$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.
+Figures \ref{fig:instellation} and \ref{fig:ThornFortUpdated} show how much of an outlier \hatp is: large, low mass, and heavily irradiated.
+
+The evolutionary state of \hatp offers even more intriguing possibilities.
+The host star may be an evolved subgiant, opening the prospect for planetary ``re-inflation'' \citep{2022AJ....163...53S,2022AJ....163..120G,2023arXiv230306728G} as the planet's insolation increased with the star's rapid luminosity increase in this part of the short-lived HR diagram.
+The tidal gravity of the nearby massive host star may amplify mass loss rates even further \citep{2007A&A...472..329E,2023ApJ...945L..36T}.
+Its status as a rare inflated Hot Saturn makes \object{HAT-P-67 b} a promising and laboratory, uniquely suited for testing the runaway inflationary predictions of Ohmic dissipation and XUV photoevaporation.
 
@@
 In practice, this limitation means that in-transit and out-of-transit observational phases were rarely possible on the same night.
-Instead, we organized the observations into four campaigns to coincide with \object{HAT-P-67 b} transits on the nights beginning 2020 April 28, 2020; May 22, 2020; June 15, 2020; and 2022 April 28.
+Instead, we organized the observations into four campaigns to coincide with \object{HAT-P-67 b} transits on the nights beginning 2020 April 27, 2020; May 21, 2020; June 14, 2020; and 2022 April 28.
 These campaigns have out-of-transit observations at least one night before and one night after, and often two nights on either side of the transit.
-Two more transits were obtained in 2022 June-July without the accompanying visits immediately before and after.
-The in-transit nights had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.
-We also obtained random-in-phase low-priority ``P4'' queue-filler observations.
+Two more transit snapshots were obtained in 2022 June-July without the accompanying visits immediately before and after.
+The in-transit campaigns had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.
+We also obtained random-in-phase low-priority ``P4'' queue-filler observations \citep{2007PASP..119..556S}.
 These out-of-transit snapshot observations typically received 4 or fewer individual exposures.
-We observed HAT-P-67 with HPF for a total of 41 visits on 39 unique nights, with two of those nights observing both an east and a west HET track.
-The total on-source integration time exceeds 13.8 hours.
+We observed HAT-P-67 with HPF for a total of 41 visits on 39 unique nights, with two of those nights observing both the east and west HET tracks.
+The total on-source integration time exceeds 13.8 hours, over $N=152$ individual spectra.
 Table \ref{tabHPFLog} summarizes the log of observations.
 
-The observation schedule was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature \citep{2022ApJ...939L..11S}.
+The observation schedule was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833 \AA~ feature \citep{2022ApJ...939L..11S}.
 The small BERV still means the redward Helium line wing has significant telluric contamination between 10834$-$10836 \AA, but the core and blue line wings appear relatively pristine.
 
-Only 19 out of the 39 nights possess A0V telluric calibration standard stars.  These standard stars were used to spot-check our telluric masking.
+Only 19 out of the 39 nights possess A0V telluric calibration standard stars.
+These standard stars were used to spot-check our telluric masking.
+Figure \ref{TESSoverview} indicates the epochs of select HPF visits overlaid on the \emph{TESS} time-series lightcurve.
 
@@
     \tablehead{
-        \colhead{Date}   &
+        \colhead{Night-of}   &
         \colhead{Track} &
@@
     \enddata
-    \tablecomments{All exposure times were 308.85~s except for observations from 2020-07-21 to 2021-03-30, which were 511.20~s.
+    \tablecomments{The night-of refers to the local date at the start of the night.
+All exposure times were 308.85~s except for observations from 2020-07-21 to 2021-03-30, which were 511.20~s.
 Column 2 describes the HET ``track'', restricted to either East (E) or West (W).
@@
 We selected sources based on \emph{Gaia} DR3 $T_\mathrm{eff}$ estimates and similar $\log{g}$,  and availability of at least one sector of TESS 2-minute cadence data.
-We also visually spot-checked these lightcurves to understand artifacts and windowing effects.
+We visually spot-checked these lightcurves to understand artifacts and windowing effects.
 
@@
 The DR3 parallax places the system about 8.7\% farther than previously estimated by \citet{2017AJ....153..211Z}, which adopted a \emph{Gaia} DR1-informed parallax of $2.92\pm0.23$ mas, including a systematic $-0.325$ mas bias term \citep{2016ApJ...831L...6S}.
-Its coarse \emph{Gaia}-based estimates for RV and Doppler broadening are consistent with the more precise values published in \citet{2017AJ....153..211Z}.
 The wide companion HAT-P-67B has nearly identical parallax ($2.58\pm0.05$ mas) and proper motions, confirming its interpretation as co-moving, with a projected separation of about 3400 AU.
@@
 In practice, the 0.15 magnitude jitter appears too coarse to perceive any genuine astrophysical variability, with no conspicuous trend seen.
-We can therefore place a relatively mild constraint that the star is stable at the $\sim30\%$ level over periods of tens to hundreds of years.
+We can therefore place a relatively mild constraint that the star appears stable at the $\sim30\%$ level over periods of tens to hundreds of years.
 
-HAT-P-67A was saturated in ZTF, but the M-dwarf companion HAT-P-67B had up to thousands of visits across several years.
+HAT-P-67A was saturated in ZTF \citep{2019PASP..131a8002B}, but the M-dwarf companion HAT-P-67B had up to thousands of visits across several years.
 The data quality appeared too poor to perceive any genuine astrophysical variability, with the indication of some lunar background signals in the periodogram.
@@
 \subsection{Other archives}
-\hatp has one $R\sim8000$ spectrum from the Intermediate Dispersion Spectrograph on the INT, centered near 4000 \AA.
+\authorcomment1{Slated for removal:}  
+\textcolor{lightgray}{\hatp has one $R\sim8000$ spectrum from the Intermediate Dispersion Spectrograph on the INT, centered near 4000 \AA.
 It has 26 photometry points from \emph{Pan-STARRS} spread across its 5 filters.
 The other archival observations have been previously reported by \citet{2017AJ....153..211Z}, including Keck HIRES, Keck NIRC2, and WIYN High-Resolution Infrared Camera.
-Overall the system appears relatively unstudied outside of the discovery paper.
+Overall the system appears relatively unstudied outside of the discovery paper.}
 
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figures/tf2018_fig2_update2023_HAT.png}
-    \caption{Mass-radius trends for inflated hot sub-Saturns and hot Jupiters, form modeled after Figure 2 from \citet{2018AJ....155..214T} and updated with NASA Exoplanet Archive confirmed planets.
-The trend lines show the mass-radius relationship for equilibrium temperatures of 500, 1000, 1250, 1500, and 2000 K, assuming the mean composition and mean heating efficiency from the original figure.
-HAT-P-67~b stands alone as occupying the ``Ohmic Dissipation Ridge'', defined by the lack of inflated sub-Saturns, and explained by short lifetimes from runaway inflation and mass loss.}
-    \label{fig:ThornFortUpdated}
-\end{figure}
-
 This dearth of hot Saturns has persisted into the \emph{TESS} era.

### 2023-05-11 paper/paper1/ms.tex
Uncomitted changes

@@
 \subsection{Gaia DR3}\label{analysisgaiaDR3}
-\citet{2017AJ....153..211Z} previously derived stellar radius estimates of 2.1-2.7 $R_\odot$ through Spectral Energy Distribution (SED) isochrone fitting as part of a joint orbit fit.
+\citet{2017AJ....153..211Z} previously derived stellar radius estimates of 2.1-2.7 $R_\odot$ through Spectral Energy Distribution (SED) and isochrone fitting as part of a joint orbit fit.
 We systematically increase those stellar radius estimates by 8.7\% to match the greater Gaia \emph{DR3} distance (\S \ref{gaiadr3}).
-For a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius.
-This update systematically decreases the estimate for the already-low density of HAT-P-67 by 28\%, to a mere 0.035 g$\;$cm$^{-3}$, albeit with significant uncertainties from the weak mass constraint.
+For a fixed $R_p/R_\star$ from the measured transit depth, the larger $R_\star$ implies a proportionally larger planet radius.
+This update systematically decreases the estimate for the already-low density of HAT-P-67 by 28\%, to a mere $<$0.035 g$\;$cm$^{-3}$, albeit with significant uncertainties from the weak mass constraint.
+The luminosity increases by 18\%, to about 10.3 $L_\odot$.
 
@@
 We fit a Keplerian orbit model to the TESS lightcurve using the \texttt{exoplanet} framework \citep{exoplanet:joss}.
-We obtained a best fit orbital period of $4.81011$ days, non-zero eccentricity of 0.19, an impact parameter of 0.46, planet-to-star radius ratio of 0.0823, transit depth of 0.74\%, and $T_0$ of 1958.07933 in BTJD.
-These properties are consistent with the previously reported values from \citet{2017AJ....153..211Z} and the updated ephemeris of \citet{2022ApJS..259...62I}.
-Figure \ref{fig:TESSoverview} shows an overview of all the TESS Sectors demarcated with the epochs of HPF measurements.
-Figure \ref{fig:transit} shows the best-fit orbit overlaid on the detrended TESS lightcurve.
-Table \ref{tabOrbit} lists one of the previous orbit determinations and the orbital solution reported here.
+We obtained revised orbital properties shown in Table \ref{tabOrbit}.
+These properties are broadly consistent with the previously reported values from \citet{2017AJ....153..211Z} and the updated ephemeris of \citet{2022ApJS..259...62I}.
+Figure \ref{fig:TESSoverview} shows an overview of all the TESS Sectors with a green GP trendline in green highlighting the out-of-transit modulations, and the exoplanet transit model in orange.
+Figure \ref{fig:transit} shows the best-fit orbit overlaid in purple on the detrended TESS lightcurve, which is binned in the orange dots.
+Table \ref{tabOrbit} lists only one of the previous orbit determinations---also assuming a circular orbit---compared with the orbital solution reported here.
 
@@
 
-The TESS Sector 26 lightcurve exhibits a weak $\sim$3 ppt peak-to-valley out-of-transit modulation on timescales comparable to the exoplanet orbit.
-TESS Sectors 51-53 do not show as conspicuous a modulation signal.
+The TESS Sector 26 lightcurve exhibits a weak $\sim$3 ppt peak-to-valley out-of-transit modulation.
+TESS Sectors 51-53 do not show as conspicuous a modulation signal, but still show some ostensibly stellar variability.
 The ebb and flow of the modulation can be seen in the minimally processed TESS lightcurve in Figure \ref{fig:TESSoverview}.
@@
 
-If we attribute this TESS modulation signal to stellar activity, we obtain a rotation period $P_\mathrm{rot}$ between 4.7 and 5.9 days.
-We can constrain the expected rotation period based on our revised stellar radius estimate, stellar rotation rate from $v\sin{i}$, and the observation of $i\sim90^\circ$ from orbit fitting and Doppler tomography \citep{2017AJ....153..211Z}.
+We can constrain the expected stellar rotation period based on the stellar radius estimate, $v\sin{i}$, and the observation of $i\sim90^\circ$ from orbit fitting and Doppler tomography \citep{2017AJ....153..211Z}.
 We adopt a high limit of $v\sin{i}=35.8\pm1.1$ km/s and a lower $v\sin{i}=30.9\pm2$ km/s value if macroturbulence is accounted for.
@@
 The geometrical constraint comports with the 4.7-day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9-day per-Sector fits, slightly preferring the lower 4.7-day modulation as the stellar rotation period.
-The 5.9-day value would require a stellar radius over 3.2$R_\odot$, which appears consistent with only an eccentric orbit model combined with the Geneva isochrone \citep{2017AJ....153..211Z}.
+The 5.9-day value would require a stellar radius over 3.2$R_\odot$, which appears implausible.
 
 \subsubsection{Lightcurve modulation amplitude}
-We computed the peak-to-valley modulation for the 1000-source \emph{TESS} comparison sample, defined as the difference between the 90$^{th}$ to 10$^{th}$ percentile of each normalized \emph{TESS} lightcurve.
+\authorcomment1{Slated for removal:}
+\textcolor{lightgray}{We computed the peak-to-valley modulation for the 1000-source \emph{TESS} comparison sample, defined as the difference between the 90$^{th}$ to 10$^{th}$ percentile of each normalized \emph{TESS} lightcurve.
 Most lightcurves appear consistent with negligible astrophysical variability and/or variability predominated by instrumental artifacts.
 \object{HAT-P-67}'s 0.36$\%$ lightcurve modulation ranked in the 87$^{th}$ percentile of the ensemble, about 0.5$\times$ above the median.
-Sources more variable than HAT-P-67 exhibited 3-5$\times$ its amplitude of modulation.
+Sources more variable than HAT-P-67 exhibited 3-5$\times$ its amplitude of modulation.}
 
@@
 \subsection{Revised system evolutionary state}\label{secMISTtracks}
-As discussed in Section \ref{analysisgaiaDR3}, the slightly increased distance and radius imply a slightly more luminous host star than previously estimated.
+The slightly increased distance and radius imply an 18\% more luminous host star than previously estimated.
 Figure \ref{fig:evolTracks} shows evolutionary tracks using the solar-metallicity MESA \citep{2011ApJS..192....3P,2013ApJS..208....4P,2015ApJS..220...15P} Isochrones and Stellar Tracks \citep[MIST;][]{2016ApJS..222....8D,2016ApJ...823..102C} for HAT-P-67.
-The tracks show that a 1.8 Gyr, 1.64 $M_\odot$ \hatp~ could be at the end of its main sequence lifetime (teal track), yielding a gradual rise in incident radiation to \hatpb.
+The tracks show that a 1.8 Gyr, 1.64 $M_\odot$ \hatp~ could be at the end of its main sequence lifetime (teal track), yielding a gradual rise in incident radiation over the lifetime of \hatpb.
 Alternatively, a 1.54 $M_\odot$ evolutionary track would send \hatp~ along the subgiant branch at an age over 2.2 Gyr, with a rapid 50\% increase in luminosity, potentially leading to ``re-inflation'' of the planet \citep{2021ApJ...909L..16T}.
 Either evolutionary track appears consistent with the observed SED, stellar surface gravity, and available constraints from spectral fitting.
-We therefore adopt a MIST-based 2$\pm$0.2 Gyr age for the system, in-between the previous Geneva and Dartmouth-based scenarios.
+We therefore adopt a MIST-based 2$\pm$0.2 Gyr age for the system, in-between the previous Geneva and Dartmouth-based scenarios \citep{2017AJ....153..211Z}.
+Additional metallicity and rotation effects could slightly alter the evolutionary tracks and therefore increase uncertainty in inferred ages and masses.
 
@@
 So even though the HPF points were more numerous, their marginal value for RV orbit determination was subdued owing to the lower RV information content in the near-IR for this relatively rapidly rotating F star.
-Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$, slightly decreasing the uncertainty compared to the previous $1\sigma$ limit.
+Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$ \kms---assuming a circular orbit---slightly decreasing the uncertainty compared to the previous $1\sigma$ limit.
 Table \ref{tabOrbit} lists the revised properties, with minor differences from the existing values.
-Notably, our fit does not jointly model the Doppler tomographic signals reported in \citep{2017AJ....153..211Z}, which would further constrain the impact parameter.
+Notably, our fit does not jointly model the Doppler tomographic signals reported in \citep{2017AJ....153..211Z}, which could further constrain the impact parameter.
 Additionally, our input $\rstar$ was slightly lower than the best-fit value derived from \emph{Gaia DR3} and SED fitting.
-%\authorcomment1{Quang Tran: please verify and revise.}
+\authorcomment1{Quang Tran: please verify and revise.}
 

### 2023-05-11 paper/paper1/ms.tex
The idea for grazing exospheres I pitched at an ExoUpdate many months ago

@@
 
+\subsection{Extended Helium exospheres in non-transiting planets}
+
+We measured a large extent of Helium escape along the arc of the orbit, but we necessarily can place only coarse constraints on the vertical extent--in the direction perpendicular to the orbital path, $\pm z$.
+We estimate the detectable vertical extent must be at least a few stellar radii, such that we still could have detected Helium escape in a hypothetical HAT-P-67b-like system even if it were non-transiting, in a ``near miss'' configuration.
+We propose a new category of semi-transiting planet, dubbed ``exospheric grazers'', in which the planet does not produce a detectable white-light transit depth, but does produce measureable \emph{line}-based exospheric absorption.
+This category appears to have been neglected due to the assumption that exospheres were only easily detectable at several planetary radii, and therefore fractions of a stellar radius.
+While large tails have been seen previously in Ly$\alpha$, the scarcity of UV resources prohibited searches of this kind.
+The discovery of large Helium tails in HAT-P-32b (Zhang et al.
+2023) and HAT-P-67b suggest that the identification of these exospheric grazers may be achievable with current instrumentation and possibly existing archival data from near-IR RV-planet searches.
+
+The configuration would consist of a HAT-P-67b-like planet undergoing profound mass loss, with a jet-like column of material either spouting from the poles, or lofted there through gas dynamics, or otherwise confined by bow-shock redirection.
+A process for identifying strong candidates could select close-in planets or planet candidates discovered from non-transiting techniques, such as RVs or TTVs.
+The best candidates would be planets with $M\sin{i}$, orbital periods, and insolations consistent with a hot Saturn mass.
+A followup program could be devised to acquire in-transit spectroscopy to search for \ion{He}{1} 10830~\AA, or other spectral tracers of mass loss.
+
+A few benefits of of this planet category arise.
+First, they would expand the sample of planets for which the planetary winds could be measured, by relaxing the narrow geometrical transit probability of $1-10^\circ$ to something closer to $\pm30^\circ$, depending on the mass loss and gas dynamics.
+In particular, the smallest stars such as white dwarfs and M-dwarfs could see the search space for exospheres increase by $10-100\times$.
+Second, the range of viewing angles would serve as a natural experiment for constraining the vertical extent of outflows in the first place.
+The typical bow shock 3D morphology could be deduced from a sample of otherwise-similar planets with a range of orbital inclinations.
+Non-detections would therefore be valuable, especially in cases where $\sin{i}$ could be constrained independently.
+In practice these additional constraints are rarely possible.
+Finally, for some promising planet candidates a distinctive helium signal could validate the planet, assuming the signal could be disambiguated from stellar variability via velocity structure and phasing.
+
 \section{Conclusions}

### 2023-05-11 paper/paper1/ms.tex
A few more sentences on the grazing exospheres

@@
 Non-detections would therefore be valuable, especially in cases where $\sin{i}$ could be constrained independently.
-In practice these additional constraints are rarely possible.
-Finally, for some promising planet candidates a distinctive helium signal could validate the planet, assuming the signal could be disambiguated from stellar variability via velocity structure and phasing.
+In practice these additional constraints are rarely possible, so ensemble statistical methods may have to be employed.
+Finally, for some promising planet candidates a distinctive helium signal could validate the planet, assuming the signal could be disambiguated from stellar variability.
+That disambiguation may be feasible, since the velocity structure and phasing of stellar and planetary Helium signals diverge due to stellar wind confinement and a launching from a predictable planetary rest frame.
+The elusive category of young planets could be ideal, since their large radii and high intrinsic temperatures and high incident XUV radiation may yield large mass loss rates if they have recently migrated to an interior location through disk migration.
+This category is especially valuable if discovered through near-IR RV searches, since abundant multi-epoch spectroscopy may already contain the requisite stellar variability baselines.
 

### 2023-05-15 paper/paper1/ms.tex
Will send a draft to Caroline today, reading through now.

@@
 
-\keywords{stars: fundamental parameters ---  stars: statistics}
+\keywords{Exoplanet atmospheres, Exoplanet evolution, Exoplanet atmospheric dynamics, Stellar winds, Exoplanet atmospheric variability}
 
@@
 A runaway inflation scenario predicts an inevitable and profound mass loss rate for inflated hot Saturns.
-As the planet's atmosphere overflows its Roche lobe at an ever-increasing pace instantaneous mass loss rates may exceed $\dot{M}>10^{13}$, about 10$\times$ larger than those previously seen in atmospheric escape measurements to date \citep{2022arXiv221116243D}.
+As the planet's atmosphere overflows its Roche lobe at an ever-increasing pace instantaneous mass loss rates may exceed $\dot{M}>10^{13}$ g/s, over 10$\times$ larger than those previously seen in atmospheric escape measurements to date \citep{2022arXiv221116243D}.
 Inflated hot Saturns therefore make excellent targets for direct measurement of atmospheric escape.
@@
 Ly$\alpha$, \ion{He}{1} 10833 \AA, and H$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2022arXiv221116243D,2023MNRAS.518.4357O}, but each of these has its own observational limitations.
-Ly $\alpha$ can suffer from interstellar medium \ion{H}{1} absorption censoring its low-velocity line core, for example.
+Ly$\alpha$ can suffer from interstellar medium \ion{H}{1} absorption censoring its low-velocity line core, for example.
 Here we focus on \ion{He}{1} 10833 \AA, which offers some advantages.
@@
 Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
-Its $\sim$0.05 g~cm$^{-3}$ density places it below the 1.0 g~cm$^{-3}$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.
-Figures \ref{fig:instellation} and \ref{fig:ThornFortUpdated} show how much of an outlier \hatp is: large, low mass, and heavily irradiated.
+Its $\sim$0.05 g~cm$^{-3}$ density places it firmly below the 1.0 g~cm$^{-3}$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.
+Figures \ref{fig:instellation} and \ref{fig:ThornFortUpdated} show how much of an outlier \hatpb~ is: large, low mass, and heavily irradiated.
 
@@
 These standard stars were used to spot-check our telluric masking.
-Figure \ref{TESSoverview} indicates the epochs of select HPF visits overlaid on the \emph{TESS} time-series lightcurve.
+Figure \ref{fig:TESSoverview} indicates the epochs of select HPF visits overlaid on the \emph{TESS} time-series lightcurve.
 
@@
 The vanishing $<36$ m/s reflex motion of the star is imperceptible at this scale.
-The horizontal dashed lines indicate the moments of transit ingress (-0.03), mid-center (0.0), and egress (+0.03).
+The horizontal dashed lines indicate the moments of transit ingress (-0.03), mid-center (0.0), and egress (+0.03), demarcated as \texttt{TRANSIT} in the figure.
+
+We define 4 additional distinct groups of phases with adjectival qualifiers in anticipation of the need to discuss bulk trends: \texttt{PRE}, \texttt{POST}, \texttt{CONTROL}, and \texttt{BASELINE}.
+The \texttt{BASELINE} phases define the out-of-transit baseline.
+The ``control'' spectra designate phases just before the baseline, but not used to define the baseline, to inspect minor correlation structure in the spectra without dividing it out.
+Table \ref{tabHPFLog} lists the adjectival qualifiers for each HPF visit.
 
@@
 We chose a 6400 K PHOENIX \citep{husser13} solar metallicity photospheric spectral template with $\log{g}=3.5$, scaled to the solid angle seen by \hatpb.
-The F7IV-V \object[tau Boo]{$\tau$ Boo} serves as the closest analog with available synthetic x-ray coronal spectra \citep{2011A&A...532A...6S}.
+The F7IV-V \object[tau Boo]{$\tau$ Boo} serves as the closest analog with available synthetic X-ray coronal spectra \citep{2011A&A...532A...6S}.
 But \hatp resides closer to the Kraft break than does \object[tau Boo]{$\tau$ Boo}, and the move to hotter F stars may be associated with weakening of the stellar wind and other atmospheric changes leading to the prospect of much lower XUV luminosity for HAT-P-67 \citep{2022ApJ...930....7A}.
@@
 
+\begin{figure}
+    \includegraphics[width=0.8\linewidth]{figures/homogeneous.png}
+    \caption{Isotropic mass loss}
+    \label{fig:IsotropicMdot}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.8\linewidth]{figures/asym.png}
+    \caption{Asymmetric dayside mass loss}
+    \label{fig:DaysideMdot}
+\end{figure}
+
 Stellar wind confinement \citep{2022ApJ...926..226M} arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.
@@
 Whereas traditional Doppler Tomography treats the scanning reticle as an opaque planetary disk, here the reticle resembles a transmissive filter with a wavelength center and width that varies in space and time.
-We rank this effect as second-order and ignore it for now.
-%%We can understand this transmissive Doppler tomography effect through an example of a pathological limiting case.
-Imagine the escaping atmsosphere were concentrated in a 50\% transmissive cylinder coming out of the orbital plane, as in an idealized transparent bipolar outflow.
-This cyclinder would possess the planet's bulk velocity of about $-30$ km/s at the moment of transit ingress, placing the locus of absorption at about 10832.4 \AA.
-But the absorptive cylinder would intercept a finite range of stellar limb velocities, broadening the apparent width of the absorption line.
+We rank this effect as second-order and return to it in the Discussion Section \ref{vsini-interplay}.
 
@@
 Nevertheless, we can project the time series trends in their Figures 3 and 4 to recreate a qualitative history and fate of \hatpb~ under the assumptions of XUV photoevaporation.
-Broadly, the planet would have started with an initial mass up to 50$\%$ more massive than it is now, with $R\sim\;$1.4 $R_\mathrm{Jup}$, for an initial density of $\sim$0.2 g/cm$^-3$.
+Broadly, the planet would have started with an initial mass up to 50$\%$ greater than at present, with $R\sim\;$1.4 $R_\mathrm{Jup}$, for an initial density of $\sim$0.2 g/cm$^-3$.
 It would lose mass at a rate of tens of Earth masses per Gyr for its 1 Gyr lifetime, expanding modestly until it reaches the critical $\sim$0.1 g/cm$^-3$ threshold, at which point the mass loss rate increases to its current value.
@@
 In Section \ref{secMISTtracks} MIST evolutionary tracks showed two equally plausible states: the tail-end of the main sequence or a recently evolved sub-giant.
-Figure X employs these tracks to assess what the impact on \hatpb~could be, assuming that the orbital location has not changed over the system lifetime (\emph{i.e.} star-planet or planet-planet migration has been negligible).
+Figure \ref{fig:OhmicInflate} employs these tracks to assess the re-inflationary impact of \hatpb~could be, assuming that the orbital location has not changed over the system lifetime.
 The second panel from the top illustrates a countervailing effect: the decrease in Ohmic dissipation heating efficiency, $\epsilon$, could counteract the increase of stellar flux, assuming the functional form for $\hat{\epsilon}_G$ described by \citet{2018AJ....155..214T}.
@@
 Nevertheless, the similarity of the curve is remarkable since it arrives at approximately the correct planet radius at the right age.
-The modeled mass is slightly higher than, but consistent with the RV-measured mass, and could imply a large and increasing mass loss rate over its lifetime.
+The modeled mass is slightly higher than, but consistent with the RV-measured mass, and would imply a large and increasing mass loss rate over its lifetime.
 
@@
 
-We, therefore, attribute this cliff in the $M_p$ vs $R_p$ diagram to Ohmic dissipation.
+We, therefore, attribute this cliff in the $M_p$ vs $R_p$ diagram to either Ohmic dissipation, XUV photoevaporation, or both.
 \citet{2018AJ....155..214T} emphasized the positive feedback loop as a cause for the lack of sub-Saturns and noted an alternative interpretation-- mass-dependent migration segregation.
@@
 Furthermore, the runaway evaporation of hot Saturns was naturally predicted by the Ohmic dissipation mechanism, whereas mass-dependent migration has only been developed as a post-diction.
+
+One key observation may tip the scales in favor of XUV photoevaporation as the predominant cause of mass-loss.
+The conspicuous leading tail favors preferential mass loss on the highly irradiated planet dayside.
+While Ohmic dissipation would exhibit preferential dayside heating, it is the ability of XUV photons to create a planetary wind that tilts the balance.
+
+Finally we consider the prospect that the planetary mass is much lower than its 1-$\sigma$ bound, such that the white-light planetary radius \emph{is} the Hill radius (we have previously assumed the Hill radius is 2.7 planetary radii).
+This extreme scenario could manifest enormous mass loss rates, with the planet atmosphere's reservoir of mass fleeing the gravitational potential well directly, without the cushion of an exosphere.
+This terminal Roche Lobe overflow would have several observational predictions.
+Heavy elements woud easily leak into the planetary wind, yielding possibly many observable metal lines in the UV.
+These may be observable even under more mild conditions, due to lofting of metals into the upper atmosphere, so some care would be required to quantitatively distinguish these two scenarios.
 
@@
 \section{Discussion}
-\subsection{Orbital constraints}
-We premised our joint \emph{TESS} lightcurve and HPF RV time series orbit fit on a circular orbit.
+%\subsection{Prospects for a non-circular orbit}
+%\authorcomment1{Slated for removal:}  
+%\textcolor{lightgray}{We premised our joint \emph{TESS} lightcurve and HPF RV time series orbit fit on a circular orbit.
+Here we consider how a finite eccentricity orbit could effect the observations and lead to the illusion of a leading tail...
+[...]}
 
@@
 The conventional interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8-day orbital period of planet b.
-The cause for such orbital and rotational synchronization would then ostensibly be star-planet tidal interactions.
-We examine the prospect of tides in the next subsection.
+The cause for such orbital and rotational synchronization would then be either coincidence or secular star-planet tidal interactions.
+For the latter, disk migration could have naturally ceased near the co-rotation radius, leaving the planet to reside naturally near the stellar $P_\mathrm{rot}$.
 
-Alternatively, the extreme mass loss and credibility of the Ohmic dissipation model motivate the prospect of Star Planet Magnetic Interaction (SPMI) that we consider now.
+Alternatively, Star Planet Magnetic Interaction (SPMI) could be at play.
 In this scenario, the magnetic field of the planet permeates the space between the star and the planet.
@@
 The planet can interact with the star if the Alfv\'en speed exceeds the stellar wind speed controlling the bulk motion of the intervening medium.
-The magnetic field of the planet is not known, but the ohmic dissipation mechanism favors a limited range in the magnetic field strength: large enough to cause significant dissipative energy generation, but not too large to shut down charged particle motion entirely.
-\citet{2011ApJ...738....1B} estimate this range as between about 1-30~G.
+The non-detection of variability in the \ion{Ca}{2} H and K lines and H$\alpha$ lines appears to disfavor this SPMI interpretation, since SPMI could be expected to cause variations in these diagnostics.
 
-The non-detection of variability in the \ion{Ca}{2} H and K lines and H~$\alpha$ lines appears to disfavor this SPMI interpretation.
+It is hypothetically possible---albeit unlikely---that mass loss could be great enough to produce variability in the wide band \emph{TESS} lightcurve.
+The HPF spectra reveal up to 10\% signal depth over a few Angstroms.
+The TESS bandpass barely includes 10830 \AA, at a location of diminishing throughput, so it appears impractical that Helium alone could cause the TESS signal.
+Hypothetically, dust dedged up in the mass loss process could cause a large enough broadband flux loss to manifest in TESS.
+We may expect to see some variable reddening in that case.
+A putative H$\alpha$ line would have to be about 30\% deep over 10 \AA~ wide to manifest perceptibly in the TESS data.
+Such an implausibly deep line likely would have been observed as perturbations in the Keck HIRES spectra, even with its limited phasing.
 
-\subsection{Extended Helium exospheres in non-transiting planets}
+\subsection{Implications for exosphere detection in non-transiting planets}
 
-We measured a large extent of Helium escape along the arc of the orbit, but we necessarily can place only coarse constraints on the vertical extent--in the direction perpendicular to the orbital path, $\pm z$.
+We measured a large extent of Helium escape along the arc of the orbit, but we necessarily can place only coarse constraints on the vertical extent---in the direction perpendicular to the orbital path, $\pm z$.
 We estimate the detectable vertical extent must be at least a few stellar radii, such that we still could have detected Helium escape in a hypothetical HAT-P-67b-like system even if it were non-transiting, in a ``near miss'' configuration.
-We propose a new category of semi-transiting planet, dubbed ``exospheric grazers'', in which the planet does not produce a detectable white-light transit depth, but does produce measureable \emph{line}-based exospheric absorption.
+We propose a new category of semi-transiting planet, dubbed ``exospheric grazers'', in which the planet does not produce a detectable white-light transit depth, but \emph{does} produce measureable \emph{line}-based exospheric absorption.
 This category appears to have been neglected due to the assumption that exospheres were only easily detectable at several planetary radii, and therefore fractions of a stellar radius.
@@
 The discovery of large Helium tails in HAT-P-32b (Zhang et al.
-2023) and HAT-P-67b suggest that the identification of these exospheric grazers may be achievable with current instrumentation and possibly existing archival data from near-IR RV-planet searches.
+2023) and now HAT-P-67b suggest that the identification of these exospheric grazers may be achievable with current instrumentation and possibly existing archival data from near-IR RV-planet searches.
 
@@
 Finally, for some promising planet candidates a distinctive helium signal could validate the planet, assuming the signal could be disambiguated from stellar variability.
-That disambiguation may be feasible, since the velocity structure and phasing of stellar and planetary Helium signals diverge due to stellar wind confinement and a launching from a predictable planetary rest frame.
-The elusive category of young planets could be ideal, since their large radii and high intrinsic temperatures and high incident XUV radiation may yield large mass loss rates if they have recently migrated to an interior location through disk migration.
+That disambiguation may be feasible, since the velocity structure and phasing of stellar and planetary Helium signals diverge due to stellar wind confinement and the launching from a predictable planetary rest frame.
+The elusive category of young planets could make ideal targets, since their large radii and high intrinsic temperatures and high incident XUV radiation may yield large mass loss rates if they have recently migrated to an interior location through disk migration.
 This category is especially valuable if discovered through near-IR RV searches, since abundant multi-epoch spectroscopy may already contain the requisite stellar variability baselines.
+
+\subsection{Interplay with rotating stellar disk} \label{vsini-interplay}
+
+As aluded to previously, the interplay between the rotating stellar disk and the Helium line absorption sets up a subtle Doppler tomography-like signal.
+
+We can understand this transmissive Doppler tomography effect through an example of four pathological limiting cases, illustrated in Figure \ref{fig:interplayvsini}.
+Imagine the escaping atmsosphere were concentrated in a 20\% transmissive cylinder coming out of the orbital plane, as in an idealized transparent bipolar outflow.
+This cyclinder would possess the planet's bulk velocity of about $-30$ km/s at the moment of transit ingress, placing the locus of absorption at about 10832.4 \AA.
+But the absorptive cylinder would intercept a finite range of stellar limb velocities.
+There would exist a constructive interference at the moment when the planet radial velocity shifts the \ion{He}{1} 10830 \AA line to share the same observed wavelength as the stellar lines at that limb position.
+
+\begin{figure*}[t]
+    \includegraphics[width=\linewidth]{figures/disperse_vsini_interplay_v0p1.pdf}
+    \caption{Illustration of the interplay between a transiting columnar exosphere (extreme case) and a rotating stellar disk.
+The top row shows a non-rotating (negligble $v\sin{i}$) case, with sharp stellar lines.
+The motion of the planet can be seen easily, and the signals align at the planet's zero velocity (center of the disk).
+The bottom row shows the rapidly rotating case.
+Depending on the planet orbital speed and stellar rotational speeds, the signals can align at some pair wavelength before and after transit mid-center.
+The alignment of the signals acts to \emph{suppress} the signal since the planet exosphere is blocking the fainter-on-average flux.
+If the gas is spread out uniformly over the disk---instead of in a vertical column---the signals simply multiply.}
+    \label{fig:interplayvsini}
+\end{figure*}
 

### 2023-05-15 paper/paper1/ms.tex
Delete the interplay with vsini subsection per CVM guidance

@@
 
-\subsection{Interplay with rotating stellar disk} \label{vsini-interplay}
-
-As aluded to previously, the interplay between the rotating stellar disk and the Helium line absorption sets up a subtle Doppler tomography-like signal.
-
-We can understand this transmissive Doppler tomography effect through an example of four pathological limiting cases, illustrated in Figure \ref{fig:interplayvsini}.
-Imagine the escaping atmsosphere were concentrated in a 20\% transmissive cylinder coming out of the orbital plane, as in an idealized transparent bipolar outflow.
-This cyclinder would possess the planet's bulk velocity of about $-30$ km/s at the moment of transit ingress, placing the locus of absorption at about 10832.4 \AA.
-But the absorptive cylinder would intercept a finite range of stellar limb velocities.
-There would exist a constructive interference at the moment when the planet radial velocity shifts the \ion{He}{1} 10830 \AA line to share the same observed wavelength as the stellar lines at that limb position.
-
-\begin{figure*}[t]
-    \includegraphics[width=\linewidth]{figures/disperse_vsini_interplay_v0p1.pdf}
-    \caption{Illustration of the interplay between a transiting columnar exosphere (extreme case) and a rotating stellar disk.
-The top row shows a non-rotating (negligble $v\sin{i}$) case, with sharp stellar lines.
-The motion of the planet can be seen easily, and the signals align at the planet's zero velocity (center of the disk).
-The bottom row shows the rapidly rotating case.
-Depending on the planet orbital speed and stellar rotational speeds, the signals can align at some pair wavelength before and after transit mid-center.
-The alignment of the signals acts to \emph{suppress} the signal since the planet exosphere is blocking the fainter-on-average flux.
-If the gas is spread out uniformly over the disk---instead of in a vertical column---the signals simply multiply.}
-    \label{fig:interplayvsini}
-\end{figure*}
-
 \section{Conclusions}

### 2023-05-15 paper/paper1/ms.tex
New figure and caption comparing OD and Photoionization

@@
 Recently, \citet{2023ApJ...945L..36T} showed that hot Saturns can undergo catastrophic erosion by stellar X-ray and Extreme UV (XUV) photoevaporative mass loss.
-Planets with densities less than $\sim$1 g~cm$^{-3}$ achieve mass loss rates of up to $10^3$ $M_\oplus /$Gyr setting up a positive feedback loop: the planet increases in radius, overflowing its Roche lobe, fueling greater mass loss, and increasing in radius even further.
-This vicious cycle systematically depopulates the mass-radius plane with a cliff defined by the $\sim$1 g~cm$^{-3}$ dividing line.
+Planets with densities less than $\sim$0.1 g~cm$^{-3}$ achieve mass loss rates of up to $10^3$ $M_\oplus /$Gyr setting up a positive feedback loop: the planet increases in radius, overflowing its Roche lobe, fueling greater mass loss, and increasing in radius even further.
+This vicious cycle systematically depopulates the mass-radius plane with a cliff defined by the $\sim$0.1 g~cm$^{-3}$ dividing line.
 
@@
 Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
-Its $\sim$0.05 g~cm$^{-3}$ density places it firmly below the 1.0 g~cm$^{-3}$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.
+Its $\sim$0.05 g~cm$^{-3}$ density places it firmly below the 0.1 g~cm$^{-3}$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.
 Figures \ref{fig:instellation} and \ref{fig:ThornFortUpdated} show how much of an outlier \hatpb~ is: large, low mass, and heavily irradiated.
@@
 \begin{figure}[t]
-    \includegraphics[width=\linewidth]{figures/tf2018_fig2_theory.png}
-    \caption{Ohmic dissipation runaway inflation timescale in the exoplanet mass-radius diagram.
+    \includegraphics[width=\linewidth]{figures/thorn2023_theory.png}
+    \caption{Runaway inflation timescale in the exoplanet mass-radius diagram.
+The shading of the top panel shows $\tau_\mathrm{infl}$ from Ohmic dissipation, the bottom panel shows $\tau_\mathrm{infl}\equiv M/\dot{M}$ from photoionization-driven mass loss.
 Individual planets with confident mass and radius detections are shown as small black dots.
-Helium non-detections are shown in red squares with all detections of atmospheric escape coming from \citet{2022arXiv221116243D}.
-\hatpb~ resides in a sparsely populated region with a vanishingly short inflationary timescale, making it unstable to runaway evaporation with large mass loss expected.}
+Helium non-detections are shown in red squares, atmospheric escape detections from any origin in green circles \citep{2022arXiv221116243D}.
+Under either scenario, \hatpb~ resides in a sparsely populated region with short inflationary timescale, making it unstable to runaway evaporation with large mass loss expected.
+Photoionization better predicts the depopulation of sources in the upper left low density region of the diagram, defined by the 0.1 g cm$^{-3}$ iso-density dashed white line.}
     \label{fig:tf2018_theory}

### 2023-05-15 paper/paper1/ms.tex
Placeholder for hydrodynamic simulation text

@@
 
+\subsection{3D Hydrodynamic simulations}
+\authorcomment1{Insert Morgan Macleod text here.}
+\textcolor{lightgray}{Habitasse platea dictumst vestibulum rhoncus est pellentesque elit ullamcorper dignissim.
+Odio ut sem nulla pharetra.
+Odio ut sem nulla pharetra diam sit amet nisl suscipit.
+Accumsan tortor posuere ac ut.
+Ornare arcu dui vivamus arcu felis bibendum ut tristique.
+Nunc faucibus a pellentesque sit amet porttitor eget.
+Mauris rhoncus aenean vel elit.
+Sed vulputate mi sit amet mauris commodo.
+Quis lectus nulla at volutpat diam ut venenatis.
+Sed id semper risus in hendrerit gravida rutrum quisque non.
+Est placerat in egestas erat imperdiet sed.
+Viverra adipiscing at in tellus integer feugiat scelerisque varius.
+Quam viverra orci sagittis eu volutpat odio facilisis mauris sit.
+Morbi tristique senectus et netus et malesuada.
+Duis tristique sollicitudin nibh sit amet.
+Libero nunc consequat interdum varius sit amet mattis vulputate.
+Velit ut tortor pretium viverra suspendisse potenti nullam ac.
+Viverra accumsan in nisl nisi scelerisque eu ultrices vitae.
+Quis commodo odio aenean sed adipiscing diam donec.}
+
 The overall observation of a leading tail comports with either of these two physical mechanisms, and we suspect both are at play in \hatpb.
@@
 The planet's equilibrium temperature increases as the stellar luminosity gradually increases on the main sequence.
+The second panel from top shows the corresponding estimate for anomalous heating efficiency from \citet{2018AJ....155..214T}.
 The Ohmic dissipation model makes predictions for runaway inflation, depending on the incident stellar flux.
-The heuristic scaling relation for the inflation timescale predicts unusually small values in this extreme regime but illustrates the countervailing effects of the top two panels.}
+The heuristic scaling relation for the inflation timescale predicts vanishingly short inflationary lifetimes in this extreme regime but illustrates the countervailing effects of the top two panels.}
     \label{fig:OhmicInflate}

### 2023-05-15 paper/paper1/ms.tex
Expand XUV figure caption per CVM guidance

@@
 So there remains significant uncertainty about the applicability of the \object[tau Boo]{$\tau$ Boo} XUV spectrum to HAT-P-67.
-We scaled the synthetic SED of \object[tau Boo]{$\tau$ Boo} retrieved from X-exoplanets \citep{2011A&A...532A...6S} so that the integral of ground-state ionizing photons ($\lambda<504\AA$) exhibited $L_X/L_\mathrm{bol} \in [10^{-7}, 10^{-5}]$.
+We scaled the synthetic SED of \object[tau Boo]{$\tau$ Boo} retrieved from X-exoplanets \citep{2011A&A...532A...6S} so that the integral of ground-state ionizing photons ($\lambda<504\AA$) exhibited $L_X/L_\mathrm{bol} \in [10^{-6}, 10^{-4}]$.
 Figure \ref{fig:XUV} shows two conceivable SEDs with these high and low radiation hardness.
@@
     \includegraphics[width=\linewidth]{figures/XUV_flux_schematic.png}
-    \caption{Synthetic XUV radiation scenarios for \hatpb.  }
+    \caption{Synthetic XUV radiation scenarios for \hatpb.
+The low and high XUV scenarios correspond to $L_X/L_\mathrm{bol}$ of $10^{-6}$ and $10^{-4}$, where $L_X$ is defined as He 1 $^1$S Ionizing photons that trigger the recombination cascade needed for observing the He 2 $^3$S Ionization metastable state.
+He 2 $^3$S Ionizing photons depopulate the state and suppress the observability of \ion{He}{1} 10830 \AA.
+The XUV flux of HAT-P-67 is uncertain.}
     \label{fig:XUV}
@@
 The theory-inspired mass loss rates above correspond to 1D Parker wind \ion{He}{1} feature depths and widths similar to what we observe, as evinced in Figure \ref{fig:pwinds}, with $\dot{M}_\mathrm{1D}\sim100$ M$_\oplus$/Gyr.
-%\authorcomment1{To be continued--- interpret this congruence}.
 
@@
 \section{Discussion}
-%\subsection{Prospects for a non-circular orbit}
-%\authorcomment1{Slated for removal:}  
-%\textcolor{lightgray}{We premised our joint \emph{TESS} lightcurve and HPF RV time series orbit fit on a circular orbit.
-Here we consider how a finite eccentricity orbit could effect the observations and lead to the illusion of a leading tail...
-[...]}
 

### 2023-05-15 paper/paper1/ms.tex
Grammarly run through

@@
 As the planet's atmosphere overflows its Roche lobe at an ever-increasing pace instantaneous mass loss rates may exceed $\dot{M}>10^{13}$ g/s, over 10$\times$ larger than those previously seen in atmospheric escape measurements to date \citep{2022arXiv221116243D}.
-Inflated hot Saturns therefore make excellent targets for direct measurement of atmospheric escape.
+Inflated hot Saturns, therefore, make excellent targets for direct measurement of atmospheric escape.
 
@@
 The trend lines show the mass-radius relationship for equilibrium temperatures of 500, 1000, 1250, 1500, and 2000 K, assuming the mean composition and mean heating efficiency from the original figure.
-HAT-P-67~b stands alone in a region defined by the lack of inflated sub-Saturns, and explained by short lifetimes from runaway inflation and mass loss.}
+HAT-P-67~b stands alone in a region defined by the lack of inflated sub-Saturns and explained by short lifetimes from runaway inflation and mass loss.}
     \label{fig:ThornFortUpdated}
@@
 The tidal gravity of the nearby massive host star may amplify mass loss rates even further \citep{2007A&A...472..329E,2023ApJ...945L..36T}.
-Its status as a rare inflated Hot Saturn makes \object{HAT-P-67 b} a promising and laboratory, uniquely suited for testing the runaway inflationary predictions of Ohmic dissipation and XUV photoevaporation.
+Its status as a rare inflated Hot Saturn makes \object{HAT-P-67 b} a promising laboratory, uniquely suited for testing the runaway inflationary predictions of Ohmic dissipation and XUV photoevaporation.
 
@@
     \enddata
-    \tablecomments{The night-of refers to the local date at the start of the night.
+    \tablecomments{The ``night of'' refers to the local date at the start of the night.
 All exposure times were 308.85~s except for observations from 2020-07-21 to 2021-03-30, which were 511.20~s.
 Column 2 describes the HET ``track'', restricted to either East (E) or West (W).
-The thresholds for the prepositional description in Column 3 is defined in the text.
 Column 5 is the normalized phase $\phi \in(-0.5, 0.5)$, with zero at midtransit.}
@@
     \includegraphics[width=\linewidth]{figures/best_fit_orbit.png}
-    \caption{Best fit orbit overlaid on the composite TESS lightcurve.}
+    \caption{Best fit orbit overlaid on the composite TESS lightcurve.
+Revised planet properties are consistent with \citet{2017AJ....153..211Z}, with a systematic shift from a revised \emph{Gaia} DR3 distance.}
     \label{fig:transit}
@@
 The TESS Sector 26 lightcurve exhibits a weak $\sim$3 ppt peak-to-valley out-of-transit modulation.
-TESS Sectors 51-53 do not show as conspicuous a modulation signal, but still show some ostensibly stellar variability.
+TESS Sectors 51-53 do not show as conspicuous a modulation signal but still show some ostensibly stellar variability.
 The ebb and flow of the modulation can be seen in the minimally processed TESS lightcurve in Figure \ref{fig:TESSoverview}.
@@
     \includegraphics[width=0.98\linewidth]{figures/MIST_only_HATP.png}
-    \caption{MIST evolutionary model tracks for HAT-P-67.  The $T_\mathrm{eff}$ and luminosity of \hatp (gray circle) are consistent with either the late main sequence or recently evolved subgiant.}
+    \caption{MIST evolutionary model tracks for HAT-P-67.
+The $T_\mathrm{eff}$ and luminosity of \hatp (gray circle) are consistent with either the late main sequence or recently evolved subgiant.
+The labeled numbers indicate age in Gyr.}
     \label{fig:evolTracks}
@@
 Either evolutionary track appears consistent with the observed SED, stellar surface gravity, and available constraints from spectral fitting.
-We therefore adopt a MIST-based 2$\pm$0.2 Gyr age for the system, in-between the previous Geneva and Dartmouth-based scenarios \citep{2017AJ....153..211Z}.
+We, therefore, adopt a MIST-based 2$\pm$0.2 Gyr age for the system, in-between the previous Geneva and Dartmouth-based scenarios \citep{2017AJ....153..211Z}.
 Additional metallicity and rotation effects could slightly alter the evolutionary tracks and therefore increase uncertainty in inferred ages and masses.
@@
     \includegraphics[width=\linewidth]{figures/HAT-P-67b_rv.pdf}
-    \caption{RV orbit fit including both HPF and Keck HIRES data points.}
+    \caption{RV orbit fit including both HPF and Keck HIRES data points.
+The RV information content in HPF is much less than in Keck HIRES for this F5 spectral type, and so the joint fit constrains the mass to roughly a Saturn mass.}
     \label{fig:RVfit}
@@
 The \texttt{BASELINE} phases define the out-of-transit baseline.
-The ``control'' spectra designate phases just before the baseline, but not used to define the baseline, to inspect minor correlation structure in the spectra without dividing it out.
+The ``control'' spectra designate phases just before the baseline but are not used to define the baseline, to inspect minor correlation structure in the spectra without dividing it out.
 Table \ref{tabHPFLog} lists the adjectival qualifiers for each HPF visit.
@@
     \includegraphics[width=\linewidth]{figures/HAT_P_67b_Helium10830EW_byCampaign.png}
-    \caption{Time series EW lightcurve of Helium absorption in HAT-P-67b.  The system exhibits a characteristic absorption leading up to transit, followed by a sharp decline after transit passage.  }
+    \caption{Equivalent width lightcurve of Helium absorption in HAT-P-67b.  The system exhibits a characteristic absorption leading up to transit, followed by a sharp decline after transit passage.}
     \label{fig:HPFtimeseries}
@@
 Figure \ref{fig:centroids} shows the centroid positions of the Helium excess feature.
-The bulk velocity drifts of the planet outflow can be seen with a few conspicuous trends.
+The bulk velocity drifts of the planet's outflow can be seen with a few conspicuous trends.
 The pre-transit phases ($-0.3$ to $+0.03$) show a slight tendency towards blueshift relative to stellar restframe, with an accelerating blueshift from phases $-0.3$ to $-0.15$, albeit with some visit-to-visit scatter.
@@
 That large fraction of an orbit translates to about 0.1 AU, 130 planetary radii, and well outside of the Roche Lobe, with its Hill radius of merely 2.6 planetary radii.
-We are detecting Roche lobe overflow, gas that is entirely unbound from the planet.
+We are detecting Roche lobe overflow, escaping material that is entirely unbound from the planet.
 The bulk of the detectable unbound gas may be understood as following its own Keplerian trajectory at a slightly shorter period orbit, pulling away from the planet parallel to the orbital path.
@@
 We scaled the synthetic SED of \object[tau Boo]{$\tau$ Boo} retrieved from X-exoplanets \citep{2011A&A...532A...6S} so that the integral of ground-state ionizing photons ($\lambda<504\AA$) exhibited $L_X/L_\mathrm{bol} \in [10^{-6}, 10^{-4}]$.
-Figure \ref{fig:XUV} shows two conceivable SEDs with these high and low radiation hardness.
+Figure \ref{fig:XUV} shows two conceivable SEDs with these high and low radiation hardnesses.
 
@@
 Equipped with these two SEDs of differing radiation hardness, we explored different mass loss rates and exosphere temperatures.
-Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 10^{13}$ g/s, and $T_0=9100$~K, with the a medium XUV spectrum ($L_x/L_\mathrm{bol}=10^{-5}$).
+Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 10^{13}$ g/s, and $T_0=9100$~K, with an XUV spectrum possessing $L_x/L_\mathrm{bol}=10^{-5}$.
 This mass loss rate would imply a characteristic lifetime of $\sim$2000 Myr.
@@
 The spectrum was generated with a mass loss rate of $10^{13}$ g/s, exosphere gas temperature of 9100 K, and with an XUV luminosity $L_x/L_\mathrm{bol}=10^{-5}$ intermediate between those shown in Figure \ref{fig:XUV}.
-The lines have about the same  equivalent width, while additional unmodeled velocity dispersion of the gas can explain differences between the line shapes of model and data.
+The lines have about the same equivalent width, while additional unmodeled velocity dispersion of the gas can explain differences between the line shapes of the model and data.
 Overall the 1D models may be too simplistic to represent the inherently 3D structure of the outflow.}
@@
 
-In order to examine the in-transit velocity structure, we have to consider the interplay of a two subtle geometrical effects.
-First, the planet's Roche lobe is small enough (2.7 $R_\mathrm{p}$) that the majority of the projected stellar disk should be filled with gas unbound from the planet, even at the time of mid-transit.
+In order to examine the in-transit velocity structure, we have to consider the interplay of two subtle geometrical effects.
+First, the planet's Roche lobe is small enough (2.7 $R_\mathrm{p}$) that the majority of the projected stellar disk should be filled with escaping material unbound from the planet, even at the time of mid-transit.
 In other words, only a small fraction of the \ion{He}{1} excess signal would be expected to trace the planet's motion, as opposed to the hypothetical in-transit signal for WASP-107~b that definitively traces out the planet's orbital path \citep{2022ApJ...926..226M}.
@@
 Whereas traditional Doppler Tomography treats the scanning reticle as an opaque planetary disk, here the reticle resembles a transmissive filter with a wavelength center and width that varies in space and time.
-We rank this effect as second-order and return to it in the Discussion Section \ref{vsini-interplay}.
+The interplay of spatial and spectral illumination and absorption can yield minor second-order effects, and overall we anticipate those effects to be secondary compared to the mere existence of absorbing material spanning the entire stellar disk.
 
@@
 Chiefly, numerical simulations \citep{2013ApJ...763...13W} and analytic theory \citep{2016ApJ...819..116G} indicate that Ohmic dissipation can stall the contraction of hot Jupiters, but cannot easily ``re-inflate'' them after having undergone a traditional cooling curve.
-Heat transfer from the atmosphere to a cooled core simply proceeds too slowly, on order of tens of Gyr \citep{2016ApJ...819..116G}.
-This path dependence to Ohmic dissipation would restrict the allowed evolutionary histories of \hatpb, to have arrived to its current location within a few to tens of Myr.
+Heat transfer from the atmosphere to a cooled core simply proceeds too slowly, on the order of tens of Gyr \citep{2016ApJ...819..116G}.
+This path dependence of Ohmic dissipation would restrict the allowed evolutionary histories of \hatpb, to have arrived at its current location within a few to tens of Myr.
 This short time window prefers a physical mechanism such as disk migration, which would be faster than secular eccentric migration with an outer companion.
 \emph{In-situ} formation of a hot Saturn at these close-in separations may be implausible \citep{2018ARA&A..56..175D}.
-Other caveats like unknowns in planetary magnetic fields, zonal band geometries, and dayside/nightside temperature differences make it impossible to uniqely prescribe Ohmic dissipation, and instead several additional factors may also be at play \citep{2021A&A...645A..79S}.
-
-\subsection{XUV Photoevaporation}
+Other caveats like unknowns in planetary magnetic fields, zonal band geometries, and dayside/nightside temperature differences make it impossible to uniquely prescribe Ohmic dissipation, and instead, several additional factors may also be at play \citep{2021A&A...645A..79S}.
+
+\subsection{XUV Irradiation-driven mass loss}
 XUV photoevaporation heats the upper layers in the atmosphere, driving a hydrodynamic wind \citep{2009ApJ...693...23M}.
@@
 
-The combined effects of photoevaporation, anomalous heating, and tidal gravity are predicted to have especially drastic outcomes for inflated hot Saturns \citep{2023ApJ...945L..36T} such as \hatp, where the low densities lead to large mass loss rates:
+The combined effects of photoevaporation, anomalous heating, and tidal gravity are predicted to have especially drastic outcomes for inflated hot Saturns \citep{2023ApJ...945L..36T} such as \hatpb, where the low densities lead to large mass loss rates:
 
@@
 
+\noindent where $K_t$ is the tidal gravity term, and $\eta \sim 0.4$ comes from \citet{2022A&A...663A.122C}.
 Assuming $\log{L_\mathrm{XUV}/L_\mathrm{bol}}=-4.2$, we would expect \hatpb~ to exhibit $\dot{M}\sim10^2$ M$_\oplus$/Gyr.
@@
 
-\citet{2017AJ....153..211Z} estimated that \hatpb~received about twice the incident flux as a Zero Age Main Sequence (ZAMS) \hatp, based on comparison to the Geneva isochrones.
+\citet{2017AJ....153..211Z} estimated that \hatpb~received about twice the incident flux as a Zero Age Main Sequence (ZAMS) HAT-P-67, based on comparison to the Geneva isochrones.
 In Section \ref{secMISTtracks} MIST evolutionary tracks showed two equally plausible states: the tail-end of the main sequence or a recently evolved sub-giant.
@@
 Perversely, the $\epsilon_G(T_\mathrm{eq})$ may tend to \emph{decrease} over time since the heating efficiency appears to peak at 2.5\% at 1600 K \citep{2018AJ....155..214T}, and reduce to about 1\% at 1900 K.
-So it's possible that the inflation timescale would remain relatively unchanged over the planet lifetime, despite a doubling of incident radiation.
+So inflation timescales may remain relatively unchanged over the planet lifetime, despite a doubling of incident radiation.
 
@@
 The conspicuous leading tail favors preferential mass loss on the highly irradiated planet dayside.
-While Ohmic dissipation would exhibit preferential dayside heating, it is the ability of XUV photons to create a planetary wind that tilts the balance.
-
-Finally we consider the prospect that the planetary mass is much lower than its 1-$\sigma$ bound, such that the white-light planetary radius \emph{is} the Hill radius (we have previously assumed the Hill radius is 2.7 planetary radii).
-This extreme scenario could manifest enormous mass loss rates, with the planet atmosphere's reservoir of mass fleeing the gravitational potential well directly, without the cushion of an exosphere.
-This terminal Roche Lobe overflow would have several observational predictions.
-Heavy elements woud easily leak into the planetary wind, yielding possibly many observable metal lines in the UV.
-These may be observable even under more mild conditions, due to lofting of metals into the upper atmosphere, so some care would be required to quantitatively distinguish these two scenarios.
+It is not clear to what extent Ohmic dissipation can imbue preferential dayside mass loss, and on balance, we attribute the observation of a large leading tail as supporting the XUV-irradiation-driven mass loss scenario.
+
+Finally, we consider the prospect that the planetary mass is much lower than the 1-$\sigma$ estimate, such that the white-light planetary radius \emph{is} the Hill radius (we have previously assumed the Hill radius is 2.7 planetary radii).
+This extreme scenario could manifest enormous mass loss rates, with the atmosphere's reservoir of mass fleeing the gravitational potential well directly, without the cushion of an exosphere.
+This terminal Roche Lobe overflow should have observational consequences.
+In particular, heavy elements would easily leak into the planetary wind, yielding possibly many observable metal lines in the UV.
+These may be observable even under mild conditions, due to the lofting of metals into the upper atmosphere, so some care would be required to quantitatively distinguish these two scenarios.
 
@@
 Helium non-detections are shown in red squares, atmospheric escape detections from any origin in green circles \citep{2022arXiv221116243D}.
-Under either scenario, \hatpb~ resides in a sparsely populated region with short inflationary timescale, making it unstable to runaway evaporation with large mass loss expected.
-Photoionization better predicts the depopulation of sources in the upper left low density region of the diagram, defined by the 0.1 g cm$^{-3}$ iso-density dashed white line.}
+Under either scenario, \hatpb~ resides in a sparsely populated region with a short inflationary timescale, making it unstable to runaway evaporation with large mass loss expected.
+Photoionization better predicts the depopulation of sources in the upper left low-density region of the diagram, defined by the 0.1 g cm$^{-3}$ iso-density dashed white line.}
     \label{fig:tf2018_theory}
@@
 The planet can interact with the star if the Alfv\'en speed exceeds the stellar wind speed controlling the bulk motion of the intervening medium.
-The non-detection of variability in the \ion{Ca}{2} H and K lines and H$\alpha$ lines appears to disfavor this SPMI interpretation, since SPMI could be expected to cause variations in these diagnostics.
+The non-detection of variability in the \ion{Ca}{2} H and K lines and H$\alpha$ lines appears to disfavor this SPMI interpretation since SPMI could be expected to cause variations in these diagnostics.
 
@@
 The TESS bandpass barely includes 10830 \AA, at a location of diminishing throughput, so it appears impractical that Helium alone could cause the TESS signal.
-Hypothetically, dust dedged up in the mass loss process could cause a large enough broadband flux loss to manifest in TESS.
+Hypothetically, dust dredged up in the mass loss process could cause a large enough broadband flux loss to manifest in TESS.
 We may expect to see some variable reddening in that case.
@@
 We estimate the detectable vertical extent must be at least a few stellar radii, such that we still could have detected Helium escape in a hypothetical HAT-P-67b-like system even if it were non-transiting, in a ``near miss'' configuration.
-We propose a new category of semi-transiting planet, dubbed ``exospheric grazers'', in which the planet does not produce a detectable white-light transit depth, but \emph{does} produce measureable \emph{line}-based exospheric absorption.
+We propose a new category of semi-transiting planet, dubbed ``exospheric grazers'', in which the planet does not produce a detectable white-light transit depth, but \emph{does} produce measurable \emph{line}-based exospheric absorption.
 This category appears to have been neglected due to the assumption that exospheres were only easily detectable at several planetary radii, and therefore fractions of a stellar radius.
@@
 
-The configuration would consist of a HAT-P-67b-like planet undergoing profound mass loss, with a jet-like column of material either spouting from the poles, or lofted there through gas dynamics, or otherwise confined by bow-shock redirection.
+The configuration would consist of a HAT-P-67b-like planet undergoing profound mass loss, with a jet-like column of material spouting from the poles, lofted there through gas dynamics, or otherwise confined by bow-shock redirection.
 A process for identifying strong candidates could select close-in planets or planet candidates discovered from non-transiting techniques, such as RVs or TTVs.
 The best candidates would be planets with $M\sin{i}$, orbital periods, and insolations consistent with a hot Saturn mass.
-A followup program could be devised to acquire in-transit spectroscopy to search for \ion{He}{1} 10830~\AA, or other spectral tracers of mass loss.
-
-A few benefits of of this planet category arise.
+A follow-up program could be devised to acquire in-transit spectroscopy to search for \ion{He}{1} 10830~\AA, or other spectral tracers of mass loss.
+
+A few benefits of this planet category arise.
 First, they would expand the sample of planets for which the planetary winds could be measured, by relaxing the narrow geometrical transit probability of $1-10^\circ$ to something closer to $\pm30^\circ$, depending on the mass loss and gas dynamics.
@@
 In practice these additional constraints are rarely possible, so ensemble statistical methods may have to be employed.
-Finally, for some promising planet candidates a distinctive helium signal could validate the planet, assuming the signal could be disambiguated from stellar variability.
-That disambiguation may be feasible, since the velocity structure and phasing of stellar and planetary Helium signals diverge due to stellar wind confinement and the launching from a predictable planetary rest frame.
+Finally, for some promising planet candidates, a distinctive helium signal could validate the planet, assuming the signal could be disambiguated from stellar variability.
+That disambiguation may be feasible since the velocity structure and phasing of stellar and planetary Helium signals diverge due to stellar wind confinement and the launching from a predictable planetary rest frame.
 The elusive category of young planets could make ideal targets, since their large radii and high intrinsic temperatures and high incident XUV radiation may yield large mass loss rates if they have recently migrated to an interior location through disk migration.

### 2023-05-22 paper/paper1/ms.tex
Start of post-CVM paper draft 0p5 edits

@@
 
-Atmospheric escape appears to be a compulsory phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5$-$2.0~$R_\oplus$ planets \citep{2017AJ....154..109F}.
-The leading candidate physical mechanisms for this rapid transition between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2013ApJ...776....2L,2017ApJ...847...29O} a=nd core-powered mass loss \citep{2019MNRAS.487...24G}.
+Atmospheric escape appears to be a compulsory phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5$-$2.0~$R_\oplus$ planets within 100 day periods \citep{2017AJ....154..109F}.
+The leading candidate physical mechanisms for this rapid transition between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2013ApJ...776....2L,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G}.
 Whatever the cause, some large fraction of planets must undergo transformative atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations such as transiting planets.

### 2023-05-22 paper/paper1/ms.tex
Add paragraph stating the layout of the paper at end of intro

@@
 \begin{document}
-\shorttitle{HPF spectral analysis}
+\shorttitle{Runaway Mass Loss in HAT-P-67b}
 \shortauthors{TBD}
@@
 These intrinsic or extrinsic factors may include proximity to the host star, low surface gravity, and high energy incident radiation.
-The small planet radius gap between 1.5$-$2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of eroding to their final rocky state.
-
-Inflated hot Saturns stand out as an especially extreme category that should exhibit mass loss.
-Their low gravitational potentials should let go of their atmospheres more readily than their steadfast Hot Jupiter counterparts.
+
+Inflated hot Saturns ($T_\mathrm{eq}>1000\;$K, $M_p \lesssim 0.3 M_\mathrm{Jup}$) stand out as an especially extreme category that should exhibit mass loss.
+Their low gravitational potentials should let go of their atmospheres more readily than their steadfast hot Jupiter counterparts.
 Their lower gravity yields larger atmospheric scale heights making them easier to detect in transmission spectroscopy.
-And their large transit depths and short periods should make them easy to detect in large numbers, like Hot Jupiters.
+And their large transit depths and short periods should make them easy to detect in large numbers, like hot Jupiters.
 
@@
 This heating leads to runaway inflation and ultimately complete disintegration.
-In this scenario, the inflationary half-life may be so short as to lead to a low probability of observing members in the class among the overall population, and hence the apparent lack of inflated sub-Saturns \citep{2023ApJ...945L..36T}.
+In this scenario, the inflationary half-life becomes so short that the probability of observing members in the class decreases sharply with density, causing the apparent lack of inflated sub-Saturns \citep{2023ApJ...945L..36T}.
 
@@
 Here, lightly thermally ionized atmospheric flows induce drag in a planetary magnetic field, weakly coupling the stellar incident energy into the planetary interior.
-\citet{2018AJ....155..214T} recognized the above two hypotheses for the lack of sub-Saturns, while statistically favoring Ohmic dissipation as the mechanism responsible for inflating Hot Jupiters.
+\citet{2018AJ....155..214T} recognized the above two hypotheses for the lack of sub-Saturns, while statistically favoring Ohmic dissipation as the mechanism responsible for inflating hot Jupiters.
 Therefore Ohmic dissipation stands out as a leading physical mechanism for inflation and mass loss.
@@
 
-\section{Observations}
+We assemble both archival, previously published, and new observations of the HAT-P-67 system, chronicled in Section \ref{secObs}.
+In Section \ref{secAnalysis} we refine the stellar and planet properties based on those observations, including distance, radius, and orbit re-analyses.
+The Helium excess detection is presented in \ref{secHeAnalysis}, with deep dives on the signal's trend with orbital phase.
+We use this orbital structure to reconstruct the geometry and mass loss of the escaping Helium exosphere, with both 1D and 3D models (Section \ref{secResults}).
+We assess the physical mechanisms (Section \ref{secPhysicalMechanisms}) giving rise to the escaping atmosphere, weighing the distinctive predictions of XUV irradation and Ohmic dissipation.
+Finally in Section \ref{secDiscuss}, we question the assumptions in our approach, discuss the overall congruence of predictions and observations, and highlight some implications for future exosphere studies.
+
+\section{Observations}\label{secObs}
 \subsection{Habitable Zone Planet Finder (HPF)}
@@
 
-\section{Analysis}
+\section{Analysis} \label{secAnalysis}
 
@@
 
-\subsection{HPF analysis I: RV fitting}
+\subsection{HPF analysis I: RV fitting}\label{secRVfit}
 
@@
 
-\subsection{HPF analysis II: \ion{He}{1} 10833 \AA}
+\subsection{HPF analysis II: \ion{He}{1} 10833 \AA} \label{secHeAnalysis}
 The preparation for analyzing the Helium feature followed a similar but slightly different procedure than that used for the RV, namely, we used \texttt{Goldilocks}\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}} for 2D echellogram reduction.
@@
 
-\section{Atmospheric Escape}
+\section{Atmospheric Escape}\label{secResults}
 
@@
 
-\section{Causal Interpretations} \label{secDiscuss}
+\section{Causal Interpretations} \label{secPhysicalMechanisms}
 
@@
 
-\subsection{3D Hydrodynamic simulations}
+\subsection{3D Hydrodynamic simulations}\label{sec3Dsimulations}
 \authorcomment1{Insert Morgan Macleod text here.}
@@
     \tablecaption{
-        Coarse Inflation Timescales for Hot Jupiters
+        Coarse Inflation Timescales for hot Jupiters
         \label{tabHeSM}
@@
 
-\section{Discussion}
+\section{Discussion}\label{secDiscuss}
 

### 2023-05-22 paper/paper1/ms.tex
More CVM text edits from draft markup

@@
 We obtain a range of $3.2 < P_\mathrm{rot}  < 4.8 $ days.
-This range may be typical for F stars that have not yet evolved too far into the sub-giant branch \citep{2022ApJ...930....7A}.
+This range is typical for F stars that have not yet evolved too far into the sub-giant branch \citep{2022ApJ...930....7A}.
 The geometrical constraint comports with the 4.7-day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9-day per-Sector fits, slightly preferring the lower 4.7-day modulation as the stellar rotation period.
@@
 Table \ref{tabOrbit} lists the revised properties, with minor differences from the existing values.
-Notably, our fit does not jointly model the Doppler tomographic signals reported in \citep{2017AJ....153..211Z}, which could further constrain the impact parameter.
-Additionally, our input $\rstar$ was slightly lower than the best-fit value derived from \emph{Gaia DR3} and SED fitting.
 \authorcomment1{Quang Tran: please verify and revise.}
@@
 This tool outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb \citep[LFC,][]{2019Optic...6..233M}.
-The observations were usually acquired with the LFC turned off, so this unilluminated spectrum was discarded.
+The observations were acquired with the LFC turned off, so this unilluminated spectrum was discarded.
 
@@
 As mentioned previously, the telluric masking near 10836 \AA~ censors our view of the existence (or not) of any redshifted lobe in this region.
-A more careful treatment of the telluric absorption could rescue some of the data in this region.
 The excess detections exhibit a bulk blueshift of up to 30~km/s.
@@
 Helium absorption occurs predominantly before the planet is in-transit, indicating a \emph{leading} tail escaping the planet.
-The excess occurs as early as 30\% of the orbital path.
-That large fraction of an orbit translates to about 0.1 AU, 130 planetary radii, and well outside of the Roche Lobe, with its Hill radius of merely 2.6 planetary radii.
+The leading tail is detected 0.1 AU away from the planet, or 130 planetary radii, well outside of the Roche Lobe at $<2.6$ planetary radii.
 We are detecting Roche lobe overflow, escaping material that is entirely unbound from the planet.
@@
 The large size of the gas stream overfills the transit chord, which means both the advancing blue side and receding red side of the rotating star are nearly continuously obscured in this spin-orbit-aligned system \citep{2017AJ....153..211Z}.
-The planet transits near the Stellar equator \citep{2017AJ....153..211Z}, meaning the transit chord covers about 10$\%$ of the projected stellar surface area.
+The planet transits near the stellar equator \citep{2017AJ....153..211Z}, meaning the transit chord covers about 10$\%$ of the projected stellar surface area.
 Hypothetically a nearly 100$\%$ opaque optically thick stream of gas covering only the transit chord could reproduce the observed 10$\%$ absorption excess.
@@
 \subsection{1D Parker wind models and mass loss rates}\label{pwinds}
-The dramatic leading tail of atmospheric escape suggests that more complicated 3D hydrodynamic simulations coupled with stellar wind \citep{2022ApJ...926..226M} may be needed to depict the geometry faithfully.
-Here we explore one-dimensional (1D) models, which offer ease of interpretation and rapid calculation.
+First we explore one-dimensional (1D) models, which offer ease of interpretation and rapid calculation.
 We employ the open-source \texttt{p-winds} code \citep{2022A&A...659A..62D}, which implements a transonic 1D Parker wind model with radiative transfer of the Helium 10830 triplet \citep{2018ApJ...855L..11O,2020A&A...636A..13L}.
@@
 The predicted Helium ionization depends sensitively on the XUV flux \citep{2019ApJ...881..133O}.
-Ideally, we would have a measurement of the XUV spectrum of \hatp, but the limited facilities and distance of the source preclude these challenging observations.
+Ideally, we would have a measurement of the XUV spectrum of HAT-P-67, but the limited facilities and distance of the source preclude these challenging observations.
 Instead, we constructed panchromatic X-ray to visible SEDs by scaling and stitching together synthetic spectra to provide a range of high and low $L_X/L_\mathrm{bol}$.
@@
 At least a few shortcomings limit the applicability of this 1D Parker wind model.
-First, the model-dependent line profile (\emph{i.e.
-width and depth}) is degenerate with XUV flux, $\dot{M}$, and $T_0$, and so a range of these parameters can be fine-tuned to obtain a large range of mass loss rates consistent with the data and our limited understanding of the XUV flux.
+First, the model-dependent line profile (\emph{i.e.} width and depth) is degenerate with XUV flux, $\dot{M}$, and $T_0$, and so a range of these parameters can be fine-tuned to obtain a large range of mass loss rates consistent with the data and our limited understanding of the XUV flux.
 These known degeneracies have been pointed out previously \citep{2022AJ....164..234V,2019ApJ...881..133O}, but the problem for \hatpb~ appears somewhat more acute since XUV data are scarce for F-type stars near the Kraft break.
@@
 
-\subsection{HAT-P-67 b analogues}
+\subsection{Other planets likely to be evaporating}
 

### 2023-05-24 paper/paper1/ms.tex
Delete Other Archives section

@@
 
-\subsection{Other archives}
-\authorcomment1{Slated for removal:}  
-\textcolor{lightgray}{\hatp has one $R\sim8000$ spectrum from the Intermediate Dispersion Spectrograph on the INT, centered near 4000 \AA.
-It has 26 photometry points from \emph{Pan-STARRS} spread across its 5 filters.
-The other archival observations have been previously reported by \citet{2017AJ....153..211Z}, including Keck HIRES, Keck NIRC2, and WIYN High-Resolution Infrared Camera.
-Overall the system appears relatively unstudied outside of the discovery paper.}
-
 \section{Analysis} \label{secAnalysis}

### 2023-05-24 paper/paper1/ms.tex
Remove Lightcurve modulation subsection

@@
 
-\subsubsection{Lightcurve modulation amplitude}
-\authorcomment1{Slated for removal:}
-\textcolor{lightgray}{We computed the peak-to-valley modulation for the 1000-source \emph{TESS} comparison sample, defined as the difference between the 90$^{th}$ to 10$^{th}$ percentile of each normalized \emph{TESS} lightcurve.
-Most lightcurves appear consistent with negligible astrophysical variability and/or variability predominated by instrumental artifacts.
-\object{HAT-P-67}'s 0.36$\%$ lightcurve modulation ranked in the 87$^{th}$ percentile of the ensemble, about 0.5$\times$ above the median.
-Sources more variable than HAT-P-67 exhibited 3-5$\times$ its amplitude of modulation.}
-
 \input{tables/revise_props_tbl.tex}

### 2023-05-24 paper/paper1/ms.tex
Figures revised per CVM guidance
Revising figures per CVM

@@
 \shorttitle{Runaway Mass Loss in HAT-P-67b}
-\shortauthors{TBD}
+\shortauthors{Gully-Santiago et al.}
 
@@
     \includegraphics[width=\linewidth]{figures/HAT_P_67b_He_spectrum.png}
-    \caption{Overlay of all 128 individual HPF exposures of HAT-P-67, spanning 2020-2022.
+    \caption{Overlay of all 152 individual HPF exposures of HAT-P-67, spanning 2020-2022.
 Variability is seen in the \ion{He}{1} 10833 \AA~ triplet, denoted by the vertical orange shaded band, but not in the adjacent regions.
@@
     \label{fig:HPFheliumOverview}
+\end{figure}
+
+Figure \ref{fig:HPFperCampaign} shows the spectra for four campaigns, with before and after spectra showing conspicuous excess absorption during transit and 1 day before transit, but negligible excess absorption after transit.
+The individual transits show significant morphological variation, with substructure in the bulk line-of-sight velocity distribution.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/HAT_P_67b_byCampaign_Spectra.png}
+    \caption{Four observing campaigns centered on an in-transit epoch with before-and-after visits typically separated by 1 night.
+The after-transit spectra tend to show negligible absorption.
+Line-of-sight velocity substructure can be seen in the before and during transit epochs.}
+    \label{fig:HPFperCampaign}
 \end{figure}
@@
     \centering
-    \subfloat{\includegraphics[width=5cm]{figures/centroid_overview10833.png} }
-    \hskip-3em
-    \subfloat{\includegraphics[width=4cm]{figures/centroid_inset10833.png}}
+    \includegraphics[width=\linewidth]{figures/centroid_overview10833.png}
+    %\hskip-3em
+    %\subfloat{\includegraphics[width=4cm]{figures/centroid_inset10833.png}}
     \caption{Line centroid positions of the  \ion{He}{1} 10830 \AA~ feature.
-\emph{left}: The overview panel shows a slight blueshift relative to the stellar restframe, and a weak excess blueshift trend after planet egress.
-\emph{right:} The detailed zoom-in of the in-transit phase shows a redshift relative to the planet restframe at ingress and a blueshift relative to the planet restframe near egress.
+A slight blueshift relative to the stellar restframe (vertical line) can be seen, with a weak excess blueshift trend after planet egress.
 The line-of-sight velocity distribution of 2-3 \AA~ means that the gas distribution exhibits both advancing and receding lobes at all phases other than post-egress.}

### 2023-05-25 paper/paper1/ms.tex
Decimate the exospheric grazers subsection

@@
 \begin{document}
-\shorttitle{Runaway Mass Loss in HAT-P-67b}
+\shorttitle{Runaway Mass Loss in the HAT-P-67 system}
 \shortauthors{Gully-Santiago et al.}
@@
 The spectrum was generated with a mass loss rate of $10^{13}$ g/s, exosphere gas temperature of 9100 K, and with an XUV luminosity $L_x/L_\mathrm{bol}=10^{-5}$ intermediate between those shown in Figure \ref{fig:XUV}.
-The lines have about the same equivalent width, while additional unmodeled velocity dispersion of the gas can explain differences between the line shapes of the model and data.
+The \texttt{p-winds} model yields the \ion{He}{1} 10830 triplet lines (colored dashed lines), with a cumulative feature in black possessing about the same equivalent width as the data, shown as the in-transit mean.
+Additional unmodeled velocity dispersion of the gas can explain differences between the line shapes of the model and data.
 Overall the 1D models may be too simplistic to represent the inherently 3D structure of the outflow.}
@@
 2023) and now HAT-P-67b suggest that the identification of these exospheric grazers may be achievable with current instrumentation and possibly existing archival data from near-IR RV-planet searches.
-
-The configuration would consist of a HAT-P-67b-like planet undergoing profound mass loss, with a jet-like column of material spouting from the poles, lofted there through gas dynamics, or otherwise confined by bow-shock redirection.
-A process for identifying strong candidates could select close-in planets or planet candidates discovered from non-transiting techniques, such as RVs or TTVs.
-The best candidates would be planets with $M\sin{i}$, orbital periods, and insolations consistent with a hot Saturn mass.
-A follow-up program could be devised to acquire in-transit spectroscopy to search for \ion{He}{1} 10830~\AA, or other spectral tracers of mass loss.
-
-A few benefits of this planet category arise.
-First, they would expand the sample of planets for which the planetary winds could be measured, by relaxing the narrow geometrical transit probability of $1-10^\circ$ to something closer to $\pm30^\circ$, depending on the mass loss and gas dynamics.
-In particular, the smallest stars such as white dwarfs and M-dwarfs could see the search space for exospheres increase by $10-100\times$.
-Second, the range of viewing angles would serve as a natural experiment for constraining the vertical extent of outflows in the first place.
-The typical bow shock 3D morphology could be deduced from a sample of otherwise-similar planets with a range of orbital inclinations.
-Non-detections would therefore be valuable, especially in cases where $\sin{i}$ could be constrained independently.
-In practice these additional constraints are rarely possible, so ensemble statistical methods may have to be employed.
-Finally, for some promising planet candidates, a distinctive helium signal could validate the planet, assuming the signal could be disambiguated from stellar variability.
-That disambiguation may be feasible since the velocity structure and phasing of stellar and planetary Helium signals diverge due to stellar wind confinement and the launching from a predictable planetary rest frame.
-The elusive category of young planets could make ideal targets, since their large radii and high intrinsic temperatures and high incident XUV radiation may yield large mass loss rates if they have recently migrated to an interior location through disk migration.
-This category is especially valuable if discovered through near-IR RV searches, since abundant multi-epoch spectroscopy may already contain the requisite stellar variability baselines.
+Non-transiting, strongly irradiated planets with well-constrained orbits may make ideal targets for detection of this phenomenon.
 

### 2023-05-25 paper/paper1/ms.tex
Describe revised two-panel plot per CVM guidance

@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
     \includegraphics[width=\linewidth]{figures/thorn2023_theory.png}
     \caption{Runaway inflation timescale in the exoplanet mass-radius diagram.
-The shading of the top panel shows $\tau_\mathrm{infl}$ from Ohmic dissipation, the bottom panel shows $\tau_\mathrm{infl}\equiv M/\dot{M}$ from photoionization-driven mass loss.
+The shading of the left panel shows $\tau_\mathrm{infl}$ from Ohmic dissipation, the right panel shows $\tau_\mathrm{infl}\equiv M/\dot{M}$ from photoionization-driven mass loss.
 Individual planets with confident mass and radius detections are shown as small black dots.
@@
     \label{fig:tf2018_theory}
-\end{figure}
+\end{figure*}
 

### 2023-06-05 paper/paper1/ms.tex
CVM rewrites the title! Much better.
Start of major re-arrangement of Sections 4 and 5, per CVM draft comments

@@
 
-\title{A large leading tail of atmospheric escape in the HAT-P-67 b system}
+\title{A large and variable leading tail of Helium in a sub-Saturn undergoing runaway inflation}
 
@@
 We use this orbital structure to reconstruct the geometry and mass loss of the escaping Helium exosphere, with both 1D and 3D models (Section \ref{secResults}).
-We assess the physical mechanisms (Section \ref{secPhysicalMechanisms}) giving rise to the escaping atmosphere, weighing the distinctive predictions of XUV irradation and Ohmic dissipation.
+We assess the physical mechanisms (Section \ref{secPhysMech}) giving rise to the escaping atmosphere, weighing the distinctive predictions of XUV irradation and Ohmic dissipation.
 Finally in Section \ref{secDiscuss}, we question the assumptions in our approach, discuss the overall congruence of predictions and observations, and highlight some implications for future exosphere studies.
@@
 
-\section{Causal Interpretations} \label{secPhysicalMechanisms}
-
 \subsection{Causes for the leading tail} \label{secLeading}
-Several physical phenomena could give rise to a leading tail geometry.  Here we explore the predominant two physical effects: orbital shear and stellar wind confinement.
+Several physical phenomena could give rise to a leading tail geometry.  Here we explore the predominant two dynamical effects: orbital shear and stellar wind confinement.
 
@@
 
-\subsection{Ohmic Dissipation and runaway escape}
-\object{HAT-P-67 b} exhibits both dramatic atmospheric escape and significant radius inflation.
-Ohmic dissipation stands out as a physical mechanism that could be responsible for both of these outstanding attributes.
-\citet{2011ApJ...738....1B} showed that Ohmic heating acts to inflate hot Jupiters, with planets $\lesssim 0.5 M_\mathrm{Jup}$ overflowing their Roche lobes and leading to evaporation on Gyr timescales.
-The Ohmic heating scenario requires only a modest planetary magnetic field ($\gtrsim$1 G) and an equilibrium temperature great enough to thermally ionize some modest fraction of neutral metals, such as the low ionization species of \ion{Na}{1} and \ion{K}{1}.
-The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K \citep{2011ApJ...738....1B,2012ApJ...745..138M,2016ApJ...819..116G,2018AJ....155..214T,2022A&A...658L...7K}, where the conductivity is strong enough to cause an effective drag without being so strong that magnetic braking slows the planetary wind.
-HAT-P-67 b's $\sim$2000 K sits to the higher end, but still in a region of high Ohmic dissipation heating efficiency.
-A proposed order-of-magnitude scaling law predicts an inflation timescale, Eq.
-20 in \citet{2011ApJ...738....1B}:
+\section{Mechanisms Driving Atmospheric Escape}\label{secPhysMech}
 
-\begin{equation}
-    \tau_{\textit{infl}}\sim \left(\frac{0.01}{\epsilon} \right) \left(\frac{M}{M_{J}}\right)^2 \left(\frac{R_{J}}{R}\right)^3 \left(\frac{1500 \textrm{K}}{T_\mathrm{eff}}\right)^4 \textrm{Gyr}.
-\label{eqInflate}
-\end{equation}
-
-\noindent yielding an incredibly short $<$5 Myr timescale for \hatpb, assuming a typical $\epsilon\sim0.01$.
-The order of magnitude of this inflation timescale is so fleetingly short that---according to this scenario---\hatpb~must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
-Under this interpretation, \hatpb~ would represent an example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic Dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
-At Roche lobe overflow, a 5 Myr inflation timescale may imply an instantaneous $\dot{M}_\mathrm{infl}>10^{3}$ M$_\oplus$/Gyr.
-
-A few caveats complicate the unambiguous causal interpretation of Ohmic dissipation.
-Chiefly, numerical simulations \citep{2013ApJ...763...13W} and analytic theory \citep{2016ApJ...819..116G} indicate that Ohmic dissipation can stall the contraction of hot Jupiters, but cannot easily ``re-inflate'' them after having undergone a traditional cooling curve.
-Heat transfer from the atmosphere to a cooled core simply proceeds too slowly, on the order of tens of Gyr \citep{2016ApJ...819..116G}.
-This path dependence of Ohmic dissipation would restrict the allowed evolutionary histories of \hatpb, to have arrived at its current location within a few to tens of Myr.
-This short time window prefers a physical mechanism such as disk migration, which would be faster than secular eccentric migration with an outer companion.
-\emph{In-situ} formation of a hot Saturn at these close-in separations may be implausible \citep{2018ARA&A..56..175D}.
-Other caveats like unknowns in planetary magnetic fields, zonal band geometries, and dayside/nightside temperature differences make it impossible to uniquely prescribe Ohmic dissipation, and instead, several additional factors may also be at play \citep{2021A&A...645A..79S}.
-
-\subsection{XUV Irradiation-driven mass loss}
+\subsection{XUV Irradiation-driven runaway}
 XUV photoevaporation heats the upper layers in the atmosphere, driving a hydrodynamic wind \citep{2009ApJ...693...23M}.
@@
 
-\subsection{Constraining mass loss rate}
-The theory-inspired mass loss rates above correspond to 1D Parker wind \ion{He}{1} feature depths and widths similar to what we observe, as evinced in Figure \ref{fig:pwinds}, with $\dot{M}_\mathrm{1D}\sim100$ M$_\oplus$/Gyr.
+\subsection{Ohmic Dissipation-driven runaway}
+Ohmic dissipation stands out as a physical mechanism that could be responsible for both dramatic atmospheric escape and its significant radius inflation.
+\citet{2011ApJ...738....1B} showed that Ohmic heating acts to inflate hot Jupiters, with planets $\lesssim 0.5 M_\mathrm{Jup}$ overflowing their Roche lobes and leading to evaporation on Gyr timescales.
+The Ohmic heating scenario requires only a modest planetary magnetic field ($\gtrsim$1 G) and an equilibrium temperature great enough to thermally ionize some modest fraction of neutral metals, such as the low ionization species of \ion{Na}{1} and \ion{K}{1}.
+The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K \citep{2011ApJ...738....1B,2012ApJ...745..138M,2016ApJ...819..116G,2018AJ....155..214T,2022A&A...658L...7K}, where the conductivity is strong enough to cause an effective drag without being so strong that magnetic braking slows the planetary wind.
+HAT-P-67 b's $\sim$2000 K sits to the higher end, but still in a region of high Ohmic dissipation heating efficiency.
+A proposed order-of-magnitude scaling law predicts an inflation timescale, Eq.
+20 in \citet{2011ApJ...738....1B}:
 
-First, the scaling law arguments that produced Equation \ref{eqInflate} were only proposed as order of magnitude estimates not to be taken too faithfully.
-So a $10\times$ higher inflation timescale of 50 Myr would yield $\dot{M}_\mathrm{infl}\sim10^{14}$ g/s, still a very large mass loss rate, but only a factor of 5 away from the baseline 1D model.
+\begin{equation}
+    \tau_{\textit{infl}}\sim \left(\frac{0.01}{\epsilon} \right) \left(\frac{M}{M_{J}}\right)^2 \left(\frac{R_{J}}{R}\right)^3 \left(\frac{1500 \textrm{K}}{T_\mathrm{eff}}\right)^4 \textrm{Gyr}.
+\label{eqInflate}
+\end{equation}
+
+\noindent yielding an incredibly short $<$5 Myr timescale for \hatpb, assuming a typical $\epsilon\sim0.01$.
+The order of magnitude of this inflation timescale is so fleetingly short that---according to this scenario---\hatpb~must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
+Under this interpretation, \hatpb~ would represent an example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic Dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
+At Roche lobe overflow, a 5 Myr inflation timescale may imply an instantaneous $\dot{M}_\mathrm{infl}>10^{3}$ M$_\oplus$/Gyr.
+
+A few caveats complicate the unambiguous causal interpretation of Ohmic dissipation.
+First, the scaling law arguments that produced Equation \ref{eqInflate} were only proposed as coarse scaling law estimates, with numerical simulations needed to quantify inflation timescales for individual systems.
+Accordingly, a $10\times$ higher inflation timescale of 50 Myr---allowed by the coarse scaling law---would yield $\dot{M}_\mathrm{infl}\sim10^{14}$ g/s, still a very large mass loss rate, and only a factor of 5 away from the baseline 1D model.
 Factors of a few uncertainties in the Ohmic dissipation efficiency $\epsilon$ may also contribute.
 
-As mentioned in Section \ref{pwinds}, inferring the mass loss rate from observations is strongly model dependent.
-The ionization fraction profile, exosphere temperature $T_0$, and $\dot{M}$ are all at least partially degenerate.
-In particular, the uncertain XUV-to-NUV flux ratio confounds the interpretation of the observed Helium signal.
-Even the ``high XUV'' scenario in Figure \ref{fig:XUV} does not have enough ground-state ionizing photons to penetrate to within 5 $R_p$ of the planet's surface, in a 1D Parker wind model.
-This means that at best only 1 in $10^{6}$ Helium atoms participate in the observability of the Helium metastable triplet lines in the baseline 1D Parker wind model.
-Turning down the XUV flux makes the signal even less observable.
-A larger mass loss rate would be needed to explain the same observed HPF Helium absorption, if say only 1 in $10^{7}$ helium atoms are populating the metastable state.
+Second, numerical simulations \citep{2013ApJ...763...13W} and analytic theory \citep{2016ApJ...819..116G} indicate that Ohmic dissipation can stall the contraction of hot Jupiters, but cannot easily ``re-inflate'' them after having undergone a traditional cooling curve.
+Heat transfer from the atmosphere to a cooled core appears to proceed too slowly, on the order of tens of Gyr \citep{2016ApJ...819..116G}.
+This path dependence of Ohmic dissipation would restrict the allowed evolutionary histories of \hatpb, to have arrived at its current location within a few to tens of Myr.
+This short time window prefers a physical mechanism such as disk migration, which would be faster than secular eccentric migration with an outer companion.
+\emph{In-situ} formation of a hot Saturn at these close-in separations may be implausible \citep{2018ARA&A..56..175D}.
+
+Other caveats like unknowns in planetary magnetic fields, zonal band geometries, and dayside/nightside temperature differences make it impossible to uniquely prescribe Ohmic dissipation, and instead, several additional factors may also be at play \citep{2021A&A...645A..79S}.
 

### 2023-06-05 paper/paper1/ms.tex
Revising text

@@
 \subsection{Ohmic Dissipation-driven runaway}
+The Ohmic dissipation mechanism made two key observable predictions.
+Heating efficiency should initially increase as a function of equilibrium temperature, then degrade as irradiation exceeds equilibrium temperatures of about 2000 K.
+Second, hot Saturns ($\lesssim0.5 M_\mathrm{Jup}$) should undergo runaway evaporation, whereas hot Jupiters ($\gtrsim 1 M_\mathrm{Jup}$) should reach stable equilibrium---albeit inflated---radii after Gyr timescales.
+Both of these outcomes predated data that could validate them, and these outcomes differ from the behavior of other heating mechanisms, such as photoevaporation or tides.
+
 Ohmic dissipation stands out as a physical mechanism that could be responsible for both dramatic atmospheric escape and its significant radius inflation.
@@
 
-\subsection{Evaporative annihilation as the cause of a lack of sub-Saturns}
-The Ohmic dissipation mechanism made two key observable predictions.
-Heating efficiency should initially increase as a function of equilibrium temperature, then degrade as irradiation exceeds equilibrium temperatures of about 2000 K.
-Second, hot Saturns ($\lesssim0.5 M_\mathrm{Jup}$) should undergo runaway evaporation, whereas hot Jupiters ($\gtrsim 1 M_\mathrm{Jup}$) should reach stable equilibrium---albeit inflated---radii after Gyr timescales.
-Both of these outcomes predated data that could adequately validate them, and these outcomes differ from the behavior of other heating mechanisms, such as photoevaporation or tides.
-When applied to an ensemble of planet systems, the Ohmic dissipation mechanism would expect a dearth of inflated hot Saturns.
+\subsection{Weighing the causes for a lack of sub-Saturns}
 
-\citet{2018AJ....155..214T} statistically favored Ohmic dissipation based on evidence for a turnover in the heating efficiency of hot Jupiters in a sample of 281 Giant planets.
-Furthermore, \citet{2018AJ....155..214T} also highlighted the lack of inflated sub-Saturns as an anomaly: by that time, the observational capability existed to detect such sources in large numbers and yet they were not found.
+When applied to an ensemble of planet systems, both the XUV irradiation and Ohmic dissipation mechanisms expect a void in the planet mass-radius plane.
+However, the theories make different quantitative predictions in the placement of the dividing lines between stable and unstable populations.
+We illustrate these differences in Figure \ref{fig:tf2018_theory}, which shades the mass-radius plane with predictions for the inflation timescale for planets with HAT-P-67b-like conditions.
+The XUV irradiation timescale better matches the distribution of planets, with the 0.1 $g\;cm^{-3}$ density contour setting a conspicuous dividing line in density.
+The Ohmic dissipation shading predicts short inflation timescales extending into a region of Jupiter-mass planets with radii commonly observed.
+The better match of observed exoplanet demographics to the XUV irradiation shading disfavors Ohmic dissipation.
 
-This dearth of hot Saturns has persisted into the \emph{TESS} era.
-Figure \ref{fig:ThornFortUpdated} highlights the region of highly irradiated close-in planets with $N>5000$ planets accessed through the NASA Exoplanet Archive.
-\hatpb~ occupies a relative void in this region.
+Under either scenario, HAT-P-67b resides in an extremely short-lifetime region.
+HAT-P-32b offers an interesting test case since it has recently been shown to exhibit a large helium excess \authorcomment1{cite ZJ}.
+It resides just slightly denser than the 0.1 $g\;cm^{-3}$ dividing line, with XUV predicting over 10$\times$ longer inflationary timescale for HAT-P-32b than for HAT-P-67b, while Ohmic dissipation expects merely a factor of 3 difference.
 
-The observation that \hatpb---the most inflated hot Saturn searched for atmospheric escape to date---exhibits mass loss indicative of a terminal fate leads us to a natural explanation for the dearth of inflated hot Saturns.
-The inflationary lifetime of hot Saturns is so short that observing planets of this class is unlikely.
-\hatpb~ appears to be one of the rare planets that we happen to catch a glimpse of before it has been annihilated.
-The lack of inflated hot Saturns is analogous to the small planet radius gap \citep{2017AJ....154..109F}, with Ohmic dissipation replacing core-powered mass loss as a heating mechanism, and with photoevaporation still at play.
-
-We, therefore, attribute this cliff in the $M_p$ vs $R_p$ diagram to either Ohmic dissipation, XUV photoevaporation, or both.
-\citet{2018AJ....155..214T} emphasized the positive feedback loop as a cause for the lack of sub-Saturns and noted an alternative interpretation-- mass-dependent migration segregation.
-While both scenarios are conceivable, the evidence of strong evaporation of \hatpb~ favors the evaporation scenario.
-Furthermore, the runaway evaporation of hot Saturns was naturally predicted by the Ohmic dissipation mechanism, whereas mass-dependent migration has only been developed as a post-diction.
-
-One key observation may tip the scales in favor of XUV photoevaporation as the predominant cause of mass-loss.
+One other key observation may tip the scales in favor of XUV irradiation.
 The conspicuous leading tail favors preferential mass loss on the highly irradiated planet dayside.
@@
 In particular, heavy elements would easily leak into the planetary wind, yielding possibly many observable metal lines in the UV.
-These may be observable even under mild conditions, due to the lofting of metals into the upper atmosphere, so some care would be required to quantitatively distinguish these two scenarios.
 

### 2023-06-05 paper/paper1/ms.tex
Comment-out the How We Constructed the Contours discussion, which was probably too wordy and pedantic

@@
 It resides just slightly denser than the 0.1 $g\;cm^{-3}$ dividing line, with XUV predicting over 10$\times$ longer inflationary timescale for HAT-P-32b than for HAT-P-67b, while Ohmic dissipation expects merely a factor of 3 difference.
+HAT-P-32b exhibits a more symmetric leading and trailing tail, whereas HAT-P-67b stands out as exhibiting evidence for preferential mass loss on the highly irradiated planet dayside.
+These differences may make this pair an especially valuable laboratory for discriminating among theories of atmospheric escape.
 
-One other key observation may tip the scales in favor of XUV irradiation.
-The conspicuous leading tail favors preferential mass loss on the highly irradiated planet dayside.
-It is not clear to what extent Ohmic dissipation can imbue preferential dayside mass loss, and on balance, we attribute the observation of a large leading tail as supporting the XUV-irradiation-driven mass loss scenario.
-
-Finally, we consider the prospect that the planetary mass is much lower than the 1-$\sigma$ estimate, such that the white-light planetary radius \emph{is} the Hill radius (we have previously assumed the Hill radius is 2.7 planetary radii).
+Finally, we consider the prospect that the planetary mass of HAT-P67b is much lower than the 1-$\sigma$ estimate, such that the white-light planetary radius \emph{is} the Hill radius (we have previously assumed the Hill radius is 2.7 planetary radii).
 This extreme scenario could manifest enormous mass loss rates, with the atmosphere's reservoir of mass fleeing the gravitational potential well directly, without the cushion of an exosphere.
@@
 
-As seen in Figure \ref{fig:ThornFortUpdated}, \hatpb~has few other known analogs.
-Figure \ref{fig:tf2018_theory} illustrates why: the inflationary lifetime for planets with comparable mass, radius, and $T_\mathrm{eq}$ is exceptionally short, and so they are rare.
-We constructed the $\tau_\mathrm{infl}$ contours in the following way.
+%We constructed the $\tau_\mathrm{infl}$ contours in the following way.
 We censored the $\tau_\mathrm{infl}$ to regions in the mass-radius plane where numerical simulations of Ohmic dissipation resulted in runaway inflation \citet{2011ApJ...738....1B}.

### 2023-06-05 paper/paper1/ms.tex
Fully remove the how we constructed OD contours paragraph
Add a paragraph on variability

@@
     \includegraphics[width=0.8\linewidth]{figures/homogeneous.png}
-    \caption{Isotropic mass loss}
+    \caption{3D hydrodynamic simulations of HAT-P-67b with isotropic mass loss.
+The upper image shows density along a slice in the orbital plane.
+The bottom two panels show trens in orbital phase, with (top) column density and (bottom) line-of-sight velocity.}
     \label{fig:IsotropicMdot}
@@
     \includegraphics[width=0.8\linewidth]{figures/asym.png}
-    \caption{Asymmetric dayside mass loss}
+    \caption{Same as \ref{fig:IsotropicMdot}, but with mass loss concentrated to the planet dayside.
+The substellar point exhibits the greatest mass loss, reducing to near zero at the planet terminator.
+A predominantly leading tail is produced.}
     \label{fig:DaysideMdot}
@@
 \subsection{3D Hydrodynamic simulations}\label{sec3Dsimulations}
+We explore the observational impact of dayside mass loss with 3D hydodynamic models.
+The mechanics follow previous such simulations on WASP 107~b \citep{2022ApJ...926..226M} and HAT-P-32~b (Zhang et al.
+2023).
+We modified the simulations to match the system properties of HAT-P-67~b.
+We ran two simulations: one in which the planetary boundary conditions are identical everywhere on the sphere of the planet (the homogeneous or isotropic case).
+In the
+other (asymmetric or anisotropic case) we let the temperature correspond to the incident irradiation through a $\cos(\theta)$ term where $\theta$ is the substellar angle.
+Figures \ref{fig:IsotropicMdot} and \ref{fig:DaysideMdot} compare these two scenarios.
+The dayside heating case clearly produces a large leading tail comparable to the scale observed in the Helium excess absorption.
 \authorcomment1{Insert Morgan Macleod text here.}
-\textcolor{lightgray}{Habitasse platea dictumst vestibulum rhoncus est pellentesque elit ullamcorper dignissim.
-Odio ut sem nulla pharetra.
-Odio ut sem nulla pharetra diam sit amet nisl suscipit.
-Accumsan tortor posuere ac ut.
-Ornare arcu dui vivamus arcu felis bibendum ut tristique.
-Nunc faucibus a pellentesque sit amet porttitor eget.
-Mauris rhoncus aenean vel elit.
-Sed vulputate mi sit amet mauris commodo.
-Quis lectus nulla at volutpat diam ut venenatis.
-Sed id semper risus in hendrerit gravida rutrum quisque non.
-Est placerat in egestas erat imperdiet sed.
-Viverra adipiscing at in tellus integer feugiat scelerisque varius.
-Quam viverra orci sagittis eu volutpat odio facilisis mauris sit.
-Morbi tristique senectus et netus et malesuada.
-Duis tristique sollicitudin nibh sit amet.
-Libero nunc consequat interdum varius sit amet mattis vulputate.
-Velit ut tortor pretium viverra suspendisse potenti nullam ac.
-Viverra accumsan in nisl nisi scelerisque eu ultrices vitae.
-Quis commodo odio aenean sed adipiscing diam donec.}
 
-The overall observation of a leading tail comports with either of these two physical mechanisms, and we suspect both are at play in \hatpb.
-Both cases appear needed to create the conditions of high enough column density to populate the \ion{He}{1} metastable triplet to detectable levels while imbuing the velocity substructure that we see.
-Here we interpret the bulk velocity substructure in Figure \ref{fig:centroids} under a combination of the two.
+Orbtial shear, stellar wind confinement, and preferential mass loss may all consipire to create the conditions of high enough column density to populate the \ion{He}{1} metastable triplet to detectable levels while imbuing the velocity substructure that we see.
+Here we interpret the bulk velocity substructure in Figure \ref{fig:centroids} under these gas dynamics mechanisms.
 We attribute the pre-transit arc to stellar wind acceleration.
@@
 
+\subsection{Variable planetary wind}
+Figure \ref{fig:centroids} and \ref{fig:HPFperCampaign} show differences in the Helium line profiles over months-long and years-long timescales.
+The line profiles are qualitatively similar, but show slightly different tendencies towards redshifting.
+For example, the centroid of the Helium line during the April 2022 transit appears slightly blueshifted relative to the stellar rest frame.
+In comparison, the May 2020 transit probes the same planetary phases, yet resides slightly redshifted at transit midcenter.
+We interpret this line profile variability as indicative of genuine planetary wind variability, which can arise from the interplay of stellar and planetary winds \citep{2009ApJ...693...23M} and weather-like feedbacks in the planetary upper atmosphere.
+
 \section{Mechanisms Driving Atmospheric Escape}\label{secPhysMech}
 
-\subsection{XUV Irradiation-driven runaway}
+\subsection{XUV Irradiation-driven mass loss}
 XUV photoevaporation heats the upper layers in the atmosphere, driving a hydrodynamic wind \citep{2009ApJ...693...23M}.
@@
 
-\subsection{Ohmic Dissipation-driven runaway}
+\subsection{Ohmic Dissipation-driven mass loss}
 The Ohmic dissipation mechanism made two key observable predictions.
@@
 
-Ohmic dissipation stands out as a physical mechanism that could be responsible for both dramatic atmospheric escape and its significant radius inflation.
+Ohmic dissipation may therefore be responsible for both dramatic atmospheric escape and significant radius inflation.
 \citet{2011ApJ...738....1B} showed that Ohmic heating acts to inflate hot Jupiters, with planets $\lesssim 0.5 M_\mathrm{Jup}$ overflowing their Roche lobes and leading to evaporation on Gyr timescales.
@@
 When applied to an ensemble of planet systems, both the XUV irradiation and Ohmic dissipation mechanisms expect a void in the planet mass-radius plane.
-However, the theories make different quantitative predictions in the placement of the dividing lines between stable and unstable populations.
-We illustrate these differences in Figure \ref{fig:tf2018_theory}, which shades the mass-radius plane with predictions for the inflation timescale for planets with HAT-P-67b-like conditions.
+However, the theories make different quantitative predictions for the placement of the dividing lines between stable and unstable populations.
+We illustrate these differences in Figure \ref{fig:tf2018_theory}, which shades the mass-radius plane with predictions for the inflation timescale under HAT-P-67b-like conditions.
 The XUV irradiation timescale better matches the distribution of planets, with the 0.1 $g\;cm^{-3}$ density contour setting a conspicuous dividing line in density.
@@
 Under either scenario, HAT-P-67b resides in an extremely short-lifetime region.
-HAT-P-32b offers an interesting test case since it has recently been shown to exhibit a large helium excess \authorcomment1{cite ZJ}.
+Its nearest analog, HAT-P-32b, offers an interesting test case since it has recently been shown to exhibit a large helium excess \authorcomment1{cite ZJ}.
 It resides just slightly denser than the 0.1 $g\;cm^{-3}$ dividing line, with XUV predicting over 10$\times$ longer inflationary timescale for HAT-P-32b than for HAT-P-67b, while Ohmic dissipation expects merely a factor of 3 difference.
 HAT-P-32b exhibits a more symmetric leading and trailing tail, whereas HAT-P-67b stands out as exhibiting evidence for preferential mass loss on the highly irradiated planet dayside.
-These differences may make this pair an especially valuable laboratory for discriminating among theories of atmospheric escape.
+These differences may make this pair an especially valuable laboratory for developing theories of atmospheric escape.
 
@@
 \end{figure*}
-
-%We constructed the $\tau_\mathrm{infl}$ contours in the following way.
-We censored the $\tau_\mathrm{infl}$ to regions in the mass-radius plane where numerical simulations of Ohmic dissipation resulted in runaway inflation \citet{2011ApJ...738....1B}.
-We interpolate the $T_\mathrm{eq}$ trendlines from Fig.
-\ref{fig:ThornFortUpdated} to compute $\tau_\mathrm{infl}$ from Equation \ref{eqInflate}, including the best fit Gaussian prescription for $\hat{\epsilon}_G$ from Eq.
-34 of \citet{2018AJ....155..214T}.
-This trend should exhibit significant uncertainty owing to the order-of-magnitude nature of the scaling relation, source-to-source scatter in $\hat{\epsilon}_G$, and to what extent $\hat{\epsilon}_G$ applies for planets less than $0.5 M_\mathrm{Jup}$, which were excluded in the derivation of $\hat{\epsilon}_G$ owing to their scarcity.
-Nevertheless, this contour appears to match the bulk trends: planets tend to reside in either the non-inflationary, stable locus or the inflationary-yet-stable locus.
-A relatively few $\sim$dozens of planets approach the ``cosmic shoreline'' of inflationary lifetimes in the tens of Myr.
-The detection of atmospheric escape along this frontier (green circles in Figure \ref{fig:tf2018_theory}) supports this interpretation.
-More observations and theoretical modeling of atmospheric escape along this ridge could help better understand its realized versus expected shape.
 
@@
 We propose a new category of semi-transiting planet, dubbed ``exospheric grazers'', in which the planet does not produce a detectable white-light transit depth, but \emph{does} produce measurable \emph{line}-based exospheric absorption.
-This category appears to have been neglected due to the assumption that exospheres were only easily detectable at several planetary radii, and therefore fractions of a stellar radius.
+This category appears to have been neglected due to the assumption that exospheres were only easily detectable at several planetary radii.
 While large tails have been seen previously in Ly$\alpha$, the scarcity of UV resources prohibited searches of this kind.
@@
     \includegraphics[width=0.5\linewidth]{figures/Ca8662_phase_2D_diagram_resid.png}
-    \caption{Non-detection of variability in the Calcium IR Triplet line at 8862 $\AA$.  No other HPF lines appear to show any variability.}
+    \caption{Non-detection of variability in the Calcium IR Triplet line at 8862 \AA.  No other HPF lines appear to show any variability.}
     \label{fig:CaPhaseScan}

### 2023-06-05 paper/paper1/ms.tex
3D hydro section is a placeholder
Add an abstract

@@
 \begin{abstract}
-    To be overhauled...
+    Atmospheric escape and its associated mass loss shape the fate of exoplanets, with statistical evidence for photoevaporation imprinted across the mass-radius-insolation distribution.
+The Habitable Zone Planet Finder (HPF) Spectrograph Exospheres program aims to expand the search across a diverse range of planet and host star properties via the 10830 Ångstrom Helium triplet, a sensitive probe of active atmospheric escape.
+Here we present a detection of 10\% absorption depth during transit spectroscopy of the highly irradiated, low-gravity, inflated hot Saturn HAT-P-67b.
+The 13.8 hours of on-sky integration time over 41 HET tracks provides enough out-of-transit phase coverage as to reveal comparably deep absorption preceding the transit, evincing a large leading tail.
+This configuration can be understood as the escaping material overflowing its small Roche lobe, and advecting most of the gas into the stellar—and not planetary---rest frame, consistent with the Doppler velocity structure seen in the Helium line profiles.
+We, therefore, attribute the leading tail to a combination of Keplerian shear and stellar wind confinement, with preferential mass loss from dayside heating.
+We see some transit-to-transit variability in the line profile, consistent with the interplay of stellar and planetary wind.
+We employ 1D Parker wind models and 3D hydrodynamic models to estimate the mass loss rate, finding values on the order of $>10^{13}$ g/s, with large uncertainties owing to the unknown XUV flux of the F host star.
+The large mass loss in HAT-P-67b represents a rare example of an inflated hot Saturn, a class of planets predicted by Thorngren and Fortney (2018) to have been statistically depopulated through runaway inflation.
+We explore two physical mechanisms for runaway evaporation: Ohmic Dissipation and XUV irradiation, slightly favoring the latter.
 \end{abstract}
@@
 The dayside heating case clearly produces a large leading tail comparable to the scale observed in the Helium excess absorption.
-\authorcomment1{Insert Morgan Macleod text here.}
+\authorcomment1{The above paragraph is a placeholder stub slated for revision from Morgan.}
 

### 2023-06-05 paper/paper1/ms.tex
Add a conclusion

@@
 
+We have presented a multi-year spectroscopic survey of HAT-P-67~b, a low density, heavily irradiated Saturn-mass (or lower) planet.
+We identified a large leading tail, with a much weaker trailing tail, which we found to be consistent with preferential dayside mass loss.
+HAT-P-67~b stands out as an outlier in the mass-radius plane, which we examine through the lens of different mechanisms for anomalous heating.
+Both XUV irradiation and Ohmic dissipation predict runaway inflation for such inflated hot Saturns, and we quantitatively weigh these two scenarios, finding XUV irrdation as more straightforwardly predictive of the overall demographic population of exoplanets observed to date.
+
+We report in-transit line profile variability, which we attribute to the delicate interplay of planetary and stellar winds.
+We identify several avenues for future work, including additional monitoring of the line profile variability to probe the stellar-and-planetary wind interaction.
+The large signal should be perceptible in other spectral tracers, such as metal lines in the UV.
+We offer a list other planets that may be likely to exhibit mass loss under the Ohmic Dissipation and XUV irradiation scenarios.
+
 \clearpage

### 2023-06-21 paper/paper1/ms.tex
Version 0.6 of paper destined for OVERLEAF.
Direct edits from Overleaf, including GS, and MM

@@
 
+% This is the version destined for Overleaf on June 7th, 2023.
 \title{A large and variable leading tail of Helium in a sub-Saturn undergoing runaway inflation}
@@
 A runaway inflation scenario predicts an inevitable and profound mass loss rate for inflated hot Saturns.
-As the planet's atmosphere overflows its Roche lobe at an ever-increasing pace instantaneous mass loss rates may exceed $\dot{M}>10^{13}$ g/s, over 10$\times$ larger than those previously seen in atmospheric escape measurements to date \citep{2022arXiv221116243D}.
+As the planet's atmosphere overflows its Roche lobe at an ever-increasing pace, instantaneous mass loss rates may exceed $\dot{M}>10^{13}$ g/s, over 10$\times$ larger than those previously seen in atmospheric escape measurements to date \citep{2022arXiv221116243D}.
 Inflated hot Saturns, therefore, make excellent targets for direct measurement of atmospheric escape.
@@
 In particular, metastable Helium's ability to be observed at high spectral resolution from the ground has been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.
-\ion{He}{1} has resulted in at least 14 systems with detections, including \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
+\ion{He}{1} has resulted in at least 14 systems with detections, including \object[GJ 3470]{GJ 3470 b} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
 An observational picture of mass loss in hot Saturns appears to be lacking, at least in part due to their intrinsic rarity.
@@
 Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
-Its $\sim$0.05 g~cm$^{-3}$ density places it firmly below the 0.1 g~cm$^{-3}$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.
+Its $\sim$0.05 g~cm$^{-3}$ density places it below the 0.1 g~cm$^{-3}$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.
 Figures \ref{fig:instellation} and \ref{fig:ThornFortUpdated} show how much of an outlier \hatpb~ is: large, low mass, and heavily irradiated.
 
-The evolutionary state of \hatp offers even more intriguing possibilities.
-The host star may be an evolved subgiant, opening the prospect for planetary ``re-inflation'' \citep{2022AJ....163...53S,2022AJ....163..120G,2023arXiv230306728G} as the planet's insolation increased with the star's rapid luminosity increase in this part of the short-lived HR diagram.
-The tidal gravity of the nearby massive host star may amplify mass loss rates even further \citep{2007A&A...472..329E,2023ApJ...945L..36T}.
-Its status as a rare inflated Hot Saturn makes \object{HAT-P-67 b} a promising laboratory, uniquely suited for testing the runaway inflationary predictions of Ohmic dissipation and XUV photoevaporation.
+The evolutionary state of HAT-P-67~b offers even more intriguing possibilities.
+The host star may be an evolved subgiant, opening the prospect for planetary re-inflation \citep{2022AJ....163...53S, 2022AJ....163..120G, 2023arXiv230306728G} as the planet's insolation increased with the star's rapid luminosity increase in this part of the short-lived HR diagram.
+The tidal gravity of the nearby massive host star may amplify mass loss rates even further \citep{2007A&A...472..329E, 2023ApJ...945L..36T}.
+Its status as a rare inflated Hot Saturn makes HAT-P-67~b a promising laboratory, uniquely suited for testing the runaway inflationary predictions of Ohmic dissipation and XUV photoevaporation.
 
 We assemble both archival, previously published, and new observations of the HAT-P-67 system, chronicled in Section \ref{secObs}.
-In Section \ref{secAnalysis} we refine the stellar and planet properties based on those observations, including distance, radius, and orbit re-analyses.
-The Helium excess detection is presented in \ref{secHeAnalysis}, with deep dives on the signal's trend with orbital phase.
+In Section \ref{secAnalysis}, we refine the stellar and planet properties based on those observations, including distance, radius, and orbit re-analyses.
+The Helium excess detection is presented in Section \ref{secHeAnalysis}, with deep dives on the signal's trend with orbital phase.
 We use this orbital structure to reconstruct the geometry and mass loss of the escaping Helium exosphere, with both 1D and 3D models (Section \ref{secResults}).
@@
 The in-transit campaigns had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.
-We also obtained random-in-phase low-priority ``P4'' queue-filler observations \citep{2007PASP..119..556S}.
+We also obtained random-in-phase lower-priority P1-4 reconnaissance observations \citep{2007PASP..119..556S}.
 These out-of-transit snapshot observations typically received 4 or fewer individual exposures.
@@
 Previously, \hatpb~transits had only been detected with \emph{HATNet} \citep{2004PASP..116..266B} and followed up with KeplerCam on the FLWO 1.2 m telescope \citep{2017AJ....153..211Z}.
-These ground-based photometers were not intended to measure long-term stellar variability signals.
+These ground-based photometers were not intended to measure weak, long-term stellar variability signals.
 We, therefore, examined the \emph{TESS} lightcurves for out-of-transit photometric variability.
-The revised precision and continuous coverage of \emph{TESS} can refine the orbital solution.
+The revised precision and continuous coverage of \emph{TESS} can also refine the orbital solution.
 
@@
 Here we included the new TESS lightcurves and the existing Keck HIRES points reported in Table 3 of \citet{2017AJ....153..211Z}.
-The HPF points exhibited an RV jitter of $\sim164\;\kms$, a few times larger than the typical Keck HIRES measurements.
+The HPF points exhibited an RV jitter of $\sim164\;\ms$, a few times larger than the typical Keck HIRES measurements.
 So even though the HPF points were more numerous, their marginal value for RV orbit determination was subdued owing to the lower RV information content in the near-IR for this relatively rapidly rotating F star.
@@
 The pre-transit phases ($-0.3$ to $+0.03$) show a slight tendency towards blueshift relative to stellar restframe, with an accelerating blueshift from phases $-0.3$ to $-0.15$, albeit with some visit-to-visit scatter.
-The post-transit observations ($+0.03$ to $+0.015$) exhibit weak-albeit-significant equivalent widths, as denoted by their smaller marker size.
+The post-transit observations ($+0.03$ to $+0.15$) exhibit weak-albeit-significant equivalent widths, as denoted by their smaller marker size.
 The centroids dramatically accelerate to larger bulk blueshifts, as low as 10831 \AA.
 
-The densely sampled in-transit phases are shown as a zoomed-in, oversized inset.
-Here we can see the planetary rest frame as the dotted line cutting across the panel.
-At the moment of planet ingress, the centroids exhibit a redshifted absorption relative to the planet restframe.
+At the moment of transit midcenter, the centroids exhibit a redshifted absorption relative to the planet restframe.
 Measurements from April 2022 and May 2020 transits partially overlap in phase coverage while yielding slightly different line centroid locations.
-Both visits appear consistent with near-zero restframe velocity.
-The May 2020 visit shows a slight trend towards alignment with the planet restframe.
+Both time series sequences appear consistent with near-zero bulk restframe velocity, but with significant variability in the line profile substructure.
+The May 2020 sequence shows a slight trend towards alignment with the planet restframe.
 The April 2020 and June 2020 partial transits sampled phases close to planet egress, with a clear blueshift relative to both the star and planet.
@@
 So there remains significant uncertainty about the applicability of the \object[tau Boo]{$\tau$ Boo} XUV spectrum to HAT-P-67.
-We scaled the synthetic SED of \object[tau Boo]{$\tau$ Boo} retrieved from X-exoplanets \citep{2011A&A...532A...6S} so that the integral of ground-state ionizing photons ($\lambda<504\AA$) exhibited $L_X/L_\mathrm{bol} \in [10^{-6}, 10^{-4}]$.
+We scaled the synthetic SED of \object[tau Boo]{$\tau$ Boo} retrieved from X-exoplanets \citep{2011A&A...532A...6S} so that the integral of ground-state ionizing photons ($\lambda<504\;$\AA) exhibited $L_X/L_\mathrm{bol} \in [10^{-6}, 10^{-4}]$.
 Figure \ref{fig:XUV} shows two conceivable SEDs with these high and low radiation hardnesses.
@@
 Equipped with these two SEDs of differing radiation hardness, we explored different mass loss rates and exosphere temperatures.
-Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 10^{13}$ g/s, and $T_0=9100$~K, with an XUV spectrum possessing $L_x/L_\mathrm{bol}=10^{-5}$.
+Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 2\times 10^{13}$ g/s, and $T_0=14000$~K, with an XUV spectrum possessing $L_x/L_\mathrm{bol}=10^{-5}$.
 This mass loss rate would imply a characteristic lifetime of $\sim$2000 Myr.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/pwinds_data_overlay.png}
+    \includegraphics[width=\linewidth]{figures/pwinds_May2020_14000_2e13Mdot_medXUV_formal_rv copy.png}
     \caption{Simulated 1D Parker wind model of Helium absorption in \hatpb.
-The spectrum was generated with a mass loss rate of $10^{13}$ g/s, exosphere gas temperature of 9100 K, and with an XUV luminosity $L_x/L_\mathrm{bol}=10^{-5}$ intermediate between those shown in Figure \ref{fig:XUV}.
-The \texttt{p-winds} model yields the \ion{He}{1} 10830 triplet lines (colored dashed lines), with a cumulative feature in black possessing about the same equivalent width as the data, shown as the in-transit mean.
-Additional unmodeled velocity dispersion of the gas can explain differences between the line shapes of the model and data.
+The spectrum was generated with a mass loss rate of $2\times10^{13}$ g/s, exosphere gas temperature of 14000 K, and with an XUV luminosity $L_x/L_\mathrm{bol}=10^{-5}$ intermediate between those shown in Figure \ref{fig:XUV}.
+The \texttt{p-winds} model yields the \ion{He}{1} 10830 triplet lines (colored dashed lines), with a cumulative feature in black resembling the data, shown as the May 2020 in-transit mean.
+Additional 3D velocity dispersion of the gas can explain differences between the line shapes of the model and data.
 Overall the 1D models may be too simplistic to represent the inherently 3D structure of the outflow.}
@@
 
-Orbtial shear, stellar wind confinement, and preferential mass loss may all consipire to create the conditions of high enough column density to populate the \ion{He}{1} metastable triplet to detectable levels while imbuing the velocity substructure that we see.
+Orbtial shear, stellar wind confinement, and preferential mass loss may all conspire to create the conditions of high enough column density to populate the \ion{He}{1} metastable triplet to detectable levels while imbuing the velocity substructure that we see.
 Here we interpret the bulk velocity substructure in Figure \ref{fig:centroids} under these gas dynamics mechanisms.
@@
 \end{equation}
-
-\noindent where $K_t$ is the tidal gravity term, and $\eta \sim 0.4$ comes from \citet{2022A&A...663A.122C}.
+ where $K_t$ is the tidal gravity term, and $\eta \sim 0.4$ comes from \citet{2022A&A...663A.122C}.
 Assuming $\log{L_\mathrm{XUV}/L_\mathrm{bol}}=-4.2$, we would expect \hatpb~ to exhibit $\dot{M}\sim10^2$ M$_\oplus$/Gyr.
@@
 Broadly, the planet would have started with an initial mass up to 50$\%$ greater than at present, with $R\sim\;$1.4 $R_\mathrm{Jup}$, for an initial density of $\sim$0.2 g/cm$^-3$.
-It would lose mass at a rate of tens of Earth masses per Gyr for its 1 Gyr lifetime, expanding modestly until it reaches the critical $\sim$0.1 g/cm$^-3$ threshold, at which point the mass loss rate increases to its current value.
-Having lost a significant portion of its mass, its orbit expands to conserve angular momentum.
+It would lose mass at a rate of tens of Earth masses per Gyr for its 1 Gyr lifetime, expanding modestly until it reaches the critical $\sim$0.1 g/cm$^{-3}$ threshold, at which point the mass loss rate increases to its current value.
 It will last only tens of Myr in its current state before losing almost all of its envelope and settling as a $5-15$ M$_\oplus$ core with a final radius of 0.2$-$0.3 R$_\mathrm{Jup}$.
@@
 The Ohmic dissipation mechanism made two key observable predictions.
-Heating efficiency should initially increase as a function of equilibrium temperature, then degrade as irradiation exceeds equilibrium temperatures of about 2000 K.
+Anomalous heating efficiency, $\epsilon$, should initially increase as a function of equilibrium temperature, then degrade as irradiation exceeds equilibrium temperatures of about 2000 K.
 Second, hot Saturns ($\lesssim0.5 M_\mathrm{Jup}$) should undergo runaway evaporation, whereas hot Jupiters ($\gtrsim 1 M_\mathrm{Jup}$) should reach stable equilibrium---albeit inflated---radii after Gyr timescales.
@@
 A few caveats complicate the unambiguous causal interpretation of Ohmic dissipation.
-First, the scaling law arguments that produced Equation \ref{eqInflate} were only proposed as coarse scaling law estimates, with numerical simulations needed to quantify inflation timescales for individual systems.
+First, the scaling law arguments that produced Equation \ref{eqInflate} were only proposed as coarse estimates, with numerical simulations needed to quantify inflation timescales for individual systems.
 Accordingly, a $10\times$ higher inflation timescale of 50 Myr---allowed by the coarse scaling law---would yield $\dot{M}_\mathrm{infl}\sim10^{14}$ g/s, still a very large mass loss rate, and only a factor of 5 away from the baseline 1D model.
@@
 In Section \ref{secMISTtracks} MIST evolutionary tracks showed two equally plausible states: the tail-end of the main sequence or a recently evolved sub-giant.
-Figure \ref{fig:OhmicInflate} employs these tracks to assess the re-inflationary impact of \hatpb~could be, assuming that the orbital location has not changed over the system lifetime.
-The second panel from the top illustrates a countervailing effect: the decrease in Ohmic dissipation heating efficiency, $\epsilon$, could counteract the increase of stellar flux, assuming the functional form for $\hat{\epsilon}_G$ described by \citet{2018AJ....155..214T}.
-Together the effects nearly cancel when computing the inflationary lifetimes, yielding nearly identical curves in the bottom panel.
+Figure \ref{fig:OhmicInflate} employs these tracks to quantify the prospects for re-inflation  of \hatpb.
+
+We further assume that the orbital location has not changed over the system lifetime, that the planet's response to anomalous heating stimulus is instantaneous, and that the anomalous heating efficiency $\hat{\epsilon}_G$ peaks at $T_\mathrm{eq}=1750$ K as derived by \citet{2018AJ....155..214T}.
+
+We conclude that reinflation likely does not have a significant effect on the evolution of HAT-P-67~b: inflation timescales remain relatively unchanged over the planet lifetime, despite a 50\% spike in incident radiation in the sub-giant scenario.
+The reason is subtle, as we describe next.
+
+The second panel from the top illustrates a countervailing effect: the increase in flux actually triggers a decrease in anomalous heating efficiency, $\epsilon$.
+The greater stellar energy couples into the planet less effectively than the weaker radiation did, roughly balancing out.
+Together the effects nearly cancel when computing the inflationary lifetimes, yielding nearly identical curves in the bottom panel: a secularly evolving main sequence history gives almost the same inflation timescale as a rapidly increasing subgiant.
+It is important to emphasize that the anomalous heating efficiency found by \citet{2018AJ....155..214T} is agnostic to what the actual heating mechanism is: either XUV Irradiation or Ohmic Dissipation both have to obey the trend of $\hat{\epsilon}_G(T_\mathrm{eq})$.
+
 The third panel recreates the numerically computed curve for $0.5\;M_\mathrm{Jup}$, $T_\mathrm{eq}=$1800 K from \citep{2011ApJ...738....1B}, which should be considered as representative since it was not necessarily tailored to the evolutionary history of \hatpb.
-Nevertheless, the similarity of the curve is remarkable since it arrives at approximately the correct planet radius at the right age.
-The modeled mass is slightly higher than, but consistent with the RV-measured mass, and would imply a large and increasing mass loss rate over its lifetime.
+Nevertheless, the similarity of the curve is remarkable since it arrives at approximately the correct planet radius at the right age for about the right initial mass.
 
@@
 \end{figure}
-
-A doubling of insolation would place the young \hatpb~at a 20\% lower equilibrium temperature of 1600 K.
-Perversely, the $\epsilon_G(T_\mathrm{eq})$ may tend to \emph{decrease} over time since the heating efficiency appears to peak at 2.5\% at 1600 K \citep{2018AJ....155..214T}, and reduce to about 1\% at 1900 K.
-So inflation timescales may remain relatively unchanged over the planet lifetime, despite a doubling of incident radiation.
 
@@
 
-\begin{deluxetable}{lLLCR}
+\begin{deluxetable*}{lLLCRR}
     \tablewidth{0pc}
-    \tabletypesize{\scriptsize}
     \tablecaption{
@@
     \tablehead{
+        \colhead{ }   &
+        \colhead{ } &
+        \colhead{ }   &
+        \colhead{ } &
+        \colhead{(OD)} & 
+        \colhead{(XUV)} \\
         \colhead{Planet}   &
@@
         \colhead{$T_\mathrm{eq}$} &
+        \colhead{$\tau_\mathrm{infl}$} &
         \colhead{$\tau_\mathrm{infl}$} \\
@@
         \colhead{K} &
+        \colhead{Myr} & 
         \colhead{Myr}
@@
     \enddata
-    %\tablecomments{Inflation timescale assumes $\epsilon=0.01$.}  Not true, we use the empirical estimate
-\end{deluxetable}
+    \tablecomments{XUV Inflation timescale assumes $L_X/L_\mathrm{bol}=6.3\times10^{-4}$ (Equation 5 of Sanz-Forcada et al.
+2011), which is an overestimate for HAT-P-67 and old/slowly-rotating host stars.}
+\end{deluxetable*}
 
@@
 
+    GS acknowledges support provided by NASA through the NASA Hubble Fellowship grant HST-HF2-51519.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
+
     This paper includes data collected with the TESS mission, obtained from the MAST data archive at the Space Telescope Science Institute (STScI).

### 2023-06-21 paper/paper1/ms.tex
claridying comment from GS in abstract

@@
 We employ 1D Parker wind models and 3D hydrodynamic models to estimate the mass loss rate, finding values on the order of $>10^{13}$ g/s, with large uncertainties owing to the unknown XUV flux of the F host star.
-The large mass loss in HAT-P-67b represents a rare example of an inflated hot Saturn, a class of planets predicted by Thorngren and Fortney (2018) to have been statistically depopulated through runaway inflation.
+The large mass loss in HAT-P-67b represents a rare example of an inflated hot Saturn, a class of planets recently identified to be rare as their atmospheres are predicted to evaporate quickly.
 We explore two physical mechanisms for runaway evaporation: Ohmic Dissipation and XUV irradiation, slightly favoring the latter.

### 2023-06-21 paper/paper1/ms.tex
Confirm consistency of figure and Temperature label, flagged by Morgan

@@
 The cause for their underabundance remains an open question, with two leading candidate explanations.
-Tidal migration mechanisms may be mass-dependent in such a way as to proceed efficiently for Jupiter-mass planets, but inefficiently for the lower-mass Saturns.
+Tidal migration mechanisms may be mass-dependent in such a way as to proceed efficiently for Jupiter-mass planets, but inefficiently for the lower-mass Saturns \citep{2018AJ....155..214T,2018ARA&A..56..175D}.
 In this scenario, sub-Saturn mass planets never make it to the close-in orbital separations that would lead to the conditions needed for inflation in the first place.
@@
 Equipped with these two SEDs of differing radiation hardness, we explored different mass loss rates and exosphere temperatures.
-Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 2\times 10^{13}$ g/s, and $T_0=14000$~K, with an XUV spectrum possessing $L_x/L_\mathrm{bol}=10^{-5}$.
-This mass loss rate would imply a characteristic lifetime of $\sim$2000 Myr.
+Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 2\times 10^{13}$ g/s, and $T_0=14\,000$~K, with an XUV spectrum possessing $L_x/L_\mathrm{bol}=10^{-5}$.
+This mass loss rate would imply a characteristic lifetime of $\sim$1000 Myr.
 The model spectrum exhibits approximately the same equivalent width as our HPF observations, making it a hypothetical scenario among a family of partially degnerate solutions.
@@
     \caption{Simulated 1D Parker wind model of Helium absorption in \hatpb.
-The spectrum was generated with a mass loss rate of $2\times10^{13}$ g/s, exosphere gas temperature of 14000 K, and with an XUV luminosity $L_x/L_\mathrm{bol}=10^{-5}$ intermediate between those shown in Figure \ref{fig:XUV}.
+The spectrum was generated with a mass loss rate of $2\times10^{13}$ g/s, exosphere gas temperature of $14\,000\;$K, and with an XUV luminosity $L_x/L_\mathrm{bol}=10^{-5}$ intermediate between those shown in Figure \ref{fig:XUV}.
 The \texttt{p-winds} model yields the \ion{He}{1} 10830 triplet lines (colored dashed lines), with a cumulative feature in black resembling the data, shown as the May 2020 in-transit mean.

### 2023-06-22 paper/paper1/ms.tex
Remove the 3D Hydrodynamic modeling in favor of Res ipsa loquitur argument

@@
 
-\subsection{Causes for the leading tail} \label{secLeading}
-Several physical phenomena could give rise to a leading tail geometry.  Here we explore the predominant two dynamical effects: orbital shear and stellar wind confinement.
+\subsection{Physical mechanisms guiding the leading tail} \label{secLeading}
+Several physical phenomena control the geometry and extent of the escaping material.
+Here we explore the three predominant dynamical effects: orbital shear, stellar wind confinement, and day-/night- side mass loss asymmetries.
 
@@
 Stellar wind confinement \citep{2022ApJ...926..226M} arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.
-A trailing tail may also be present, but would not undergo the same boost in density, and would be rapidly carried away alongside the stellar wind.
-This asymmetry could yield the appearance of a leading tail even if mass loss proceeds isotropically, or the asymmetry could be reinforced by an additional dayside/nightside asymmetry.
+A trailing tail may also be present, but may not undergo the same boost in density, and could be rapidly carried away alongside the stellar wind.
+Hypothetically, a stellar-wind-induced asymmetry could result, yielding the appearance of a leading or trailing tail even if mass loss proceeds isotropically at first.
 Examples of this asymmetry can be seen in 3D MHD modeling of WASP 107~b \citep{2022ApJ...926..226M}.
 
-\subsection{3D Hydrodynamic simulations}\label{sec3Dsimulations}
-We explore the observational impact of dayside mass loss with 3D hydodynamic models.
-The mechanics follow previous such simulations on WASP 107~b \citep{2022ApJ...926..226M} and HAT-P-32~b (Zhang et al.
-2023).
-We modified the simulations to match the system properties of HAT-P-67~b.
-We ran two simulations: one in which the planetary boundary conditions are identical everywhere on the sphere of the planet (the homogeneous or isotropic case).
-In the
-other (asymmetric or anisotropic case) we let the temperature correspond to the incident irradiation through a $\cos(\theta)$ term where $\theta$ is the substellar angle.
-Figures \ref{fig:IsotropicMdot} and \ref{fig:DaysideMdot} compare these two scenarios.
-The dayside heating case clearly produces a large leading tail comparable to the scale observed in the Helium excess absorption.
-\authorcomment1{The above paragraph is a placeholder stub slated for revision from Morgan.}
-
-Orbtial shear, stellar wind confinement, and preferential mass loss may all conspire to create the conditions of high enough column density to populate the \ion{He}{1} metastable triplet to detectable levels while imbuing the velocity substructure that we see.
+\subsection{Direct Evidence for Day-/Night- side mass loss asymmetry}\label{secPrimaFacie}
+Oribtal shear, stellar wind confinement, and preferential dayside mass loss may all conspire to create the conditions of high enough column density to populate the \ion{He}{1} metastable triplet to detectable levels while imbuing the velocity substructure that we see.
 Here we interpret the bulk velocity substructure in Figure \ref{fig:centroids} under these gas dynamics mechanisms.
@@
 The ``sweet spot'' for this phenomenon appears to prefer equilibrium temperatures in the range of $1500<T_\mathrm{eq}<2000$ K \citep{2011ApJ...738....1B,2012ApJ...745..138M,2016ApJ...819..116G,2018AJ....155..214T,2022A&A...658L...7K}, where the conductivity is strong enough to cause an effective drag without being so strong that magnetic braking slows the planetary wind.
-HAT-P-67 b's $\sim$2000 K sits to the higher end, but still in a region of high Ohmic dissipation heating efficiency.
+HAT-P-67~b's $\sim$2000 K sits to the higher end, but still in a region of high Ohmic dissipation heating efficiency.
 A proposed order-of-magnitude scaling law predicts an inflation timescale, Eq.

### 2023-06-26 paper/paper1/ms.tex
Removal of the 3D content

@@
 This configuration can be understood as the escaping material overflowing its small Roche lobe, and advecting most of the gas into the stellar—and not planetary---rest frame, consistent with the Doppler velocity structure seen in the Helium line profiles.
-We, therefore, attribute the leading tail to a combination of Keplerian shear and stellar wind confinement, with preferential mass loss from dayside heating.
+The prominent leading tail serves as direct evidence for dayside mass loss with a strong day-/night- side asymmetry.
+A combination of Keplerian shear and stellar wind confinement control the extent and optical depth of the tail.
 We see some transit-to-transit variability in the line profile, consistent with the interplay of stellar and planetary wind.
-We employ 1D Parker wind models and 3D hydrodynamic models to estimate the mass loss rate, finding values on the order of $>10^{13}$ g/s, with large uncertainties owing to the unknown XUV flux of the F host star.
-The large mass loss in HAT-P-67b represents a rare example of an inflated hot Saturn, a class of planets recently identified to be rare as their atmospheres are predicted to evaporate quickly.
+We employ 1D Parker wind models to estimate the mass loss rate, finding values on the order of $2\times10^{13}$ g/s, with large uncertainties owing to the unknown XUV flux of the F host star.
+The large mass loss in HAT-P-67~b represents a valuable example of an inflated hot Saturn, a class of planets recently identified to be rare as their atmospheres are predicted to evaporate quickly.
 We explore two physical mechanisms for runaway evaporation: Ohmic Dissipation and XUV irradiation, slightly favoring the latter.
@@
 The Helium excess detection is presented in Section \ref{secHeAnalysis}, with deep dives on the signal's trend with orbital phase.
-We use this orbital structure to reconstruct the geometry and mass loss of the escaping Helium exosphere, with both 1D and 3D models (Section \ref{secResults}).
+We use this orbital structure to reconstruct the geometry and mass loss of the escaping Helium exosphere, with 1D Parker wind models (Section \ref{secResults}).
 We assess the physical mechanisms (Section \ref{secPhysMech}) giving rise to the escaping atmosphere, weighing the distinctive predictions of XUV irradation and Ohmic dissipation.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/pwinds_May2020_14000_2e13Mdot_medXUV_formal_rv copy.png}
+    \includegraphics[width=\linewidth]{figures/pwinds_May2020_14000_2e13Mdot_medXUV_formal_rv.png}
     \caption{Simulated 1D Parker wind model of Helium absorption in \hatpb.
@@
 
-\begin{figure}
-    \includegraphics[width=0.8\linewidth]{figures/homogeneous.png}
-    \caption{3D hydrodynamic simulations of HAT-P-67b with isotropic mass loss.
-The upper image shows density along a slice in the orbital plane.
-The bottom two panels show trens in orbital phase, with (top) column density and (bottom) line-of-sight velocity.}
-    \label{fig:IsotropicMdot}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=0.8\linewidth]{figures/asym.png}
-    \caption{Same as \ref{fig:IsotropicMdot}, but with mass loss concentrated to the planet dayside.
-The substellar point exhibits the greatest mass loss, reducing to near zero at the planet terminator.
-A predominantly leading tail is produced.}
-    \label{fig:DaysideMdot}
-\end{figure}
-
 Stellar wind confinement \citep{2022ApJ...926..226M} arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.
 A trailing tail may also be present, but may not undergo the same boost in density, and could be rapidly carried away alongside the stellar wind.
-Hypothetically, a stellar-wind-induced asymmetry could result, yielding the appearance of a leading or trailing tail even if mass loss proceeds isotropically at first.
+A stellar-wind-induced asymmetry could result, yielding the appearance of a leading or trailing tail even if mass loss proceeds isotropically at first.
 Examples of this asymmetry can be seen in 3D MHD modeling of WASP 107~b \citep{2022ApJ...926..226M}.
@@
 \subsection{Direct Evidence for Day-/Night- side mass loss asymmetry}\label{secPrimaFacie}
-Oribtal shear, stellar wind confinement, and preferential dayside mass loss may all conspire to create the conditions of high enough column density to populate the \ion{He}{1} metastable triplet to detectable levels while imbuing the velocity substructure that we see.
-Here we interpret the bulk velocity substructure in Figure \ref{fig:centroids} under these gas dynamics mechanisms.
-We attribute the pre-transit arc to stellar wind acceleration.
+The observation of such a prominent leading tail leads us to the inescapable conclusion that HAT-P-67~b is predominantly losing mass on the dayside.
+An isotropic mass loss would manifest a comparably conspicuous trailing tail, which we do not observe.
+Stellar wind confinement alone should be expected to produce minor asymmetries such as those seen in the modeling of WASP 107~b \citep{2022ApJ...926..226M}, but in order to obtain the vastly dominant leading tail, an enhancing systematic effect is needed.
+The schematic illustration in Figure \ref{fig:KeplerianShear} depicts this interplay.
+
+Importantly, orbital shear, stellar wind confinement, preferential dayside mass loss, and radiative transfer must all conspire to create the conditions of high enough column density to populate the \ion{He}{1} metastable triplet to detectable levels while imbuing the velocity substructure that we see.
+The detailed 3D modeling of the interplay of these effects is beyond the scope of the current work, but is feasible with adaptations to existing 3D simulations.
+
+Here we interpret the bulk velocity substructure in Figure \ref{fig:centroids} under these conceptual gas dynamics mechanisms.
+We attribute the mild pre-transit arc to stellar wind acceleration.
 The stellar wind is initially too weak to plow the dense escaping gas until a separation of 60-130 planetary radii ($+0.15$ orbital phase), the inflection point in an enormous bow shock.

### 2023-06-26 paper/paper1/ms.tex
Start of addressing Brendan Bowler Comments Issue #29
Page 1-2

@@
 % This is the version destined for Overleaf on June 7th, 2023.
-\title{A large and variable leading tail of Helium in a sub-Saturn undergoing runaway inflation}
+\title{A Large and Variable Leading Tail of Helium in a Sub-Saturn Undergoing Runaway Inflation}
 
@@
     Atmospheric escape and its associated mass loss shape the fate of exoplanets, with statistical evidence for photoevaporation imprinted across the mass-radius-insolation distribution.
-The Habitable Zone Planet Finder (HPF) Spectrograph Exospheres program aims to expand the search across a diverse range of planet and host star properties via the 10830 Ångstrom Helium triplet, a sensitive probe of active atmospheric escape.
+The Habitable Zone Planet Finder (HPF) Spectrograph Exospheres program aims to expand the search across a diverse range of planet and host star properties via the 10830 \AA~ Helium triplet, a sensitive probe of active atmospheric escape.
 Here we present a detection of 10\% absorption depth during transit spectroscopy of the highly irradiated, low-gravity, inflated hot Saturn HAT-P-67b.
-The 13.8 hours of on-sky integration time over 41 HET tracks provides enough out-of-transit phase coverage as to reveal comparably deep absorption preceding the transit, evincing a large leading tail.
+The 13.8 hours of on-sky integration time over 39 nights provides enough out-of-transit phase coverage as to reveal comparably deep absorption preceding the transit, revealing a large leading tail.
 This configuration can be understood as the escaping material overflowing its small Roche lobe, and advecting most of the gas into the stellar—and not planetary---rest frame, consistent with the Doppler velocity structure seen in the Helium line profiles.
@@
 
-Uncertainty in system ages, evaporation timescales, and dominating physical mechanisms, degrade our ability to foretell if any given planet will exhibit ongoing signatures of atmospheric escape.
-Episodic stellar wind gusts and other forms of astrophysical variance could also subdue the appearance of atmospheric escape, even where we expect it most.
+Uncertainty in system ages, evaporation timescales, and dominating physical mechanisms degrade our ability to foretell if any given planet will exhibit ongoing signatures of atmospheric escape.
+Episodic stellar wind gusts and other forms of astrophysical variability could also subdue the appearance of atmospheric escape, even where we expect it most.
 The 48 published non-detections of atmospheric escape \citep{2022arXiv221116243D} must encode these natural whims in a way that we have not yet disentangled.
@@
 
-Inflated hot Saturns ($T_\mathrm{eq}>1000\;$K, $M_p \lesssim 0.3 M_\mathrm{Jup}$) stand out as an especially extreme category that should exhibit mass loss.
+Inflated hot Saturns stand out as an especially extreme category that should exhibit mass loss.
+This category is defined as having masses at or somewhat less than Saturn's ($M_p \lesssim 0.3 M_\mathrm{Jup}$), with equilibrium temperatures high enough to cause radius inflation($T_\mathrm{eq}>1000\;$K).
 Their low gravitational potentials should let go of their atmospheres more readily than their steadfast hot Jupiter counterparts.
-Their lower gravity yields larger atmospheric scale heights making them easier to detect in transmission spectroscopy.
-And their large transit depths and short periods should make them easy to detect in large numbers, like hot Jupiters.
+Their lower gravity yields larger atmospheric scale heights, making them easier to detect in transmission spectroscopy.
+And their large transit depths and short periods should make them readily detectable in large numbers, like hot Jupiters.
 

### 2023-06-26 paper/paper1/ms.tex
Page 2 reference additions

@@
 The large mass loss in HAT-P-67~b represents a valuable example of an inflated hot Saturn, a class of planets recently identified to be rare as their atmospheres are predicted to evaporate quickly.
-We explore two physical mechanisms for runaway evaporation: Ohmic Dissipation and XUV irradiation, slightly favoring the latter.
+We explore two physical mechanisms for runaway evaporation: Ohmic dissipation and XUV irradiation, slightly favoring the latter.
 \end{abstract}
@@
 Inflated hot Saturns stand out as an especially extreme category that should exhibit mass loss.
-This category is defined as having masses at or somewhat less than Saturn's ($M_p \lesssim 0.3 M_\mathrm{Jup}$), with equilibrium temperatures high enough to cause radius inflation($T_\mathrm{eq}>1000\;$K).
+This category is defined as having masses comparable to Saturn's ($M_p \sim 0.3 M_\mathrm{Jup}$), with equilibrium temperatures high enough to expect radius inflation($T_\mathrm{eq}>1000\;$K).
 Their low gravitational potentials should let go of their atmospheres more readily than their steadfast hot Jupiter counterparts.
@@
 But inflated hot Saturns are rare \citep{2018AJ....155..214T}.
-The cause for their underabundance remains an open question, with two leading candidate explanations.
-Tidal migration mechanisms may be mass-dependent in such a way as to proceed efficiently for Jupiter-mass planets, but inefficiently for the lower-mass Saturns \citep{2018AJ....155..214T,2018ARA&A..56..175D}.
+The cause for their underabundance remains an open question, with at least two conceivable explanations.
+Tidal migration mechanisms---either high-eccentricity or disk-based---could hypothetically proceed in a mass-dependent manner, efficiently for Jupiter-mass planets, but inefficiently for the lower-mass Saturns \citep{2018AJ....155..214T,2018ARA&A..56..175D}.
 In this scenario, sub-Saturn mass planets never make it to the close-in orbital separations that would lead to the conditions needed for inflation in the first place.
@@
 As the planet's atmosphere overflows its Roche lobe at an ever-increasing pace, instantaneous mass loss rates may exceed $\dot{M}>10^{13}$ g/s, over 10$\times$ larger than those previously seen in atmospheric escape measurements to date \citep{2022arXiv221116243D}.
-Inflated hot Saturns, therefore, make excellent targets for direct measurement of atmospheric escape.
+Inflated hot Saturns, therefore, make excellent targets for direct measurement of atmospheric escape and to test the underlying mechanisms of mass loss.
 
@@
 The ability to detect even immense mass loss hinges on its observability in spectral tracers.
-Ly$\alpha$, \ion{He}{1} 10833 \AA, and H$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2022arXiv221116243D,2023MNRAS.518.4357O}, but each of these has its own observational limitations.
+Ly$\alpha$, \ion{He}{1} 10833 \AA, and H$\alpha$ have emerged as the most amenable to detection \citep{2000ApJ...537..916S,2003Natur.422..143V,2012ApJ...751...86J,2018NatAs...2..714Y,2018ApJ...855L..11O,2018Natur.557...68S, 2022arXiv221116243D,2023MNRAS.518.4357O}, but each of these has its own observational limitations.
 Ly$\alpha$ can suffer from interstellar medium \ion{H}{1} absorption censoring its low-velocity line core, for example.
@@
 
-\subsection{Ohmic Dissipation-driven mass loss}
+\subsection{Ohmic dissipation-driven mass loss}
 The Ohmic dissipation mechanism made two key observable predictions.
@@
 The order of magnitude of this inflation timescale is so fleetingly short that---according to this scenario---\hatpb~must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
-Under this interpretation, \hatpb~ would represent an example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic Dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
+Under this interpretation, \hatpb~ would represent an example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
 At Roche lobe overflow, a 5 Myr inflation timescale may imply an instantaneous $\dot{M}_\mathrm{infl}>10^{3}$ M$_\oplus$/Gyr.
@@
 Together the effects nearly cancel when computing the inflationary lifetimes, yielding nearly identical curves in the bottom panel: a secularly evolving main sequence history gives almost the same inflation timescale as a rapidly increasing subgiant.
-It is important to emphasize that the anomalous heating efficiency found by \citet{2018AJ....155..214T} is agnostic to what the actual heating mechanism is: either XUV Irradiation or Ohmic Dissipation both have to obey the trend of $\hat{\epsilon}_G(T_\mathrm{eq})$.
+It is important to emphasize that the anomalous heating efficiency found by \citet{2018AJ....155..214T} is agnostic to what the actual heating mechanism is: either XUV Irradiation or Ohmic dissipation both have to obey the trend of $\hat{\epsilon}_G(T_\mathrm{eq})$.
 
@@
 The large signal should be perceptible in other spectral tracers, such as metal lines in the UV.
-We offer a list other planets that may be likely to exhibit mass loss under the Ohmic Dissipation and XUV irradiation scenarios.
+We offer a list other planets that may be likely to exhibit mass loss under the Ohmic dissipation and XUV irradiation scenarios.
 

### 2023-06-26 paper/paper1/ms.tex
Up to page 6 now

@@
 \ion{He}{1} has resulted in at least 14 systems with detections, including \object[GJ 3470]{GJ 3470 b} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
-An observational picture of mass loss in hot Saturns appears to be lacking, at least in part due to their intrinsic rarity.
+The sample of detections includes both hot Jupiters and lower mass planets, but lacks inflated hot Saturns owing to their intrinsic rarity below the 0.1 g~cm$^{-3}$ threshold.
+An observational picture of mass loss in inflated hot Saturns appears to be lacking for this reason.
 
@@
 
-Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, an inflated hot Saturn orbiting an F type sub-giant at an orbital separation of 0.06 AU and a 4.8-day orbital period \citep{2017AJ....153..211Z}.
-Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
+Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, a transiting inflated hot Saturn orbiting an F5 sub giant at an orbital separation of 0.06 AU and a 4.8-day orbital period \citep{2017AJ....153..211Z}.
+Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity ($\log{g_p}<2.3$, cgs) makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
 Its $\sim$0.05 g~cm$^{-3}$ density places it below the 0.1 g~cm$^{-3}$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.
@@
 The evolutionary state of HAT-P-67~b offers even more intriguing possibilities.
-The host star may be an evolved subgiant, opening the prospect for planetary re-inflation \citep{2022AJ....163...53S, 2022AJ....163..120G, 2023arXiv230306728G} as the planet's insolation increased with the star's rapid luminosity increase in this part of the short-lived HR diagram.
-The tidal gravity of the nearby massive host star may amplify mass loss rates even further \citep{2007A&A...472..329E, 2023ApJ...945L..36T}.
-Its status as a rare inflated Hot Saturn makes HAT-P-67~b a promising laboratory, uniquely suited for testing the runaway inflationary predictions of Ohmic dissipation and XUV photoevaporation.
+The planet may have undergone re-inflation \citep{2022AJ....163...53S, 2022AJ....163..120G, 2023arXiv230306728G}, as the host star evolved through the subgiant phase-- with the planet's insolation increasing with the star's rapid luminosity increase in this part of the short-lived HR diagram.
+The tidal gravity of the nearby massive ($M_\star \sim1.6\;M_\odot$) host star may amplify mass loss rates even further \citep{2007A&A...472..329E, 2023ApJ...945L..36T}.
+Its status as a rare inflated hot Saturn makes HAT-P-67~b a promising laboratory, uniquely suited for testing the runaway inflationary predictions of Ohmic dissipation and XUV photoevaporation.
 
@@
 In Section \ref{secAnalysis}, we refine the stellar and planet properties based on those observations, including distance, radius, and orbit re-analyses.
-The Helium excess detection is presented in Section \ref{secHeAnalysis}, with deep dives on the signal's trend with orbital phase.
+The Helium excess detection is presented in Section \ref{secHeAnalysis}, with analysis of the signal's trend with orbital phase.
 We use this orbital structure to reconstruct the geometry and mass loss of the escaping Helium exosphere, with 1D Parker wind models (Section \ref{secResults}).
@@
 HAT-P-67A (\emph{Gaia DR3 1358614983131339392}) has a parallax of $2.69\pm0.01$ mas in \emph{Gaia} DR3, placing it at about 372$\pm$1.4 pc.
-Minor corrections to the parallax uncertainty \citep{2021MNRAS.506.2269E} and bias \citep{2021A&A...649A...4L} appear negligible for the $G=9.98$ source.
+Minor corrections to the parallax uncertainty \citep{2021MNRAS.506.2269E} and bias \citep{2021A&A...649A...4L} appear negligible for the $G=9.98$ mag source.
 The DR3 parallax places the system about 8.7\% farther than previously estimated by \citet{2017AJ....153..211Z}, which adopted a \emph{Gaia} DR1-informed parallax of $2.92\pm0.23$ mas, including a systematic $-0.325$ mas bias term \citep{2016ApJ...831L...6S}.
@@
 
-We can constrain the expected stellar rotation period based on the stellar radius estimate, $v\sin{i}$, and the observation of $i\sim90^\circ$ from orbit fitting and Doppler tomography \citep{2017AJ....153..211Z}.
+We can constrain the expected stellar rotation period based on the stellar radius estimate, $v\sin{i_\star}$, and the observation of the planet's orbital inclination $i_p\sim90^\circ$ from orbit fitting and Doppler tomography \citep{2017AJ....153..211Z}.
+We assume spin-orbit alignment, $i_\star \sim i_p$.
 We adopt a high limit of $v\sin{i}=35.8\pm1.1$ km/s and a lower $v\sin{i}=30.9\pm2$ km/s value if macroturbulence is accounted for.
 We obtain a range of $3.2 < P_\mathrm{rot}  < 4.8 $ days.
-This range is typical for F stars that have not yet evolved too far into the sub-giant branch \citep{2022ApJ...930....7A}.
+This range is typical for F stars that have not yet evolved too far into the sub giant branch \citep{2022ApJ...930....7A}.
 The geometrical constraint comports with the 4.7-day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9-day per-Sector fits, slightly preferring the lower 4.7-day modulation as the stellar rotation period.
@@
 
-We conclude that reinflation likely does not have a significant effect on the evolution of HAT-P-67~b: inflation timescales remain relatively unchanged over the planet lifetime, despite a 50\% spike in incident radiation in the sub-giant scenario.
+We conclude that reinflation likely does not have a significant effect on the evolution of HAT-P-67~b: inflation timescales remain relatively unchanged over the planet lifetime, despite a 50\% spike in incident radiation in the sub giant scenario.
 The reason is subtle, as we describe next.

### 2023-06-26 paper/paper1/ms.tex
onto page 7

@@
 The slightly increased distance and radius imply an 18\% more luminous host star than previously estimated.
-Figure \ref{fig:evolTracks} shows evolutionary tracks using the solar-metallicity MESA \citep{2011ApJS..192....3P,2013ApJS..208....4P,2015ApJS..220...15P} Isochrones and Stellar Tracks \citep[MIST;][]{2016ApJS..222....8D,2016ApJ...823..102C} for HAT-P-67.
+Figure \ref{fig:evolTracks} shows evolutionary tracks using the solar-metallicity MESA \citep{2011ApJS..192....3P,2013ApJS..208....4P,2015ApJS..220...15P} Isochrones and Stellar Tracks \citep[MIST;][]{2016ApJS..222....8D,2016ApJ...823..102C} for HAT-P-67, which has [Fe/H]$=-0.08\pm0.05$ \citep{2017AJ....153..211Z}.
 The tracks show that a 1.8 Gyr, 1.64 $M_\odot$ \hatp~ could be at the end of its main sequence lifetime (teal track), yielding a gradual rise in incident radiation over the lifetime of \hatpb.
@@
 Either evolutionary track appears consistent with the observed SED, stellar surface gravity, and available constraints from spectral fitting.
-We, therefore, adopt a MIST-based 2$\pm$0.2 Gyr age for the system, in-between the previous Geneva and Dartmouth-based scenarios \citep{2017AJ....153..211Z}.
+We, therefore, adopt a MIST-based 2.0$\pm$0.2 Gyr age for the system, in-between the previous Geneva and Dartmouth-based scenarios \citep{2017AJ....153..211Z}.
 Additional metallicity and rotation effects could slightly alter the evolutionary tracks and therefore increase uncertainty in inferred ages and masses.
@@
 Instead, we constructed panchromatic X-ray to visible SEDs by scaling and stitching together synthetic spectra to provide a range of high and low $L_X/L_\mathrm{bol}$.
-We chose a 6400 K PHOENIX \citep{husser13} solar metallicity photospheric spectral template with $\log{g}=3.5$, scaled to the solid angle seen by \hatpb.
+We chose a 6400 K PHOENIX \citep{husser13} solar metallicity photospheric spectral template with $\log{g}=3.5$---the closest PHOENIX grid point to published and updated values available--- scaled to the solid angle seen by \hatpb.
 The F7IV-V \object[tau Boo]{$\tau$ Boo} serves as the closest analog with available synthetic X-ray coronal spectra \citep{2011A&A...532A...6S}.

### 2023-06-26 paper/paper1/ms.tex
page 7 part 2

@@
 
-We reduced and analyzed the HPF data first for orbit fitting via precision radial velocity (PRV) measurements following the procedures described in \citet{2021AJ....161..173T} and updated for joint lightcurve and RV fits \citep{2022AJ....163..225T}.
+We conducted orbit fitting via precision radial velocity (PRV) measurements following the procedures described in \citet{2021AJ....161..173T} and updated for joint lightcurve and RV fits \citep{2022AJ....163..225T}, but without a joint Gaussian Process modeling procedure \citep{2023ApJ...950..162T}.
 Here we included the new TESS lightcurves and the existing Keck HIRES points reported in Table 3 of \citet{2017AJ....153..211Z}.
@@
 So even though the HPF points were more numerous, their marginal value for RV orbit determination was subdued owing to the lower RV information content in the near-IR for this relatively rapidly rotating F star.
-Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$ \kms---assuming a circular orbit---slightly decreasing the uncertainty compared to the previous $1\sigma$ limit.
+Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$ \kms, assuming a circular orbit and a $K>10$ \kms prior.
+The slightly decreasing the uncertainty compared to the previous $1\sigma$ limit.
 Table \ref{tabOrbit} lists the revised properties, with minor differences from the existing values.

### 2023-06-26 paper/paper1/ms.tex
Put in some caveats about the mass constraints

@@
 So even though the HPF points were more numerous, their marginal value for RV orbit determination was subdued owing to the lower RV information content in the near-IR for this relatively rapidly rotating F star.
-Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$ \kms, assuming a circular orbit and a $K>10$ \kms prior.
-The slightly decreasing the uncertainty compared to the previous $1\sigma$ limit.
+The period and $T_0$ were fixed from the \emph{TESS} transits, and we assume a circular orbit with $K>10$ \kms.
+The semiamplitude prior acts as a mass constraint, excluding planets with masses so low that the radius would exceed the Hill radius (Roche lobe overflow).
+Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$ \ms, a relatively weak constraint, but consistent with broadly Saturn-mass planets.
 Table \ref{tabOrbit} lists the revised properties, with minor differences from the existing values.
-\authorcomment1{Quang Tran: please verify and revise.}
+Hypothetically, a truly Roche lobe overflow planet could be consistent with the available data, so our constraint could be considered an upper limit.
 

### 2023-06-26 paper/paper1/ms.tex
Improved discussion about the mass constraint

@@
 Table \ref{tabOrbit} lists the revised properties, with minor differences from the existing values.
-Hypothetically, a truly Roche lobe overflow planet could be consistent with the available data, so our constraint could be considered an upper limit.
+The semiamplitude prior accounts for the apparent improvement in the mass constraint.
+Hypothetically, a truly Roche lobe overflow planet could be consistent with the available data, so our mass constraint could be considered an upper limit.
 

### 2023-06-27 paper/paper1/ms.tex
Up to page 8 now

@@
 The period and $T_0$ were fixed from the \emph{TESS} transits, and we assume a circular orbit with $K>10$ \kms.
-The semiamplitude prior acts as a mass constraint, excluding planets with masses so low that the radius would exceed the Hill radius (Roche lobe overflow).
+The semiamplitude prior acts as a mass constraint, excluding planets with masses so low that the observed radius would exceed the Hill radius (Roche lobe overflow).
 Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$ \ms, a relatively weak constraint, but consistent with broadly Saturn-mass planets.
@@
 \subsection{HPF analysis II: \ion{He}{1} 10833 \AA} \label{secHeAnalysis}
-The preparation for analyzing the Helium feature followed a similar but slightly different procedure than that used for the RV, namely, we used \texttt{Goldilocks}\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}} for 2D echellogram reduction.
+The preparation for analyzing the Helium feature followed a similar but slightly different procedure than that used for the RV, namely, we used \texttt{Goldilocks}\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}} for 2D \'echellogram reduction.
 This tool outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb \citep[LFC,][]{2019Optic...6..233M}.

### 2023-06-27 paper/paper1/ms.tex
Up to page 10

@@
 
-We masked spectral regions predicted to have significant telluric lines with a template generated by \texttt{telfit} \citep{2014AJ....148...53G}.
-We shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W} as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A,2022ApJ...935..167A}.
-We flattened the spectra to two pre-selected continuum indices highlighted as vertical blue bands in Figure \ref{fig:HPFheliumOverview}.
+We masked spectral regions predicted to have significant telluric lines with a template generated by \texttt{telfit} \citep{2014AJ....148...53G} then shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W}, as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A,2022ApJ...935..167A}.
+The spectral continuum was flattened and normalized to two pre-selected continuum indices highlighted as vertical blue bands in Figure \ref{fig:HPFheliumOverview}.
 The sky-subtraction, telluric masking, barycentric correction, flattening, and all of our other standard pre-processing steps were carried out in the open-source Python interface \texttt{muler} \citep{2022JOSS....7.4302G}.
 
-Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 region of interest, with all 152 individual exposures overlaid.
+Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 \AA~ region of interest, with all 152 individual exposures overlaid.
 We see variability in the Helium line of up to 10\%, much greater than the $<1\%$ pixel-to-pixel variation.
@@
     \includegraphics[width=\linewidth]{figures/phase_2D_diagram_resid.png}
-    \caption{Absorption depth phase scan over the entire HAT-P-67b orbit from 41 visits with HPF.  }
+    \caption{Absorption depth phase scan over the entire HAT-P-67b orbit from 41 visits with HPF.
+The planet orbital rest frame is shown as the black sine wave.
+Gaps in data at 10834-10836 \AA arise from telluric masking.
+Unmasked telluric lines are perceptible at 10825 \AA.}
     \label{fig:HPFscanResid}
@@
 Helium absorption occurs predominantly before the planet is in-transit, indicating a \emph{leading} tail escaping the planet.
-The leading tail is detected 0.1 AU away from the planet, or 130 planetary radii, well outside of the Roche Lobe at $<2.6$ planetary radii.
+The leading tail is detected 0.1 AU away from the planet, or 130 planetary radii, well outside of the Roche lobe at $<2.6$ planetary radii.
 We are detecting Roche lobe overflow, escaping material that is entirely unbound from the planet.
@@
 Assuming the gas has a spatially uniform optical depth of about 0.1 would reproduce the 10\% absorption excess.
+
+The leading tail geometry seen in in HAT-P-67~b contrasts with the morphology of the HAT-P-32~b system, which exhibits giant symmetric tidal tails with comparable absorption depth preceding and trailing the planet \citep{doi:10.1126/sciadv.adf8736}.
+These systems represent two of the most extended features associated with exoplanets, and we compare and contrast them in the Section \ref{secDiscuss}.
 

### 2023-06-27 paper/paper1/ms.tex

@@
 First we explore one-dimensional (1D) models, which offer ease of interpretation and rapid calculation.
-We employ the open-source \texttt{p-winds} code \citep{2022A&A...659A..62D}, which implements a transonic 1D Parker wind model with radiative transfer of the Helium 10830 triplet \citep{2018ApJ...855L..11O,2020A&A...636A..13L}.
+We employ the open-source \texttt{p-winds} code \citep{2022A&A...659A..62D}, which implements a transonic 1D Parker wind model with radiative transfer of the Helium 10830 \AA~ triplet \citep{2018ApJ...855L..11O,2020A&A...636A..13L}.
 
@@
     \caption{Synthetic XUV radiation scenarios for \hatpb.
-The low and high XUV scenarios correspond to $L_X/L_\mathrm{bol}$ of $10^{-6}$ and $10^{-4}$, where $L_X$ is defined as He 1 $^1$S Ionizing photons that trigger the recombination cascade needed for observing the He 2 $^3$S Ionization metastable state.
+The low and high XUV scenarios correspond to $L_X/L_\mathrm{bol}$ of $10^{-6}$ and $10^{-4}$, where $L_X$ is defined as He 1 $^1$S Ionizing photons that trigger the recombination cascade needed for observing the He 2 $^3$S ionization metastable state.
 He 2 $^3$S Ionizing photons depopulate the state and suppress the observability of \ion{He}{1} 10830 \AA.
@@
 
-We measured a large extent of Helium escape along the arc of the orbit, but we necessarily can place only coarse constraints on the vertical extent---in the direction perpendicular to the orbital path, $\pm z$.
+We measured a large extent of Helium escape along the arc of the orbit, but we necessarily can place only coarse constraints on the vertical extent---in the direction perpendicular to the orbital plane, $\pm z$.
 We estimate the detectable vertical extent must be at least a few stellar radii, such that we still could have detected Helium escape in a hypothetical HAT-P-67b-like system even if it were non-transiting, in a ``near miss'' configuration.
@@
 While large tails have been seen previously in Ly$\alpha$, the scarcity of UV resources prohibited searches of this kind.
-The discovery of large Helium tails in HAT-P-32b (Zhang et al.
-2023) and now HAT-P-67b suggest that the identification of these exospheric grazers may be achievable with current instrumentation and possibly existing archival data from near-IR RV-planet searches.
+The discovery of large Helium tails in HAT-P-32~b \citep{doi:10.1126/sciadv.adf8736} and now HAT-P-67~b suggest that the identification of these exospheric grazers may be achievable with current instrumentation and possibly existing archival data from near-IR RV-planet searches.
 Non-transiting, strongly irradiated planets with well-constrained orbits may make ideal targets for detection of this phenomenon.

### 2023-06-30 paper/paper1/ms.tex
State of the paper on Friday, June 30, 2023

@@
 \newcommand{\UCSC}{Department of Astronomy \& Astrophysics, University of California, Santa Cruz, 1156 High St, Santa Cruz, CA 95064, USA}
+\newcommand{\Tata}{Department of Astronomy and Astrophysics, Tata Institute of Fundamental Research, Homi Bhabha Road, Colaba, Mumbai 400005, India}
+
 % -------------------------------------------------------
@@
 \author[0000-0001-8720-5612]{Joe P.\ Ninan}
+\affil{\Tata}
+
 \affil{\PSUAA}
@@
 
-Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, a transiting inflated hot Saturn orbiting an F5 sub giant at an orbital separation of 0.06 AU and a 4.8-day orbital period \citep{2017AJ....153..211Z}.
+Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, a transiting inflated hot Saturn orbiting an F5 subgiant at an orbital separation of 0.06 AU and a 4.8-day orbital period \citep{2017AJ....153..211Z}.
 Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity ($\log{g_p}<2.3$, cgs) makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
@@
 We obtain a range of $3.2 < P_\mathrm{rot}  < 4.8 $ days.
-This range is typical for F stars that have not yet evolved too far into the sub giant branch \citep{2022ApJ...930....7A}.
+This range is typical for F stars that have not yet evolved too far into the subgiant branch \citep{2022ApJ...930....7A}.
 The geometrical constraint comports with the 4.7-day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9-day per-Sector fits, slightly preferring the lower 4.7-day modulation as the stellar rotation period.
@@
 
-We conclude that reinflation likely does not have a significant effect on the evolution of HAT-P-67~b: inflation timescales remain relatively unchanged over the planet lifetime, despite a 50\% spike in incident radiation in the sub giant scenario.
+We conclude that reinflation likely does not have a significant effect on the evolution of HAT-P-67~b: inflation timescales remain relatively unchanged over the planet lifetime, despite a 50\% spike in incident radiation in the subgiant scenario.
 The reason is subtle, as we describe next.
@@
 Under either scenario, HAT-P-67b resides in an extremely short-lifetime region.
-Its nearest analog, HAT-P-32b, offers an interesting test case since it has recently been shown to exhibit a large helium excess \authorcomment1{cite ZJ}.
+Its nearest analog, HAT-P-32b, offers an interesting test case since it has recently been shown to exhibit a large helium excess \citep{doi:10.1126/sciadv.adf8736}.
 It resides just slightly denser than the 0.1 $g\;cm^{-3}$ dividing line, with XUV predicting over 10$\times$ longer inflationary timescale for HAT-P-32b than for HAT-P-67b, while Ohmic dissipation expects merely a factor of 3 difference.
@@
     \texttt{jupyter} \citep{Kluyver2016jupyter},
-    \texttt{p-winds}, \citep{2022A&A...659A..62D}
+    \texttt{p-winds}, \citep{2022A&A...659A..62D},
+    \texttt{HxRGproc}, \citep{2018SPIE10709E..2UN}
 }

### 2023-06-30 paper/paper1/ms.tex
end of the day

@@
 \newcommand{\Tata}{Department of Astronomy and Astrophysics, Tata Institute of Fundamental Research, Homi Bhabha Road, Colaba, Mumbai 400005, India}
+\newcommand{\Steward}{Steward Observatory, The University of Arizona, 933 N. Cherry Ave, Tucson, AZ 85721, USA}
 
@@
 \author[0000-0001-9626-0613]{Daniel M. Krolikowski}
-\affil{\UTAustin}
+\affil{\Steward}
+%\affil{\UTAustin}
 
@@
     Atmospheric escape and its associated mass loss shape the fate of exoplanets, with statistical evidence for photoevaporation imprinted across the mass-radius-insolation distribution.
-The Habitable Zone Planet Finder (HPF) Spectrograph Exospheres program aims to expand the search across a diverse range of planet and host star properties via the 10830 \AA~ Helium triplet, a sensitive probe of active atmospheric escape.
+The Habitable Zone Planet Finder (HPF) Spectrograph Exospheres program aims to expand the search across a diverse range of planet and host star properties via the 10833 \AA~ Helium triplet, a sensitive probe of active atmospheric escape.
 Here we present a detection of 10\% absorption depth during transit spectroscopy of the highly irradiated, low-gravity, inflated hot Saturn HAT-P-67b.
@@
         \colhead{Desc.} &
-        \colhead{BTJD} &
+        \colhead{BJD} &
         \colhead{$N_\mathrm{exp}$} &
@@
         \colhead{} &
-        \colhead{(days)} &
+        \colhead{2457000.00+} &
         \colhead{} &
@@
 HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS,][]{2014SPIE.9143E..20R} in Sectors 24, 26, 51, 52, 53 with 2-minute cadence, and in Sector 25 with 30-minute (FFI) cadence.
-The Sector 25 FFI data appeared malformed, possibly due to problems with pipeline CCD smear correction, and was disregarded.
+The Sector 25 FFI data fell just barely off the TESS detectors, in collateral pixels where no starlight ever hit the detector.
 
@@
 So even though the HPF points were more numerous, their marginal value for RV orbit determination was subdued owing to the lower RV information content in the near-IR for this relatively rapidly rotating F star.
-The period and $T_0$ were fixed from the \emph{TESS} transits, and we assume a circular orbit with $K>10$ \kms.
+The period and $T_0$ were fixed from the \emph{TESS} transits, and we assume a circular orbit with $K>10$ \ms.
 The semiamplitude prior acts as a mass constraint, excluding planets with masses so low that the observed radius would exceed the Hill radius (Roche lobe overflow).
@@
 
-Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 \AA~ region of interest, with all 152 individual exposures overlaid.
+Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10833 \AA~ region of interest, with all 152 individual exposures overlaid.
 We see variability in the Helium line of up to 10\%, much greater than the $<1\%$ pixel-to-pixel variation.
@@
     %\subfloat{\includegraphics[width=4cm]{figures/centroid_inset10833.png}}
-    \caption{Line centroid positions of the  \ion{He}{1} 10830 \AA~ feature.
+    \caption{Line centroid positions of the  \ion{He}{1} 10833 \AA~ feature.
 A slight blueshift relative to the stellar restframe (vertical line) can be seen, with a weak excess blueshift trend after planet egress.
@@
 \section{Atmospheric Escape}\label{secResults}
+
+\subsection{Signal inconsistent with stellar activity interpretation}
+The planet's orbital period is close to the stellar rotational period, so the prospect of stellar activity contamination arises.
+Overall, the HPF spectra disfavor a stellar activity interpretation for a few reasons.
+First, a hypothetical stellar origin of Helium 10833 \AA~ variability should be accompanied by variability in other tracers.
+Instead, the \ion{Ca}{2} Infrared Triplet (IRT) shows stable line profiles in our HPF spectra.
+The Appendix Section \ref{appendixSec} discusses these and other non-detections.
+Second, the velocity substructure and phasing appears inconsistent with stellar activity: the gradual rise and then abrupt truncation of the Helium excess at the moment of planet egress (Figure \ref{fig:HPFtimeseries}) appears inconsistent with a more smoothly varying stellar variability.
+Finally, the weak post-egress excess appears blueshifted to wavelengths as short as 10830 \AA, which would fall entirely outside of the original Helium spectral line's rotationally broadened profile, ruling out a heritage from the star's surface.
+
+The recent discovery of giant tidal tails in HAT-P-32~b \citep{doi:10.1126/sciadv.adf8736} provides an additional anchor.
+HAT-P-32~b is in many ways the most analogous known system to HAT-P-67~b, having comparably low mass and comparably large radius for similar insolation around an F star.
+In HAT-P-32~b the planetary interpretation is unambiguous owing to the different stellar rotation and orbital periods.
+In Section \ref{secLackofSaturns} we show that radius inflation mechanisms expect similar and large mass loss rates for both of these systems.
 
@@
 First we explore one-dimensional (1D) models, which offer ease of interpretation and rapid calculation.
-We employ the open-source \texttt{p-winds} code \citep{2022A&A...659A..62D}, which implements a transonic 1D Parker wind model with radiative transfer of the Helium 10830 \AA~ triplet \citep{2018ApJ...855L..11O,2020A&A...636A..13L}.
+We employ the open-source \texttt{p-winds} code \citep{2022A&A...659A..62D}, which implements a transonic 1D Parker wind model with radiative transfer of the Helium 10833 \AA~ triplet \citep{2018ApJ...855L..11O,2020A&A...636A..13L}.
 
@@
 The low and high XUV scenarios correspond to $L_X/L_\mathrm{bol}$ of $10^{-6}$ and $10^{-4}$, where $L_X$ is defined as He 1 $^1$S Ionizing photons that trigger the recombination cascade needed for observing the He 2 $^3$S ionization metastable state.
-He 2 $^3$S Ionizing photons depopulate the state and suppress the observability of \ion{He}{1} 10830 \AA.
+He 2 $^3$S Ionizing photons depopulate the state and suppress the observability of \ion{He}{1} 10833 \AA.
 The XUV flux of HAT-P-67 is uncertain.}
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/pwinds_May2020_14000_2e13Mdot_medXUV_formal_rv.png}
+    \includegraphics[width=\linewidth]{figures/pwinds_May2020_14000_2e13Mdot_medXUV_formal_rv_rev.png}
     \caption{Simulated 1D Parker wind model of Helium absorption in \hatpb.
 The spectrum was generated with a mass loss rate of $2\times10^{13}$ g/s, exosphere gas temperature of $14\,000\;$K, and with an XUV luminosity $L_x/L_\mathrm{bol}=10^{-5}$ intermediate between those shown in Figure \ref{fig:XUV}.
-The \texttt{p-winds} model yields the \ion{He}{1} 10830 triplet lines (colored dashed lines), with a cumulative feature in black resembling the data, shown as the May 2020 in-transit mean.
+The \texttt{p-winds} model yields the \ion{He}{1} 10833 triplet lines (colored dashed lines), with a cumulative feature in black resembling the data, shown as the May 2020 in-transit mean.
 Additional 3D velocity dispersion of the gas can explain differences between the line shapes of the model and data.
@@
 \subsection{Direct Evidence for Day-/Night- side mass loss asymmetry}\label{secPrimaFacie}
-The observation of such a prominent leading tail leads us to the inescapable conclusion that HAT-P-67~b is predominantly losing mass on the dayside.
+The observation of such a prominent leading tail leads us to the inescapable conclusion that HAT-P-67~b is predominantly losing mass on the planet's dayside.
 An isotropic mass loss would manifest a comparably conspicuous trailing tail, which we do not observe.
@@
 
-\subsection{Weighing the causes for a lack of sub-Saturns}
+\subsection{Weighing the causes for a lack of sub-Saturns}\label{secLackofSaturns}
 
@@
 We predict that these few other inflated \hatpb-analogs should show evidence for significant atmospheric escape, comparable to what we see for \hatpb.
-These sources make excellent targets for \ion{He}{1} 10830 observations, and/or other atmospheric escape diagnostics.
+These sources make excellent targets for \ion{He}{1} 10833 observations, and/or other atmospheric escape diagnostics.
 As emphasized, there are significant uncertainties in the inflation timescale, but at least its order-of-magnitude value gives us a quantitative and justified way to prioritize target selection.
@@
     \tablecaption{
-        Coarse Inflation Timescales for hot Jupiters
+        Coarse Inflation Timescales for Other Systems
         \label{tabHeSM}
@@
 The HPF spectra reveal up to 10\% signal depth over a few Angstroms.
-The TESS bandpass barely includes 10830 \AA, at a location of diminishing throughput, so it appears impractical that Helium alone could cause the TESS signal.
+The TESS bandpass barely includes 10833 \AA, at a location of diminishing throughput, so it appears impractical that Helium alone could cause the TESS signal.
 Hypothetically, dust dredged up in the mass loss process could cause a large enough broadband flux loss to manifest in TESS.

### 2023-07-03 paper/paper1/ms.tex
Addressing comments from Suvrath M

@@
 \begin{abstract}
-    Atmospheric escape and its associated mass loss shape the fate of exoplanets, with statistical evidence for photoevaporation imprinted across the mass-radius-insolation distribution.
+    Atmospheric escape shapes the fate of exoplanets, with statistical evidence for transformative mass loss imprinted across the mass-radius-insolation distribution.
 The Habitable Zone Planet Finder (HPF) Spectrograph Exospheres program aims to expand the search across a diverse range of planet and host star properties via the 10833 \AA~ Helium triplet, a sensitive probe of active atmospheric escape.
-Here we present a detection of 10\% absorption depth during transit spectroscopy of the highly irradiated, low-gravity, inflated hot Saturn HAT-P-67b.
-The 13.8 hours of on-sky integration time over 39 nights provides enough out-of-transit phase coverage as to reveal comparably deep absorption preceding the transit, revealing a large leading tail.
+Here we present a detection of 10\% absorption depth during transit spectroscopy of the highly irradiated, low-gravity, inflated hot Saturn HAT-P-67~b.
+The 13.8 hours of on-sky integration time over 39 nights sample the entire planet orbit, uncovering excess Helium absorption preceding the transit by up to 130 planetary radii in a large leading tail.
 This configuration can be understood as the escaping material overflowing its small Roche lobe, and advecting most of the gas into the stellar—and not planetary---rest frame, consistent with the Doppler velocity structure seen in the Helium line profiles.
 The prominent leading tail serves as direct evidence for dayside mass loss with a strong day-/night- side asymmetry.
-A combination of Keplerian shear and stellar wind confinement control the extent and optical depth of the tail.
-We see some transit-to-transit variability in the line profile, consistent with the interplay of stellar and planetary wind.
+We see some transit-to-transit variability in the line profile, consistent with the interplay of stellar and planetary winds.
 We employ 1D Parker wind models to estimate the mass loss rate, finding values on the order of $2\times10^{13}$ g/s, with large uncertainties owing to the unknown XUV flux of the F host star.
 The large mass loss in HAT-P-67~b represents a valuable example of an inflated hot Saturn, a class of planets recently identified to be rare as their atmospheres are predicted to evaporate quickly.
-We explore two physical mechanisms for runaway evaporation: Ohmic dissipation and XUV irradiation, slightly favoring the latter.
+We contrast two physical mechanisms for runaway evaporation: Ohmic dissipation and XUV irradiation, slightly favoring the latter.
 \end{abstract}
@@
 
-Atmospheric escape appears to be a compulsory phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5$-$2.0~$R_\oplus$ planets within 100 day periods \citep{2017AJ....154..109F}.
-The leading candidate physical mechanisms for this rapid transition between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2013ApJ...776....2L,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G}.
-Whatever the cause, some large fraction of planets must undergo transformative atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations such as transiting planets.
-Such signals have been searched for and increasingly found, with at least 28 detections to date \citep{2022arXiv221116243D}.
-
-Uncertainty in system ages, evaporation timescales, and dominating physical mechanisms degrade our ability to foretell if any given planet will exhibit ongoing signatures of atmospheric escape.
+Atmospheric escape appears to be a normal phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5$-$2.0~$R_\oplus$ planets within 100 day periods \citep{2017AJ....154..109F}.
+The leading candidate physical mechanisms for this rapid transition between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2013ApJ...776....2L,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G,2023arXiv230200009B}.
+Whatever the cause, some large fraction of planets undergo transformative atmospheric escape and the signal should be widely discernable.
+Such signals have been searched for, and increasingly found, in many transiting planet systems with at least 28 detections to date \citep{2022arXiv221116243D}.
+
+Uncertainty in system ages, evaporation timescales, X-ray/UV radiation, and dominating physical mechanisms degrade our ability to foretell if any given planet will exhibit ongoing signatures of atmospheric escape.
 Episodic stellar wind gusts and other forms of astrophysical variability could also subdue the appearance of atmospheric escape, even where we expect it most.
@@
 This category is defined as having masses comparable to Saturn's ($M_p \sim 0.3 M_\mathrm{Jup}$), with equilibrium temperatures high enough to expect radius inflation($T_\mathrm{eq}>1000\;$K).
-Their low gravitational potentials should let go of their atmospheres more readily than their steadfast hot Jupiter counterparts.
-Their lower gravity yields larger atmospheric scale heights, making them easier to detect in transmission spectroscopy.
+Their low gravitational potentials should let go of their atmospheres more readily than their hot Jupiter counterparts.
+Their lower gravity implies larger atmospheric scale heights, making them easier to detect in transmission spectroscopy.
 And their large transit depths and short periods should make them readily detectable in large numbers, like hot Jupiters.
@@
 Here, lightly thermally ionized atmospheric flows induce drag in a planetary magnetic field, weakly coupling the stellar incident energy into the planetary interior.
-\citet{2018AJ....155..214T} recognized the above two hypotheses for the lack of sub-Saturns, while statistically favoring Ohmic dissipation as the mechanism responsible for inflating hot Jupiters.
+A key prediction of Ohmic dissipation is that the anomalous heating efficiency $\epsilon(T_\mathrm{eq})$ should exhibit a peak around $T_\mathrm{eq}\sim1500-2000\;$K \citep{2012ApJ...745..138M,2014ApJ...794..132R,2016ApJ...819..116G}.
+\citet{2018AJ....155..214T} favored Ohmic dissipation as the mechanism responsible for inflating hot Jupiters by showing that the extent of inflation implies an underlying peak at $\sim1500\;$K.
 Therefore Ohmic dissipation stands out as a leading physical mechanism for inflation and mass loss.
@@
 In particular, metastable Helium's ability to be observed at high spectral resolution from the ground has been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.
-\ion{He}{1} has resulted in at least 14 systems with detections, including \object[GJ 3470]{GJ 3470 b} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
+\ion{He}{1} has resulted in at least 14 systems with detections (also see Table~S1 of \citealt{doi:10.1126/sciadv.adf8736} for a compilation of exoplanets with detections and non-detections of the helium excess), including \object[GJ 3470]{GJ 3470 b} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, HAT-P-18 b \citep{2021ApJ...909L..10P}, and HAT-P-32~b \citep{2022A&A...657A...6C, doi:10.1126/sciadv.adf8736}.
 The sample of detections includes both hot Jupiters and lower mass planets, but lacks inflated hot Saturns owing to their intrinsic rarity below the 0.1 g~cm$^{-3}$ threshold.
@@
 Here we present a multi-year observational campaign searching for atmospheric escape in \object{HAT-P-67 b}, a transiting inflated hot Saturn orbiting an F5 subgiant at an orbital separation of 0.06 AU and a 4.8-day orbital period \citep{2017AJ....153..211Z}.
-Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity ($\log{g_p}<2.3$, cgs) makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
+Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity ($\log{g_p}<2.3$~dex) makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
 Its $\sim$0.05 g~cm$^{-3}$ density places it below the 0.1 g~cm$^{-3}$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.

### 2023-07-05 paper/paper1/ms.tex
Addressing comments from Suvrath

@@
 
-\affil{\PSUAA}
-\affil{\PSUCEHW}
-
 \author[0000-0002-9584-6476]{Antonija Oklop{\v{c}}i{\'c}}
@@
 Inflated hot Saturns stand out as an especially extreme category that should exhibit mass loss.
-This category is defined as having masses comparable to Saturn's ($M_p \sim 0.3 M_\mathrm{Jup}$), with equilibrium temperatures high enough to expect radius inflation($T_\mathrm{eq}>1000\;$K).
+This category is defined as having masses comparable to Saturn's ($M_p \sim 0.3 M_\mathrm{Jup}$), with equilibrium temperatures high enough to expect radius inflation ($T_\mathrm{eq}>1000\;$K).
 Their low gravitational potentials should let go of their atmospheres more readily than their hot Jupiter counterparts.
 Their lower gravity implies larger atmospheric scale heights, making them easier to detect in transmission spectroscopy.
-And their large transit depths and short periods should make them readily detectable in large numbers, like hot Jupiters.
+And their large transit depths and short periods should make them readily detectable in transit searches in large numbers, like hot Jupiters.
 
@@
 A key prediction of Ohmic dissipation is that the anomalous heating efficiency $\epsilon(T_\mathrm{eq})$ should exhibit a peak around $T_\mathrm{eq}\sim1500-2000\;$K \citep{2012ApJ...745..138M,2014ApJ...794..132R,2016ApJ...819..116G}.
-\citet{2018AJ....155..214T} favored Ohmic dissipation as the mechanism responsible for inflating hot Jupiters by showing that the extent of inflation implies an underlying peak at $\sim1500\;$K.
+\citet{2018AJ....155..214T} favored Ohmic dissipation as the mechanism responsible for inflating hot Jupiters by showing that the observed sample of inflated planets implies an anomalous heating efficiency peak at equilibrium temperatures of $\sim1500\;$K.
 Therefore Ohmic dissipation stands out as a leading physical mechanism for inflation and mass loss.
@@
 As the planet's atmosphere overflows its Roche lobe at an ever-increasing pace, instantaneous mass loss rates may exceed $\dot{M}>10^{13}$ g/s, over 10$\times$ larger than those previously seen in atmospheric escape measurements to date \citep{2022arXiv221116243D}.
-Inflated hot Saturns, therefore, make excellent targets for direct measurement of atmospheric escape and to test the underlying mechanisms of mass loss.
+Inflated hot Saturns, therefore, make excellent targets for direct measurement of atmospheric escape and for testing the underlying mechanisms of mass loss.
 
@@
 The evolutionary state of HAT-P-67~b offers even more intriguing possibilities.
-The planet may have undergone re-inflation \citep{2022AJ....163...53S, 2022AJ....163..120G, 2023arXiv230306728G}, as the host star evolved through the subgiant phase-- with the planet's insolation increasing with the star's rapid luminosity increase in this part of the short-lived HR diagram.
+The planet may have undergone re-inflation \citep{2022AJ....163...53S, 2022AJ....163..120G, 2023arXiv230306728G}, as the host star evolved through the subgiant phase-- with the planet's insolation increasing with the star's rapid luminosity jump in this part of the short-lived HR diagram.
 The tidal gravity of the nearby massive ($M_\star \sim1.6\;M_\odot$) host star may amplify mass loss rates even further \citep{2007A&A...472..329E, 2023ApJ...945L..36T}.
@@
 The small BERV still means the redward Helium line wing has significant telluric contamination between 10834$-$10836 \AA, but the core and blue line wings appear relatively pristine.
+Sky emission lines land in this region, but are more easily mitigated by HPF's simultaneous sky reference fiber.
 
@@
 \subsection{Gaia DR3}\label{gaiadr3}
-The stellar system consists of a binary with an M dwarf companion HAT-P-67B (\emph{Gaia DR3 1358614983131339904}) separated on-sky by $9\farcs0$ \citep{2019MNRAS.490.5088M}.
+The stellar system consists of a binary with an M dwarf companion HAT-P-67B (\emph{Gaia DR3 1358614983131339904}) separated on-sky by $9\farcs0$ \citep{2019MNRAS.490.5088M}, well-separated from the planet-host star and not a source of contamination for the HPF observations.
 HAT-P-67A (\emph{Gaia DR3 1358614983131339392}) has a parallax of $2.69\pm0.01$ mas in \emph{Gaia} DR3, placing it at about 372$\pm$1.4 pc.
@@
 Here we included the new TESS lightcurves and the existing Keck HIRES points reported in Table 3 of \citet{2017AJ....153..211Z}.
-The HPF points exhibited an RV jitter of $\sim164\;\ms$, a few times larger than the typical Keck HIRES measurements.
-So even though the HPF points were more numerous, their marginal value for RV orbit determination was subdued owing to the lower RV information content in the near-IR for this relatively rapidly rotating F star.
+The HPF points exhibited an RV jitter of $\sim164\;\ms$, a few times larger than the typical Keck HIRES measurements, due to the lower information content in the near-IR than the visible for this relatively rapidly rotating F star.
+So even though the HPF points were more numerous, their marginal value for RV orbit determination was subdued.
 The period and $T_0$ were fixed from the \emph{TESS} transits, and we assume a circular orbit with $K>10$ \ms.
@@
 We quantified the wavelength dependence by acquiring calibration observations of blank sky in both the target and sky fiber.
-We applied this wavelength-based scale factor to each target spectrum's associated reference sky fiber to achieve near-imperceptible sky-line subtraction residuals.
+We applied this wavelength-based scale factor to each target spectrum's associated reference sky fiber to achieve sky-line subtraction residuals typically less than the photon noise \citep{2022JOSS....7.4302G}.
 A few lines exhibit residuals that may arise from genuine differences in the local atmospheric conditions between the target and sky fiber.
 
-We masked spectral regions predicted to have significant telluric lines with a template generated by \texttt{telfit} \citep{2014AJ....148...53G} then shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W}, as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A,2022ApJ...935..167A}.
+The HET's fixed-altitude design means that the airmass remains relatively constant across all pointings, lowering the telluric line variability compared to fully steerable telescopes which may sample a wider range in airmasses.
+Variability in atmospheric conditions still makes it difficult to mitigate telluric lines to within the photon noise limit, so we masked spectral regions predicted to have significant telluric lines with a template generated by \texttt{telfit} \citep{2014AJ....148...53G}.
+We then shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W}, as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A,2022ApJ...935..167A}.
 The spectral continuum was flattened and normalized to two pre-selected continuum indices highlighted as vertical blue bands in Figure \ref{fig:HPFheliumOverview}.
@@
 
+    The Center for Exoplanets and Habitable Worlds is supported by the Pennsylvania State University and the Eberly College of Science.
+
     GS acknowledges support provided by NASA through the NASA Hubble Fellowship grant HST-HF2-51519.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.

### 2023-07-05 paper/paper1/ms.tex
Suvrath comments on Introduction and TESS bandpass discussion

@@
 In particular, metastable Helium's ability to be observed at high spectral resolution from the ground has been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.
-\ion{He}{1} has resulted in at least 14 systems with detections (also see Table~S1 of \citealt{doi:10.1126/sciadv.adf8736} for a compilation of exoplanets with detections and non-detections of the helium excess), including \object[GJ 3470]{GJ 3470 b} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, HAT-P-18 b \citep{2021ApJ...909L..10P}, and HAT-P-32~b \citep{2022A&A...657A...6C, doi:10.1126/sciadv.adf8736}.
+\ion{He}{1} has resulted in at least 14 systems with detections (\citet{2022arXiv221116243D}, also see Table~S1 of \citealt{doi:10.1126/sciadv.adf8736} for a compilation of exoplanets with detections and non-detections of the helium excess).
 The sample of detections includes both hot Jupiters and lower mass planets, but lacks inflated hot Saturns owing to their intrinsic rarity below the 0.1 g~cm$^{-3}$ threshold.
@@
 The HPF spectra reveal up to 10\% signal depth over a few Angstroms.
-The TESS bandpass barely includes 10833 \AA, at a location of diminishing throughput, so it appears impractical that Helium alone could cause the TESS signal.
-Hypothetically, dust dredged up in the mass loss process could cause a large enough broadband flux loss to manifest in TESS.
+The TESS bandpass barely includes 10833 \AA, at a location of diminishing throughput.
+The Helium signal alone would manifest as a mere $\sim4$ ppm flux loss when integrated over a TESS-throughput-weighted F-star spectrum--negligible compared to the observed $0.36\%$ peak-to-valley modulation.
+An ensemble of additional lines in the red-optical cannot realistically resemble the TESS modulation.
+The inventory of such conceivable atomic lines detectable from the planet in the TESS bandpass numbers merely a few, with \ion{Ca}{2} infrared triplet and H$\alpha$ chief among them \citep{2023arXiv230606971L}.
+A putative H$\alpha$ line would have to be about 30\% deep over 10 \AA~ wide to manifest perceptibly in the TESS data.
+Such an implausibly deep and wide line likely would have been observed as perturbations in the Keck HIRES spectra, even with its limited phasing.
+Hypothetically, dust dredged up in the mass loss process could cause a large enough broadband continuum flux loss to manifest in TESS.
 We may expect to see some variable reddening in that case.
-A putative H$\alpha$ line would have to be about 30\% deep over 10 \AA~ wide to manifest perceptibly in the TESS data.
-Such an implausibly deep line likely would have been observed as perturbations in the Keck HIRES spectra, even with its limited phasing.
 

### 2023-07-06 paper/paper1/ms.tex
define rho XUV

@@
 \end{equation}
- where $K_t$ is the tidal gravity term, and $\eta \sim 0.4$ comes from \citet{2022A&A...663A.122C}.
+ where $K_t$ is the tidal gravity term, $\rho_\mathrm{XUV}$ is the planet density determined using the radius at which XUV radiation is deposited, and $\eta \sim 0.4$ comes from \citet{2022A&A...663A.122C}.
 Assuming $\log{L_\mathrm{XUV}/L_\mathrm{bol}}=-4.2$, we would expect \hatpb~ to exhibit $\dot{M}\sim10^2$ M$_\oplus$/Gyr.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/reinflation_MIST.png}
+    \includegraphics[width=\linewidth]{figures/reinflation_MIST2.png}
     \caption{Conceivable evolutionary scenarios for \hatpb.

### 2023-07-06 paper/paper1/ms.tex
Suvrath comment on blending

@@
 
-We estimated bulk characteristics of the Helium excess absorption feature by fitting a Gaussian line profile to the 10828$-$10838 \AA~region of the residual spectra.
-The single line initialized at 10833 \AA~ was intended to agglomerate all three components of the metastable triplet into a single feature, consistent with their appearance in Figure \ref{fig:HPFheliumOverview}.
+The underlying structure of the metastable \ion{He}{1} triplet consists of three quantum components, two of which ($J=$ 1 and 2) are typically blended owing to Doppler broadening from the finite temperature of the gas $T_0$.
+HAT-P-67~b exhibits blending of all three components ($J=$ 0, 1, and 2) into a single broad Gaussian-like feature seen in Figure \ref{fig:HPFheliumOverview}.
+The mere observation of this broadening implies that HAT-P-67~b probes a larger velocity dispersion than typical measurements, and may be associated with either a higher gas temperature, complex planetary wind flows, or some mix of both.
+Whatever the cause, we treat the feature as a single Gaussian line for the pupose of estimating bulk characteristics of the Helium excess absorption feature.
+We restricted the fitting to the 10828$-$10838 \AA~region of the residual spectra.
 The model constructed in this way has a total of 4 parameters: amplitude $A$, location $\lambda_c$, Gaussian width $\sigma$, and constant offset.
@@
 The spectrum was generated with a mass loss rate of $2\times10^{13}$ g/s, exosphere gas temperature of $14\,000\;$K, and with an XUV luminosity $L_x/L_\mathrm{bol}=10^{-5}$ intermediate between those shown in Figure \ref{fig:XUV}.
-The \texttt{p-winds} model yields the \ion{He}{1} 10833 triplet lines (colored dashed lines), with a cumulative feature in black resembling the data, shown as the May 2020 in-transit mean.
+The \texttt{p-winds} model yields the \ion{He}{1} 10833 triplet lines (colored thin lines), with a cumulative feature in black resembling the data, shown as the May 2020 in-transit mean.
 Additional 3D velocity dispersion of the gas can explain differences between the line shapes of the model and data.
@@
  where $K_t$ is the tidal gravity term, $\rho_\mathrm{XUV}$ is the planet density determined using the radius at which XUV radiation is deposited, and $\eta \sim 0.4$ comes from \citet{2022A&A...663A.122C}.
-Assuming $\log{L_\mathrm{XUV}/L_\mathrm{bol}}=-4.2$, we would expect \hatpb~ to exhibit $\dot{M}\sim10^2$ M$_\oplus$/Gyr.
-At a current $M\sim95\;$M$_\oplus$ and an accelerating mass loss rate, its lifetime would measure in the $\sim$100 Myr range.
+Assuming $\log{L_\mathrm{XUV}/L_\mathrm{bol}}=-4.2$, we would expect \hatpb~ to exhibit $\dot{M}\sim10^2$ M$_\oplus$/Gyr ($2\times10^{13}\;$g/s).
+At a current $M_\mathrm{p}\sim95\;$M$_\oplus$ and an accelerating mass loss rate, its lifetime would measure in the $<$100 Myr range.
 The \citet{2023ApJ...945L..36T} simulations focused on 0.75-1.25 $M_\odot$ host stars; the higher mass $\sim$1.6 $M_\odot$ \hatp would deliver greater tidal gravity for a given semi-major axis, and possibly lower $\log{L_\mathrm{XUV}/L_\mathrm{bol}}$ compared to more active G stars.

### 2023-07-07 paper/paper1/ms.tex
Add He I and Si labels to the plot per Suvrath guidance

@@
     \includegraphics[width=\linewidth]{figures/HAT_P_67b_Helium10830EW_byCampaign.png}
-    \caption{Equivalent width lightcurve of Helium absorption in HAT-P-67b.  The system exhibits a characteristic absorption leading up to transit, followed by a sharp decline after transit passage.}
+    \caption{Equivalent Width lightcurve of Helium absorption in HAT-P-67b.  The system exhibits a characteristic absorption leading up to transit, followed by a sharp decline after transit passage.}
     \label{fig:HPFtimeseries}
@@
 A large absorption signal can be seen preceding transit ingress, with some significant absorption evident before $-0.2$ in phase.
+The egress drop-off is extremely sharp, with almost no excess absorption directly after transit, as seen in the Equivalent Width (EW) timeseries (Figure \ref{fig:HPFtimeseries}).
 We construct a fractional residual absorption spectrum by subtracting off and re-normalizing to the non-varying baseline.
@@
 Figure \ref{fig:HPFscanResid} shows that significant absorption can be seen as a few percent at $-0.37$ in phase, rising to 10\% just before and during transit.
-The egress drop-off is extremely sharp, with almost no excess absorption directly after transit.
+The abrupt dropoff in helium excess at planet egress is conspicuous.
 

### 2023-07-07 paper/paper1/ms.tex
comments from Suvrath and ZJ

@@
 We observed HAT-P-67 with HPF for a total of 41 visits on 39 unique nights, with two of those nights observing both the east and west HET tracks.
-The total on-source integration time exceeds 13.8 hours, over $N=152$ individual spectra.
+The total on-source integration time exceeds 13.8 hours, with $N=152$ individual spectra possessing typical signal-to-noise ratio of 80 per pixel.
 Table \ref{tabHPFLog} summarizes the log of observations.
@@
     \caption{Overlay of all 152 individual HPF exposures of HAT-P-67, spanning 2020-2022.
-Variability is seen in the \ion{He}{1} 10833 \AA~ triplet, denoted by the vertical orange shaded band, but not in the adjacent regions.
-These snapshot spectra were barycentric corrected, and continuum flattened to the regions in the blue vertical bands.
+Variability is seen in the \ion{He}{1} 10833 \AA~ triplet near the vertical orange shaded band, but not in the adjacent Si line.
+These snapshot spectra were barycentric corrected, and continuum flattened with a linear fit to the regions in the blue vertical bands.
 Sharp telluric absorption lines have been masked in regions near 10835 and 10837.5 \AA.}
@@
     \includegraphics[width=\linewidth]{figures/HAT_P_67b_Helium10830EW_byCampaign.png}
-    \caption{Equivalent Width lightcurve of Helium absorption in HAT-P-67b.  The system exhibits a characteristic absorption leading up to transit, followed by a sharp decline after transit passage.}
+    \caption{Equivalent Width lightcurve of Helium absorption in HAT-P-67b.
+The system exhibits a characteristic absorption leading up to transit, followed by a sharp decline after transit passage.
+The EWs were computed in the orange shaded band (10832.3$-$10834.2 \AA) in Figure \ref{fig:HPFheliumOverview}.}
     \label{fig:HPFtimeseries}

### 2023-07-10 paper/paper1/ms.tex
Nearing the final submittable version of the paper
Mention the overall HPF survey

@@
 \usepackage{booktabs}
+\usepackage[T1]{fontenc}
 \usepackage{xcolor}
@@
 \newcommand{\Steward}{Steward Observatory, The University of Arizona, 933 N. Cherry Ave, Tucson, AZ 85721, USA}
+\newcommand{\HET}{Hobby-Eberly Telescope, The University of Texas at Austin, 2515 Speedway, Austin, TX 78712, USA}
 
@@
 
+\author[0000-0002-4404-0456]{Caroline V. Morley}
+\affil{\UTAustin}
+
+\author[0000-0003-2152-9248]{Jessica Luna}
+\affil{\UTAustin}
+
+\author[0000-0002-1417-8024]{Morgan MacLeod}
+\affiliation{\CFA}
+
+\author[0000-0002-9584-6476]{Antonija Oklop{\v{c}}i{\'c}}
+\affil{\Amsterdam}
+
+\author[0000-0002-1846-196X]{Aishwarya Ganesh}
+\affil{\UTAustin}
+
+\author[0000-0001-6532-6755]{Quang H. Tran}
+\affiliation{\UTAustin}
+
+\author[0000-0002-3726-4881]{Zhoujian Zhang}\thanks{NASA Sagan Fellow}
+\affiliation{\UCSC}
+
 \author[0000-0003-2649-2288]{Brendan P. Bowler}
@@
 
-\author[0000-0002-1846-196X]{Aishwarya Ganesh}
-\affil{\UTAustin}
-
-\author[0000-0001-9811-568X]{Adam L. Kraus}
-\affil{\UTAustin}
-
 \author[0000-0001-9626-0613]{Daniel M. Krolikowski}
@@
 
-\author[0000-0003-2152-9248]{Jessica Luna}
-\affil{\UTAustin}
-
-\author[0000-0002-1417-8024]{Morgan MacLeod}
-\affiliation{\CFA}
-
 \author[0000-0001-9596-7983]{Suvrath Mahadevan}
@@
 
-\author[0000-0002-4404-0456]{Caroline V. Morley}
-\affil{\UTAustin}
-
 \author[0000-0001-8720-5612]{Joe P.\ Ninan}
 \affil{\Tata}
-
-\author[0000-0002-9584-6476]{Antonija Oklop{\v{c}}i{\'c}}
-\affil{\Amsterdam}
 
@@
 
-\author[0000-0001-6532-6755]{Quang H. Tran}
-\affiliation{\UTAustin}
-
-\author[0000-0002-3726-4881]{Zhoujian Zhang}\thanks{NASA Sagan Fellow}
-\affiliation{\UCSC}
+\author[0000-0002-2259-4116]{Joseph A. Zalesky}
+\affil{\UTAustin}
+
+\author[0000-0003-2307-0629]{Gregory R. Zeimann}
+\affil{\HET}
 
 % and more...
-
-\collaboration{1}{HPF Helium Exospheres Collaboration}
 
@@
 \end{figure}
+
+The Habitable Zone Planet Finder (HPF) Helium Exospheres Collaboration has been conducting a survey of exoplanets to search for atmosphere loss via the\ion{He}{1} 10833 \AA metastable triplet.
+The survey's multiple-visit sampling strategy has enabled a search for atmospheric loss at large out-of-transit separations from the planet, recently revealing giant tidal tails of Helium escaping the hot Jupiter HAT-P-32~b \citep{doi:10.1126/sciadv.adf8736}.
 

### 2023-07-10 paper/paper1/ms.tex
Make sure all date references are UTC and not local time

@@
 In practice, this limitation means that in-transit and out-of-transit observational phases were rarely possible on the same night.
-Instead, we organized the observations into four campaigns to coincide with \object{HAT-P-67 b} transits on the nights beginning 2020 April 27, 2020; May 21, 2020; June 14, 2020; and 2022 April 28.
+Instead, we organized the observations into four campaigns to coincide with \object{HAT-P-67 b} transits on UT dates 2020 April 28, 2020; May 22, 2020; June 15, 2020; and 2022 April 29.
 These campaigns have out-of-transit observations at least one night before and one night after, and often two nights on either side of the transit.
@@
     \tablehead{
-        \colhead{Night-of}   &
+        \colhead{UTC}   &
         \colhead{Track} &
@@
     \enddata
-    \tablecomments{The ``night of'' refers to the local date at the start of the night.
-All exposure times were 308.85~s except for observations from 2020-07-21 to 2021-03-30, which were 511.20~s.
+    \tablecomments{All exposure times were 308.85~s except for observations from 2020-07-22 to 2021-03-31, which were 511.20~s.
 Column 2 describes the HET ``track'', restricted to either East (E) or West (W).
@@
 The rest of the visits sample out-of-transit phases.
-The 8 HPF visits between BTJD 2050 and 2690 are not shown.
+The 8 HPF visits between days 2050 and 2690 are not shown.
 Note the large time breaks between some consecutive panels, which correspond roughly to the duration of a TESS sector.}
@@
 
-\subsection{Signal inconsistent with stellar activity interpretation}
+\subsection{Signal Inconsistent with Stellar Activity Interpretation}
 The planet's orbital period is close to the stellar rotational period, so the prospect of stellar activity contamination arises.
@@
 
-\subsection{Direct Evidence for Day-/Night- side mass loss asymmetry}\label{secPrimaFacie}
+\subsection{Direct Evidence for Preferential Dayside Mass Loss}\label{secPrimaFacie}
 The observation of such a prominent leading tail leads us to the inescapable conclusion that HAT-P-67~b is predominantly losing mass on the planet's dayside.
@@
 
-    This material is based upon work supported by the National Aeronautics and Space Administration under Grant Number 80NSSC20K0257 for the XRP program issued through the Science Mission Directorate.
+    This material is based upon work supported by the National Aeronautics and Space Administration under Grant Number 80NSSC21K0650 for the NNH20ZDA001N-ADAP:D.2 program and 80NSSC20K0257 for the XRP program issued through the Science Mission Directorate.
 

### 2023-07-10 paper/paper1/ms.tex
Sent the previous draft to coauthors for final comments, here are some minor edits from a re-read, by CVM and MGS

@@
 Their low gravitational potentials should let go of their atmospheres more readily than their hot Jupiter counterparts.
-Their lower gravity implies larger atmospheric scale heights, making them easier to detect in transmission spectroscopy.
+Lower gravity also implies larger atmospheric scale heights, making them easier to detect in transmission spectroscopy.
 And their large transit depths and short periods should make them readily detectable in transit searches in large numbers, like hot Jupiters.
@@
 Planets with densities less than $\sim$0.1 g~cm$^{-3}$ achieve mass loss rates of up to $10^3$ $M_\oplus /$Gyr setting up a positive feedback loop: the planet increases in radius, overflowing its Roche lobe, fueling greater mass loss, and increasing in radius even further.
-This vicious cycle systematically depopulates the mass-radius plane with a cliff defined by the $\sim$0.1 g~cm$^{-3}$ dividing line.
+This vicious cycle systematically depopulates the mass-radius plane with a cliff defined by the $\rho_p \sim$0.1 g~cm$^{-3}$ dividing line.
 
@@
 In particular, metastable Helium's ability to be observed at high spectral resolution from the ground has been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.
-\ion{He}{1} has resulted in at least 14 systems with detections (\citet{2022arXiv221116243D}, also see Table~S1 of \citealt{doi:10.1126/sciadv.adf8736} for a compilation of exoplanets with detections and non-detections of the helium excess).
+\ion{He}{1} has resulted in at least 14 systems with detections \citep{2022arXiv221116243D}\footnote{See also Table~S1 of \citealt{doi:10.1126/sciadv.adf8736} for a compilation of exoplanets with detections and non-detections of the helium excess.}.
 The sample of detections includes both hot Jupiters and lower mass planets, but lacks inflated hot Saturns owing to their intrinsic rarity below the 0.1 g~cm$^{-3}$ threshold.
@@
 
-The Habitable Zone Planet Finder (HPF) Helium Exospheres Collaboration has been conducting a survey of exoplanets to search for atmosphere loss via the\ion{He}{1} 10833 \AA metastable triplet.
+The Habitable Zone Planet Finder (HPF) Helium Exospheres program has been conducting a survey of exoplanets to search for atmosphere loss via the \ion{He}{1} 10833 \AA~ metastable triplet.
 The survey's multiple-visit sampling strategy has enabled a search for atmospheric loss at large out-of-transit separations from the planet, recently revealing giant tidal tails of Helium escaping the hot Jupiter HAT-P-32~b \citep{doi:10.1126/sciadv.adf8736}.
@@
 Its strong insolation ($T_\mathrm{eq}\sim2000\;$K) combined with \object{HAT-P-67 b}'s extremely low surface gravity ($\log{g_p}<2.3$~dex) makes it an exceptional candidate for strong atmospheric mass loss via Roche lobe overflow.
-Its $\sim$0.05 g~cm$^{-3}$ density places it below the 0.1 g~cm$^{-3}$ threshold predicted to exhibit runaway inflation by \citet{2023ApJ...945L..36T}.
+Its $\sim$0.05 g~cm$^{-3}$ density places it below the 0.1 g~cm$^{-3}$ threshold predicted to exhibit runaway inflation \citep{2023ApJ...945L..36T}.
 Figures \ref{fig:instellation} and \ref{fig:ThornFortUpdated} show how much of an outlier \hatpb~ is: large, low mass, and heavily irradiated.
@@
 The in-transit campaigns had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.
-We also obtained random-in-phase lower-priority P1-4 reconnaissance observations \citep{2007PASP..119..556S}.
+We also obtained random-in-phase lower-priority ``P1-P4'' reconnaissance observations \citep{2007PASP..119..556S}.
 These out-of-transit snapshot observations typically received 4 or fewer individual exposures.
@@
 These properties are broadly consistent with the previously reported values from \citet{2017AJ....153..211Z} and the updated ephemeris of \citet{2022ApJS..259...62I}.
-Figure \ref{fig:TESSoverview} shows an overview of all the TESS Sectors with a green GP trendline in green highlighting the out-of-transit modulations, and the exoplanet transit model in orange.
+Figure \ref{fig:TESSoverview} shows an overview of all the TESS Sectors with a Gaussian Process trendline in green highlighting the out-of-transit modulations, and the exoplanet transit model in orange.
 Figure \ref{fig:transit} shows the best-fit orbit overlaid in purple on the detrended TESS lightcurve, which is binned in the orange dots.
@@
 Figure \ref{fig:evolTracks} shows evolutionary tracks using the solar-metallicity MESA \citep{2011ApJS..192....3P,2013ApJS..208....4P,2015ApJS..220...15P} Isochrones and Stellar Tracks \citep[MIST;][]{2016ApJS..222....8D,2016ApJ...823..102C} for HAT-P-67, which has [Fe/H]$=-0.08\pm0.05$ \citep{2017AJ....153..211Z}.
-The tracks show that a 1.8 Gyr, 1.64 $M_\odot$ \hatp~ could be at the end of its main sequence lifetime (teal track), yielding a gradual rise in incident radiation over the lifetime of \hatpb.
-Alternatively, a 1.54 $M_\odot$ evolutionary track would send \hatp~ along the subgiant branch at an age over 2.2 Gyr, with a rapid 50\% increase in luminosity, potentially leading to ``re-inflation'' of the planet \citep{2021ApJ...909L..16T}.
+The tracks show that a 1.8 Gyr, 1.64 $M_\odot$ HAT-P-67 could be at the end of its main sequence lifetime (teal track), yielding a gradual rise in incident radiation over the lifetime of \hatpb.
+Alternatively, a 1.54 $M_\odot$ evolutionary track would send HAT-P-67 along the subgiant branch at an age over 2.2 Gyr, with a rapid 50\% increase in luminosity, potentially leading to ``re-inflation'' of the planet \citep{2021ApJ...909L..16T}.
 Either evolutionary track appears consistent with the observed SED, stellar surface gravity, and available constraints from spectral fitting.
@@
 The 13.8 hours of exposure, combined with \object{HAT-P-67 b}'s short ($P\sim4.8$ day) period, means that a large fraction of the orbit has been collected, with some phases (especially near transit) heavily sampled, and some other out-of-transit phases sampled more sparsely.
+The largest gap spans merely 0.18 in phase, as seen in the Equivalent Width time series in Figure \ref{fig:HPFtimeseries}.
 For visualization purposes, we constructed a 2-D intensity phase scan, binning in phase and wavelength, and spanning the entire orbit of \object{HAT-P-67 b}.
@@
 We construct a fractional residual absorption spectrum by subtracting off and re-normalizing to the non-varying baseline.
-We define the non-varying baseline spectrum as the average over phases $0.3-0.5$, which exhibited stable spectra with the least absorption.
+We define the non-varying baseline spectrum as the average over phases $0.4-0.5$, which exhibited stable spectra with the least absorption.
 Figure \ref{fig:HPFscanResid} shows that significant absorption can be seen as a few percent at $-0.37$ in phase, rising to 10\% just before and during transit.
@@
 Excess is confidently detected from phases $-$0.3 to $+$0.03.
-The full-width at half maximum (FWHM) of the feature is about 1.8-2.6~\AA, equivalent to a line-of-sight velocity distribution in the range of 50-75~km/s.
+The full-width at half maximum (FWHM) of the feature is about 1.8$-$2.6~\AA, equivalent to a line-of-sight velocity distribution in the range of 50-75~km/s.
 Individual fits to the He feature show a typical line center uncertainty $\pm0.1$~\AA~ or better.
@@
 
-The leading tail geometry seen in in HAT-P-67~b contrasts with the morphology of the HAT-P-32~b system, which exhibits giant symmetric tidal tails with comparable absorption depth preceding and trailing the planet \citep{doi:10.1126/sciadv.adf8736}.
-These systems represent two of the most extended features associated with exoplanets, and we compare and contrast them in the Section \ref{secDiscuss}.
+The leading tail geometry seen in HAT-P-67~b contrasts with the morphology of the HAT-P-32~b system, which exhibits giant symmetric tidal tails with comparable absorption depth preceding and trailing the planet \citep{doi:10.1126/sciadv.adf8736}.
+These systems represent two of the most extended features associated with exoplanets, and we compare and contrast them in Section \ref{secDiscuss}.
 
 \subsection{1D Parker wind models and mass loss rates}\label{pwinds}
-First we explore one-dimensional (1D) models, which offer ease of interpretation and rapid calculation.
+We explore one-dimensional (1D) models, which offer ease of interpretation and rapid calculation.
 We employ the open-source \texttt{p-winds} code \citep{2022A&A...659A..62D}, which implements a transonic 1D Parker wind model with radiative transfer of the Helium 10833 \AA~ triplet \citep{2018ApJ...855L..11O,2020A&A...636A..13L}.
@@
 Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 2\times 10^{13}$ g/s, and $T_0=14\,000$~K, with an XUV spectrum possessing $L_x/L_\mathrm{bol}=10^{-5}$.
-This mass loss rate would imply a characteristic lifetime of $\sim$1000 Myr.
+This mass loss rate would imply a characteristic lifetime of $<$1000 Myr.
 The model spectrum exhibits approximately the same equivalent width as our HPF observations, making it a hypothetical scenario among a family of partially degnerate solutions.
@@
 \subsection{Variable planetary wind}
-Figure \ref{fig:centroids} and \ref{fig:HPFperCampaign} show differences in the Helium line profiles over months-long and years-long timescales.
+Figure \ref{fig:HPFperCampaign} and \ref{fig:centroids} show differences in the Helium line profiles over months-long and years-long timescales.
 The line profiles are qualitatively similar, but show slightly different tendencies towards redshifting.
@@
 Nevertheless, we can project the time series trends in their Figures 3 and 4 to recreate a qualitative history and fate of \hatpb~ under the assumptions of XUV photoevaporation.
-Broadly, the planet would have started with an initial mass up to 50$\%$ greater than at present, with $R\sim\;$1.4 $R_\mathrm{Jup}$, for an initial density of $\sim$0.2 g/cm$^-3$.
+Broadly, the planet would have started with an initial mass up to 50$\%$ greater than at present, with $R\sim\;$1.4 $R_\mathrm{Jup}$, for an initial density of $\sim$0.2 g/cm$^{-3}$.
 It would lose mass at a rate of tens of Earth masses per Gyr for its 1 Gyr lifetime, expanding modestly until it reaches the critical $\sim$0.1 g/cm$^{-3}$ threshold, at which point the mass loss rate increases to its current value.
@@
 
-    This material is based upon work supported by the National Aeronautics and Space Administration under Grant Number 80NSSC21K0650 for the NNH20ZDA001N-ADAP:D.2 program and 80NSSC20K0257 for the XRP program issued through the Science Mission Directorate.
+    This material is based upon work supported by the National Aeronautics and Space Administration under Grant Number 80NSSC21K0650 for the ADAP program, 80NSSC20K0257 for the XRP program, and 80NSSC22K0181 through the TESS Guest Investigator program issued through the Science Mission Directorate.
+
+    C.V.M. acknowledges support from the Alfred P. Sloan Foundation under grant number FG-2021-16592.
+
+    Support for program HST-AR-15805.001-A was provided by NASA through a grant from the Space Telescope Science Institute, which is operated by the Associations of Universities for Research in Astronomy, Incorporated, under NASA contract NAS5- 26555.
 

### 2023-07-12 paper/paper1/ms.tex
Update affiliation-- Gummi, and grant acknowledgement--wdc

@@
 
-\author[0000-0002-3726-4881]{Zhoujian Zhang}\thanks{NASA Sagan Fellow}
+\author[0000-0002-3726-4881]{Zhoujian Zhang}\thanks{NASA Sagan Fellows}
 \affiliation{\UCSC}
@@
 
-\author[0000-0001-7409-5688]{Guðmundur Stefánsson}
+\author[0000-0001-7409-5688]{Guðmundur Stefánsson}\thanks{NASA Sagan Fellows}
 \affil{\Princeton}
-\affil{\RUSSELL}
 
@@
     These results are based on observations obtained with the Habitable-zone Planet Finder Spectrograph on the HET.
-The HPF team acknowledges support from NSF grants AST-1006676, AST-1126413, AST-1310885, AST-1517592, AST-1310875, ATI 2009889, ATI-2009982, AST-2108512, and the NASA Astrobiology Institute (NNA09DA76A) in the pursuit of precision radial velocities in the NIR.
+The HPF team acknowledges support from NSF grants AST-1006676, AST-1126413, AST-1310885, AST-1517592, AST-1310875, ATI 2009889, ATI-2009982, AST-2108512, AST-2108801, and the NASA Astrobiology Institute (NNA09DA76A) in the pursuit of precision radial velocities in the NIR.
 The HPF team also acknowledges support from the Heising-Simons Foundation via grant 2017-0494.

### 2023-07-12 paper/paper1/ms.tex
Final few tiny prose edits from my re-reading

@@
 The large size of the gas stream overfills the transit chord, which means both the advancing blue side and receding red side of the rotating star are nearly continuously obscured in this spin-orbit-aligned system \citep{2017AJ....153..211Z}.
-The planet transits near the stellar equator \citep{2017AJ....153..211Z}, meaning the transit chord covers about 10$\%$ of the projected stellar surface area.
+If the planet transits near the stellar equator \citep{2017AJ....153..211Z}, the transit chord covers about 10$\%$ of the projected stellar surface area.
 Hypothetically a nearly 100$\%$ opaque optically thick stream of gas covering only the transit chord could reproduce the observed 10$\%$ absorption excess.
@@
 We illustrate these differences in Figure \ref{fig:tf2018_theory}, which shades the mass-radius plane with predictions for the inflation timescale under HAT-P-67b-like conditions.
-The XUV irradiation timescale better matches the distribution of planets, with the 0.1 $g\;cm^{-3}$ density contour setting a conspicuous dividing line in density.
+The XUV irradiation timescale better matches the distribution of planets, with the 0.1g~cm$^{-3}$ density contour setting a conspicuous dividing line in density.
 The Ohmic dissipation shading predicts short inflation timescales extending into a region of Jupiter-mass planets with radii commonly observed.
@@
 
-Alternatively, Star Planet Magnetic Interaction (SPMI) could be at play.
+Alternatively, Star Planet Magnetic Interaction (SPMI) could be at play \citep{2018haex.bookE..25S}.
 In this scenario, the magnetic field of the planet permeates the space between the star and the planet.
@@
 We have presented a multi-year spectroscopic survey of HAT-P-67~b, a low density, heavily irradiated Saturn-mass (or lower) planet.
-We identified a large leading tail, with a much weaker trailing tail, which we found to be consistent with preferential dayside mass loss.
+We identified a large leading tail, with a much weaker trailing tail, which we found to be direct evidence of preferential dayside mass loss.
 HAT-P-67~b stands out as an outlier in the mass-radius plane, which we examine through the lens of different mechanisms for anomalous heating.
-Both XUV irradiation and Ohmic dissipation predict runaway inflation for such inflated hot Saturns, and we quantitatively weigh these two scenarios, finding XUV irrdation as more straightforwardly predictive of the overall demographic population of exoplanets observed to date.
+Both XUV irradiation and Ohmic dissipation predict runaway inflation for such inflated hot Saturns, and we quantitatively weigh these two scenarios, finding XUV irradiation as more straightforwardly predictive of the overall demographic population of exoplanets observed to date.
 

### 2023-07-12 paper/paper1/ms.tex

@@
 The Habitable Zone Planet Finder (HPF) Spectrograph Exospheres program aims to expand the search across a diverse range of planet and host star properties via the 10833 \AA~ Helium triplet, a sensitive probe of active atmospheric escape.
-Here we present a detection of 10\% absorption depth during transit spectroscopy of the highly irradiated, low-gravity, inflated hot Saturn HAT-P-67~b.
+Here we present a detection of up to 10\% absorption depth during transit spectroscopy of the highly irradiated, low-gravity, inflated hot Saturn HAT-P-67~b.
 The 13.8 hours of on-sky integration time over 39 nights sample the entire planet orbit, uncovering excess Helium absorption preceding the transit by up to 130 planetary radii in a large leading tail.
@@
 Episodic stellar wind gusts and other forms of astrophysical variability could also subdue the appearance of atmospheric escape, even where we expect it most.
-The 48 published non-detections of atmospheric escape \citep{2022arXiv221116243D} must encode these natural whims in a way that we have not yet disentangled.
+The over 57 published non-detections of atmospheric escape \citep{2022arXiv221116243D,2023arXiv230700967G} must encode these natural whims in a way that we have not yet disentangled.
 Nevertheless, we can boost our chances of witnessing active and significant atmospheric escape by targeting sources that seem predisposed to loss.
@@
 Detections of atmospheric escape are common among large planets with strong insolation.
-\hatpb---among the most inflated planets known---is an outlier.}
+\hatpb is among the most inflated planets known.}
     \label{fig:instellation}
@@
     \includegraphics[width=\linewidth]{figures/tf2018_fig2_update2023_HAT.png}
-    \caption{Mass-radius trends for inflated hot sub-Saturns and hot Jupiters, form modeled after Figure 2 from \citet{2018AJ....155..214T} and updated with NASA Exoplanet Archive confirmed planets.
+    \caption{Mass-radius trends for inflated hot sub-Saturns and hot Jupiters, with layout following Figure 2 of \citet{2018AJ....155..214T} and updated with NASA Exoplanet Archive confirmed planets.
 The trend lines show the mass-radius relationship for equilibrium temperatures of 500, 1000, 1250, 1500, and 2000 K, assuming the mean composition and mean heating efficiency from the original figure.
-HAT-P-67~b stands alone in a region defined by the lack of inflated sub-Saturns and explained by short lifetimes from runaway inflation and mass loss.}
+HAT-P-67~b ($\star$ symbol) stands alone in a region defined by the lack of inflated sub-Saturns and explained by short lifetimes from runaway inflation and mass loss.}
     \label{fig:ThornFortUpdated}
@@
 The GP model fit to the entire composite lightcurve yields a 4.7-day period; when fit to individual sectors alone the periods hover around 5.9 days.
-
-We can constrain the expected stellar rotation period based on the stellar radius estimate, $v\sin{i_\star}$, and the observation of the planet's orbital inclination $i_p\sim90^\circ$ from orbit fitting and Doppler tomography \citep{2017AJ....153..211Z}.
+The signal is weak enough, especially in Sectors 51-53, that \emph{TESS} instrumental systematics may contribute some of the out-of-transit modulation that we see in Figure \ref{fig:TESSoverview}.
+
+We can independently constrain the expected stellar rotation period based on the stellar radius estimate, $v\sin{i_\star}$, and the observation of the planet's orbital inclination $i_p\sim90^\circ$ from orbit fitting and Doppler tomography \citep{2017AJ....153..211Z}.
 We assume spin-orbit alignment, $i_\star \sim i_p$.
@@
 The planet orbital rest frame is shown as the black sine wave.
-Gaps in data at 10834-10836 \AA arise from telluric masking.
+Gaps in data at 10834-10836 \AA~ arise from telluric masking.
 Unmasked telluric lines are perceptible at 10825 \AA.}

### 2023-07-13 paper/paper1/ms.tex
Recenter figure to show absence of leading tail and delete paragraph-- reasonable but does not add too much

@@
 \begin{figure}
-    \includegraphics[width=0.8\linewidth]{figures/KeplerianShear_v0p3.png}
+    \includegraphics[width=0.8\linewidth]{figures/KeplerianShear_v0p5_alt.png}
     \caption{Schematic of Keplerian orbital shear.
@@
 \end{figure}
-
-Stellar wind confinement \citep{2022ApJ...926..226M} arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.
-A trailing tail may also be present, but may not undergo the same boost in density, and could be rapidly carried away alongside the stellar wind.
-A stellar-wind-induced asymmetry could result, yielding the appearance of a leading or trailing tail even if mass loss proceeds isotropically at first.
-Examples of this asymmetry can be seen in 3D MHD modeling of WASP 107~b \citep{2022ApJ...926..226M}.
 

### 2023-07-13 paper/paper1/ms.tex

@@
 
-\subsection{Physical mechanisms guiding the leading tail} \label{secLeading}
-Several physical phenomena control the geometry and extent of the escaping material.
+\subsection{Direct Evidence for Preferential Dayside Mass Loss} \label{secLeading}
+Several physical phenomena could conceivably control the geometry and extent of the escaping material.
+The stellar potential controls the overall geometry through tides and the Coriolis force, resulting in lobe morphologies that lead and trail the planet \citep{2019ApJ...873...89M}.
 Here we explore the three predominant dynamical effects: orbital shear, stellar wind confinement, and day-/night- side mass loss asymmetries.
@@
 
-\subsection{Direct Evidence for Preferential Dayside Mass Loss}\label{secPrimaFacie}
 The observation of such a prominent leading tail leads us to the inescapable conclusion that HAT-P-67~b is predominantly losing mass on the planet's dayside.
 An isotropic mass loss would manifest a comparably conspicuous trailing tail, which we do not observe.
-Stellar wind confinement alone should be expected to produce minor asymmetries such as those seen in the modeling of WASP 107~b \citep{2022ApJ...926..226M}, but in order to obtain the vastly dominant leading tail, an enhancing systematic effect is needed.
-The schematic illustration in Figure \ref{fig:KeplerianShear} depicts this interplay.
 
 Importantly, orbital shear, stellar wind confinement, preferential dayside mass loss, and radiative transfer must all conspire to create the conditions of high enough column density to populate the \ion{He}{1} metastable triplet to detectable levels while imbuing the velocity substructure that we see.
-The detailed 3D modeling of the interplay of these effects is beyond the scope of the current work, but is feasible with adaptations to existing 3D simulations.
+The detailed 3D modeling of the interplay of these effects is beyond the scope of the current work, but is feasible with adaptations to existing 3D simulations \citep{2022ApJ...926..226M}.
 
@@
     \texttt{muler} \citep{2022JOSS....7.4302G},
+    \texttt{lightkurve}, \citep{geert_barentsen_2019_2565212},
     \texttt{telfit} \citep{2014AJ....148...53G},
@@
 
-\clearpage
-
 \bibliography{ms}

### 2023-07-13 paper/paper1/ms.tex
Grammarly the whole thing, closes #39

@@
 The 13.8 hours of on-sky integration time over 39 nights sample the entire planet orbit, uncovering excess Helium absorption preceding the transit by up to 130 planetary radii in a large leading tail.
-This configuration can be understood as the escaping material overflowing its small Roche lobe, and advecting most of the gas into the stellar—and not planetary---rest frame, consistent with the Doppler velocity structure seen in the Helium line profiles.
+This configuration can be understood as the escaping material overflowing its small Roche lobe and advecting most of the gas into the stellar—and not planetary---rest frame, consistent with the Doppler velocity structure seen in the Helium line profiles.
 The prominent leading tail serves as direct evidence for dayside mass loss with a strong day-/night- side asymmetry.
@@
 
-Atmospheric escape appears to be a normal phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5$-$2.0~$R_\oplus$ planets within 100 day periods \citep{2017AJ....154..109F}.
+Atmospheric escape appears to be a normal phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5$-$2.0~$R_\oplus$ planets within 100-day periods \citep{2017AJ....154..109F}.
 The leading candidate physical mechanisms for this rapid transition between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2013ApJ...776....2L,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G,2023arXiv230200009B}.
-Whatever the cause, some large fraction of planets undergo transformative atmospheric escape and the signal should be widely discernable.
+Whatever the cause, some large fraction of planets undergo transformative atmospheric escape, and the signal should be widely discernable.
 Such signals have been searched for, and increasingly found, in many transiting planet systems with at least 28 detections to date \citep{2022arXiv221116243D}.
@@
 Inflated hot Saturns may either form \emph{in-situ} or effectively migrate to close-in orbital separations \citep{2018ARA&A..56..175D}, but once they arrive, the intense irradiation overheats the planet.
-This heating leads to runaway inflation and ultimately complete disintegration.
+This heating leads to runaway inflation and, ultimately, complete disintegration.
 In this scenario, the inflationary half-life becomes so short that the probability of observing members in the class decreases sharply with density, causing the apparent lack of inflated sub-Saturns \citep{2023ApJ...945L..36T}.
@@
 Recently, \citet{2023ApJ...945L..36T} showed that hot Saturns can undergo catastrophic erosion by stellar X-ray and Extreme UV (XUV) photoevaporative mass loss.
-Planets with densities less than $\sim$0.1 g~cm$^{-3}$ achieve mass loss rates of up to $10^3$ $M_\oplus /$Gyr setting up a positive feedback loop: the planet increases in radius, overflowing its Roche lobe, fueling greater mass loss, and increasing in radius even further.
+Planets with densities less than $\sim$0.1 g~cm$^{-3}$ achieve mass loss rates of up to $10^3$ $M_\oplus /$Gyr, setting up a positive feedback loop: the planet increases in radius, overflowing its Roche lobe, fueling greater mass loss, and increasing in radius even further.
 This vicious cycle systematically depopulates the mass-radius plane with a cliff defined by the $\rho_p \sim$0.1 g~cm$^{-3}$ dividing line.
@@
 \ion{He}{1} has resulted in at least 14 systems with detections \citep{2022arXiv221116243D}\footnote{See also Table~S1 of \citealt{doi:10.1126/sciadv.adf8736} for a compilation of exoplanets with detections and non-detections of the helium excess.}.
-The sample of detections includes both hot Jupiters and lower mass planets, but lacks inflated hot Saturns owing to their intrinsic rarity below the 0.1 g~cm$^{-3}$ threshold.
+The sample of detections includes both hot Jupiters and lower mass planets but lacks inflated hot Saturns owing to their intrinsic rarity below the 0.1 g~cm$^{-3}$ threshold.
 An observational picture of mass loss in inflated hot Saturns appears to be lacking for this reason.
@@
 In Section \ref{secAnalysis}, we refine the stellar and planet properties based on those observations, including distance, radius, and orbit re-analyses.
-The Helium excess detection is presented in Section \ref{secHeAnalysis}, with analysis of the signal's trend with orbital phase.
-We use this orbital structure to reconstruct the geometry and mass loss of the escaping Helium exosphere, with 1D Parker wind models (Section \ref{secResults}).
-We assess the physical mechanisms (Section \ref{secPhysMech}) giving rise to the escaping atmosphere, weighing the distinctive predictions of XUV irradation and Ohmic dissipation.
-Finally in Section \ref{secDiscuss}, we question the assumptions in our approach, discuss the overall congruence of predictions and observations, and highlight some implications for future exosphere studies.
+The Helium excess detection is presented in Section \ref{secHeAnalysis}, with an analysis of the signal's trend with orbital phase.
+We use this orbital structure to reconstruct the geometry and mass loss of the escaping Helium exosphere with 1D Parker wind models (Section \ref{secResults}).
+We assess the physical mechanisms (Section \ref{secPhysMech}) giving rise to the escaping atmosphere, weighing the distinctive predictions of XUV irradiation and Ohmic dissipation.
+Finally, in Section \ref{secDiscuss}, we question the assumptions in our approach, discuss the overall congruence of predictions and observations, and highlight some implications for future exosphere studies.
 
@@
 We observed HAT-P-67 with HPF for a total of 41 visits on 39 unique nights, with two of those nights observing both the east and west HET tracks.
-The total on-source integration time exceeds 13.8 hours, with $N=152$ individual spectra possessing typical signal-to-noise ratio of 80 per pixel.
+The total on-source integration time exceeds 13.8 hours, with $N=152$ individual spectra possessing a typical signal-to-noise ratio of 80 per pixel.
 Table \ref{tabHPFLog} summarizes the log of observations.
@@
 The small BERV still means the redward Helium line wing has significant telluric contamination between 10834$-$10836 \AA, but the core and blue line wings appear relatively pristine.
-Sky emission lines land in this region, but are more easily mitigated by HPF's simultaneous sky reference fiber.
+Sky emission lines land in this region but are more easily mitigated by HPF's simultaneous sky reference fiber.
 
@@
 The IAU naming convention would demand HAT-P-67A\emph{b} to refer to the planet, which orbits the primary.
-Hereafter, we simply drop the A designation for notational simplicity, since the wide companion will not factor into our analysis.
+Hereafter, we simply drop the A designation for notational simplicity since the wide companion will not factor into our analysis.
 
@@
 We fit the TESS lightcurve modulation with a quasiperiodic Gaussian Process (GP) model using \texttt{celerite} \citep{celerite1,celerite2}.
-The GP model fit to the entire composite lightcurve yields a 4.7-day period; when fit to individual sectors alone the periods hover around 5.9 days.
+The GP model fit to the entire composite lightcurve yields a 4.7-day period; when fit to individual sectors alone, the periods hover around 5.9 days.
 The signal is weak enough, especially in Sectors 51-53, that \emph{TESS} instrumental systematics may contribute some of the out-of-transit modulation that we see in Figure \ref{fig:TESSoverview}.
@@
 This range is typical for F stars that have not yet evolved too far into the subgiant branch \citep{2022ApJ...930....7A}.
-The geometrical constraint comports with the 4.7-day GP-based modulation period derived from the stitched TESS lightcurve, but is lower than the 5.9-day per-Sector fits, slightly preferring the lower 4.7-day modulation as the stellar rotation period.
+The geometrical constraint comports with the 4.7-day GP-based modulation period derived from the stitched TESS lightcurve but is lower than the 5.9-day per-Sector fits, slightly preferring the lower 4.7-day modulation as the stellar rotation period.
 The 5.9-day value would require a stellar radius over 3.2$R_\odot$, which appears implausible.
@@
 The semiamplitude prior acts as a mass constraint, excluding planets with masses so low that the observed radius would exceed the Hill radius (Roche lobe overflow).
-Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$ \ms, a relatively weak constraint, but consistent with broadly Saturn-mass planets.
+Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$ \ms, a relatively weak constraint but consistent with broadly Saturn-mass planets.
 Table \ref{tabOrbit} lists the revised properties, with minor differences from the existing values.
@@
 \subsection{HPF analysis II: \ion{He}{1} 10833 \AA} \label{secHeAnalysis}
-The preparation for analyzing the Helium feature followed a similar but slightly different procedure than that used for the RV, namely, we used \texttt{Goldilocks}\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}} for 2D \'echellogram reduction.
-This tool outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb \citep[LFC,][]{2019Optic...6..233M}.
+The preparation for analyzing the Helium feature followed a similar but slightly different procedure than that used for the RV.
+Namely, we used \texttt{Goldilocks}\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}} for 2D \'echellogram reduction.
+This tool outputs 1D extracted spectra for the target and two reference fibers: blank sky and a laser frequency comb \citep[LFC,][]{2019Optic...6..233M}.
 The observations were acquired with the LFC turned off, so this unilluminated spectrum was discarded.
@@
 
-The HET's fixed-altitude design means that the airmass remains relatively constant across all pointings, lowering the telluric line variability compared to fully steerable telescopes which may sample a wider range in airmasses.
+The HET's fixed-altitude design means that the airmass remains relatively constant across all pointings, lowering the telluric line variability compared to fully steerable telescopes, which may sample a wider range of airmasses.
 Variability in atmospheric conditions still makes it difficult to mitigate telluric lines to within the photon noise limit, so we masked spectral regions predicted to have significant telluric lines with a template generated by \texttt{telfit} \citep{2014AJ....148...53G}.
@@
     \caption{Overlay of all 152 individual HPF exposures of HAT-P-67, spanning 2020-2022.
-Variability is seen in the \ion{He}{1} 10833 \AA~ triplet near the vertical orange shaded band, but not in the adjacent Si line.
-These snapshot spectra were barycentric corrected, and continuum flattened with a linear fit to the regions in the blue vertical bands.
+Variability is seen in the \ion{He}{1} 10833 \AA~ triplet near the vertical orange shaded band but not in the adjacent Si line.
+These snapshot spectra were barycentric corrected and continuum flattened with a linear fit to the regions in the blue vertical bands.
 Sharp telluric absorption lines have been masked in regions near 10835 and 10837.5 \AA.}
@@
 
-Figure \ref{fig:HPFperCampaign} shows the spectra for four campaigns, with before and after spectra showing conspicuous excess absorption during transit and 1 day before transit, but negligible excess absorption after transit.
+Figure \ref{fig:HPFperCampaign} shows the spectra for four campaigns, with before and after spectra showing conspicuous excess absorption during transit and 1 day before transit but negligible excess absorption after transit.
 The individual transits show significant morphological variation, with substructure in the bulk line-of-sight velocity distribution.
@@
 A large absorption signal can be seen preceding transit ingress, with some significant absorption evident before $-0.2$ in phase.
-The egress drop-off is extremely sharp, with almost no excess absorption directly after transit, as seen in the Equivalent Width (EW) timeseries (Figure \ref{fig:HPFtimeseries}).
+The egress drop-off is extremely sharp, with almost no excess absorption directly after transit, as seen in the Equivalent Width (EW) time series (Figure \ref{fig:HPFtimeseries}).
 We construct a fractional residual absorption spectrum by subtracting off and re-normalizing to the non-varying baseline.
@@
 HAT-P-67~b exhibits blending of all three components ($J=$ 0, 1, and 2) into a single broad Gaussian-like feature seen in Figure \ref{fig:HPFheliumOverview}.
-The mere observation of this broadening implies that HAT-P-67~b probes a larger velocity dispersion than typical measurements, and may be associated with either a higher gas temperature, complex planetary wind flows, or some mix of both.
-Whatever the cause, we treat the feature as a single Gaussian line for the pupose of estimating bulk characteristics of the Helium excess absorption feature.
+The mere observation of this broadening implies that HAT-P-67~b probes a larger velocity dispersion than typical measurements and may be associated with either a higher gas temperature, complex planetary wind flows, or some mix of both.
+Whatever the cause, we treat the feature as a single Gaussian line for the purpose of estimating bulk characteristics of the Helium excess absorption feature.
 We restricted the fitting to the 10828$-$10838 \AA~region of the residual spectra.
@@
 Measurements from April 2022 and May 2020 transits partially overlap in phase coverage while yielding slightly different line centroid locations.
-Both time series sequences appear consistent with near-zero bulk restframe velocity, but with significant variability in the line profile substructure.
+Both time series sequences appear consistent with near-zero bulk restframe velocity but with significant variability in the line profile substructure.
 The May 2020 sequence shows a slight trend towards alignment with the planet restframe.
@@
 
-Overall this pattern of velocity centroids appears consistent with the majority of the gas rapidly obeying the stellar restframe, but with a large spread in the line-of-sight velocity distribution as we would expect from a range of launch angles.
+Overall this pattern of velocity centroids appears consistent with the majority of the gas rapidly obeying the stellar restframe but with a large spread in the line-of-sight velocity distribution, as we would expect from a range of launch angles.
 We revisit the interpretations and caveats for this substructure in the next sections.
@@
 The recent discovery of giant tidal tails in HAT-P-32~b \citep{doi:10.1126/sciadv.adf8736} provides an additional anchor.
-HAT-P-32~b is in many ways the most analogous known system to HAT-P-67~b, having comparably low mass and comparably large radius for similar insolation around an F star.
+HAT-P-32~b is in many ways the most analogous known system to HAT-P-67~b, having comparably low mass and a comparably large radius for similar insolation around an F star.
 In HAT-P-32~b the planetary interpretation is unambiguous owing to the different stellar rotation and orbital periods.
@@
 The SED shows that the XUV corona model does not extend redward to 2600 \AA~photons capable of ionizing out of the 2 $^3$S Helium metastable state.
-This apparent deficit should be negligible, since the F spectral type obtains most of its NUV photons ($\lambda\sim2600$ \AA) from the Wein side of the photospheric spectrum, so the hardness of the radiation stems mostly from the assumptions of the corona flux level.
+This apparent deficit should be negligible since the F spectral type obtains most of its NUV photons ($\lambda\sim2600$ \AA) from the Wein side of the photospheric spectrum, so the hardness of the radiation stems mostly from the assumptions of the corona flux level.
 The wavelength-dependent cross section for absorption (not shown) is largest just blueward of the ionization thresholds, so the differences in the spectrum between 504 and 1000 \AA~ have relatively little impact on the overall ionization out of the metastable state.
@@
 This mass loss rate would imply a characteristic lifetime of $<$1000 Myr.
-The model spectrum exhibits approximately the same equivalent width as our HPF observations, making it a hypothetical scenario among a family of partially degnerate solutions.
+The model spectrum exhibits approximately the same equivalent width as our HPF observations, making it a hypothetical scenario among a family of partially degenerate solutions.
 
@@
 \noindent yielding an incredibly short $<$5 Myr timescale for \hatpb, assuming a typical $\epsilon\sim0.01$.
-The order of magnitude of this inflation timescale is so fleetingly short that---according to this scenario---\hatpb~must be in the runaway stage of inflation, rapidly losing mass, and growing in surface area to fuel a positive feedback loop.
+The order of magnitude of this inflation timescale is so fleetingly short that---according to this scenario---\hatpb~must be in the runaway stage of inflation, rapidly losing mass and growing in surface area to fuel a positive feedback loop.
 Under this interpretation, \hatpb~ would represent an example of a new category of planet system that is doomed to evaporate entirely due to the Ohmic dissipation mechanism, as predicted by \citet{2011ApJ...738....1B}.
@@
 
-Second, numerical simulations \citep{2013ApJ...763...13W} and analytic theory \citep{2016ApJ...819..116G} indicate that Ohmic dissipation can stall the contraction of hot Jupiters, but cannot easily ``re-inflate'' them after having undergone a traditional cooling curve.
+Second, numerical simulations \citep{2013ApJ...763...13W} and analytic theory \citep{2016ApJ...819..116G} indicate that Ohmic dissipation can stall the contraction of hot Jupiters but cannot easily ``re-inflate'' them after having undergone a traditional cooling curve.
 Heat transfer from the atmosphere to a cooled core appears to proceed too slowly, on the order of tens of Gyr \citep{2016ApJ...819..116G}.
@@
 
-We conclude that reinflation likely does not have a significant effect on the evolution of HAT-P-67~b: inflation timescales remain relatively unchanged over the planet lifetime, despite a 50\% spike in incident radiation in the subgiant scenario.
+We conclude that reinflation likely does not have a significant effect on the evolution of HAT-P-67~b: inflation timescales remain relatively unchanged over the planet's lifetime, despite a 50\% spike in incident radiation in the subgiant scenario.
 The reason is subtle, as we describe next.
@@
 The planet's equilibrium temperature increases as the stellar luminosity gradually increases on the main sequence.
-The second panel from top shows the corresponding estimate for anomalous heating efficiency from \citet{2018AJ....155..214T}.
+The second panel from the top shows the corresponding estimate for anomalous heating efficiency from \citet{2018AJ....155..214T}.
 The Ohmic dissipation model makes predictions for runaway inflation, depending on the incident stellar flux.
@@
     \caption{Runaway inflation timescale in the exoplanet mass-radius diagram.
-The shading of the left panel shows $\tau_\mathrm{infl}$ from Ohmic dissipation, the right panel shows $\tau_\mathrm{infl}\equiv M/\dot{M}$ from photoionization-driven mass loss.
+The shading of the left panel shows $\tau_\mathrm{infl}$ from Ohmic dissipation; the right panel shows $\tau_\mathrm{infl}\equiv M/\dot{M}$ from photoionization-driven mass loss.
 Individual planets with confident mass and radius detections are shown as small black dots.
@@
 The discovery of large Helium tails in HAT-P-32~b \citep{doi:10.1126/sciadv.adf8736} and now HAT-P-67~b suggest that the identification of these exospheric grazers may be achievable with current instrumentation and possibly existing archival data from near-IR RV-planet searches.
-Non-transiting, strongly irradiated planets with well-constrained orbits may make ideal targets for detection of this phenomenon.
+Non-transiting, strongly irradiated planets with well-constrained orbits may make ideal targets for the detection of this phenomenon.
 
@@
 
-We have presented a multi-year spectroscopic survey of HAT-P-67~b, a low density, heavily irradiated Saturn-mass (or lower) planet.
+We have presented a multi-year spectroscopic survey of HAT-P-67~b, a low-density, heavily irradiated Saturn-mass (or lower) planet.
 We identified a large leading tail, with a much weaker trailing tail, which we found to be direct evidence of preferential dayside mass loss.
@@
 The large signal should be perceptible in other spectral tracers, such as metal lines in the UV.
-We offer a list other planets that may be likely to exhibit mass loss under the Ohmic dissipation and XUV irradiation scenarios.
+We offer a list of other planets that may be likely to exhibit mass loss under the Ohmic dissipation and XUV irradiation scenarios.
 

### 2023-07-13 paper/paper1/ms.tex
Prep paper for submission
Whoops, ctrl-x, ctrl-v missed MIT affiliation

@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[linenumbers, twocolumn]{aastex631}
 \bibliographystyle{aasjournal}
@@
 \newcommand{\HET}{Hobby-Eberly Telescope, The University of Texas at Austin, 2515 Speedway, Austin, TX 78712, USA}
+\newcommand{\MIT}{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
 
@@
 % This is the version destined for Overleaf on June 7th, 2023.
-\title{A Large and Variable Leading Tail of Helium in a Sub-Saturn Undergoing Runaway Inflation}
+\title{A Large and Variable Leading Tail of Helium in a Hot Saturn Undergoing Runaway Inflation}
 
@@
 \affil{\Princeton}
+
+\author[0000-0001-7246-5438]{Andrew Vanderburg}
+\affil{\MIT}
 
@@
 
-\clearpage
-\pagebreak
-
 \appendix
@@
 
-\begin{figure}[b]
+\begin{figure}
     \includegraphics[width=0.5\linewidth]{figures/Ca8662_phase_2D_diagram_resid.png}

### 2023-07-13 paper/paper1/ms.tex
Collapse folders to a flat directory with all figures and tables

@@
     \centering
-    \includegraphics[width=\linewidth]{figures/HAT-P-67b_radius_valley.png}
+    \includegraphics[width=\linewidth]{HAT-P-67b_radius_valley.png}
     \caption{Overview of exoplanet demographics.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/tf2018_fig2_update2023_HAT.png}
+    \includegraphics[width=\linewidth]{tf2018_fig2_update2023_HAT.png}
     \caption{Mass-radius trends for inflated hot sub-Saturns and hot Jupiters, with layout following Figure 2 of \citet{2018AJ....155..214T} and updated with NASA Exoplanet Archive confirmed planets.
@@
     \startdata
-    \input{tables/observation_log.tex}
+    \input{observation_log.tex}
     \enddata
@@
     \centering
-    \includegraphics[width=0.98\linewidth]{figures/TESS_HAT-P-67b_overview.png}
+    \includegraphics[width=0.98\linewidth]{TESS_HAT-P-67b_overview.png}
     \caption{Overview of all available TESS Sectors showing 24 full or partial transits with 34 visits with HPF (vertical gray bars), 7 of which coincide with transits.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/best_fit_orbit.png}
+    \includegraphics[width=\linewidth]{best_fit_orbit.png}
     \caption{Best fit orbit overlaid on the composite TESS lightcurve.
@@
 
-\input{tables/revise_props_tbl.tex}
+\input{revise_props_tbl.tex}
 
@@
     \centering
-    \includegraphics[width=0.98\linewidth]{figures/MIST_only_HATP.png}
+    \includegraphics[width=0.98\linewidth]{MIST_only_HATP.png}
     \caption{MIST evolutionary model tracks for HAT-P-67.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/HAT-P-67b_rv.pdf}
+    \includegraphics[width=\linewidth]{HAT-P-67b_rv.pdf}
     \caption{RV orbit fit including both HPF and Keck HIRES data points.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/HAT_P_67b_He_spectrum.png}
+    \includegraphics[width=\linewidth]{HAT_P_67b_He_spectrum.png}
     \caption{Overlay of all 152 individual HPF exposures of HAT-P-67, spanning 2020-2022.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/HAT_P_67b_byCampaign_Spectra.png}
+    \includegraphics[width=\linewidth]{HAT_P_67b_byCampaign_Spectra.png}
     \caption{Four observing campaigns centered on an in-transit epoch with before-and-after visits typically separated by 1 night.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/HAT_P_67b_Helium10830EW_byCampaign.png}
+    \includegraphics[width=\linewidth]{HAT_P_67b_Helium10830EW_byCampaign.png}
     \caption{Equivalent Width lightcurve of Helium absorption in HAT-P-67b.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/phase_2D_diagram_resid.png}
+    \includegraphics[width=\linewidth]{phase_2D_diagram_resid.png}
     \caption{Absorption depth phase scan over the entire HAT-P-67b orbit from 41 visits with HPF.
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/centroid_overview10833.png}
+    \includegraphics[width=\linewidth]{centroid_overview10833.png}
     %\hskip-3em
-    %\subfloat{\includegraphics[width=4cm]{figures/centroid_inset10833.png}}
+    %\subfloat{\includegraphics[width=4cm]{centroid_inset10833.png}}
     \caption{Line centroid positions of the  \ion{He}{1} 10833 \AA~ feature.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/XUV_flux_schematic.png}
+    \includegraphics[width=\linewidth]{XUV_flux_schematic.png}
     \caption{Synthetic XUV radiation scenarios for \hatpb.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/pwinds_May2020_14000_2e13Mdot_medXUV_formal_rv_rev.png}
+    \includegraphics[width=\linewidth]{pwinds_May2020_14000_2e13Mdot_medXUV_formal_rv_rev.png}
     \caption{Simulated 1D Parker wind model of Helium absorption in \hatpb.
@@
 \begin{figure}
-    \includegraphics[width=0.8\linewidth]{figures/KeplerianShear_v0p5_alt.png}
+    \includegraphics[width=0.8\linewidth]{KeplerianShear_v0p5_alt.png}
     \caption{Schematic of Keplerian orbital shear.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/reinflation_MIST2.png}
+    \includegraphics[width=\linewidth]{reinflation_MIST2.png}
     \caption{Conceivable evolutionary scenarios for \hatpb.
@@
 \begin{figure*}[t]
-    \includegraphics[width=\linewidth]{figures/thorn2023_theory.png}
+    \includegraphics[width=\linewidth]{thorn2023_theory.png}
     \caption{Runaway inflation timescale in the exoplanet mass-radius diagram.
@@
     \startdata
-    \input{tables/tab_HeSM.tex}
+    \input{tab_HeSM.tex}
     \enddata
@@
 \begin{figure}
-    \includegraphics[width=0.5\linewidth]{figures/Ca8662_phase_2D_diagram_resid.png}
+    \includegraphics[width=0.5\linewidth]{Ca8662_phase_2D_diagram_resid.png}
     \caption{Non-detection of variability in the Calcium IR Triplet line at 8862 \AA.  No other HPF lines appear to show any variability.}

### 2023-07-13 paper/paper1/ms.tex
Submitted version of the paper!
Ok, this is the revised submission with the shorter abstract!

@@
 
-% and more...
+% This is the submitted version: July 13, 2023 at 3:13 pm central 
+% Revised at 3:31 pm to have a shorter abstract
 
@@
     Atmospheric escape shapes the fate of exoplanets, with statistical evidence for transformative mass loss imprinted across the mass-radius-insolation distribution.
-The Habitable Zone Planet Finder (HPF) Spectrograph Exospheres program aims to expand the search across a diverse range of planet and host star properties via the 10833 \AA~ Helium triplet, a sensitive probe of active atmospheric escape.
-Here we present a detection of up to 10\% absorption depth during transit spectroscopy of the highly irradiated, low-gravity, inflated hot Saturn HAT-P-67~b.
+Here we present transit spectroscopy of the highly irradiated, low-gravity, inflated hot Saturn HAT-P-67~b.
+The Habitable Zone Planet Finder (HPF) spectra show a detection of up to 10\% absorption depth of the 10833 \AA~ Helium triplet.
 The 13.8 hours of on-sky integration time over 39 nights sample the entire planet orbit, uncovering excess Helium absorption preceding the transit by up to 130 planetary radii in a large leading tail.
-This configuration can be understood as the escaping material overflowing its small Roche lobe and advecting most of the gas into the stellar—and not planetary---rest frame, consistent with the Doppler velocity structure seen in the Helium line profiles.
+This configuration can be understood as the escaping material overflowing its small Roche lobe and advecting most of the gas into the stellar---and not planetary---rest frame, consistent with the Doppler velocity structure seen in the Helium line profiles.
 The prominent leading tail serves as direct evidence for dayside mass loss with a strong day-/night- side asymmetry.
@@
 We employ 1D Parker wind models to estimate the mass loss rate, finding values on the order of $2\times10^{13}$ g/s, with large uncertainties owing to the unknown XUV flux of the F host star.
-The large mass loss in HAT-P-67~b represents a valuable example of an inflated hot Saturn, a class of planets recently identified to be rare as their atmospheres are predicted to evaporate quickly.
+The large mass loss in HAT-P-67 b represents a valuable example of an inflated hot Saturn, a class of planets recently identified to be rare as their atmospheres are predicted to evaporate quickly.
 We contrast two physical mechanisms for runaway evaporation: Ohmic dissipation and XUV irradiation, slightly favoring the latter.

### 2023-08-10 paper/paper1/ms.tex
Just made sure the overleaf is synced-- it is
This was the version submitted to arXiv (we had to turn off linenumbers)
whitespace changes and had to keep intermediate bbl for submission
Addressing the referee report

@@
-\documentclass[linenumbers, twocolumn]{aastex631}
+\documentclass[linenumbers, twocolumn, trackchanges]{aastex631}
 \bibliographystyle{aasjournal}
@@
 
-% This is the version destined for Overleaf on June 7th, 2023.
 \title{A Large and Variable Leading Tail of Helium in a Hot Saturn Undergoing Runaway Inflation}
@@
 \affil{\Steward}
-%\affil{\UTAustin}
 
@@
 % This is the submitted version: July 13, 2023 at 3:13 pm central
-% Revised at 3:31 pm to have a shorter abstract
+% Revised at 3:31 pm to have a shorter abstract !
 
@@
 The abrupt dropoff in helium excess at planet egress is conspicuous.
-
-% Describe construction of residual spectra
 
@@
 Some sectors exhibit lower amplitudes.
-The conventional interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8-day orbital period of planet b.
+The conventional interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage\edit1{s}---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8-day orbital period of planet b.
 The cause for such orbital and rotational synchronization would then be either coincidence or secular star-planet tidal interactions.

### 2023-08-10 paper/paper1/ms.tex
referee comment 5-- summary and ms edits

@@
 Finally, we consider the prospect that the planetary mass of HAT-P67b is much lower than the 1-$\sigma$ estimate, such that the white-light planetary radius \emph{is} the Hill radius (we have previously assumed the Hill radius is 2.7 planetary radii).
-This extreme scenario could manifest enormous mass loss rates, with the atmosphere's reservoir of mass fleeing the gravitational potential well directly, without the cushion of an exosphere.
-This terminal Roche Lobe overflow should have observational consequences.
-In particular, heavy elements would easily leak into the planetary wind, yielding possibly many observable metal lines in the UV.
+This \edit1{true Roche Lobe Overflow (RLO)} scenario could manifest enormous mass loss rates, with the atmosphere's reservoir of mass fleeing the gravitational potential well directly, without the cushion of an exosphere.
+\edit1{We propose that this terminal RLO should have a subtle-but-distinctive observational consequence.
+Since heavy elements have smaller scale heights than hydrogen/helium, the observed ratio of heavy element to lighter element lines should be inversely correlated with the number of scale heights separating the white-light radius from the Hill radius.
+All else equal, we would expect an anomalously large ratio of heavy metals compared to hydogen/Helium in the RLO case.
+The extremely large Helium excess absorption, combined with the possibility of enhanced metal line depths in HAT-P-67~b---however uncertain---motivates a search for metal-line spectral tracers that may have previously been dismissed as too unlikely to detect.}
+
+\edit1{Establishing the scale of this metal enhancement would be difficult.
+First, XUV-driven mass loss would also carry away metals in the upper atmosphere, and so careful modeling would have to be established to predict what enhancement could be reasonably expected.
+Second, few exoplanets currently have multiple atmospheric escape tracers measured, so a purely observational detection would be challenging, not to mention needing to account for metallicity.
+Eventually such a phenomenon may be possible as our inventory of systems grows and our measurement precisions improve.
+A direct mass measurement via improved RV precision would be a more direct way way to establish whether HAT-P-67~b is truly in a Roche Lobe Overflow scenario.}
 

### 2023-08-10 paper/paper1/ms.tex
Referee report item 4b

@@
   \caption{Runaway inflation timescale in the exoplanet mass-radius diagram.
-The shading of the left panel shows $\tau_\mathrm{infl}$ from Ohmic dissipation; the right panel shows $\tau_\mathrm{infl}\equiv M/\dot{M}$ from photoionization-driven mass loss.
+The shading of the left panel shows $\tau_\mathrm{infl}$ from Ohmic dissipation; the right panel shows $\tau_\mathrm{infl}\equiv M/\dot{M}$ from photoionization-driven mass loss \edit1{(assuming fixed $F_{XUV}\sim2\times 10^5$ erg/s/cm$^2$)}.
 Individual planets with confident mass and radius detections are shown as small black dots.
-Helium non-detections are shown in red squares, atmospheric escape detections from any origin in green circles \citep{2022arXiv221116243D}.
+Helium non-detections are shown in red squares, atmospheric escape detections from any \edit1{tracer} in green circles \citep{2022arXiv221116243D}.
 Under either scenario, \hatpb~ resides in a sparsely populated region with a short inflationary timescale, making it unstable to runaway evaporation with large mass loss expected.
@@
 The key figure-of-merit can be distilled to $\tau_\mathrm{infl}$, which can be thought of as an atmospheric escape spectroscopy metric \citep{2018PASP..130k4401K} for inflated planets in the shaded regime of Figure \ref{fig:tf2018_theory}.
-Table \ref{tabHeSM} presents the rank-ordered list of planets by this metric, indicating that they are mostly smaller and more massive than \hatpb.
+\edit1{The choice to adopt $\tau_\mathrm{infl}$ facilitates comparison between Ohmic Dissipation and XUV Irradiation.
+This choice introduces the plotting artifact that the dashed white line of 0.1 g/cm$^3$ density does not line up with contours of equal $\tau_\mathrm{infl}$ shading (c.f.
+\citealt{2023ApJ...945L..36T}), but both contours appear to approximately resemble the cliff in the population of inflated sub-Saturns.
+The color shading was derived by scaling HAT-P-67~b-like properties, with a fixed $F_{XUV}\sim2\times 10^5$ erg/s/cm$^2$, so the color coding should be considered as a coarse comparison between the two physical mechanisms, since individual systems should exhibit significant scatter in $F_{XUV}$.}  Table \ref{tabHeSM} presents the rank-ordered list of planets by this metric, indicating that they are mostly smaller and more massive than \hatpb.
 Only KELT-11~b shows a shorter nominal inflationary timescale than \hatpb, owing to its low mass and equilibrium temperature residing closer to the peak of $\epsilon_G(T_\mathrm{eq})$.

### 2023-08-10 paper/paper1/ms.tex
Ohmic dissipation-dominated implies RLO, we should be more upfront about that

@@
 
-\subsection{Ohmic dissipation-driven mass loss}
+\subsection{Ohmic dissipation-driven mass loss}\label{secOhmicD}
+\edit1{Ohmic dissipation can be visualized by considering the qualitative extreme of zero XUV flux.
+Here, we would predict zero radius inflation and therefore no mass loss.
+The docile upper atmosphere would lose atoms one-by-one through Jeans escape, an insignificant trickle.
+Instead, Ohmic dissipation heating increases the radius of the planet while preserving that low mass loss rate for a long time, until a critical moment: when the planet radius reaches the Hill radius, resulting in Roche Lobe Overflow.
+So XUV irradiation and Ohmic dissipation could differ in 1) the timing and duration of their mass loss phase, and 2) the mass/radius/semi-major-axis conditions needed to expect the mass loss phase for a given system.
+Since we only have a mass upper limit, HAT-P-67~b could have a mass as low as $M<0.05M_\mathrm{Jup}$, which would shrink its Hill radius to the observed planetary radius, causing the profound mass loss we see.
+The prospect of this scenario motivates quantitative consideration of Ohmic dissipation.}
+
 The Ohmic dissipation mechanism made two key observable predictions.
@@
 \subsection{Weighing the causes for a lack of sub-Saturns}\label{secLackofSaturns}
-
 When applied to an ensemble of planet systems, both the XUV irradiation and Ohmic dissipation mechanisms expect a void in the planet mass-radius plane.
@@
 
-Finally, we consider the prospect that the planetary mass of HAT-P67b is much lower than the 1-$\sigma$ estimate, such that the white-light planetary radius \emph{is} the Hill radius (we have previously assumed the Hill radius is 2.7 planetary radii).
+Finally, we consider the prospect alluded to in \S \ref{secOhmicD} that the planetary mass of HAT-P67~b is much lower than the 1-$\sigma$ estimate, such that the white-light planetary radius \emph{is} the Hill radius (we have previously assumed the Hill radius is 2.7 planetary radii).
 This \edit1{true Roche Lobe Overflow (RLO)} scenario could manifest enormous mass loss rates, with the atmosphere's reservoir of mass fleeing the gravitational potential well directly, without the cushion of an exosphere.
+
 \edit1{We propose that this terminal RLO should have a subtle-but-distinctive observational consequence.

### 2023-09-07 paper/paper1/ms.tex
Referee report item 4
item 3 from the referee report (working backwards)

@@
 
-Finally, we detect a much weaker but still significant post-egress blue-shifted absorption.
+Finally, we detect a much weaker but still significant post-egress blue-shifted absorption \edit1{perceptible in Figure \ref{fig:HPFscanResid} at 0.1 in phase and about 10831 \AA}.
 This lobe appears to decrease linearly in wavelength, corresponding to a characteristic blueshift increasing from near zero at transit midpoint to 80~km/s at 12 hours after transit.
@@
 Inefficient grazing incidence heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemispherical shape, but more concentration along the star-planet line.
-The gas increasingly experiences the star's Keplerian potential past the Roche lobe, accelerating in the direction of orbital motion, $+x$.
-The accelerating column eventually overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.
+\edit1{The gas increasingly experiences Keplerian shear past the Roche lobe, manifesting as prograde acceleration.
+In the rotating frame, the Coriolis effect causes the inward-moving gas to advance ahead of the planet.
+In the inertial frame, the gas is launched onto an orbit with a smaller periapse than the planet, and so runs ahead.
+The accelerating flow} eventually overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.
 The mass loss has to be large enough to shield the material to make it observable in the metastable \ion{He}{1} 10833 \AA~triplet.
@@
 
+\edit1{\subsection{Prospect for orbital evolution}
+  Content here...}
+
 \subsection{Cause for stellar modulation}

### 2023-09-07 paper/paper1/ms.tex
orbital evolution

@@
 \edit1{\subsection{Prospect for orbital evolution}
-  Content here...}
+  Evaporating planets may lose a large fraction of their mass through Roche lobe overflow \citep{2014ApJ...793L...3V,2015ApJ...813..101V}.
+These profoundly eroded planets should exhibit significant orbital evolution.
+The extent and direction of such orbital evolution depends on the specific angular momentum loss, integrated over the mass loss history of the planet.
+The observations presented here indicate a mass loss vector perpendicular to the orbit and towards the star.
+We can reconstruct the starting orbit if we assume the current mass loss vector has been constant throughout its mass loss history.
+Following \citet{2014ApJ...793L...3V} and \citet{2023ApJ...945L..36T} we can constrain the change in semi-major axis, a:
+  \begin{equation}
+    \frac{\dot{a}}{a} = -2 \frac{\dot{M}}{M}\left (1 - \frac{M}{M_\star} \right ).
+  \end{equation}
+}
 

### 2023-09-07 paper/paper1/ms.tex
orbital evolution

@@
 The observations presented here indicate a mass loss vector perpendicular to the orbit and towards the star.
-We can reconstruct the starting orbit if we assume the current mass loss vector has been constant throughout its mass loss history.
-Following \citet{2014ApJ...793L...3V} and \citet{2023ApJ...945L..36T} we can constrain the change in semi-major axis, a:
-  \begin{equation}
-    \frac{\dot{a}}{a} = -2 \frac{\dot{M}}{M}\left (1 - \frac{M}{M_\star} \right ).
-  \end{equation}
+A large enough mass loss rate would be evinced as a changing orbital period $\dot{P}$, which would manifest as a weak linear trend in Transit Timing Variations (TTVs).
+\citet{2017AJ....153..211Z} searched for TTVs in their ground based photometry, which spanned a baseline of about 160 days with 6 data points.
+The \emph{TESS} photometry provides over 24 full or partial transits over 8 years later, yielding a much larger lever arm for gauging the prospect of TTVs.
+Table \ref{tabOrbit} compares the period determined separately between these two datasets.
+The TESS-based period is 1-$\sigma$ longer than the \citet{2017AJ....153..211Z} period.
+A joint orbit fit of both the original lightcurves, existing and planned TESS lightcurves, and higher precision RVs will be able to better constrain orbital evolution.
+A non-detection of TTVs could still provide meaningful constraints on extreme mass loss scenarios.
 }

### 2023-09-18 paper/paper1/ms.tex
Revise Figure 14, related to Issue #45

@@
 
-\begin{figure}
-  \includegraphics[width=0.8\linewidth]{KeplerianShear_v0p5_alt.png}
-  \caption{Schematic of Keplerian orbital shear.
-Locations outside the Roche lobe experience orbital shear from the Keplerian potential.
-A wind launched primarily from the dayside will tend to form a leading tail.}
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.95\textwidth]{Fig14_KeplerianShear_revised.png}
+  \caption{\edit1{A conceivable steady-state path of mass loss from the HAT-P-67~b system.
+The inset depicts mass loss rates achieving maximum at the sub solar point, with a fall off towards zero near the planet terminator.
+The small Roche lobe of merely $<2.7R_p$ means that gas promptly experiences Keplerian orbital shear after launching past the L1 point.}  A wind launched primarily from the dayside will tend to form a leading tail.
+\edit1{The orbital overview depicts the path of the mass loss initially towards the star, decelerating into the headwind of the stellar wind, and then reversing direction outward in a blueshift.
+The observed redshift and blueshift of any given sightline will depend on the Helium ionization fraction, which depends on the shielding of gas along the line of sight.} }
   \label{fig:KeplerianShear}
-\end{figure}
+\end{figure*}
 

### 2023-12-04 paper/paper1/ms.tex

--- 2023-09-07 paper/paper1/ms.tex
@@
 The planet wind initially launches radially outward from the exobase, with the strongest wind located near the sub-stellar point, the line connecting the planet to the star along the vertical axis in the figure.
-Inefficient grazing incidence heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits not a hemispherical shape, but more concentration along the star-planet line.
+Inefficient grazing incidence heating near the terminator subdues the mass loss in the $x-$direction, meaning that this wind exhibits concentration along the star-planet line.
 \edit1{The gas increasingly experiences Keplerian shear past the Roche lobe, manifesting as prograde acceleration.
@@
 In the inertial frame, the gas is launched onto an orbit with a smaller periapse than the planet, and so runs ahead.
-The accelerating flow} eventually overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.
-The mass loss has to be large enough to shield the material to make it observable in the metastable \ion{He}{1} 10833 \AA~triplet.
-
-\begin{figure}
-  \includegraphics[width=0.8\linewidth]{KeplerianShear_v0p5_alt.png}
-  \caption{Schematic of Keplerian orbital shear.
-Locations outside the Roche lobe experience orbital shear from the Keplerian potential.
-A wind launched primarily from the dayside will tend to form a leading tail.}
+The accelerating flow} rapidly overtakes the planet completely, with the prospect of extending to hundreds of planetary radii.
+\edit1{The overview of the orbit in Figure \ref{fig:KeplerianShear} shows one conceivable path of the gas motion.
+The exact extent of the path depends on several unknowns.
+For example, } the column density has to be large enough to shield the material to make it observable in the metastable \ion{He}{1} 10833 \AA~triplet.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.95\textwidth]{Fig14_KeplerianShear_revised.png}
+  \caption{\edit1{Top-down illustration of mass loss from the HAT-P-67~b system.
+A planetary wind launched primarily from the dayside will tend to form a leading tail.
+The strongest dayside mass loss will occur at the sub-solar point, with a fall off towards zero near the planet terminator.
+The small Roche lobe of merely $<2.7R_p$ means that gas promptly experiences Keplerian orbital shear after launching past the L1 point.
+The orbital overview depicts a path of the mass loss initially towards the star, decelerating into the headwind of the stellar wind, and then reversing direction outward in a blueshift.
+The observed redshift and blueshift of any given sightline will depend on the Helium ionization fraction, which depends on the shielding of gas along the line of sight.} }
   \label{fig:KeplerianShear}
-\end{figure}
+\end{figure*}
 

### 2023-12-04 paper/paper1/ms.tex
Data editor changes started and completed in one commit.

@@
 The Sector 25 FFI data fell just barely off the TESS detectors, in collateral pixels where no starlight ever hit the detector.
+\authorcomment1{We retrieved the data via the Mikulski Archive for Space Telescopes (MAST) available publically through the public portal \dataset[10.17909/pc4f-f919]{http://doi.org/10.17909/pc4f-f919}.}
 
 We also assembled a comparison sample of about 1000 lightcurves to interpret the prevalence of lightcurve modulation and stellar activity among broadly F subgiant-like stars.
-We selected sources based on \emph{Gaia} DR3 $T_\mathrm{eff}$ estimates and similar $\log{g}$,  and availability of at least one sector of TESS 2-minute cadence data.
+We selected sources based on \emph{Gaia} DR3 \citep{2023A&A...674A...1G} $T_\mathrm{eff}$ estimates and similar $\log{g}$,  and availability of at least one sector of TESS 2-minute cadence data.
 We visually spot-checked these lightcurves to understand artifacts and windowing effects.
@@
 \subsubsection{Revised exoplanet orbital parameters}
-We assembled a composite lightcurve by stitching TESS Sectors 24, 26, 51, 52, 53, which were reduced with the default SPOC pipeline \citep{2020RNAAS...4..201C}, and lightly post-processed with \texttt{lightkurve} \citep{geert_barentsen_2019_2565212}.
+We assembled a composite lightcurve by stitching TESS Sectors 24, 26, 51, 52, 53, which were reduced with the default SPOC pipeline \citep{2020RNAAS...4..201C}, and lightly post-processed with \texttt{lightkurve} \citep{2018ascl.soft12013L,geert_barentsen_2019_2565212}.
 These TESS data exhibit an RMS scatter of better than 1 part-per-thousand (ppt) at native 2-minute sampling.
@@
   \texttt{ipython} \citep{perez07},
-  \texttt{seaborn} \citep{waskom14},
+  \texttt{seaborn} \citep{waskom14,2021JOSS....6.3021W},
   \texttt{astropy} \citep{2022ApJ...935..167A},
   \texttt{muler} \citep{2022JOSS....7.4302G},
-  \texttt{lightkurve}, \citep{geert_barentsen_2019_2565212},
+  \texttt{lightkurve}, \citep{2018ascl.soft12013L,geert_barentsen_2019_2565212},
   \texttt{telfit} \citep{2014AJ....148...53G},

### 2023-12-04 paper/paper1/ms.tex
Make the repository public and put a link to the repo in the paper.
Comparison to CARMENES data, section 6.4

@@
 \section{Analysis} \label{secAnalysis}
+
+\authorcomment1{The entire suite of project files, reproducible Jupyter Notebooks, selected data files, and revision history are publically available as a reproducible GitHub repository\footnote{\url{https://github.com/BrownDwarf/disperse}}.}
 
@@
 
+\subsection{Comparison to CARMENES detection}
+\authorcomment1{Recently, \citet{2023AJ....166...69B} reported the transmission spectrum of HAT-P-67~b using the CARMENES spectrograph \citep{2014SPIE.9147E..1FQ}.
+The point-and-stare observations were scheduled to coincide with transits, providing relatively short $<1$ hour out-of-transit baselines on either side of the transit.
+The CARMENES team detected variable \ion{He}{1} 10830 absorption, but could not uniquely attribute the variability to an exoplanet origin owing to the limited orbital phase coverage.
+The CARMENES visible channel spectrograph also covers H$\alpha$, which yielded a significant detection of Hydrogen variability through the exoplanet transit.
+The CARMENES team also detected \ion{Ca}{2} IRT and \ion{Na}{1} via cross-correlation spectroscopy, consistent with an exoplanet atmosphere origin.
+Our analysis of the \ion{Ca}{2} IRT showed much less conspicuous variability compared to the \ion{He}{1} 10830 lines, but still some hint of variability (\emph{c.f.} Figure \ref{fig:CaPhaseScan}).
+A joint analysis of both the CARMENES and HPF data may help to paint a more complete picture of these variable signals.
+}
+
 \section{Conclusions}

### 2023-12-18 paper/paper1/ms.tex
Version of the paper destined for resubmission, with Zenodo and GitHub links public

@@
 Table \ref{tabHPFLog} summarizes the log of observations.
+\authorcomment1{These HPF data are publicly available at \dataset[10.5281/zenodo.10372477]{https://zenodo.org/records/10372477}.}
 
@@
 The Sector 25 FFI data fell just barely off the TESS detectors, in collateral pixels where no starlight ever hit the detector.
-\authorcomment1{We retrieved the data via the Mikulski Archive for Space Telescopes (MAST) available publically through the public portal \dataset[10.17909/pc4f-f919]{http://doi.org/10.17909/pc4f-f919}.}
+\authorcomment1{We retrieved the data via the Mikulski Archive for Space Telescopes (MAST) available publicly through the online portal \dataset[10.17909/pc4f-f919]{http://doi.org/10.17909/pc4f-f919}.}
 
@@
 
-\authorcomment1{The entire suite of project files, reproducible Jupyter Notebooks, selected data files, and revision history are publically available as a reproducible GitHub repository\footnote{\url{https://github.com/BrownDwarf/disperse}}.}
+\authorcomment1{The entire suite of project files, reproducible Jupyter Notebooks, selected data files, and revision history are publicly available as a reproducible GitHub repository\footnote{\url{https://github.com/BrownDwarf/disperse}}.}
 
@@
   \includegraphics[width=0.5\linewidth]{Ca8662_phase_2D_diagram_resid.png}
-  \caption{Non-detection of variability in the Calcium IR Triplet line at 8862 \AA.  No other HPF lines appear to show any variability.}
+  \caption{Weak variability in the Calcium IR Triplet line at 8862 \AA.  No other HPF lines appear to show as conspicuous variability as the Helium triplet.}
   \label{fig:CaPhaseScan}
